---
title: "exploratory_analyses_with_personality"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
date: "2023-03-29"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r clear environment, echo = FALSE}
rm(list = ls())
```


```{r libraries, message = FALSE, warning = FALSE}
library(Rmisc)
library(Hmisc)
library(rio)
library(tidyverse)
library(psych)
library(gtools) # rbinding data frames
library(corrplot)
library(jtools) # for pretty printing tables
library(sjPlot) # pretty printing tables
library(sjmisc) # pretty printing
library(mice) # handling missing values
library(naniar) # visualizaing missingness & MCAR test
library(lavaan) # for FIML
library(miceadds) # for mi.anova
library(broom)
library(olsrr)
library(emmeans)

options(max.print = 100000)
```

# Data Import & Cleaning

## Import data
```{r import data}
raw_psych_hum_subj <- import("data/raw/raw_psych_hum_subj.csv")
raw_mktg_hum_subj <- import("data/raw/raw_mktg_hum_subj.csv")
raw_gen_uo_pop <- import("data/raw/raw_gen_uo_pop.csv")
pre_fall22 <- import("data/prescreen/dittersdorf_matches_f22.csv")
pre_winter23 <- import("data/prescreen/dittersdorf_matches_w23.csv")
pre_spring23 <- import("data/prescreen/dittersdorf_matches_s23.csv")
participant_list <- import("data/prescreen/dittersdorf_participants.csv")
```


Inspect data
```{r inspect raw data, results = 'hide'}
# Main Data
str(raw_psych_hum_subj, list.len = ncol(raw_psych_hum_subj))
str(raw_mktg_hum_subj, list.len = ncol(raw_mktg_hum_subj))
str(raw_gen_uo_pop, list.len = ncol(raw_gen_uo_pop))
```


## Change variables types 
```{r update var types, warning = FALSE}
raw_psych_hum_subj <- raw_psych_hum_subj %>%
  mutate(Age = as.integer(Age),
         Gender = as.factor(Gender),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors),
         id = as.factor(id))

raw_mktg_hum_subj <- raw_mktg_hum_subj %>%
  mutate(Age = as.integer(Age),
         Gender = as.factor(Gender),
         Gender_5_TEXT = as.character(Gender_5_TEXT),
         Class_Lvl_7_TEXT = as.character(Class_Lvl_7_TEXT),
         Pol_Ornt_8_TEXT = as.character(Pol_Ornt_8_TEXT),
         Ethnicity_8_TEXT = as.character(Ethnicity_8_TEXT),
         skept_open = as.character(skept_open),
         id = as.factor(id),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors))

raw_gen_uo_pop <- raw_gen_uo_pop %>%
  mutate(Gender = as.factor(Gender),
         Gender_5_TEXT = as.character(Gender_5_TEXT),
         Class_Lvl_7_TEXT = as.character(Class_Lvl_7_TEXT),
         Pol_Ornt_8_TEXT = as.character(Pol_Ornt_8_TEXT),
         skept_open = as.character(skept_open),
         id = as.factor(id),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors))
```


Inspect prescreen data
```{r inspect prescreen, results = 'hide'}
# Prescreen Data
str(pre_fall22, list.len = ncol(pre_fall22))
str(pre_winter23, list.len = ncol(pre_winter23))
str(pre_spring23, list.len = ncol(pre_spring23))
str(participant_list, list.len = ncol(participant_list))
```

Variables from prescreen:

* Values:
  + respecting, unity, protecting, preventing, equality, peace, justice, helpful, power, wealth, authority, influential, ambition, pleasures, enjoying, gratification

* Socially Desirable Responding:
  + honest, like, disturbing, regret, lose-out, rational, confident, lover, lies, cover-up, advantage, get-even, behind-back, private-talk, take-things, gossip

## Combine prescreen data

Specify unique variables to combine prescreen data sets
```{r prep prescreen dfs}
# Create unique full_name variable
pre_fall22$full_name <- paste(pre_fall22$first_name, pre_fall22$last_name, sep="_")

pre_winter23$full_name <- paste(pre_winter23$first_name, pre_winter23$last_name, sep="_")

pre_spring23$full_name <- paste(pre_spring23$first_name, pre_spring23$last_name, sep="_")

participant_list$full_name <- paste(participant_list$first_name, participant_list$last_name, sep="_")

# Create column indicating which data set rows came from

pre_fall22 <- pre_fall22 %>%
  mutate(term = "fall22")

pre_winter23 <- pre_winter23 %>%
  mutate(term = "winter23")

pre_spring23 <- pre_spring23 %>%
  mutate(term = "spring23")
```

Combine prescreen data
```{r combine prescreen dfs}
combine1 <- smartbind(pre_fall22, pre_winter23)
combined_prescreen <- smartbind(combine1, pre_spring23)

nrow(pre_fall22) + nrow(pre_winter23) + nrow(pre_spring23) # n = 1167

combined_prescreen_unique <- combined_prescreen[!duplicated(combined_prescreen$full_name), ] # keeps first row (fall22)
```

Subset key variables
```{r subset key vars}
combined_prescreen_key <- combined_prescreen_unique %>%
  select(full_name, term, respecting:gratification, honest:gossip)

participant_list_key <- participant_list %>%
  select(full_name, survey_id)
```

Merge with participant list
```{r merge participant list}
merged_prescreen <- merge(combined_prescreen_key, participant_list_key, by = "full_name")
```

Convert variable types in prescreen data
```{r inspect merged prescreen, results = 'hide'}
str(merged_prescreen, list.len = ncol(merged_prescreen))
```

```{r clean merged prescreen, warning = FALSE}
merged_prescreen <- merged_prescreen %>%
  rename("lose_out" = "lose-out", 
         "cover_up" = "cover-up",
         "get_even" = "get-even",
         "behind_back" = "behind-back",
         "private_talk" = "private-talk",
         "take_things" = "take-things",
         "id" = "survey_id")

merged_prescreen <- merged_prescreen %>%
  mutate(respecting = as.integer(respecting),
         unity = as.integer(unity),
         protecting = as.integer(protecting),
         preventing = as.integer(preventing),
         equality = as.integer(equality),
         peace = as.integer(peace),
         justice = as.integer(justice),
         helpful = as.integer(helpful),
         power = as.integer(power),
         wealth = as.integer(wealth),
         authority = as.integer(authority),
         influential = as.integer(influential),
         ambition = as.integer(ambition),
         pleasures = as.integer(pleasures),
         enjoying = as.integer(enjoying),
         gratification = as.integer(gratification),
         honest = as.integer(honest),
         like = as.integer(like),
         disturbing = as.integer(disturbing),
         regret = as.integer(regret),
         lose_out = as.integer(lose_out),
         rational = as.integer(rational),
         confident = as.integer(confident),
         lover = as.integer(lover),
         lies = as.integer(lies),
         cover_up = as.integer(cover_up),
         advantage = as.integer(advantage),
         get_even = as.integer(get_even),
         behind_back = as.integer(behind_back),
         private_talk = as.integer(private_talk),
         take_things = as.integer(take_things),
         gossip = as.integer(gossip),
         id = as.factor(id))
```


Rename values & socially desirable items in prescreen data to match names in main data:
```{r rename prescreen vars}
merged_prescreen <- merged_prescreen %>%
  rename("values_1" = "respecting",
         "values_2" = "unity",
         "values_3" = "protecting",
         "values_4" = "preventing",
         "values_5" = "equality",
         "values_6" = "peace",
         "values_7" = "justice",
         "values_8" = "helpful",
         "values_9" = "power",
         "values_10" = "wealth",
         "values_11" = "authority",
         "values_12" = "influential",
         "values_13" = "ambition",
         "values_14" = "pleasures",
         "values_15" = "enjoying",
         "values_16" = "gratification",
         "socially_desirable_1" = "honest",
         "socially_desirable_2" = "like",
         "socially_desirable_3" = "disturbing",
         "socially_desirable_4" = "regret",
         "socially_desirable_5" = "lose_out",
         "socially_desirable_6" = "rational",
         "socially_desirable_7" = "confident",
         "socially_desirable_8" = "lover",
         "socially_desirable_9" = "lies",
         "socially_desirable_10" = "cover_up",
         "socially_desirable_11" = "advantage",
         "socially_desirable_12" = "get_even",
         "socially_desirable_13" = "behind_back",
         "socially_desirable_14" = "private_talk",
         "socially_desirable_15" = "take_things",
         "socially_desirable_16" = "gossip")
```


## Combine all data

- First, combine Psych Hum Subj data with Prescreen data based on `id`
- Second, add Mktg Hum Subj data
- Third, add gen UO Pop data
```{r combine all data}
combine1 <- merge(raw_psych_hum_subj, merged_prescreen, by = "id")
combine2 <- smartbind(combine1, raw_mktg_hum_subj)
combine3 <- smartbind(combine2, raw_gen_uo_pop)
```

## Remove duplicate cases

Identify duplicate cases
```{r id duplicate cases, results = 'hide'}
# first, add unique row #s
combine3 <- combine3 %>%
  mutate(row = 1:nrow(combine3))

combine3[duplicated(combine3$id),] # Only rows 1 through 858 have unique id #s

# write.csv(combine3, "combined_data.csv")
```

Row IDs to remove:

* 13 (participant's second time completing study)
* 134 (participant didn't complete study first time)
* 145 (participant didn't complete study first time)
* 308 (participant's second time completing study)
* 672 (participant's second time completing study)
* 743 (participant didn't complete study first time)
* 790 (participant didn't complete study first time)
* 800 (participant didn't complete study first time)

Remove duplicate rows after resolving:
```{r remove duplicate cases}
combine3 <- combine3 %>%
  filter(!row %in% c(13, 134, 145, 308, 672, 743, 790, 800))
```

Check variables types again
```{r inspect var types again, results = 'hide'}
str(combine3, list.len = ncol(combine3))
```

## Remove all NA cases

Identify completely missing rows:
```{r id all NA rows, results = 'hide'}
key_vars <- combine3 %>%
  select(row, big_2_1:big_2_65, consumer_intentions_1:consumer_intentions_9, consumer_behaviors, clothing_interest_1:clothing_interest_20, ingroup_ident_1:ingroup_ident_14, values_1:values_16, socially_desirable_1:socially_desirable_16)

ncol(key_vars) # number of columns - the row # column = 141

all_NA_rows <- key_vars[rowSums(is.na(key_vars)) == 141,] # identify rows with 142 NAs (all missing values), row numbers are preserved

all_NA_rows
```

Removing rows of fully missing data:
```{r remove all NA rows}
data <- combine3 %>%
  filter(!row %in% c(859, 860, 900, 926, 927, 941, 1139, 1141, 1142, 1143, 1144, 1146, 1149, 1150, 1152)) %>% # remove rows containing all NAs
  select(-StartDate, -EndDate, -Status, -Progress, -"Duration (in seconds)", -Finished, -RecordedDate, -ResponseId, -DistributionChannel, -UserLanguage, -big_2_DO, -consumer_intentions_DO, -consumer_behaviors_DO, -clothing_interest_DO, -ingroup_ident_DO, -full_name, -code, -socially_desirable_DO, -values_DO, -email_giftcard, -term) # removing variables not in analysis
```


Rename variables:
```{r rename vars}
data <- data %>%
  rename("framing_condition" = "framing_condition_DO", 
         "norm_condition" = "norm_condition_DO")

levels(data$framing_condition)
levels(data$norm_condition)

data$framing_condition <- droplevels(data$framing_condition)
data$norm_condition <- droplevels(data$norm_condition)

levels(data$framing_condition)
levels(data$norm_condition)
```

## Inspect final data 
```{r inspect final df, results = 'hide'}
str(data, list.len = ncol(data))

# write.csv(data, "final_data.csv")
```


# Outliers

## Personality Traits
```{r}
data %>%
  select(big_2_1:big_2_65) %>%
  boxplot()
```


## Demographics

Age
```{r age outliers}
# Age
data %>%
  select(Age) %>%
  hist()

describe(data$Age) # 1999 a data entry error

data %>%
  filter(Age == 1999) # Row 1053, Year 1999 = 24 years old

data$Age[data$Age == 1999] <- 24

data %>%
  filter(row == 1053) %>%
  select(Age) # Age has been replaced with 24
```

Income

- 1 = $0-9,999
- 2 = $10,000 - 19,999
- 3 = $20,000 - 29,999
- 4 = $30,000 - 39,999
- 5 = $40,000 - 49.999
- 6 = $50,000 - 59,999
- 7 = $60,000 - 69,999
- 8 = $70,000 - 79,999
- 9 = $80,000 - 89,999
- 10 = $90,000 - 99,999
- 11 = $100,000 or more
```{r income outliers}
data %>%
  select(Income) %>%
  boxplot()

describe(data$Income)

table(data$Income)

data %>%
  filter(Income == 11 | Income == 10 | Income == 9 | Income == 8 | Income == 7) %>%
  select(Income, Age, Employment, Class_Lvl)
```

Employment

- 1 = Employed, working 1-39 hrs/wk
- 2 = Employed, working 40+ hrs/wk
- 3 = Not employed, looking for work
- 4 = Not employed, NOT looking for work
- 5 = Retired
- 6 = Not able to work

Class Level

- 1 = Freshman
- 2 = Sophomore
- 3 = Junior
- 4 = Senior
- 5 = Graduate student
- 6 = Not applicable
- 7 = Other


Gender

- 1 = woman
- 2 = man
- 3 = non-binary
- 4 = I prefer not to identify
- 5 = other (please specify)
```{r label gender levels}
levels(data$Gender) <- c("Woman", "Man", "Non-binary", "I prefer not to identify", "Other")

table(data$Gender) 

data %>%
  filter(Gender == 5) %>%
  select(Gender_5_TEXT)
```


# Missing Values

## Examine Missingness

### Personality
```{r NAs on personality}
data %>%
  select(big_2_1:big_2_65) %>%
  vis_miss()
```


## MCAR Test

A non-significant test suggests the data *is* missing completely at random.
```{r MCAR test}
test_of_mcar <- data %>%
  select(consumer_intentions_1:consumer_behaviors, clothing_interest_1:clothing_interest_20, ingroup_ident_1:ingroup_ident_14, values_1:values_16, socially_desirable_1:socially_desirable_16, Age, Gender, Income, big_2_1:big_2_65) %>%
  mcar_test()

test_of_mcar$statistic
test_of_mcar$df # Critical values are 8565.53 and 9086.26
test_of_mcar$p.value
```



# Aggregate Variables 

## Personality

### Reverse-code

```{r reverse personality items}
data_R <- data %>%
  mutate(across(c(big_2_11,
                  big_2_16,
                  big_2_26,
                  big_2_31,
                  big_2_36,
                  big_2_51,
                  big_2_12,
                  big_2_17,
                  big_2_22,
                  big_2_37,
                  big_2_42,
                  big_2_47,
                  big_2_3,
                  big_2_8,
                  big_2_23,
                  big_2_28,
                  big_2_48,
                  big_2_58,
                  big_2_4,
                  big_2_9,
                  big_2_24,
                  big_2_29,
                  big_2_44,
                  big_2_49,
                  big_2_5,
                  big_2_25,
                  big_2_30,
                  big_2_45,
                  big_2_50,
                  big_2_55,
                  big_2_63), ~6 - .)) # replace '6' with the max possible value plus 1 for any particular scale
```

### Average items

```{r aggregate personality}
data_R$extraversion <- data_R %>%
  select(big_2_1, big_2_6, big_2_11, big_2_16, big_2_21, big_2_26, big_2_31, big_2_36, big_2_41, big_2_46, big_2_51, big_2_56) %>%
  rowMeans(na.rm = TRUE) 


data_R$conscientiousness <- data_R %>%
  select(big_2_3, big_2_8, big_2_13, big_2_18, big_2_23, big_2_28, big_2_33, big_2_38, big_2_43, big_2_48, big_2_53, big_2_58) %>%
  rowMeans(na.rm = TRUE)


data_R$agreeableness <- data_R %>%
  select(big_2_2, big_2_7, big_2_12, big_2_17, big_2_22, big_2_27, big_2_32, big_2_37, big_2_42, big_2_47, big_2_52, big_2_57) %>%
  rowMeans(na.rm = TRUE)


data_R$neuroticism <- data_R %>%
  select(big_2_4, big_2_9, big_2_14, big_2_19, big_2_24, big_2_29, big_2_34, big_2_39, big_2_44, big_2_49, big_2_54, big_2_59) %>%
  rowMeans(na.rm = TRUE)


data_R$openness <- data_R %>%
  select(big_2_5, big_2_10, big_2_15, big_2_20, big_2_25, big_2_30, big_2_35, big_2_40, big_2_45, big_2_50, big_2_55, big_2_60) %>%
  rowMeans(na.rm = TRUE)


data_R$honesty <- data_R %>%
  select(big_2_61, big_2_62, big_2_63, big_2_64, big_2_65) %>%
  rowMeans(na.rm = TRUE)
```




## Clothing Interest

### Reverse-code

```{r reverse clothing items}
data_R <- data_R %>%
  mutate(across(c(clothing_interest_3,
                  clothing_interest_5,
                  clothing_interest_7,
                  clothing_interest_9,
                  clothing_interest_12,
                  clothing_interest_14,
                  clothing_interest_15,
                  clothing_interest_16,
                  clothing_interest_18,
                  clothing_interest_20), ~6 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```


### Average items
```{r aggregate clothing interest}
data_R$clothing_interest <- data_R %>%
  select(clothing_interest_1:clothing_interest_20) %>%
  rowMeans(na.rm = TRUE)
```




## In-group Identification

### Reverse-code

No items need to be reverse-coded.

### Average items
```{r aggegate ingroup ident}
data_R$ingroup_identification <- data_R %>%
  select(ingroup_ident_1:ingroup_ident_14) %>%
  rowMeans(na.rm = TRUE)
```




## Values

### Reverse-code

No items need to be reverse-coded.

### Recoding scale options

Recoding values:

* -3 = 1
* -2 = 2
* -1 = 3
* 0 = 4
* +1 = 5
* +2 = 6
* +3 = 7

```{r recode values}
table(data_R$values_1)

data_R$values_1_rec <- recode(data_R$values_1, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)

table(data_R$values_1_rec)

data_R$values_2_rec <- recode(data_R$values_2, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_3_rec <- recode(data_R$values_3, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_4_rec <- recode(data_R$values_4, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_5_rec <- recode(data_R$values_5, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_6_rec <- recode(data_R$values_6, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_7_rec <- recode(data_R$values_7, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_8_rec <- recode(data_R$values_8, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_9_rec <- recode(data_R$values_9, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_10_rec <- recode(data_R$values_10, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_11_rec <- recode(data_R$values_11, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_12_rec <- recode(data_R$values_12, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_13_rec <- recode(data_R$values_13, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_14_rec <- recode(data_R$values_14, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_15_rec <- recode(data_R$values_15, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_16_rec <- recode(data_R$values_16, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)

table(data_R$values_16)
table(data_R$values_16_rec)
```


### Average items
```{r aggregate values}
data_R$biospheric <- data_R %>%
  select(values_1_rec:values_4_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$altruistic <- data_R %>%
  select(values_5_rec:values_8_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$egoistic <- data_R %>%
  select(values_9_rec:values_13_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$hedonic <- data_R %>%
  select(values_14_rec:values_16_rec) %>%
  rowMeans(na.rm = TRUE)
```





## Socially Desirable Responding

### Reverse-code
```{r reverse code socially desirable items}
data_R <- data_R %>%
  mutate(across(c(socially_desirable_1,
                  socially_desirable_3,
                  socially_desirable_5,
                  socially_desirable_8,
                  socially_desirable_9,
                  socially_desirable_11,
                  socially_desirable_12,
                  socially_desirable_13), ~8 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```

### Average items
```{r aggregate socially desirable}
data_R$socially_desirable <- data_R %>%
  select(socially_desirable_1:socially_desirable_16) %>%
  rowMeans(na.rm = TRUE)
```




## Consumer Intentions

### Reverse-code

Higher scores mean better consumer intentions (intentions to *reduce* future consumption):
```{r reverse code consumer intentions}
data_R <- data_R %>%
  mutate(across(c(consumer_intentions_2,
                  consumer_intentions_4,
                  consumer_intentions_7,
                  consumer_intentions_9), ~8 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```

### Average items

```{r aggregate consumer intentions}
data_R$consumer_intentions <- data_R %>%
  select(consumer_intentions_1:consumer_intentions_9) %>%
  rowMeans(na.rm = TRUE)
```



### Reorder levels

Reorder the levels of norm condition:
```{r reorder norm condition levels}
data_R %>%
  group_by(norm_condition) %>%
  summarize(M = mean(consumer_intentions, na.rm = TRUE))

data_R$norm_condition <- ordered(data_R$norm_condition, levels = c("control_norm", "descriptive_norm", "convention_norm", "social_norm", "moral_norm"))
```



# Multivariate Outliers

- Influential data points will be evaluated after running model

## Scatterplot matrix
```{r scatterplot matrix}
data_R %>%
  select(consumer_intentions, extraversion, agreeableness, conscientiousness, openness, neuroticism, honesty) %>%
  pairs(upper.panel = NULL)

```


# Descriptive Statistics

## Personality 
```{r descriptives personality, echo = FALSE}
# Personality
pers_D <- data_R %>%
  group_by(framing_condition) %>%
  summarize(n = n(),
            M_E = mean(extraversion, na.rm = TRUE),
            SD_E = sd(extraversion, na.rm = TRUE),
            M_C = mean(conscientiousness, na.rm = TRUE),
            SD_C = sd(conscientiousness, na.rm = TRUE),
            M_A = mean(agreeableness, na.rm = TRUE),
            SD_A = sd(agreeableness, na.rm = TRUE),
            M_N = mean(neuroticism, na.rm = TRUE),
            SD_N = sd(neuroticism, na.rm = TRUE),
            M_O = mean(openness, na.rm = TRUE),
            SD_O = sd(openness, na.rm = TRUE),
            M_H = mean(honesty, na.rm = TRUE),
            SD_H = sd(honesty, na.rm = TRUE))

knitr::kable(pers_D, digits = 2, caption = "Descriptives for Personality Traits by Framing Condition")


pers_D2 <- data_R %>%
  group_by(norm_condition) %>%
  summarize(n = n(),
            M_E = mean(extraversion, na.rm = TRUE),
            SD_E = sd(extraversion, na.rm = TRUE),
            M_C = mean(conscientiousness, na.rm = TRUE),
            SD_C = sd(conscientiousness, na.rm = TRUE),
            M_A = mean(agreeableness, na.rm = TRUE),
            SD_A = sd(agreeableness, na.rm = TRUE),
            M_N = mean(neuroticism, na.rm = TRUE),
            SD_N = sd(neuroticism, na.rm = TRUE),
            M_O = mean(openness, na.rm = TRUE),
            SD_O = sd(openness, na.rm = TRUE),
            M_H = mean(honesty, na.rm = TRUE),
            SD_H = sd(honesty, na.rm = TRUE))

knitr::kable(pers_D2, digits = 2, caption = "Descriptives for Personality Traits by Norm Condition")


pers_D3 <- data_R %>%
  group_by(framing_condition, norm_condition) %>%
  summarize(n = n(),
            M_E = mean(extraversion, na.rm = TRUE),
            SD_E = sd(extraversion, na.rm = TRUE),
            M_C = mean(conscientiousness, na.rm = TRUE),
            SD_C = sd(conscientiousness, na.rm = TRUE),
            M_A = mean(agreeableness, na.rm = TRUE),
            SD_A = sd(agreeableness, na.rm = TRUE),
            M_N = mean(neuroticism, na.rm = TRUE),
            SD_N = sd(neuroticism, na.rm = TRUE),
            M_O = mean(openness, na.rm = TRUE),
            SD_O = sd(openness, na.rm = TRUE),
            M_H = mean(honesty, na.rm = TRUE),
            SD_H = sd(honesty, na.rm = TRUE))

knitr::kable(pers_D3, digits = 2, caption = "Descriptives for Personality Traits by Framing X Norm Condition")

```



# Personality Exploratory Analyses

## Center Covariates

- Socially desirable responding
- Clothing interest
- Values
- Ingroup identification
- Age
- Gender
- Income (not sure how to handle inconsistencies in this variable was responded to)

```{r center covariates, echo = FALSE}
data_R$socially_desirable_center <- data_R$socially_desirable - mean(data_R$socially_desirable, na.rm = TRUE)

data_R$clothing_interest_center <- data_R$clothing_interest - mean(data_R$clothing_interest, na.rm = TRUE)

data_R$Age_center <- data_R$Age - mean(data_R$Age, na.rm = TRUE)

data_R$ingroup_identification_center <- data_R$ingroup_identification - mean(data_R$ingroup_identification, na.rm = TRUE)

data_R$biospheric_center <- data_R$biospheric - mean(data_R$biospheric, na.rm = TRUE)

data_R$altruistic_center <- data_R$altruistic - mean(data_R$altruistic, na.rm = TRUE)

data_R$egoistic_center <- data_R$egoistic - mean(data_R$egoistic, na.rm = TRUE)

data_R$hedonic_center <- data_R$hedonic - mean(data_R$hedonic, na.rm = TRUE)

data_R$extraversion_center <- data_R$extraversion - mean(data_R$extraversion, na.rm = TRUE)
  
data_R$conscientiousness_center <- data_R$conscientiousness - mean(data_R$conscientiousness, na.rm = TRUE)

data_R$agreeableness_center <- data_R$agreeableness - mean(data_R$agreeableness, na.rm = TRUE)

data_R$neuroticism_center <- data_R$neuroticism - mean(data_R$neuroticism, na.rm = TRUE)

data_R$openness_center <- data_R$openness - mean(data_R$openness, na.rm = TRUE)

data_R$honesty_center <- data_R$honesty - mean(data_R$honesty, na.rm = TRUE)

```


```{r reduce levels of gender, echo = FALSE}
data_R$Gender[data_R$Gender == "Non-binary"] <- NA
data_R$Gender[data_R$Gender == "I prefer not to identify"] <- NA
data_R$Gender[data_R$Gender == "Other"] <- NA

data_R$Gender <- droplevels(data_R$Gender)
```


## with Missing Data


### Contrast Coding

Contrast coding 1:
```{r contrast coding 1}
# Gender
contrasts(data_R$Gender) <- c(-1/2, 1/2)
contrasts(data_R$Gender)

# Framing
FrameCode1 <- c(-1/2, 0, 1/2) # control vs self-enhancing
FrameCode2 <- c(-1/3, 2/3, -1/3) # arbitrary code

contrasts(data_R$framing_condition) <- cbind(FrameCode1, FrameCode2)
contrasts(data_R$framing_condition)

# Norm
contrasts(data_R$norm_condition) <- contr.helmert(5)
contrasts(data_R$norm_condition) # control vs DN
```


### Running Model

```{r exploratory personality}
exp_model1 <- lm(consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_identification_center + framing_condition*norm_condition*extraversion_center + framing_condition*norm_condition*conscientiousness_center + framing_condition*norm_condition*agreeableness_center + framing_condition*norm_condition*neuroticism_center + framing_condition*norm_condition*openness_center + framing_condition*norm_condition*honesty_center + socially_desirable_center + clothing_interest_center + Gender + Age_center, data = data_R)
```

```{r succinct summary personality, echo = FALSE}
exp_model1_summ <- summary(exp_model1)
exp_model1_summ

exp_model1_summ$coefficients %>%
  knitr::kable(digits = 3)
```

### ANOVA Output
```{r anova table personality}
anova(exp_model1) %>%
  knitr::kable(digits = 2)
```

### Regression Output
```{r pretty summary table personality}
# tab_model(exp_model1, show.se = TRUE, show.fstat = TRUE)
```



### Regression Diagnostics

#### Checking non-linearity

First, assess non-linearity using a residuals plots:
```{r}
plot(exp_model1, 1)
```

There does not appear to be a systematic pattern suggesting an uncaptured, non-linear trend.

#### Checking non-normally distributed errors

Second, assess non-normally distributed errors by plotting the residuals & using a QQ-plot:
```{r}
# storing residuals
exp_model1_aug <- augment(exp_model1)

# plotting histogram of residuals
ggplot(data = exp_model1_aug, aes(x = .resid)) + 
  geom_density(fill = "purple") + 
  stat_function(linetype = 2, 
                fun      = dnorm, 
                args     = list(mean = mean(exp_model1_aug$.resid), 
                                sd   =   sd(exp_model1_aug$.resid))) +
  theme_minimal()


# QQ-plot
ggplot(exp_model1) +
  geom_abline(color = "turquoise4") + 
  stat_qq(aes(sample = .stdresid), color = "darkorchid4", alpha = .50) +
  theme_minimal()
```

The distribution of residuals & QQ-plot suggest approximately normally distributed residuals.


#### Checking heteroscedasticity

Third, check for heteroscedasticity by looking at spread of residuals on residuals plot:
```{r}
plot(exp_model1, 1)
```

There does not appear to be an issue with heteroscedasticity.


#### Checking multivariate outliers

Outliers based on distance from model using standardized residuals:
```{r}
# using olsrr function
ols_plot_resid_stand(exp_model1)


# or grabbing from model augment output
exp_model1_aug <- augment(exp_model1)

exp_model1_aug$id <- exp_model1_aug$.rownames

std_resids <- exp_model1_aug %>% 
  select(.rownames, .std.resid) %>%
  arrange(desc(abs(.std.resid)))

print(std_resids, n = 15)
```

Examine outliers with standardized residuals greater than +/-2 or +/-3.

Outliers based on influence on model using Cook's Distance:
```{r}
# using olsrr function
ols_plot_cooksd_chart(exp_model1)

# or grabbing from model augment output
cooks_d <- exp_model1_aug %>% 
  select(.rownames, .cooksd) %>%
  arrange(desc(abs(.cooksd)))

print(cooks_d, n = 15)
```

One standard is that Cook's D values greater than 3 times the average Cook's D values are worth investigating.


#### Checking multicollinearity

Using VIFs & tolerance:
```{r}
ols_vif_tol(exp_model1) %>%
  arrange(desc(abs(VIF)))
```

Either a *low* tolerance (below 0.20 is one rule of thumb) or a *high* VIF (above 5 or 10) is an indication of a problem with multicollinearity.





### Interpretation 

Personality Results for Consumer Intentions:

  * **Extraversion** non-significant, negative predictor (b = -0.03, p = .691)
  * **Conscientiousness** non-significant, negative predictor (b = -0.08, p = .233)
  * **Agreeableness** non-significant, positive predictor (b =.11, p = .205)
  * **Neuroticism** significant, positive predictor (b = .17, p = .006)
  * **Openness** significant, positive predictor (b = .38, p < .001)
  * **Honesty** non-significant, negative predictor (b = -0.09, p = .151)

  
  * Two-way interaction between **framing condition** and **conscientiousness** (p = .014)
  
  * Two-way interaction between **norm condition** and **conscientiousness** (p = .062, non-sig tho)
  
  * Two-way interaction between **norm condition** and **neuroticism** (p = .082, non-sig tho)
  
  * Two-way interaction between **norm condition** and **honesty** (p = .076, non-sig tho)
  
  * Three-way interaction between **framing condition**, **norm condition** and **openness** (p = .008)



# Simple Effects


>>Exploratory RQ3: Is there a two-interaction between personality traits & norm condition?

>>Exploratory RQ4: Is there a three-interaction between personality traits, framing, & norm condition?


## Extraversion X Framing X Norm

First, relationship between extraversion & consumer intentions for each norm condition:
```{r}
emtrends(exp_model1, ~norm_condition, var = "extraversion_center", adjust = "none")


# On a single graph
at_list <- list(extraversion_center = seq(-2.2, 1.9, by = 1))

emmip(exp_model1, norm_condition ~ extraversion_center, at = at_list, CIs = TRUE, xlab = "Extraversion (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(exp_model1, ~ extraversion_center | norm_condition, at = at_list, CIs = TRUE, xlab = "Extraversion (centered)", ylab = "Consumer Intentions")
```

* Extraversion was non-significantly related to consumer intentions in all norm conditions.


Second, relationship between extraversion & consumer intentions for each framing condition:
```{r}
emtrends(exp_model1, ~framing_condition, var = "extraversion_center", adjust = "none")

# On a single graph
at_list <- list(extraversion_center = seq(-2.2, 1.9, by = 1))

emmip(exp_model1, framing_condition ~ extraversion_center, at = at_list, CIs = TRUE, xlab = "Extraversion (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(exp_model1, ~ extraversion_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Extraversion (centered)", ylab = "Consumer Intentions")
```

* Extraversion was non-significantly related to consumer intentions in all framing conditions.


Third, interaction between extraversion, framing, & norm condition:
```{r}
emtrends(exp_model1, ~norm_condition | framing_condition, var = "extraversion_center", adjust = "none")

# Separate graph for each framing condition
at_list <- list(extraversion_center = seq(-2.2, 1.9, by = 1))

emmip(exp_model1, norm_condition ~ extraversion_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Extraversion (centered)", ylab = "Consumer Intentions")
```

* In the control framing condition, extraversion was non-significantly related to consumer intentions in all norm conditions.

* In the pro-environmental framing condition, extraversion was non-significantly related to consumer intentions in all norm conditions.

* In the self-enhancing framing condition, extraversion was non-significantly related to consumer intentions in all norm conditions except for the social norm condition in which it was significantly, positively related to consumer intentions.


## Agreeableness X Framing X Norm

First, relationship between agreeableness & consumer intentions for each norm condition:
```{r}
emtrends(exp_model1, ~norm_condition, var = "agreeableness_center", adjust = "none")


# On a single graph
at_list <- list(agreeableness_center = seq(-2, 1.4, by = 1))

emmip(exp_model1, norm_condition ~ agreeableness_center, at = at_list, CIs = TRUE, xlab = "Agreeableness (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(exp_model1, ~ agreeableness_center | norm_condition, at = at_list, CIs = TRUE, xlab = "Agreeableness (centered)", ylab = "Consumer Intentions")
```

* Agreeableness was non-significantly related to consumer intentions in all norm conditions.


Second, relationship between agreeableness & consumer intentions for each framing condition:
```{r}
emtrends(exp_model1, ~framing_condition, var = "agreeableness_center", adjust = "none")

# On a single graph
at_list <- list(agreeableness_center = seq(-2, 1.4, by = 1))

emmip(exp_model1, framing_condition ~ agreeableness_center, at = at_list, CIs = TRUE, xlab = "Agreeableness (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(exp_model1, ~ agreeableness_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Agreeableness (centered)", ylab = "Consumer Intentions")
```

* Agreeableness was non-significantly related to consumer intentions in all framing conditions.


Third, interaction between agreeableness, framing, & norm condition:
```{r}
emtrends(exp_model1, ~norm_condition | framing_condition, var = "agreeableness_center", adjust = "none")

# Separate graph for each framing condition
at_list <- list(agreeableness_center = seq(-2, 1.4, by = 1))

emmip(exp_model1, norm_condition ~ agreeableness_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Agreeableness (centered)", ylab = "Consumer Intentions")
```

* In the control framing condition, agreeableness was non-significantly related to consumer intentions in all norm conditions.

* In the pro-environmental framing condition, agreeableness was non-significantly related to consumer intentions in all norm conditions.

* In the self-enhancing framing condition, agreeableness was non-significantly related to consumer intentions in all norm conditions except for the convention condition in which it was significantly, positively related to consumer intentions.




## Conscientiousness X Framing X Norm

First, relationship between conscientiousness & consumer intentions for each norm condition:
```{r}
emtrends(exp_model1, ~norm_condition, var = "conscientiousness_center", adjust = "none")


# On a single graph
at_list <- list(conscientiousness_center = seq(-2.1, 1.7, by = 1))

emmip(exp_model1, norm_condition ~ conscientiousness_center, at = at_list, CIs = TRUE, xlab = "Conscientiousness (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(exp_model1, ~ conscientiousness_center | norm_condition, at = at_list, CIs = TRUE, xlab = "Conscientiousness (centered)", ylab = "Consumer Intentions")
```

* Agreeableness was non-significantly related to consumer intentions in all norm conditions except for the social norm condition in which it was significantly, negatively related to consumer intentions.


Second, relationship between conscientiousness & consumer intentions for each framing condition:
```{r}
emtrends(exp_model1, ~framing_condition, var = "conscientiousness_center", adjust = "none")

# On a single graph
at_list <- list(conscientiousness_center = seq(-2.1, 1.7, by = 1))

emmip(exp_model1, framing_condition ~ conscientiousness_center, at = at_list, CIs = TRUE, xlab = "Conscientiousness (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(exp_model1, ~ conscientiousness_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Conscientiousness (centered)", ylab = "Consumer Intentions")
```

* Conscientiousness was significantly, negatively related to consumer intentions in the control framing condition, but non-significantly related in the pro-environmental and self-enhancing conditions.


Third, interaction between conscientiousness, framing, & norm condition:
```{r}
emtrends(exp_model1, ~norm_condition | framing_condition, var = "conscientiousness_center", adjust = "none")

# Separate graph for each framing condition
at_list <- list(conscientiousness_center = seq(-2.1, 1.7, by = 1))

emmip(exp_model1, norm_condition ~ conscientiousness_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Conscientiousness (centered)", ylab = "Consumer Intentions")
```

* In the control framing condition, conscientiousness was significantly, negatively related to consumer intentions in the **control norm** and **social norm** conditions, but non-significantly related in the descriptive norm, convention, and moral norm conditions.

* In the pro-environmental framing condition, conscientiousness was non-significantly related to consumer intentions in all norm conditions.

* In the self-enhancing framing condition, conscientiousness was non-significantly related to consumer intentions in all norm conditions except for the moral norm condition in which it was significantly, positively related to consumer intentions.




## Openness X Framing X Norm

First, relationship between openness & consumer intentions for each norm condition:
```{r}
emtrends(exp_model1, ~norm_condition, var = "openness_center", adjust = "none")


# On a single graph
at_list <- list(openness_center = seq(-2.5, 1.4, by = 1))

emmip(exp_model1, norm_condition ~ openness_center, at = at_list, CIs = TRUE, xlab = "Openness (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(exp_model1, ~ openness_center | norm_condition, at = at_list, CIs = TRUE, xlab = "Openness (centered)", ylab = "Consumer Intentions")
```

* Openness was significantly, positively related to consumer intentions in all norm conditions except for the descriptive norm condition in which it was non-significantly related.


Second, relationship between openness & consumer intentions for each framing condition:
```{r}
emtrends(exp_model1, ~framing_condition, var = "openness_center", adjust = "none")

# On a single graph
at_list <- list(openness_center = seq(-2.5, 1.4, by = 1))

emmip(exp_model1, framing_condition ~ openness_center, at = at_list, CIs = TRUE, xlab = "Openness (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(exp_model1, ~ openness_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Openness (centered)", ylab = "Consumer Intentions")
```

* Openness was significantly, positively related to consumer intentions in all framing conditions.


Third, interaction between openness, framing, & norm condition:
```{r}
emtrends(exp_model1, ~norm_condition | framing_condition, var = "openness_center", adjust = "none")

# Separate graph for each framing condition
at_list <- list(openness_center = seq(-2.5, 1.4, by = 1))

emmip(exp_model1, norm_condition ~ openness_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Openness (centered)", ylab = "Consumer Intentions")
```

* In the control framing condition, openness was significantly, positively related to consumer intentions in the **convention** and **social norm** conditions, and non-significantly related in the control norm, descriptive norm, and moral norm conditions.

* In the pro-environmental framing condition, openness was significantly, positively related to consumer intentions in the **convention** and **moral norm** conditions, and non-significantly related in the control norm, descriptive norm, and social norm conditions.

* In the self-enhancing framing condition, openness was significantly, positively related to consumer intentions in the **control norm** condition and non-significantly related in all other norm conditions.



## Neuroticism X Framing X Norm

First, relationship between neuroticism & consumer intentions for each norm condition:
```{r}
emtrends(exp_model1, ~norm_condition, var = "neuroticism_center", adjust = "none")


# On a single graph
at_list <- list(neuroticism_center = seq(-2.25, 2.15, by = 1))

emmip(exp_model1, norm_condition ~ neuroticism_center, at = at_list, CIs = TRUE, xlab = "Neuroticism (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(exp_model1, ~ neuroticism_center | norm_condition, at = at_list, CIs = TRUE, xlab = "Neuroticism (centered)", ylab = "Consumer Intentions")
```

* Neuroticism was significantly, positively related to consumer intentions in the convention condition and non-significantly related in all other norm conditions.


Second, relationship between neuroticism & consumer intentions for each framing condition:
```{r}
emtrends(exp_model1, ~framing_condition, var = "neuroticism_center", adjust = "none")

# On a single graph
at_list <- list(neuroticism_center = seq(-2.25, 2.15, by = 1))

emmip(exp_model1, framing_condition ~ neuroticism_center, at = at_list, CIs = TRUE, xlab = "Neuroticism (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(exp_model1, ~ neuroticism_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Neuroticism (centered)", ylab = "Consumer Intentions")
```

* Neuroticism was non-significantly, positively related to consumer intentions in all framing conditions.


Third, interaction between neuroticism, framing, & norm condition:
```{r}
emtrends(exp_model1, ~norm_condition | framing_condition, var = "neuroticism_center", adjust = "none")

# Separate graph for each framing condition
at_list <- list(neuroticism_center = seq(-2.25, 2.15, by = 1))

emmip(exp_model1, norm_condition ~ neuroticism_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Neuroticism (centered)", ylab = "Consumer Intentions")
```

* In the control framing condition, neuroticism was significantly, positively related to consumer intentions in the **control norm** condition, and non-significantly related in all other norm conditions.

* In the pro-environmental framing condition, neuroticism was significantly, positively related to consumer intentions in the **control norm** condition, and non-significantly related in all other norm conditions.

* In the self-enhancing framing condition, neuroticism was significantly, positively related to consumer intentions in the **moral norm** condition, and non-significantly related in all other norm conditions.



## Honesty X Framing X Norm

First, relationship between honesty & consumer intentions for each norm condition:
```{r}
emtrends(exp_model1, ~norm_condition, var = "honesty_center", adjust = "none")

# On a single graph
at_list <- list(honesty_center = seq(-2.5, 2.6, by = 1))

emmip(exp_model1, norm_condition ~ honesty_center, at = at_list, CIs = TRUE, xlab = "Honesty (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(exp_model1, ~ honesty_center | norm_condition, at = at_list, CIs = TRUE, xlab = "Honesty (centered)", ylab = "Consumer Intentions")
```

* Honesty was significantly, negatively related to consumer intentions in the convention condition and non-significantly related in all other norm conditions.


Second, relationship between honesty & consumer intentions for each framing condition:
```{r}
emtrends(exp_model1, ~framing_condition, var = "honesty_center", adjust = "none")

# On a single graph
at_list <- list(honesty_center = seq(-2.5, 2.6, by = 1))

emmip(exp_model1, framing_condition ~ honesty_center, at = at_list, CIs = TRUE, xlab = "Honesty (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(exp_model1, ~ honesty_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Honesty (centered)", ylab = "Consumer Intentions")
```

* Honesty was non-significantly, positively related to consumer intentions in all framing conditions.


Third, interaction between honesty, framing, & norm condition:
```{r}
emtrends(exp_model1, ~norm_condition | framing_condition, var = "honesty_center", adjust = "none")

# Separate graph for each framing condition
at_list <- list(honesty_center = seq(-2.5, 2.6, by = 1))

emmip(exp_model1, norm_condition ~ honesty_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Honesty (centered)", ylab = "Consumer Intentions")
```

* In the control framing condition, honesty was non-significantly related to consumer intentions in all norm conditions.

* In the pro-environmental framing condition, honesty was significantly, negatively related to consumer intentions in the **descriptive norm** condition, and non-significantly related in all other norm conditions.

* In the self-enhancing framing condition, honesty was significantly, negatively related to consumer intentions in the **descriptive norm** condition, and non-significantly related in all other norm conditions.