---
title: "Analysis using Multiple Imputation (scmfcs)"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
date: "2023-03-29"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r clear environment, echo = FALSE}
rm(list = ls())
```


```{r libraries, message = FALSE, warning = FALSE, include = FALSE}
library(Rmisc)
library(Hmisc)
library(rio)
library(tidyverse)
library(psych)
library(gtools) # rbinding data frames
library(corrplot)
library(jtools) # for pretty printing tables
library(sjPlot) # pretty printing tables
library(sjmisc) # pretty printing
library(mice) # handling missing values
library(naniar) # visualizaing missingness & MCAR test
library(miceadds) # for mi.anova
library(emmeans) # simple effects analyses
library(broom)     # for extracting residuals and outlier indices
library(olsrr)     # for creating outlier plots
library(smcfcs) # for multiple imputation with interactions
library(mitools) # for pooling MI results
library(marginaleffects) # for plotting marginal means 
library(installr)
library(epiDisplay) # for frequency tables
library(papaja) # for APA printing
library(car) # for Anova function (type III ss)
library(lsr) # for etaSquared
library(modeest) # for mode (using mlv function)
library(cowplot) # for plot_grid to display multiple plots
library(pwr)
library(pwr2)


options(max.print = 100000) # max rows to print in output
options(scipen = 1000) # turn off sci notation
```

# Data Import & Cleaning

## Import data
```{r import data}
raw_psych_hum_subj <- import("data/raw/raw_psych_hum_subj.csv")
raw_mktg_hum_subj <- import("data/raw/raw_mktg_hum_subj.csv")
raw_gen_uo_pop <- import("data/raw/raw_gen_uo_pop.csv")
pre_fall22 <- import("data/prescreen/dittersdorf_matches_f22.csv")
pre_winter23 <- import("data/prescreen/dittersdorf_matches_w23.csv")
pre_spring23 <- import("data/prescreen/dittersdorf_matches_s23.csv")
participant_list <- import("data/prescreen/dittersdorf_participants.csv")
```



Fix age before converting variable types
```{r}
table(raw_psych_hum_subj$Age) # 18 years old = 18
table(raw_mktg_hum_subj$Age) # 1999 = 24
table(raw_gen_uo_pop$Age)

raw_psych_hum_subj$Age[raw_psych_hum_subj$Age == "18 years old"] <- 18
raw_mktg_hum_subj$Age[raw_mktg_hum_subj$Age == 1999] <- 24

table(raw_psych_hum_subj$Age) # 18 years old = 18
table(raw_mktg_hum_subj$Age) # 1999 = 24
```



## Combine dataframes 
```{r update var types, warning = FALSE}
raw_psych_hum_subj <- raw_psych_hum_subj %>%
  mutate(Age = as.integer(Age),
         Gender = as.factor(Gender),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors),
         skepticism = as.factor(skepticism),
         id = as.factor(id),
         source = strrep("psych_hsp", times = 1))

levels(raw_psych_hum_subj$framing_condition_DO)

raw_mktg_hum_subj <- raw_mktg_hum_subj %>%
  mutate(Age = as.integer(Age),
         Gender = as.factor(Gender),
         Gender_5_TEXT = as.character(Gender_5_TEXT),
         Class_Lvl_7_TEXT = as.character(Class_Lvl_7_TEXT),
         Pol_Ornt_8_TEXT = as.character(Pol_Ornt_8_TEXT),
         Ethnicity_8_TEXT = as.character(Ethnicity_8_TEXT),
         skept_open = as.character(skept_open),
         skepticism = as.factor(skepticism),
         id = as.factor(id),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors),
         source = strrep("mktg_hsp", times = 1))

raw_gen_uo_pop <- raw_gen_uo_pop %>%
  mutate(Gender = as.factor(Gender),
         Gender_5_TEXT = as.character(Gender_5_TEXT),
         Class_Lvl_7_TEXT = as.character(Class_Lvl_7_TEXT),
         Pol_Ornt_8_TEXT = as.character(Pol_Ornt_8_TEXT),
         skept_open = as.character(skept_open),
         skepticism = as.factor(skepticism),
         id = as.factor(id),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors),
         source = strrep("gen_UO", times = 1))
```


Specify unique variables to combine prescreen data sets
```{r prep prescreen dfs}
# Create unique full_name variable
pre_fall22$full_name <- paste(pre_fall22$first_name, pre_fall22$last_name, sep="_")

pre_winter23$full_name <- paste(pre_winter23$first_name, pre_winter23$last_name, sep="_")

pre_spring23$full_name <- paste(pre_spring23$first_name, pre_spring23$last_name, sep="_")

participant_list$full_name <- paste(participant_list$first_name, participant_list$last_name, sep="_")

# Create column indicating which data set rows came from

pre_fall22 <- pre_fall22 %>%
  mutate(term = "fall22")

pre_winter23 <- pre_winter23 %>%
  mutate(term = "winter23")

pre_spring23 <- pre_spring23 %>%
  mutate(term = "spring23")
```


Combine prescreen data
```{r combine prescreen dfs}
combine1 <- smartbind(pre_fall22, pre_winter23)
combined_prescreen <- smartbind(combine1, pre_spring23)

# nrow(pre_fall22) + nrow(pre_winter23) + nrow(pre_spring23) # n = 1167

combined_prescreen_unique <- combined_prescreen[!duplicated(combined_prescreen$full_name), ] # keeps first row (fall22)
```

Subset key variables
```{r subset key vars}
combined_prescreen_key <- combined_prescreen_unique %>%
  dplyr::select(full_name, term, respecting:gratification, honest:gossip)

participant_list_key <- participant_list %>%
  dplyr::select(full_name, survey_id)
```

Merge with participant list
```{r merge participant list}
merged_prescreen <- merge(combined_prescreen_key, participant_list_key, by = "full_name")
```


Rename SDR items to match
```{r clean merged prescreen, warning = FALSE, include = FALSE}
merged_prescreen <- merged_prescreen %>%
  rename("lose_out" = "lose-out", 
         "cover_up" = "cover-up",
         "get_even" = "get-even",
         "behind_back" = "behind-back",
         "private_talk" = "private-talk",
         "take_things" = "take-things",
         "id" = "survey_id")
```

Convert variable types
```{r}
merged_prescreen <- merged_prescreen %>%
  mutate(respecting = as.integer(respecting),
         unity = as.integer(unity),
         protecting = as.integer(protecting),
         preventing = as.integer(preventing),
         equality = as.integer(equality),
         peace = as.integer(peace),
         justice = as.integer(justice),
         helpful = as.integer(helpful),
         power = as.integer(power),
         wealth = as.integer(wealth),
         authority = as.integer(authority),
         influential = as.integer(influential),
         ambition = as.integer(ambition),
         pleasures = as.integer(pleasures),
         enjoying = as.integer(enjoying),
         gratification = as.integer(gratification),
         honest = as.integer(honest),
         like = as.integer(like),
         disturbing = as.integer(disturbing),
         regret = as.integer(regret),
         lose_out = as.integer(lose_out),
         rational = as.integer(rational),
         confident = as.integer(confident),
         lover = as.integer(lover),
         lies = as.integer(lies),
         cover_up = as.integer(cover_up),
         advantage = as.integer(advantage),
         get_even = as.integer(get_even),
         behind_back = as.integer(behind_back),
         private_talk = as.integer(private_talk),
         take_things = as.integer(take_things),
         gossip = as.integer(gossip),
         id = as.factor(id))
```


Rename values & socially desirable items in prescreen data to match names in main data:
```{r rename prescreen vars, include = FALSE}
merged_prescreen <- merged_prescreen %>%
  rename("values_1" = "respecting",
         "values_2" = "unity",
         "values_3" = "protecting",
         "values_4" = "preventing",
         "values_5" = "equality",
         "values_6" = "peace",
         "values_7" = "justice",
         "values_8" = "helpful",
         "values_9" = "power",
         "values_10" = "wealth",
         "values_11" = "authority",
         "values_12" = "influential",
         "values_13" = "ambition",
         "values_14" = "pleasures",
         "values_15" = "enjoying",
         "values_16" = "gratification",
         "socially_desirable_1" = "honest",
         "socially_desirable_2" = "like",
         "socially_desirable_3" = "disturbing",
         "socially_desirable_4" = "regret",
         "socially_desirable_5" = "lose_out",
         "socially_desirable_6" = "rational",
         "socially_desirable_7" = "confident",
         "socially_desirable_8" = "lover",
         "socially_desirable_9" = "lies",
         "socially_desirable_10" = "cover_up",
         "socially_desirable_11" = "advantage",
         "socially_desirable_12" = "get_even",
         "socially_desirable_13" = "behind_back",
         "socially_desirable_14" = "private_talk",
         "socially_desirable_15" = "take_things",
         "socially_desirable_16" = "gossip")
```


Combine all data

- First, combine Psych Hum Subj data with Prescreen data based on `id`
- Second, add Mktg Hum Subj data
- Third, add gen UO Pop data
```{r combine all data}
combine1 <- merge(raw_psych_hum_subj, merged_prescreen, by = "id")
combine2 <- smartbind(combine1, raw_mktg_hum_subj)
combine3 <- smartbind(combine2, raw_gen_uo_pop)
```


## Remove duplicate cases

Identify duplicate cases
```{r id duplicate cases, results = 'hide'}
# first, add unique row #s
combine3 <- combine3 %>%
  mutate(row = 1:nrow(combine3))

combine3[duplicated(combine3$id),] # Only rows 1 through 858 have unique id #s

# write.csv(combine3, "combined_data.csv")
```

Row IDs to remove:

* 13 (participant's second time completing study)
* 134 (participant didn't complete study first time)
* 145 (participant didn't complete study first time)
* 308 (participant's second time completing study)
* 672 (participant's second time completing study)
* 743 (participant didn't complete study first time)
* 790 (participant didn't complete study first time)
* 800 (participant didn't complete study first time)

Remove duplicate rows after resolving:
```{r remove duplicate cases}
combine3 <- combine3 %>%
  filter(!row %in% c(13, 134, 145, 308, 672, 743, 790, 800))
```


## Remove rows of all NAs

Identify completely missing rows:
```{r id all NA rows, results = 'hide'}
key_vars <- combine3 %>%
  dplyr::select(row, big_2_1:big_2_65, consumer_intentions_1:consumer_intentions_9, consumer_behaviors, clothing_interest_1:clothing_interest_20, ingroup_ident_1:ingroup_ident_14, values_1:values_16, socially_desirable_1:socially_desirable_16, source)

ncol(key_vars) # number of columns - the row # & source column = 141

all_NA_rows <- key_vars[rowSums(is.na(key_vars)) == 141,] # identify rows with 141 NAs (all missing values), row numbers are preserved

all_NA_rows
```

Removing rows of fully missing data
```{r remove all NA rows}
data <- combine3 %>%
  dplyr::filter(!row %in% c(859, 860, 900, 926, 927, 941, 1139, 1141, 1142, 1143, 1144, 1146, 1149, 1150, 1152)) %>% # remove rows containing all NAs
  dplyr::select(-StartDate, -EndDate, -Status, -Progress, -"Duration (in seconds)", -Finished, -RecordedDate, -ResponseId, -DistributionChannel, -UserLanguage, -big_2_DO, -consumer_intentions_DO, -consumer_behaviors_DO, -clothing_interest_DO, -ingroup_ident_DO, -full_name, -code, -socially_desirable_DO, -values_DO, -email_giftcard, -term) # removing variables not in analysis
```


## Number per source
```{r}
table(data$source)
```

* 850 = psych human subjects pool
* 276 = mktg human subjects pool
* 7 = general UO pop


Rename variables
```{r rename vars}
data <- data %>%
  rename("framing_condition" = "framing_condition_DO", 
         "norm_condition" = "norm_condition_DO")
```

Drop unused levels
```{r include = FALSE}
levels(data$framing_condition)
levels(data$norm_condition)

data$framing_condition <- droplevels(data$framing_condition)
data$norm_condition <- droplevels(data$norm_condition)

levels(data$framing_condition)
levels(data$norm_condition)
```


Re-order levels of norm condition
```{r}
data$norm_condition <- factor(data$norm_condition, levels = c("control_norm", "descriptive_norm", "convention_norm", "social_norm", "moral_norm"))
```


## Inspect final data 
```{r inspect final df, results = 'hide'}
str(data, list.len = ncol(data))

# write.csv(data, "final_data.csv")
```


# Aggregate Variables 

## Personality

### Reverse-code

```{r reverse personality items}
data_R <- data %>%
  mutate(across(c(big_2_11,
                  big_2_16,
                  big_2_26,
                  big_2_31,
                  big_2_36,
                  big_2_51,
                  big_2_12,
                  big_2_17,
                  big_2_22,
                  big_2_37,
                  big_2_42,
                  big_2_47,
                  big_2_3,
                  big_2_8,
                  big_2_23,
                  big_2_28,
                  big_2_48,
                  big_2_58,
                  big_2_4,
                  big_2_9,
                  big_2_24,
                  big_2_29,
                  big_2_44,
                  big_2_49,
                  big_2_5,
                  big_2_25,
                  big_2_30,
                  big_2_45,
                  big_2_50,
                  big_2_55,
                  big_2_63), ~6 - .)) # replace '6' with the max possible value plus 1 for any particular scale
```

### Average items

```{r aggregate personality}
data_R$extraversion <- data_R %>%
  dplyr::select(big_2_1, big_2_6, big_2_11, big_2_16, big_2_21, big_2_26, big_2_31, big_2_36, big_2_41, big_2_46, big_2_51, big_2_56) %>%
  rowMeans(na.rm = TRUE) 


data_R$conscientiousness <- data_R %>%
  dplyr::select(big_2_3, big_2_8, big_2_13, big_2_18, big_2_23, big_2_28, big_2_33, big_2_38, big_2_43, big_2_48, big_2_53, big_2_58) %>%
  rowMeans(na.rm = TRUE)


data_R$agreeableness <- data_R %>%
  dplyr::select(big_2_2, big_2_7, big_2_12, big_2_17, big_2_22, big_2_27, big_2_32, big_2_37, big_2_42, big_2_47, big_2_52, big_2_57) %>%
  rowMeans(na.rm = TRUE)


data_R$neuroticism <- data_R %>%
  dplyr::select(big_2_4, big_2_9, big_2_14, big_2_19, big_2_24, big_2_29, big_2_34, big_2_39, big_2_44, big_2_49, big_2_54, big_2_59) %>%
  rowMeans(na.rm = TRUE)


data_R$openness <- data_R %>%
  dplyr::select(big_2_5, big_2_10, big_2_15, big_2_20, big_2_25, big_2_30, big_2_35, big_2_40, big_2_45, big_2_50, big_2_55, big_2_60) %>%
  rowMeans(na.rm = TRUE)


data_R$honesty <- data_R %>%
  dplyr::select(big_2_61, big_2_62, big_2_63, big_2_64, big_2_65) %>%
  rowMeans(na.rm = TRUE)
```

### Visually inspect
```{r warning = FALSE}
data_R %>%
  dplyr::select(extraversion, agreeableness, conscientiousness, openness, neuroticism, honesty) %>%
  hist()
```


## Clothing Interest

### Reverse-code

```{r reverse clothing items}
data_R <- data_R %>%
  mutate(across(c(clothing_interest_3,
                  clothing_interest_5,
                  clothing_interest_7,
                  clothing_interest_9,
                  clothing_interest_12,
                  clothing_interest_14,
                  clothing_interest_15,
                  clothing_interest_16,
                  clothing_interest_18,
                  clothing_interest_20), ~6 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```


### Average items
```{r aggregate clothing interest}
data_R$clothing_interest <- data_R %>%
  dplyr::select(clothing_interest_1:clothing_interest_20) %>%
  rowMeans(na.rm = TRUE)
```


### Visually Inspect
```{r}
data_R %>%
  dplyr::select(clothing_interest) %>%
  hist()
```



## In-group Identification

### Reverse-code

No items need to be reverse-coded.

### Average items
```{r aggegate ingroup ident}
data_R$ingroup_identification <- data_R %>%
  dplyr::select(ingroup_ident_1:ingroup_ident_14) %>%
  rowMeans(na.rm = TRUE)
```

### Visually Inspect

```{r}
data_R %>%
  dplyr::select(ingroup_identification) %>%
  hist()
```

## Values

### Reverse-code

No items need to be reverse-coded.

### Recoding scale options

Recoding values:

* -3 = 1
* -2 = 2
* -1 = 3
* 0 = 4
* +1 = 5
* +2 = 6
* +3 = 7

```{r recode values}
table(data_R$values_1)

data_R$values_1_rec <- dplyr::recode(data_R$values_1, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)

table(data_R$values_1_rec)

data_R$values_2_rec <- dplyr::recode(data_R$values_2, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_3_rec <- dplyr::recode(data_R$values_3, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_4_rec <- dplyr::recode(data_R$values_4, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_5_rec <- dplyr::recode(data_R$values_5, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_6_rec <- dplyr::recode(data_R$values_6, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_7_rec <- dplyr::recode(data_R$values_7, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_8_rec <- dplyr::recode(data_R$values_8, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_9_rec <- dplyr::recode(data_R$values_9, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_10_rec <- dplyr::recode(data_R$values_10, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_11_rec <- dplyr::recode(data_R$values_11, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_12_rec <- dplyr::recode(data_R$values_12, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_13_rec <- dplyr::recode(data_R$values_13, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_14_rec <- dplyr::recode(data_R$values_14, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_15_rec <- dplyr::recode(data_R$values_15, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_16_rec <- dplyr::recode(data_R$values_16, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)

table(data_R$values_16)
table(data_R$values_16_rec)
```


### Average items
```{r aggregate values}
data_R$biospheric <- data_R %>%
  dplyr::select(values_1_rec:values_4_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$altruistic <- data_R %>%
  dplyr::select(values_5_rec:values_8_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$egoistic <- data_R %>%
  dplyr::select(values_9_rec:values_13_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$hedonic <- data_R %>%
  dplyr::select(values_14_rec:values_16_rec) %>%
  rowMeans(na.rm = TRUE)
```


### Visually inspect
```{r}
values_df <- data_R %>%
  dplyr::select(biospheric, altruistic, egoistic, hedonic)

values_df %>%
  hist()
```

### Frequency tables
```{r}
# Biospheric values
tab1(values_df$biospheric, sort.group = "descending", cum.percent = TRUE, missing = FALSE, horiz = TRUE)

# Altruistic values
tab1(values_df$altruistic, sort.group = "descending", cum.percent = TRUE, missing = FALSE, horiz = TRUE)

# Egoistic values
tab1(values_df$egoistic, sort.group = "descending", cum.percent = TRUE, missing = FALSE, horiz = TRUE)

# Hedonic values
tab1(values_df$hedonic, sort.group = "descending", cum.percent = TRUE, missing = FALSE, horiz = TRUE)
```




## Socially Desirable Responding

### Reverse-code
```{r reverse code socially desirable items}
data_R <- data_R %>%
  mutate(across(c(socially_desirable_1,
                  socially_desirable_3,
                  socially_desirable_5,
                  socially_desirable_8,
                  socially_desirable_9,
                  socially_desirable_11,
                  socially_desirable_12,
                  socially_desirable_13), ~8 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```

### Average items
```{r aggregate socially desirable}
data_R$self_deceptive_sdr <- data_R %>%
  dplyr::select(socially_desirable_1:socially_desirable_8) %>%
  rowMeans(na.rm = TRUE)
  
data_R$impress_manag_sdr <- data_R %>%
  dplyr::select(socially_desirable_9:socially_desirable_16) %>%
  rowMeans(na.rm = TRUE)
```

### Visually inspect

```{r warning = FALSE}
data_R %>%
  dplyr::select(self_deceptive_sdr, impress_manag_sdr) %>%
  hist()
```


## Consumer Intentions

### Reverse-code

Higher scores mean better consumer intentions (intentions to *reduce* future consumption):
```{r reverse code consumer intentions}
data_R <- data_R %>%
  mutate(across(c(consumer_intentions_2,
                  consumer_intentions_4,
                  consumer_intentions_7,
                  consumer_intentions_9), ~8 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```

### Average items

```{r aggregate consumer intentions}
data_R$consumer_intentions <- data_R %>%
  dplyr::select(consumer_intentions_1:consumer_intentions_9) %>%
  rowMeans(na.rm = TRUE)
```

### Visually inspect

```{r warning = FALSE}
data_R %>%
  dplyr::select(consumer_intentions) %>%
  hist()
```




# Contrast Coding 

Subset variables
```{r echo = FALSE}
data_R_alt <- data_R %>%
  dplyr::select(hedonic, egoistic, altruistic, biospheric, ingroup_identification, Age, clothing_interest, self_deceptive_sdr, impress_manag_sdr, consumer_intentions, consumer_behaviors, Gender, framing_condition, norm_condition)
```

Contrast Coding using ifelse() approach:
```{r alt coding}
# Framing
data_R_alt$FramingCode1 <- ifelse(data_R_alt$framing_condition == "control_framing", -1/2, ifelse(data_R_alt$framing_condition == "self_enh_framing", 1/2, 0))

data_R_alt$FramingCode2 <- ifelse(data_R_alt$framing_condition == "pro_env_framing", 2/3, -1/3)


# Norm
data_R_alt$NormCode1 <- ifelse(data_R_alt$norm_condition == "moral_norm", 4, -1)

data_R_alt$NormCode2 <- ifelse(data_R_alt$norm_condition == "social_norm", 3, ifelse(data_R_alt$norm_condition == "moral_norm", 0, -1))

data_R_alt$NormCode3 <- ifelse(data_R_alt$norm_condition == "convention_norm", 2, ifelse(data_R_alt$norm_condition == "moral_norm", 0, ifelse(data_R_alt$norm_condition == "social_norm", 0, -1)))
data_R_alt$NormCode4 <- ifelse(data_R_alt$norm_condition == "descriptive_norm", 1, ifelse(data_R_alt$norm_condition == "control_norm", -1, 0))


## Adding contrast codes to Framing & Norm Condition
# Framing
FrameCode1 <- c(-1/2, 0, 1/2) # control vs self-enhancing
FrameCode2 <- c(-1/3, 2/3, -1/3) # arbitrary code

contrasts(data_R_alt$framing_condition) <- cbind(FrameCode1, FrameCode2)
contrasts(data_R_alt$framing_condition)

# Norm
contrasts(data_R_alt$norm_condition) <- contr.helmert(5)
contrasts(data_R_alt$norm_condition) # control vs DN

# Gender
levels(data_R_alt$Gender) <- c("Woman", "Man", "Non-binary", "I prefer not to identify", "Other")

data_R_alt$Gender[data_R_alt$Gender == "Non-binary"] <- NA
data_R_alt$Gender[data_R_alt$Gender == "I prefer not to identify"] <- NA
data_R_alt$Gender[data_R_alt$Gender == "Other"] <- NA

data_R_alt$Gender <- droplevels(data_R_alt$Gender)


contrasts(data_R_alt$Gender) <- c(1, 0)
levels(data_R_alt$Gender)
```


# Multiple Imputation 

## Examine Missingness

```{r}
data_R_alt %>%
  dplyr::select(framing_condition, norm_condition, hedonic, egoistic, altruistic, biospheric, ingroup_identification, self_deceptive_sdr, impress_manag_sdr, consumer_intentions, consumer_behaviors, Age, Gender, clothing_interest) %>%
  vis_miss()

n_missing <- data_R_alt %>%
  dplyr::select(framing_condition, norm_condition, hedonic, egoistic, altruistic, biospheric, ingroup_identification, self_deceptive_sdr, impress_manag_sdr, consumer_intentions, consumer_behaviors, Age, Gender, clothing_interest) %>%
  lapply(function(x) sum(is.na(x)))

n_missing

# percent missing
lapply(n_missing, function(x) (x/nrow(data_R_alt))*100)
```

Variables with NO missing data:

* ingroup_identification
* clothing_interest
* consumer_intentions
* framing_condition
* norm_condition



## Adding interaction terms
```{r include = FALSE}
data_R_alt <- data_R_alt %>%
  mutate(framing1Xbiospheric = (FramingCode1)*(biospheric),
         framing2Xbiospheric = (FramingCode2)*(biospheric),
         norm1Xbiospheric = (NormCode1)*(biospheric),
         norm2Xbiospheric = (NormCode2)*(biospheric),
         norm3Xbiospheric = (NormCode3)*(biospheric),
         norm4Xbiospheric = (NormCode4)*(biospheric),
         framing1Xnorm1Xbiospheric = (FramingCode1)*(NormCode1)*(biospheric),
         framing1Xnorm2Xbiospheric = (FramingCode1)*(NormCode2)*(biospheric),
         framing1Xnorm3Xbiospheric = (FramingCode1)*(NormCode3)*(biospheric),
         framing1Xnorm4Xbiospheric = (FramingCode1)*(NormCode4)*(biospheric),
         framing2Xnorm1Xbiospheric = (FramingCode2)*(NormCode1)*(biospheric),
         framing2Xnorm2Xbiospheric = (FramingCode2)*(NormCode2)*(biospheric),
         framing2Xnorm3Xbiospheric = (FramingCode2)*(NormCode3)*(biospheric),
         framing2Xnorm4Xbiospheric = (FramingCode2)*(NormCode4)*(biospheric),
         
         framing1Xaltruistic = (FramingCode1)*(altruistic),
         framing2Xaltruistic = (FramingCode2)*(altruistic),
         norm1Xaltruistic = (NormCode1)*(altruistic),
         norm2Xaltruistic = (NormCode2)*(altruistic),
         norm3Xaltruistic = (NormCode3)*(altruistic),
         norm4Xaltruistic = (NormCode4)*(altruistic),
         framing1Xnorm1Xaltruistic = (FramingCode1)*(NormCode1)*(altruistic),
         framing1Xnorm2Xaltruistic = (FramingCode1)*(NormCode2)*(altruistic),
         framing1Xnorm3Xaltruistic = (FramingCode1)*(NormCode3)*(altruistic),
         framing1Xnorm4Xaltruistic = (FramingCode1)*(NormCode4)*(altruistic),
         framing2Xnorm1Xaltruistic = (FramingCode2)*(NormCode1)*(altruistic),
         framing2Xnorm2Xaltruistic = (FramingCode2)*(NormCode2)*(altruistic),
         framing2Xnorm3Xaltruistic = (FramingCode2)*(NormCode3)*(altruistic),
         framing2Xnorm4Xaltruistic = (FramingCode2)*(NormCode4)*(altruistic),
         
         framing1Xegoistic = (FramingCode1)*(egoistic),
         framing2Xegoistic = (FramingCode2)*(egoistic),
         norm1Xegoistic = (NormCode1)*(egoistic),
         norm2Xegoistic = (NormCode2)*(egoistic),
         norm3Xegoistic = (NormCode3)*(egoistic),
         norm4Xegoistic = (NormCode4)*(egoistic),
         framing1Xnorm1Xegoistic = (FramingCode1)*(NormCode1)*(egoistic),
         framing1Xnorm2Xegoistic = (FramingCode1)*(NormCode2)*(egoistic),
         framing1Xnorm3Xegoistic = (FramingCode1)*(NormCode3)*(egoistic),
         framing1Xnorm4Xegoistic = (FramingCode1)*(NormCode4)*(egoistic),
         framing2Xnorm1Xegoistic = (FramingCode2)*(NormCode1)*(egoistic),
         framing2Xnorm2Xegoistic = (FramingCode2)*(NormCode2)*(egoistic),
         framing2Xnorm3Xegoistic = (FramingCode2)*(NormCode3)*(egoistic),
         framing2Xnorm4Xegoistic = (FramingCode2)*(NormCode4)*(egoistic),
         
         framing1Xhedonic = (FramingCode1)*(hedonic),
         framing2Xhedonic = (FramingCode2)*(hedonic),
         norm1Xhedonic = (NormCode1)*(hedonic),
         norm2Xhedonic = (NormCode2)*(hedonic),
         norm3Xhedonic = (NormCode3)*(hedonic),
         norm4Xhedonic = (NormCode4)*(hedonic),
         framing1Xnorm1Xhedonic = (FramingCode1)*(NormCode1)*(hedonic),
         framing1Xnorm2Xhedonic = (FramingCode1)*(NormCode2)*(hedonic),
         framing1Xnorm3Xhedonic = (FramingCode1)*(NormCode3)*(hedonic),
         framing1Xnorm4Xhedonic = (FramingCode1)*(NormCode4)*(hedonic),
         framing2Xnorm1Xhedonic = (FramingCode2)*(NormCode1)*(hedonic),
         framing2Xnorm2Xhedonic = (FramingCode2)*(NormCode2)*(hedonic),
         framing2Xnorm3Xhedonic = (FramingCode2)*(NormCode3)*(hedonic),
         framing2Xnorm4Xhedonic = (FramingCode2)*(NormCode4)*(hedonic),
         
         framing1Xingroup = (FramingCode1)*(ingroup_identification),
         framing2Xingroup = (FramingCode2)*(ingroup_identification),
         norm1Xingroup = (NormCode1)*(ingroup_identification),
         norm2Xingroup = (NormCode2)*(ingroup_identification),
         norm3Xingroup = (NormCode3)*(ingroup_identification),
         norm4Xingroup = (NormCode4)*(ingroup_identification),
         framing1Xnorm1Xingroup = (FramingCode1)*(NormCode1)*(ingroup_identification),
         framing1Xnorm2Xingroup = (FramingCode1)*(NormCode2)*(ingroup_identification),
         framing1Xnorm3Xingroup = (FramingCode1)*(NormCode3)*(ingroup_identification),
         framing1Xnorm4Xingroup = (FramingCode1)*(NormCode4)*(ingroup_identification),
         framing2Xnorm1Xingroup = (FramingCode2)*(NormCode1)*(ingroup_identification),
         framing2Xnorm2Xingroup = (FramingCode2)*(NormCode2)*(ingroup_identification),
         framing2Xnorm3Xingroup = (FramingCode2)*(NormCode3)*(ingroup_identification),
         framing2Xnorm4Xingroup = (FramingCode2)*(NormCode4)*(ingroup_identification))
```



## Imputation model

```{r}
set.seed(114950518)
```

- check out mice.impute.smcfcs 

```{r echo = FALSE}
imps <- smcfcs(data_R_alt, 
               smtype = "lm", 
               smformula = "consumer_intentions ~ framing_condition + norm_condition + framing_condition*norm_condition + ingroup_identification + framing1Xingroup + framing2Xingroup + norm1Xingroup + norm2Xingroup + norm3Xingroup + norm4Xingroup + framing1Xnorm1Xingroup + framing1Xnorm2Xingroup + framing1Xnorm3Xingroup + framing1Xnorm4Xingroup + framing2Xnorm1Xingroup + framing2Xnorm2Xingroup + framing2Xnorm3Xingroup + framing2Xnorm4Xingroup + clothing_interest + self_deceptive_sdr + impress_manag_sdr + biospheric + framing1Xbiospheric + framing2Xbiospheric + norm1Xbiospheric + norm2Xbiospheric + norm3Xbiospheric + norm4Xbiospheric + framing1Xnorm1Xbiospheric + framing1Xnorm2Xbiospheric + framing1Xnorm3Xbiospheric + framing1Xnorm4Xbiospheric + framing2Xnorm1Xbiospheric + framing2Xnorm2Xbiospheric + framing2Xnorm3Xbiospheric + framing2Xnorm4Xbiospheric + altruistic + framing1Xaltruistic + framing2Xaltruistic + norm1Xaltruistic + norm2Xaltruistic + norm3Xaltruistic + norm4Xaltruistic + framing1Xnorm1Xaltruistic + framing1Xnorm2Xaltruistic + framing1Xnorm3Xaltruistic + framing1Xnorm4Xaltruistic + framing2Xnorm1Xaltruistic + framing2Xnorm2Xaltruistic + framing2Xnorm3Xaltruistic + framing2Xnorm4Xaltruistic + egoistic + framing1Xegoistic + framing2Xegoistic + norm1Xegoistic + norm2Xegoistic + norm3Xegoistic + norm4Xegoistic + framing1Xnorm1Xegoistic + framing1Xnorm2Xegoistic + framing1Xnorm3Xegoistic + framing1Xnorm4Xegoistic + framing2Xnorm1Xegoistic + framing2Xnorm2Xegoistic + framing2Xnorm3Xegoistic + framing2Xnorm4Xegoistic + hedonic + framing1Xhedonic + framing2Xhedonic + norm1Xhedonic + norm2Xhedonic + norm3Xhedonic + norm4Xhedonic + framing1Xnorm1Xhedonic + framing1Xnorm2Xhedonic + framing1Xnorm3Xhedonic + framing1Xnorm4Xhedonic + framing2Xnorm1Xhedonic + framing2Xnorm2Xhedonic + framing2Xnorm3Xhedonic + framing2Xnorm4Xhedonic + consumer_behaviors + Gender + Age", 
               method = c("norm","norm","norm","norm","","norm","","norm","norm","","logreg","logreg","","","","","","","","","FramingCode1*biospheric","FramingCode2*biospheric","NormCode1*biospheric","NormCode2*biospheric","NormCode3*biospheric","NormCode4*biospheric","FramingCode1*NormCode1*biospheric","FramingCode1*NormCode2*biospheric","FramingCode1*NormCode3*biospheric","FramingCode1*NormCode4*biospheric","FramingCode2*NormCode1*biospheric","FramingCode2*NormCode2*biospheric","FramingCode2*NormCode3*biospheric","FramingCode2*NormCode4*biospheric","FramingCode1*altruistic","FramingCode2*altruistic","NormCode1*altruistic","NormCode2*altruistic","NormCode3*altruistic","NormCode4*altruistic","FramingCode1*NormCode1*altruistic","FramingCode1*NormCode2*altruistic","FramingCode1*NormCode3*altruistic","FramingCode1*NormCode4*altruistic","FramingCode2*NormCode1*altruistic","FramingCode2*NormCode2*altruistic","FramingCode2*NormCode3*altruistic","FramingCode2*NormCode4*altruistic","FramingCode1*egoistic","FramingCode2*egoistic","NormCode1*egoistic","NormCode2*egoistic","NormCode3*egoistic","NormCode4*egoistic","FramingCode1*NormCode1*egoistic","FramingCode1*NormCode2*egoistic","FramingCode1*NormCode3*egoistic","FramingCode1*NormCode4*egoistic","FramingCode2*NormCode1*egoistic","FramingCode2*NormCode2*egoistic","FramingCode2*NormCode3*egoistic","FramingCode2*NormCode4*egoistic","FramingCode1*hedonic","FramingCode2*hedonic","NormCode1*hedonic","NormCode2*hedonic","NormCode3*hedonic","NormCode4*hedonic","FramingCode1*NormCode1*hedonic","FramingCode1*NormCode2*hedonic","FramingCode1*NormCode3*hedonic","FramingCode1*NormCode4*hedonic","FramingCode2*NormCode1*hedonic","FramingCode2*NormCode2*hedonic","FramingCode2*NormCode3*hedonic","FramingCode2*NormCode4*hedonic","","","","","","","","","","","","","",""))
```


Storing imputed data sets
```{r echo = FALSE}
impobject <- imputationList(imps$impDatasets)
```

Restrict range of values on imputed variables
```{r}
# bio values
impobject$imputations[[1]]$biospheric <- ifelse(impobject$imputations[[1]]$biospheric > 7, 7, impobject$imputations[[1]]$biospheric)

impobject$imputations[[2]]$biospheric <- ifelse(impobject$imputations[[2]]$biospheric > 7, 7, impobject$imputations[[2]]$biospheric)

impobject$imputations[[3]]$biospheric <- ifelse(impobject$imputations[[3]]$biospheric > 7, 7, impobject$imputations[[3]]$biospheric)

impobject$imputations[[4]]$biospheric <- ifelse(impobject$imputations[[4]]$biospheric > 7, 7, impobject$imputations[[4]]$biospheric)

impobject$imputations[[5]]$biospheric <- ifelse(impobject$imputations[[5]]$biospheric > 7, 7, impobject$imputations[[5]]$biospheric)


# alt values
impobject$imputations[[1]]$altruistic <- ifelse(impobject$imputations[[1]]$altruistic > 7, 7, impobject$imputations[[1]]$altruistic)

impobject$imputations[[2]]$altruistic <- ifelse(impobject$imputations[[2]]$altruistic > 7, 7, impobject$imputations[[2]]$altruistic)

impobject$imputations[[3]]$altruistic <- ifelse(impobject$imputations[[3]]$altruistic > 7, 7, impobject$imputations[[3]]$altruistic)

impobject$imputations[[4]]$altruistic <- ifelse(impobject$imputations[[4]]$altruistic > 7, 7, impobject$imputations[[4]]$altruistic)

impobject$imputations[[5]]$altruistic <- ifelse(impobject$imputations[[5]]$altruistic > 7, 7, impobject$imputations[[5]]$altruistic)


# ego values
impobject$imputations[[1]]$egoistic <- ifelse(impobject$imputations[[1]]$egoistic > 7, 7, impobject$imputations[[1]]$egoistic)

impobject$imputations[[2]]$egoistic <- ifelse(impobject$imputations[[2]]$egoistic > 7, 7, impobject$imputations[[2]]$egoistic)

impobject$imputations[[3]]$egoistic <- ifelse(impobject$imputations[[3]]$egoistic > 7, 7, impobject$imputations[[3]]$egoistic)

impobject$imputations[[4]]$egoistic <- ifelse(impobject$imputations[[4]]$egoistic > 7, 7, impobject$imputations[[4]]$egoistic)

impobject$imputations[[5]]$egoistic <- ifelse(impobject$imputations[[5]]$egoistic > 7, 7, impobject$imputations[[5]]$egoistic)


# hed values
impobject$imputations[[1]]$hedonic <- ifelse(impobject$imputations[[1]]$hedonic > 7, 7, impobject$imputations[[1]]$hedonic)

impobject$imputations[[2]]$hedonic <- ifelse(impobject$imputations[[2]]$hedonic > 7, 7, impobject$imputations[[2]]$hedonic)

impobject$imputations[[3]]$hedonic <- ifelse(impobject$imputations[[3]]$hedonic > 7, 7, impobject$imputations[[3]]$hedonic)

impobject$imputations[[4]]$hedonic <- ifelse(impobject$imputations[[4]]$hedonic > 7, 7, impobject$imputations[[4]]$hedonic)

impobject$imputations[[5]]$hedonic <- ifelse(impobject$imputations[[5]]$hedonic > 7, 7, impobject$imputations[[5]]$hedonic)


# self-deceptive enhancement
with(impobject, describe(self_deceptive_sdr))

impobject$imputations[[4]]$self_deceptive_sdr <- ifelse(impobject$imputations[[4]]$self_deceptive_sdr < 1, 1, impobject$imputations[[4]]$self_deceptive_sdr)


# impr manag
with(impobject, describe(impress_manag_sdr))

# Age
describe(data_R_alt$Age)
with(impobject, describe(Age))

impobject$imputations[[1]]$Age <- ifelse(impobject$imputations[[1]]$Age < 18, 18, impobject$imputations[[1]]$Age)

impobject$imputations[[2]]$Age <- ifelse(impobject$imputations[[2]]$Age < 18, 18, impobject$imputations[[2]]$Age)

impobject$imputations[[3]]$Age <- ifelse(impobject$imputations[[3]]$Age < 18, 18, impobject$imputations[[3]]$Age)

impobject$imputations[[4]]$Age <- ifelse(impobject$imputations[[4]]$Age < 18, 18, impobject$imputations[[4]]$Age)

impobject$imputations[[5]]$Age <- ifelse(impobject$imputations[[5]]$Age < 18, 18, impobject$imputations[[5]]$Age)
```


## Centering continuous predictors
```{r echo = FALSE}
# Biospheric values
impobject$imputations[[1]]$biospheric_center <- impobject$imputations[[1]]$biospheric - mean(impobject$imputations[[1]]$biospheric)

impobject$imputations[[2]]$biospheric_center <- impobject$imputations[[2]]$biospheric - mean(impobject$imputations[[2]]$biospheric)

impobject$imputations[[3]]$biospheric_center <- impobject$imputations[[3]]$biospheric - mean(impobject$imputations[[3]]$biospheric)

impobject$imputations[[4]]$biospheric_center <- impobject$imputations[[4]]$biospheric - mean(impobject$imputations[[4]]$biospheric)

impobject$imputations[[5]]$biospheric_center <- impobject$imputations[[5]]$biospheric - mean(impobject$imputations[[5]]$biospheric)


# Altruistic values
impobject$imputations[[1]]$altruistic_center <- impobject$imputations[[1]]$altruistic - mean(impobject$imputations[[1]]$altruistic)

impobject$imputations[[2]]$altruistic_center <- impobject$imputations[[2]]$altruistic - mean(impobject$imputations[[2]]$altruistic)

impobject$imputations[[3]]$altruistic_center <- impobject$imputations[[3]]$altruistic - mean(impobject$imputations[[3]]$altruistic)

impobject$imputations[[4]]$altruistic_center <- impobject$imputations[[4]]$altruistic - mean(impobject$imputations[[4]]$altruistic)

impobject$imputations[[5]]$altruistic_center <- impobject$imputations[[5]]$altruistic - mean(impobject$imputations[[5]]$altruistic)


# Egoistic values
impobject$imputations[[1]]$egoistic_center <- impobject$imputations[[1]]$egoistic - mean(impobject$imputations[[1]]$egoistic)

impobject$imputations[[2]]$egoistic_center <- impobject$imputations[[2]]$egoistic - mean(impobject$imputations[[2]]$egoistic)

impobject$imputations[[3]]$egoistic_center <- impobject$imputations[[3]]$egoistic - mean(impobject$imputations[[3]]$egoistic)

impobject$imputations[[4]]$egoistic_center <- impobject$imputations[[4]]$egoistic - mean(impobject$imputations[[4]]$egoistic)

impobject$imputations[[5]]$egoistic_center <- impobject$imputations[[5]]$egoistic - mean(impobject$imputations[[5]]$egoistic)


# Hedonic values
impobject$imputations[[1]]$hedonic_center <- impobject$imputations[[1]]$hedonic - mean(impobject$imputations[[1]]$hedonic)

impobject$imputations[[2]]$hedonic_center <- impobject$imputations[[2]]$hedonic - mean(impobject$imputations[[2]]$hedonic)

impobject$imputations[[3]]$hedonic_center <- impobject$imputations[[3]]$hedonic - mean(impobject$imputations[[3]]$hedonic)

impobject$imputations[[4]]$hedonic_center <- impobject$imputations[[4]]$hedonic - mean(impobject$imputations[[4]]$hedonic)

impobject$imputations[[5]]$hedonic_center <- impobject$imputations[[5]]$hedonic - mean(impobject$imputations[[5]]$hedonic)



# Ingroup identification
impobject$imputations[[1]]$ingroup_center <- impobject$imputations[[1]]$ingroup_identification - mean(impobject$imputations[[1]]$ingroup_identification)

impobject$imputations[[2]]$ingroup_center <- impobject$imputations[[2]]$ingroup_identification - mean(impobject$imputations[[2]]$ingroup_identification)

impobject$imputations[[3]]$ingroup_center <- impobject$imputations[[3]]$ingroup_identification - mean(impobject$imputations[[3]]$ingroup_identification)

impobject$imputations[[4]]$ingroup_center <- impobject$imputations[[4]]$ingroup_identification - mean(impobject$imputations[[4]]$ingroup_identification)

impobject$imputations[[5]]$ingroup_center <- impobject$imputations[[5]]$ingroup_identification - mean(impobject$imputations[[5]]$ingroup_identification)


# Age
impobject$imputations[[1]]$Age_center <- impobject$imputations[[1]]$Age - mean(impobject$imputations[[1]]$Age)

impobject$imputations[[2]]$Age_center <- impobject$imputations[[2]]$Age - mean(impobject$imputations[[2]]$Age)

impobject$imputations[[3]]$Age_center <- impobject$imputations[[3]]$Age - mean(impobject$imputations[[3]]$Age)

impobject$imputations[[4]]$Age_center <- impobject$imputations[[4]]$Age - mean(impobject$imputations[[4]]$Age)

impobject$imputations[[5]]$Age_center <- impobject$imputations[[5]]$Age - mean(impobject$imputations[[5]]$Age)



# Clothing interest
impobject$imputations[[1]]$clothing_center <- impobject$imputations[[1]]$clothing_interest - mean(impobject$imputations[[1]]$clothing_interest)

impobject$imputations[[2]]$clothing_center <- impobject$imputations[[2]]$clothing_interest - mean(impobject$imputations[[2]]$clothing_interest)

impobject$imputations[[3]]$clothing_center <- impobject$imputations[[3]]$clothing_interest - mean(impobject$imputations[[3]]$clothing_interest)

impobject$imputations[[4]]$clothing_center <- impobject$imputations[[4]]$clothing_interest - mean(impobject$imputations[[4]]$clothing_interest)

impobject$imputations[[5]]$clothing_center <- impobject$imputations[[5]]$clothing_interest - mean(impobject$imputations[[5]]$clothing_interest)



# Self deceptive SDR
impobject$imputations[[1]]$self_dec_center <- impobject$imputations[[1]]$self_deceptive_sdr - mean(impobject$imputations[[1]]$self_deceptive_sdr)

impobject$imputations[[2]]$self_dec_center <- impobject$imputations[[2]]$self_deceptive_sdr - mean(impobject$imputations[[2]]$self_deceptive_sdr)

impobject$imputations[[3]]$self_dec_center <- impobject$imputations[[3]]$self_deceptive_sdr - mean(impobject$imputations[[3]]$self_deceptive_sdr)

impobject$imputations[[4]]$self_dec_center <- impobject$imputations[[4]]$self_deceptive_sdr - mean(impobject$imputations[[4]]$self_deceptive_sdr)

impobject$imputations[[5]]$self_dec_center <- impobject$imputations[[5]]$self_deceptive_sdr - mean(impobject$imputations[[5]]$self_deceptive_sdr)


# Impression management SDR
impobject$imputations[[1]]$impress_manag_center <- impobject$imputations[[1]]$impress_manag_sdr - mean(impobject$imputations[[1]]$impress_manag_sdr)

impobject$imputations[[2]]$impress_manag_center <- impobject$imputations[[2]]$impress_manag_sdr - mean(impobject$imputations[[2]]$impress_manag_sdr)

impobject$imputations[[3]]$impress_manag_center <- impobject$imputations[[3]]$impress_manag_sdr - mean(impobject$imputations[[3]]$impress_manag_sdr)

impobject$imputations[[4]]$impress_manag_center <- impobject$imputations[[4]]$impress_manag_sdr - mean(impobject$imputations[[4]]$impress_manag_sdr)

impobject$imputations[[5]]$impress_manag_center <- impobject$imputations[[5]]$impress_manag_sdr - mean(impobject$imputations[[5]]$impress_manag_sdr)


# Coding Gender
contrasts(impobject$imputations[[1]]$Gender) <- c(1/2, -1/2)
contrasts(impobject$imputations[[2]]$Gender) <- c(1/2, -1/2)
contrasts(impobject$imputations[[3]]$Gender) <- c(1/2, -1/2)
contrasts(impobject$imputations[[4]]$Gender) <- c(1/2, -1/2)
contrasts(impobject$imputations[[5]]$Gender) <- c(1/2, -1/2)
```



Convert `scmfcs` object to a `mids` object (to make the object compatible with `mice`, and thus, `emmeans`):
```{r}
mids_obj <- datlist2mids(impobject)
```

Complete data set:
```{r complete imputed data set, include = FALSE}
complete_data <- complete(mids_obj, "long")
```


# Descriptive Statistics

n per Condition
```{r}
data_R_alt %>%
  group_by(framing_condition, norm_condition) %>%
  summarise(n = n()) %>% 
  knitr::kable(digits = 2)

data_R_alt %>%
  group_by(norm_condition) %>%
  summarise(n = n())

data_R_alt %>%
  group_by(framing_condition) %>%
  summarise(n = n())
```


Descriptives for variables with NO missing data

Variables with NO missing data:

* ingroup_identification
* clothing_interest
* consumer_intentions
* framing_condition
* norm_condition

```{r}
with(mids_obj, psych::describe(clothing_interest)) # describe
with(mids_obj, sd(clothing_interest)) # sd
with(mids_obj, mlv(clothing_interest, method = "mfv")) # mode
with(mids_obj, tab1(clothing_interest, decimal = 2, sort.group = "decreasing", graph = FALSE)) # frequency table
with(mids_obj, hist(clothing_interest, main = "Histogram of Clothing Interest", xlab = "Clothing Interest", ylab = "Frequency", cex.lab = 1.2, cex.main = 1.5)) # histogram


with(mids_obj, psych::describe(ingroup_identification))
with(mids_obj, sd(ingroup_identification))
with(mids_obj, mlv(ingroup_identification, method = "mfv"))
with(mids_obj, tab1(ingroup_identification, sort.group = "decreasing", graph = FALSE)) 
with(mids_obj, hist(ingroup_identification, main = "Histogram of Ingroup Identification", xlab = "Ingroup Identification", ylab = "Frequency", cex.lab = 1.2, cex.main = 1.5))


with(mids_obj, psych::describe(consumer_intentions))
with(mids_obj, sd(consumer_intentions))
with(mids_obj, mlv(consumer_intentions, method = "mfv"))
with(mids_obj, tab1(consumer_intentions, decimal = 2, sort.group = "decreasing", graph = FALSE))
with(mids_obj, hist(consumer_intentions, main = "Histogram of Consumer Intentions", xlab = "Consumer Intentions", ylab = "Frequency", cex.lab = 1.2, cex.main = 1.5)) 
```

Descriptive Statistics for Consumer Intentions
```{r}
data_R_alt %>%
  group_by(framing_condition, norm_condition) %>%
  summarise(mean = mean(consumer_intentions),
            sd = sd(consumer_intentions)) %>% 
  knitr::kable(digits = 2)
```


Descriptives for variables with missing data:

* Biospheric values
* Altruistic values
* Egoistic values
* Hedonic values
* Self-deceptive enhancement
* Impression management
* Age

* Gender
* Consumer behaviors

Values
```{r}
data_R_alt %>%
  dplyr::select(biospheric) %>%
  describe()

with(mids_obj, psych::describe(biospheric)) # describe
with(mids_obj, mean(biospheric)) # mean
with(mids_obj, sd(biospheric)) # sd
with(mids_obj, skew(biospheric)) # skew
with(mids_obj, mlv(biospheric, method = "mfv")) # mode
with(mids_obj, tab1(biospheric, decimal = 2, sort.group = "decreasing", graph = FALSE)) # frequency table


data_R_alt %>%
  dplyr::select(altruistic) %>%
  describe()

with(mids_obj, psych::describe(altruistic))
with(mids_obj, mean(altruistic)) # mean
with(mids_obj, sd(altruistic)) # sd
with(mids_obj, skew(altruistic)) # skew
with(mids_obj, mlv(altruistic, method = "mfv"))
with(mids_obj, tab1(altruistic, sort.group = "decreasing", graph = FALSE)) 

data_R_alt %>%
  dplyr::select(egoistic) %>%
  describe()

with(mids_obj, psych::describe(egoistic))
with(mids_obj, mean(egoistic)) # mean
with(mids_obj, sd(egoistic)) # sd
with(mids_obj, skew(egoistic)) # skew
with(mids_obj, mlv(egoistic, method = "mfv"))
with(mids_obj, tab1(egoistic, decimal = 2, sort.group = "decreasing", graph = FALSE))


data_R_alt %>%
  dplyr::select(hedonic) %>%
  describe()

with(mids_obj, psych::describe(hedonic))
with(mids_obj, mean(hedonic)) # mean
with(mids_obj, sd(hedonic)) # sd
with(mids_obj, skew(hedonic)) # skew
with(mids_obj, mlv(hedonic, method = "mfv"))
with(mids_obj, tab1(hedonic, decimal = 2, sort.group = "decreasing", graph = FALSE))


# plotting multiple histograms
imp5_data <- complete_data %>% 
  filter(.imp == 5)

par(mfrow = c(2,2))

hist(imp5_data$biospheric, main = "Histogram of Biospheric Values", xlab = "Biospheric Values", ylab = "Frequency", cex.lab = 1.2, cex.main = 1.2) # histogram

hist(imp5_data$altruistic, main = "Histogram of Altruistic Values", xlab = "Altruistic Values", ylab = "Frequency", cex.lab = 1.2, cex.main = 1.2)

hist(imp5_data$egoistic, main = "Histogram of Egoistic Values", xlab = "Egoistic Values", ylab = "Frequency", cex.lab = 1.2, cex.main = 1.2)

hist(imp5_data$hedonic, main = "Histogram of Hedonic Values", xlab = "Hedonic Values", ylab = "Frequency", cex.lab = 1.2, cex.main = 1.2)

```


Socially desirable responding & age
```{r}
data_R_alt %>%
  dplyr::select(self_deceptive_sdr) %>%
  describe()

with(mids_obj, psych::describe(self_deceptive_sdr))
with(mids_obj, mean(self_deceptive_sdr)) # mean
with(mids_obj, sd(self_deceptive_sdr)) # sd
with(mids_obj, skew(self_deceptive_sdr)) # skew
with(mids_obj, mlv(self_deceptive_sdr, method = "mfv"))
with(mids_obj, tab1(self_deceptive_sdr, decimal = 2, sort.group = "decreasing", graph = FALSE))

data_R_alt %>%
  dplyr::select(impress_manag_sdr) %>%
  describe()

with(mids_obj, psych::describe(impress_manag_sdr))
with(mids_obj, mean(impress_manag_sdr)) # mean
with(mids_obj, sd(impress_manag_sdr)) # sd
with(mids_obj, skew(impress_manag_sdr)) # skew
with(mids_obj, mlv(impress_manag_sdr, method = "mfv"))
with(mids_obj, tab1(impress_manag_sdr, decimal = 2, sort.group = "decreasing", graph = FALSE))

data_R_alt %>%
  dplyr::select(Age) %>%
  describe()

with(mids_obj, psych::describe(Age))
with(mids_obj, mean(Age)) # mean
with(mids_obj, sd(Age)) # sd
with(mids_obj, skew(Age)) # skew
with(mids_obj, mlv(Age, method = "mfv"))
with(mids_obj, tab1(Age, decimal = 2, sort.group = "decreasing", graph = FALSE))


par(mfrow = c(2,2))

hist(imp5_data$self_deceptive_sdr, main = "Histogram of Self-deceptive Enhancement", xlab = "Self-deceptive Enhancement", ylab = "Frequency", cex.lab = 1.2, cex.main = 1.2)

hist(imp5_data$impress_manag_sdr, main = "Histogram of Impression Management", xlab = "Impression Management", ylab = "Frequency", cex.lab = 1.2, cex.main = 1.2)

hist(imp5_data$Age, main = "Histogram of Age", xlab = "Age", ylab = "Frequency", cex.lab = 1.2, cex.main = 1.2)

```




# Regression Analysis (DV = Consumer Intentions)

## Running Model
```{r include = FALSE}
mod_mice <- with(mids_obj, lm(consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center))
```

```{r include = FALSE}
pool_obj <- pool(mod_mice)
pool_obj
```


## Pooled Regression Results

Using `mice` package:
```{r echo = FALSE}
pool_summ <- summary(pool(mod_mice))
pool_summ %>%
  knitr::kable(digits = 3)
```

APA style table for regression summary
```{r}
apa_table(pool_summ,
          caption = "Table 1 Pooled Regression Results",
          note = "DV = Consumer Intentions")
```


## Standardized Regression Coefficients

Using scale()
```{r include = FALSE}
mod_mice_std <- with(mids_obj, lm(scale(consumer_intentions) ~ framing_condition*norm_condition*scale(biospheric) + framing_condition*norm_condition*scale(altruistic) + framing_condition*norm_condition*scale(egoistic) + framing_condition*norm_condition*scale(hedonic) + framing_condition*norm_condition*scale(ingroup_identification) + scale(self_deceptive_sdr) + scale(impress_manag_sdr) + scale(clothing_interest) + Gender + scale(Age)))
```


```{r}
pool_summ_std <- summary(pool(mod_mice_std))

pool_summ_std %>%
  knitr::kable(digits = 3)
```

APA style table for regression summary
```{r}
apa_table(pool_summ_std,
          caption = "Table 1b Pooled Standardized Regression Results",
          note = "DV = Consumer Intentions")
```



## Pooled Anova Results

Using mi.anova()

- Uses D2 test
```{r include = FALSE}
anova_mod3 <- mi.anova(mi.res = mids_obj, formula = "consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center", type = 3)
```

```{r}
anova_mod3 %>%
  knitr::kable(digits = c(2, 2, 2, 2, 3, 3, 3))
```


Using Anova()
```{r include = FALSE, echo = FALSE, warning = FALSE}
anova_mod2 <- with(mids_obj, Anova(lm(consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center), type = "III"))
```

doesn't have a pooling option
```{r}
# anova_mod2
```



# Simple Effects

Averaging scores across imputations
```{r}
complete_data_subset <- complete_data %>%
  dplyr::select(.imp, .id, consumer_intentions, consumer_behaviors, Gender, framing_condition, norm_condition, biospheric_center, altruistic_center, egoistic_center, hedonic_center, ingroup_center, Age_center, clothing_center, self_dec_center, impress_manag_center)

average_df <- complete_data_subset %>% 
  group_by(.id) %>%
  transmute(.imp = .imp, 
            consumer_behaviors = consumer_behaviors, 
            Gender = Gender,
            framing_condition = framing_condition,
            norm_condition = norm_condition,
            biospheric_center = mean(biospheric_center),
         altruistic_center = mean(altruistic_center),
         egoistic_center = mean(egoistic_center),
         hedonic_center = mean(hedonic_center),
         ingroup_center = mean(ingroup_center),
         Age_center = mean(Age_center),
         clothing_center = mean(clothing_center),
         self_dec_center = mean(self_dec_center),
         impress_manag_center = mean(impress_manag_center),
         consumer_intentions = mean(consumer_intentions))


average_df <- average_df %>%
  filter(.imp == 1)
```


Labels to use with facet_wrap
```{r}
norm_labs <- c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")
names(norm_labs) <- c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm")

frame_labs <- c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")
names(frame_labs) <- c("control_framing","pro_env_framing","self_enh_framing")
```


Text Settings
```{r}
text_settings <- theme(text = element_text(size = 20)) +
  theme(plot.title = element_text(size = 20, face = 'bold')) +
  theme(axis.title.x = element_text(face = 'bold')) +
  theme(axis.title.y = element_text(face = 'bold')) +
  theme(axis.text.x = element_text(size = 20)) +
  theme(axis.text.y = element_text(size = 20)) +
  theme(axis.ticks = element_blank())
```

## Estimated Marginal Means
```{r}
cell_emmeans <- emmeans(mod_mice, ~ norm_condition*framing_condition)
cell_emmeans %>%
  knitr::kable(digits = c(NA,NA,2,2,2,2,3))

frame_emmeans <- emmeans(mod_mice, ~ framing_condition)
frame_emmeans %>%
  knitr::kable(digits = 2)

norm_emmeans <- emmeans(mod_mice, ~ norm_condition)
norm_emmeans %>%
  knitr::kable(digits = 2)
```


## Framing Condition

>>H1: Consumer intentions/behaviors will be lower in the self-enhancing framing than in the pro-environmental or control framing conditions.

Comparing each level of framing condition
```{r}
frame_emmeans

# custom contrasts
SE_F_EMM <- c(0,0,1)
C_F_EMM <- c(1,0,0)
PE_F_EMM <- c(0,1,0)

framing_comparisons <- contrast(frame_emmeans, 
                          method = list("SE Frame - Control Frame" = SE_F_EMM - C_F_EMM,
                                        "SE Frame - PE Frame" = SE_F_EMM - PE_F_EMM), adjust = "tukey")
                          
framing_comparisons %>%
  knitr::kable(digits = c(NA,2,2,2,2,3))

# confidence intervals
framing_comparisons %>% confint() %>%
  knitr::kable(digits = 2)

# effect sizes
sigma_pool <- mean(pool_obj$glanced$sigma)
df_resid_pool <- mean(pool_obj$glanced$df.residual)

eff_size(framing_comparisons, sigma = sigma_pool, edf = df_resid_pool) %>% knitr::kable(digits = 2)
```

Exploratory multiple comparisons
```{r}
# All pairwise comparisons of framing conditions
frame_means2 <- emmeans(mod_mice, pairwise ~ framing_condition, adjust = "tukey")

framing_comparisons2 <- contrast(frame_means2)
framing_comparisons2 %>%
  knitr::kable(digits = c(NA,2,2,2,2,3))

# confidence intervals
framing_comparisons2 %>% confint() %>%
  knitr::kable(digits = 2)

# effect sizes
eff_size(framing_comparisons2, sigma = sigma_pool, edf = df_resid_pool) %>% knitr::kable(digits = 2)
```


```{r}
# without data overlaid
emmip(mod_mice, ~ framing_condition, CIs = TRUE, CIarg = list(lwd = 2, alpha = 0.5), xlab = "Framing Condition", ylab = "Consumer Intentions") + scale_x_discrete(breaks=c("control_framing","pro_env_framing","self_enh_framing"),
        labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +theme_apa() + text_settings
                                                                                                       
# with data overlaid (scores averaged across imputations)
emmip(mod_mice, ~ framing_condition, CIs = TRUE, CIarg = list(lwd = 1, alpha = 0.5), xlab = "Framing Condition", ylab = "Consumer Intentions") + geom_point(data = average_df, aes(x = framing_condition, y = consumer_intentions), alpha = 0.1, color = "blue") + scale_x_discrete(breaks=c("control_framing","pro_env_framing","self_enh_framing"),
        labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) + theme_apa() + text_settings
```





## Norm Condition

>>H2: Consumer intentions/behaviors will be lower in each norm condition compared to the control norm condition.

Comparing each level of norm condition
```{r}
norm_emmeans

# custom contrasts
Control_N_EMM <- c(1,0,0,0,0)
DN_EMM <- c(0,1,0,0,0)
Conv_EMM <- c(0,0,1,0,0)
SN_EMM <- c(0,0,0,1,0)
MN_EMM <- c(0,0,0,0,1)

norm_comparisons <- contrast(norm_emmeans, 
                          method = list("Descriptive Norm - Control" = DN_EMM - Control_N_EMM,
                                        "Convention - Control" = Conv_EMM - Control_N_EMM,
                                        "Social Norm - Control" = SN_EMM - Control_N_EMM,
                                        "Moral Norm - Control" = MN_EMM - Control_N_EMM), adjust = "tukey")

                          
norm_comparisons %>%
  knitr::kable(digits = c(NA,2,2,2,2,3))

# confidence intervals
norm_comparisons %>% confint() %>%
  knitr::kable(digits = 2)

# effect sizes
eff_size(norm_comparisons, sigma = sigma_pool, edf = df_resid_pool) %>% knitr::kable(digits = 2)
```

Exploratory multiple comparisons
```{r}
# All pairwise comparisons of framing conditions
norm_means2 <- emmeans(mod_mice, pairwise ~ norm_condition, adjust = "tukey")

norm_comparisons2 <- contrast(norm_means2)
norm_comparisons2 %>%
  knitr::kable(digits = c(NA,2,2,2,2,3))

# confidence intervals
norm_comparisons2 %>% confint() %>%
  knitr::kable(digits = 2)

# effect sizes
eff_size(norm_comparisons2, sigma = sigma_pool, edf = df_resid_pool) %>% knitr::kable(digits = 2)
```


```{r}
# without data overlaid
emmip(mod_mice, ~ norm_condition, CIs = TRUE, CIarg = list(lwd = 2, alpha = 0.5), xlab = "Norm Condition", ylab = "Consumer Intentions") + scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"),
        labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + theme_apa() + text_settings

# with data overlaid
emmip(mod_mice, ~ norm_condition, CIs = TRUE, xlab = "Norm Condition", ylab = "Consumer Intentions") + geom_point(data = average_df, aes(x = norm_condition, y = consumer_intentions), alpha = 0.1, color = "blue") + scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + theme_apa() + text_settings
```



## Framing X Norm

>>H3: There will be a two-way interaction between framing & norm condition such that the effect of each norm will be stronger in the self-enhancing framing than in the pro-environmental or control framing conditions.

Comparing differences in cell means
```{r}
cell_emmeans

# custom contrasts
cf_cn_emm <- c(1,rep(0,14)) ## control framings
cf_dn_emm <- c(0,1,rep(0,13))
cf_conv_emm <- c(0,0,1,rep(0,12))
cf_sn_emm <- c(0,0,0,1,rep(0,11))
cf_mn_emm <- c(0,0,0,0,1,rep(0,10))

pf_cn_emm <- c(0,0,0,0,0,1,rep(0,9)) ## pro-environmental framings
pf_dn_emm <- c(0,0,0,0,0,0,1,rep(0,8))
pf_conv_emm <- c(rep(0,7),1,(rep(0,7)))
pf_sn_emm <- c(rep(0,8),1,(rep(0,6)))
pf_mn_emm <- c(rep(0,9),1,(rep(0,5)))

sf_cn_emm <- c(rep(0,10),1,(rep(0,4))) ## self-enhancing framings
sf_dn_emm <- c(rep(0,11),1,(rep(0,3)))
sf_conv_emm <- c(rep(0,12),1,(rep(0,2)))
sf_sn_emm <- c(rep(0,13),1,0)
sf_mn_emm <- c(rep(0,14),1)

FxN_comparisons <- contrast(cell_emmeans, 
                          method = list("Control Frame + DN - Control Frame + Ctrl" = cf_dn_emm - cf_cn_emm,
                                        "Control Frame + Conv - Control Frame + Ctrl" = cf_conv_emm - cf_cn_emm,
                                        "Control Frame + SN - Control Frame + Ctrl" = cf_sn_emm - cf_cn_emm,
                                        "Control Frame + MN - Control Frame + Ctrl" = cf_mn_emm - cf_cn_emm,
                                        "PE Frame + DN - PE Frame + Ctrl" = pf_dn_emm - pf_cn_emm,
                                        "PE Frame + Conv - PE Frame + Ctrl" = pf_conv_emm - pf_cn_emm,
                                        "PE Frame + SN - PE Frame + Ctrl" = pf_sn_emm - pf_cn_emm,
                                        "PE Frame + MN - PE Frame + Ctrl" = pf_mn_emm - pf_cn_emm,
                                        "SE Frame + DN - SE Frame + Ctrl" = sf_dn_emm - sf_cn_emm,
                                        "SE Frame + Conv - SE Frame + Ctrl" = sf_conv_emm - sf_cn_emm,
                                        "SE Frame + SN - SE Frame + Ctrl" = sf_sn_emm - sf_cn_emm,
                                        "SE Frame + MN - SE Frame + Ctrl" = sf_mn_emm - sf_cn_emm), adjust = "sidak")

FxN_comparisons %>%
  knitr::kable(digits = c(NA,2,2,2,2,3))

# confidence intervals
FxN_comparisons %>% confint() %>%
  knitr::kable(digits = 2)
```

Pairwise comparisons
```{r}
FxN_pairwise <- contrast(FxN_comparisons, "pairwise")

FxN_pairwise %>% knitr::kable(digits = c(NA,2,2,2,2,3))

# effect sizes
eff_size(FxN_comparisons, sigma = sigma_pool, edf = df_resid_pool) %>% knitr::kable(digits = 2)
```



Exploratory multiple comparisons
```{r}
# All pairwise comparisons of norm conditions across framing conditions
norm_means2 <- emmeans(mod_mice, pairwise ~ norm_condition | framing_condition, adjust = "tukey")

norm_means2$emmeans %>% knitr::kable(digits = 2)

norm_comparisons2 <- norm_means2$contrasts
norm_comparisons2 %>%
  knitr::kable(digits = c(NA,NA,2,2,2,2,3))

# confidence intervals
norm_comparisons2 %>% confint() %>%
  knitr::kable(digits = 2)

# effect sizes
eff_size(norm_comparisons2, sigma = sigma_pool, edf = df_resid_pool) %>% knitr::kable(digits = 2)
```

Pairwise comparisons
```{r}
norm2_pairwise <- contrast(norm_comparisons2, "pairwise")

norm2_pairwise %>% knitr::kable(digits = c(NA,NA,2,2,2,2,3))

# effect sizes
eff_size(norm2_pairwise, sigma = sigma_pool, edf = df_resid_pool) %>% knitr::kable(digits = 2)
```


```{r}
# without data overlaid
emmip(mod_mice, framing_condition ~ norm_condition, CIs = TRUE, CIarg = list(lwd = 2, alpha = 0.5), xlab = "Norm Condition", ylab = "Consumer Intentions") + scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"),
        labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) + theme_apa() + text_settings

# with data overlaid
emmip(mod_mice, ~ norm_condition | framing_condition, CIs = TRUE, CIarg = list(lwd = 1, alpha = 0.5), xlab = "Norm Condition", ylab = "Consumer Intentions") + geom_point(data = average_df, aes(x = norm_condition, y = consumer_intentions, color = norm_condition), alpha = 0.2, show.legend = FALSE) + scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"),
        labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) + theme_apa() + text_settings
```




## All control/framing conditions compared to control/control condition

>> Exploratory RQ2: Which combination of framing and norm condition produced the strongest reductions in consumer intentions compared to the control condition?

```{r}
#chosen_values <- list(norm_condition = c("control_norm", "descriptive_norm"), framing_condition = c("control_framing", "pro_env_framing", "self_enh_framing"))

cell_int_means <- emmeans(mod_mice, pairwise ~ norm_condition*framing_condition, adjust = "tukey")

cell_int_means$emmeans %>%
  knitr::kable(digits = 2)

cell_int_means$contrasts %>%
  knitr::kable(digits = c(NA,2,2,2,2,3))

# confidence intervals
cell_int_means %>% confint() %>%
  knitr::kable(digits = 2)

# effect sizes
eff_size(cell_int_means, sigma = sigma_pool, edf = df_resid_pool) %>% knitr::kable(digits = 2)
```


```{r}
emmip(mod_mice, framing_condition ~ norm_condition, CIs = FALSE, xlab = "Norm Condition", ylab = "Consumer Intentions")
```






# Exploratory Analyses

## Effect of framings across norm conditions 

Comparing consumer intentions for each norm condition between each framing condition:
```{r}
# Control norm
chosen_values <- list(norm_condition = c("control_norm"), framing_condition = c("control_framing", "pro_env_framing", "self_enh_framing"))

control_norm_means <- emmeans(mod_mice, pairwise ~ norm_condition*framing_condition, at = chosen_values, adjust = "tukey")

control_norm_means$emmeans %>% 
  knitr::kable(digits = 2)

control_norm_means$contrasts %>%
  knitr::kable(digits = c(NA,2,2,2,2,3))

eff_size(control_norm_means, sigma = sigma_pool, edf = df_resid_pool) %>%
  knitr::kable(digits = 2)
```



```{r}
# Descriptive norm
chosen_values <- list(norm_condition = c("descriptive_norm"), framing_condition = c("control_framing", "pro_env_framing", "self_enh_framing"))

descr_norm_means <- emmeans(mod_mice, pairwise ~ norm_condition*framing_condition, at = chosen_values, adjust = "tukey")

descr_norm_means$emmeans %>%
  knitr::kable(digits = 2)

descr_norm_means$contrasts %>%
  knitr::kable(digits = c(NA,2,2,2,2,3))

eff_size(descr_norm_means, sigma = sigma_pool, edf = df_resid_pool) %>%
  knitr::kable(digits = 2)
```



```{r}
# Convention norm
chosen_values <- list(norm_condition = c("convention_norm"), framing_condition = c("control_framing", "pro_env_framing", "self_enh_framing"))

conv_norm_means <- emmeans(mod_mice, pairwise ~ norm_condition*framing_condition, at = chosen_values, adjust = "tukey")

conv_norm_means$emmeans %>%
  knitr::kable(digits = 2)

conv_norm_means$contrasts %>%
  knitr::kable(digits = c(NA,2,2,2,2,3))

eff_size(conv_norm_means, sigma = sigma_pool, edf = df_resid_pool) %>%
  knitr::kable(digits = 2)
```



```{r}
# Social norm
chosen_values <- list(norm_condition = c("social_norm"), framing_condition = c("control_framing", "pro_env_framing", "self_enh_framing"))

soc_norm_means <- emmeans(mod_mice, pairwise ~ norm_condition*framing_condition, at = chosen_values, adjust = "tukey")

soc_norm_means$emmeans %>%
  knitr::kable(digits = 2)

soc_norm_means$contrasts %>%
  knitr::kable(digits = c(NA,2,2,2,2,3))

eff_size(soc_norm_means, sigma = sigma_pool, edf = df_resid_pool) %>%
  knitr::kable(digits = 2)
```



```{r}
# Moral norm
chosen_values <- list(norm_condition = c("moral_norm"), framing_condition = c("control_framing", "pro_env_framing", "self_enh_framing"))

moral_norm_means <- emmeans(mod_mice, pairwise ~ norm_condition*framing_condition, at = chosen_values, adjust = "tukey")

moral_norm_means$emmeans %>%
  knitr::kable(digits = 2)

moral_norm_means$contrasts %>%
  knitr::kable(digits = c(NA,2,2,2,2,3))

eff_size(moral_norm_means, sigma = sigma_pool, edf = df_resid_pool) %>%
  knitr::kable(digits = 2)
```



## Gender Interactions 

Gender X Norm
```{r}
emmeans(mod_mice, ~ norm_condition*Gender*framing_condition, adjust = "tukey")

emmip(mod_mice, norm_condition ~ Gender, at = at_list, CIs = TRUE, CIarg = list(lwd = 1, alpha = 0.8), xlab = "Gender", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) +theme_apa() + text_settings
```

Gender X Framing
```{r}
emmip(mod_mice, framing_condition ~ Gender, at = at_list, CIs = TRUE, CIarg = list(lwd = 1, alpha = 0.8), xlab = "Gender", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +theme_apa() + text_settings
```

Gender X Norm X Framing
```{r}
emmip(mod_mice, norm_condition ~ Gender | framing_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 1, alpha = 0.8), xlab = "Gender", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +theme_apa() + text_settings
```



# Post-hoc Power Analysis 

- Using final sample size (n = 1133) and a small effect size

from Cohen (1988):

f2 = R^2/(1 - R^2)
R2 = f^2/(1 + f^2)

Small: f2 = .02, Small: R2 = .02


Model A (full model): PA = 95
Denominator df: n-PA = 1133-95 = 1038

Effects where numerator df: PA-PC = 4

  * Main effect of norm
  * Values X norm interactions
  * Ingroup x norm interactions
```{r}
# If effect size were small and df_resid = 1038
pwr.f2.test(u = 4, # Numerator df (PA-PC) 
            v = 1038, # Denominator df (n - PA)
            f2 = .02, 
            sig.level = .05,
            power = NULL) # power = .97
```


Effects where numerator df: PA-PC = 2

  * Main effect of framing
  * Values X framing interactions
  * Ingroup x framing interactions
```{r}
# If effect size were small and df_resid = 1038
pwr.f2.test(u = 2, # Numerator df (PA-PC) 
            v = 1038, # Denominator df (n - PA)
            f2 = .02, 
            sig.level = .05,
            power = NULL) # power = .99
```


Effects where numerator df: PA-PC = 8

  * Norm x Framing interaction
  * Values X framing x norm interactions
  * Ingroup x framing x norm interactions
```{r}
# If effect size were small and df_resid = 1038
pwr.f2.test(u = 8, # Numerator df (PA-PC) 
            v = 1038, # Denominator df (n - PA)
            f2 = .02, 
            sig.level = .05,
            power = NULL) # power = .93
```


Effects where numerator df: PA-PC = 1

  * Biospheric values
  * Altruistic values
  * Egoistic values
  * Hedonic values
  * Ingroup identification
  * Self-deceptive enhancement
  * Impression management
  * Clothing interest
  * Age
  * Gender

```{r}
# If effect size were small and df_resid = 1038
pwr.f2.test(u = 1, # Numerator df (PA-PC) 
            v = 1038, # Denominator df (n - PA)
            f2 = .02, 
            sig.level = .05,
            power = NULL) # power = .995
```


Checking p-values from Pooled ANOVA table
```{r}
# p-value for biospheric values
pf(60.76, df1 = 1, df2 = 182541.21, lower.tail = FALSE)

# p-value for framing condition
pf(1.94, df1 = 2, df2 = 277911.15, lower.tail = FALSE)
```

Q: Which of the pooled ANOVA effects would be significant if the non-adjusted denominator df, 1038, were used?

df1 = 1:

* F-critical value when df1 = 1 & df2 = 1038: Fcv = 3.8504

* F-critical value when df1 = 1 & df2 = 9999: Fcv = 3.8424



df1 = 2:

* F-critical value when df1 = 2 & df2 = 1038: Fcv = 3.0044

* F-critical value when df1 = 2 & df2 = 9999: Fcv = 2.9966



df1 = 4:

* F-critical value when df1 = 4 & df2 = 1038: Fcv = 2.3805

* F-critical value when df1 = 4 & df2 = 9999: Fcv = 2.3728



df1 = 8:

* F-critical value when df1 = 8 & df2 = 1038: Fcv = 1.9473

* F-critical value when df1 = 8 & df2 = 9999: Fcv = 1.9393

