---
title: "exploratory_personality_with_MI"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
date: "2023-03-29"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r clear environment, echo = FALSE}
rm(list = ls())
```


```{r libraries, message = FALSE, warning = FALSE}
library(Rmisc)
library(Hmisc)
library(rio)
library(tidyverse)
library(psych)
library(gtools) # rbinding data frames
library(corrplot)
library(jtools) # for pretty printing tables
library(sjPlot) # pretty printing tables
library(sjmisc) # pretty printing
library(mice) # handling missing values
library(naniar) # visualizaing missingness & MCAR test
library(miceadds) # for mi.anova
library(emmeans) # simple effects analyses
library(broom)     # for extracting residuals and outlier indices
library(olsrr)     # for creating outlier plots
library(smcfcs) # for multiple imputation with interactions
library(mitools) # for pooling MI results
library(marginaleffects) # for plotting marginal means 
library(installr)

options(max.print = 100000) # max rows to print in output
options(scipen = 1000) # turn off sci notation
```

# Data Import & Cleaning

## Import data
```{r import data}
raw_psych_hum_subj <- import("data/raw/raw_psych_hum_subj.csv")
raw_mktg_hum_subj <- import("data/raw/raw_mktg_hum_subj.csv")
raw_gen_uo_pop <- import("data/raw/raw_gen_uo_pop.csv")
pre_fall22 <- import("data/prescreen/dittersdorf_matches_f22.csv")
pre_winter23 <- import("data/prescreen/dittersdorf_matches_w23.csv")
pre_spring23 <- import("data/prescreen/dittersdorf_matches_s23.csv")
participant_list <- import("data/prescreen/dittersdorf_participants.csv")
```


Inspect data
```{r inspect raw data, results = 'hide'}
# Main Data
str(raw_psych_hum_subj, list.len = ncol(raw_psych_hum_subj))
str(raw_mktg_hum_subj, list.len = ncol(raw_mktg_hum_subj))
str(raw_gen_uo_pop, list.len = ncol(raw_gen_uo_pop))
```


## Change variables types 
```{r update var types, warning = FALSE}
raw_psych_hum_subj <- raw_psych_hum_subj %>%
  mutate(Age = as.integer(Age),
         Gender = as.factor(Gender),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors),
         skepticism = as.factor(skepticism),
         id = as.factor(id))

raw_mktg_hum_subj <- raw_mktg_hum_subj %>%
  mutate(Age = as.integer(Age),
         Gender = as.factor(Gender),
         Gender_5_TEXT = as.character(Gender_5_TEXT),
         Class_Lvl_7_TEXT = as.character(Class_Lvl_7_TEXT),
         Pol_Ornt_8_TEXT = as.character(Pol_Ornt_8_TEXT),
         Ethnicity_8_TEXT = as.character(Ethnicity_8_TEXT),
         skept_open = as.character(skept_open),
         skepticism = as.factor(skepticism),
         id = as.factor(id),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors))

raw_gen_uo_pop <- raw_gen_uo_pop %>%
  mutate(Gender = as.factor(Gender),
         Gender_5_TEXT = as.character(Gender_5_TEXT),
         Class_Lvl_7_TEXT = as.character(Class_Lvl_7_TEXT),
         Pol_Ornt_8_TEXT = as.character(Pol_Ornt_8_TEXT),
         skept_open = as.character(skept_open),
         skepticism = as.factor(skepticism),
         id = as.factor(id),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors))
```


Inspect prescreen data
```{r inspect prescreen, results = 'hide'}
# Prescreen Data
str(pre_fall22, list.len = ncol(pre_fall22))
str(pre_winter23, list.len = ncol(pre_winter23))
str(pre_spring23, list.len = ncol(pre_spring23))
str(participant_list, list.len = ncol(participant_list))
```

Variables from prescreen:

* Values:
  + respecting, unity, protecting, preventing, equality, peace, justice, helpful, power, wealth, authority, influential, ambition, pleasures, enjoying, gratification

* Socially Desirable Responding:
  + honest, like, disturbing, regret, lose-out, rational, confident, lover, lies, cover-up, advantage, get-even, behind-back, private-talk, take-things, gossip

## Combine prescreen data

Specify unique variables to combine prescreen data sets
```{r prep prescreen dfs}
# Create unique full_name variable
pre_fall22$full_name <- paste(pre_fall22$first_name, pre_fall22$last_name, sep="_")

pre_winter23$full_name <- paste(pre_winter23$first_name, pre_winter23$last_name, sep="_")

pre_spring23$full_name <- paste(pre_spring23$first_name, pre_spring23$last_name, sep="_")

participant_list$full_name <- paste(participant_list$first_name, participant_list$last_name, sep="_")

# Create column indicating which data set rows came from

pre_fall22 <- pre_fall22 %>%
  mutate(term = "fall22")

pre_winter23 <- pre_winter23 %>%
  mutate(term = "winter23")

pre_spring23 <- pre_spring23 %>%
  mutate(term = "spring23")
```

Combine prescreen data
```{r combine prescreen dfs}
combine1 <- smartbind(pre_fall22, pre_winter23)
combined_prescreen <- smartbind(combine1, pre_spring23)

nrow(pre_fall22) + nrow(pre_winter23) + nrow(pre_spring23) # n = 1167

combined_prescreen_unique <- combined_prescreen[!duplicated(combined_prescreen$full_name), ] # keeps first row (fall22)
```

Subset key variables
```{r subset key vars}
combined_prescreen_key <- combined_prescreen_unique %>%
  select(full_name, term, respecting:gratification, honest:gossip)

participant_list_key <- participant_list %>%
  select(full_name, survey_id)
```

Merge with participant list
```{r merge participant list}
merged_prescreen <- merge(combined_prescreen_key, participant_list_key, by = "full_name")
```

Convert variable types in prescreen data
```{r inspect merged prescreen, results = 'hide'}
str(merged_prescreen, list.len = ncol(merged_prescreen))
```

```{r clean merged prescreen, warning = FALSE}
merged_prescreen <- merged_prescreen %>%
  rename("lose_out" = "lose-out", 
         "cover_up" = "cover-up",
         "get_even" = "get-even",
         "behind_back" = "behind-back",
         "private_talk" = "private-talk",
         "take_things" = "take-things",
         "id" = "survey_id")

merged_prescreen <- merged_prescreen %>%
  mutate(respecting = as.integer(respecting),
         unity = as.integer(unity),
         protecting = as.integer(protecting),
         preventing = as.integer(preventing),
         equality = as.integer(equality),
         peace = as.integer(peace),
         justice = as.integer(justice),
         helpful = as.integer(helpful),
         power = as.integer(power),
         wealth = as.integer(wealth),
         authority = as.integer(authority),
         influential = as.integer(influential),
         ambition = as.integer(ambition),
         pleasures = as.integer(pleasures),
         enjoying = as.integer(enjoying),
         gratification = as.integer(gratification),
         honest = as.integer(honest),
         like = as.integer(like),
         disturbing = as.integer(disturbing),
         regret = as.integer(regret),
         lose_out = as.integer(lose_out),
         rational = as.integer(rational),
         confident = as.integer(confident),
         lover = as.integer(lover),
         lies = as.integer(lies),
         cover_up = as.integer(cover_up),
         advantage = as.integer(advantage),
         get_even = as.integer(get_even),
         behind_back = as.integer(behind_back),
         private_talk = as.integer(private_talk),
         take_things = as.integer(take_things),
         gossip = as.integer(gossip),
         id = as.factor(id))
```


Rename values & socially desirable items in prescreen data to match names in main data:
```{r rename prescreen vars}
merged_prescreen <- merged_prescreen %>%
  rename("values_1" = "respecting",
         "values_2" = "unity",
         "values_3" = "protecting",
         "values_4" = "preventing",
         "values_5" = "equality",
         "values_6" = "peace",
         "values_7" = "justice",
         "values_8" = "helpful",
         "values_9" = "power",
         "values_10" = "wealth",
         "values_11" = "authority",
         "values_12" = "influential",
         "values_13" = "ambition",
         "values_14" = "pleasures",
         "values_15" = "enjoying",
         "values_16" = "gratification",
         "socially_desirable_1" = "honest",
         "socially_desirable_2" = "like",
         "socially_desirable_3" = "disturbing",
         "socially_desirable_4" = "regret",
         "socially_desirable_5" = "lose_out",
         "socially_desirable_6" = "rational",
         "socially_desirable_7" = "confident",
         "socially_desirable_8" = "lover",
         "socially_desirable_9" = "lies",
         "socially_desirable_10" = "cover_up",
         "socially_desirable_11" = "advantage",
         "socially_desirable_12" = "get_even",
         "socially_desirable_13" = "behind_back",
         "socially_desirable_14" = "private_talk",
         "socially_desirable_15" = "take_things",
         "socially_desirable_16" = "gossip")
```


## Combine all data

- First, combine Psych Hum Subj data with Prescreen data based on `id`
- Second, add Mktg Hum Subj data
- Third, add gen UO Pop data
```{r combine all data}
combine1 <- merge(raw_psych_hum_subj, merged_prescreen, by = "id")
combine2 <- smartbind(combine1, raw_mktg_hum_subj)
combine3 <- smartbind(combine2, raw_gen_uo_pop)
```

## Remove duplicate cases

Identify duplicate cases
```{r id duplicate cases, results = 'hide'}
# first, add unique row #s
combine3 <- combine3 %>%
  mutate(row = 1:nrow(combine3))

combine3[duplicated(combine3$id),] # Only rows 1 through 858 have unique id #s

# write.csv(combine3, "combined_data.csv")
```

Row IDs to remove:

* 13 (participant's second time completing study)
* 134 (participant didn't complete study first time)
* 145 (participant didn't complete study first time)
* 308 (participant's second time completing study)
* 672 (participant's second time completing study)
* 743 (participant didn't complete study first time)
* 790 (participant didn't complete study first time)
* 800 (participant didn't complete study first time)

Remove duplicate rows after resolving:
```{r remove duplicate cases}
combine3 <- combine3 %>%
  filter(!row %in% c(13, 134, 145, 308, 672, 743, 790, 800))
```

Check variables types again
```{r inspect var types again, results = 'hide'}
str(combine3, list.len = ncol(combine3))
```

## Remove all NA cases

Identify completely missing rows:
```{r id all NA rows, results = 'hide'}
key_vars <- combine3 %>%
  select(row, big_2_1:big_2_65, consumer_intentions_1:consumer_intentions_9, consumer_behaviors, clothing_interest_1:clothing_interest_20, ingroup_ident_1:ingroup_ident_14, values_1:values_16, socially_desirable_1:socially_desirable_16)

ncol(key_vars) # number of columns - the row # column = 141

all_NA_rows <- key_vars[rowSums(is.na(key_vars)) == 141,] # identify rows with 142 NAs (all missing values), row numbers are preserved

all_NA_rows
```

Removing rows of fully missing data:
```{r remove all NA rows}
data <- combine3 %>%
  filter(!row %in% c(859, 860, 900, 926, 927, 941, 1139, 1141, 1142, 1143, 1144, 1146, 1149, 1150, 1152)) %>% # remove rows containing all NAs
  select(-StartDate, -EndDate, -Status, -Progress, -"Duration (in seconds)", -Finished, -RecordedDate, -ResponseId, -DistributionChannel, -UserLanguage, -big_2_DO, -consumer_intentions_DO, -consumer_behaviors_DO, -clothing_interest_DO, -ingroup_ident_DO, -full_name, -code, -socially_desirable_DO, -values_DO, -email_giftcard, -term) # removing variables not in analysis
```


Rename variables:
```{r rename vars}
data <- data %>%
  rename("framing_condition" = "framing_condition_DO", 
         "norm_condition" = "norm_condition_DO")

levels(data$framing_condition)
levels(data$norm_condition)

data$framing_condition <- droplevels(data$framing_condition)
data$norm_condition <- droplevels(data$norm_condition)

levels(data$framing_condition)
levels(data$norm_condition)

levels(data$skepticism)
```

## Inspect final data 
```{r inspect final df, results = 'hide'}
str(data, list.len = ncol(data))

# write.csv(data, "final_data.csv")
```


## Demographics

Age
```{r age outliers}
# Age
data %>%
  select(Age) %>%
  hist()

describe(data$Age) # 1999 a data entry error

data %>%
  filter(Age == 1999) # Row 1053, Year 1999 = 24 years old

data$Age[data$Age == 1999] <- 24

data %>%
  filter(row == 1053) %>%
  select(Age) # Age has been replaced with 24
```


Gender

- 1 = woman
- 2 = man
- 3 = non-binary
- 4 = I prefer not to identify
- 5 = other (please specify)
```{r label gender levels}
levels(data$Gender) <- c("Woman", "Man", "Non-binary", "I prefer not to identify", "Other")
```


# Aggregate Variables 

## Personality

### Reverse-code

```{r reverse personality items}
data_R <- data %>%
  mutate(across(c(big_2_11,
                  big_2_16,
                  big_2_26,
                  big_2_31,
                  big_2_36,
                  big_2_51,
                  big_2_12,
                  big_2_17,
                  big_2_22,
                  big_2_37,
                  big_2_42,
                  big_2_47,
                  big_2_3,
                  big_2_8,
                  big_2_23,
                  big_2_28,
                  big_2_48,
                  big_2_58,
                  big_2_4,
                  big_2_9,
                  big_2_24,
                  big_2_29,
                  big_2_44,
                  big_2_49,
                  big_2_5,
                  big_2_25,
                  big_2_30,
                  big_2_45,
                  big_2_50,
                  big_2_55,
                  big_2_63), ~6 - .)) # replace '6' with the max possible value plus 1 for any particular scale
```

### Average items

```{r aggregate personality}
data_R$extraversion <- data_R %>%
  select(big_2_1, big_2_6, big_2_11, big_2_16, big_2_21, big_2_26, big_2_31, big_2_36, big_2_41, big_2_46, big_2_51, big_2_56) %>%
  rowMeans(na.rm = TRUE) 


data_R$conscientiousness <- data_R %>%
  select(big_2_3, big_2_8, big_2_13, big_2_18, big_2_23, big_2_28, big_2_33, big_2_38, big_2_43, big_2_48, big_2_53, big_2_58) %>%
  rowMeans(na.rm = TRUE)


data_R$agreeableness <- data_R %>%
  select(big_2_2, big_2_7, big_2_12, big_2_17, big_2_22, big_2_27, big_2_32, big_2_37, big_2_42, big_2_47, big_2_52, big_2_57) %>%
  rowMeans(na.rm = TRUE)


data_R$neuroticism <- data_R %>%
  select(big_2_4, big_2_9, big_2_14, big_2_19, big_2_24, big_2_29, big_2_34, big_2_39, big_2_44, big_2_49, big_2_54, big_2_59) %>%
  rowMeans(na.rm = TRUE)


data_R$openness <- data_R %>%
  select(big_2_5, big_2_10, big_2_15, big_2_20, big_2_25, big_2_30, big_2_35, big_2_40, big_2_45, big_2_50, big_2_55, big_2_60) %>%
  rowMeans(na.rm = TRUE)


data_R$honesty <- data_R %>%
  select(big_2_61, big_2_62, big_2_63, big_2_64, big_2_65) %>%
  rowMeans(na.rm = TRUE)
```




## Clothing Interest

### Reverse-code

```{r reverse clothing items}
data_R <- data_R %>%
  mutate(across(c(clothing_interest_3,
                  clothing_interest_5,
                  clothing_interest_7,
                  clothing_interest_9,
                  clothing_interest_12,
                  clothing_interest_14,
                  clothing_interest_15,
                  clothing_interest_16,
                  clothing_interest_18,
                  clothing_interest_20), ~6 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```


### Average items
```{r aggregate clothing interest}
data_R$clothing_interest <- data_R %>%
  select(clothing_interest_1:clothing_interest_20) %>%
  rowMeans(na.rm = TRUE)
```




## In-group Identification

### Reverse-code

No items need to be reverse-coded.

### Average items
```{r aggegate ingroup ident}
data_R$ingroup_identification <- data_R %>%
  select(ingroup_ident_1:ingroup_ident_14) %>%
  rowMeans(na.rm = TRUE)
```




## Values

### Reverse-code

No items need to be reverse-coded.

### Recoding scale options

Recoding values:

* -3 = 1
* -2 = 2
* -1 = 3
* 0 = 4
* +1 = 5
* +2 = 6
* +3 = 7

```{r recode values}
table(data_R$values_1)

data_R$values_1_rec <- recode(data_R$values_1, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)

table(data_R$values_1_rec)

data_R$values_2_rec <- recode(data_R$values_2, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_3_rec <- recode(data_R$values_3, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_4_rec <- recode(data_R$values_4, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_5_rec <- recode(data_R$values_5, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_6_rec <- recode(data_R$values_6, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_7_rec <- recode(data_R$values_7, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_8_rec <- recode(data_R$values_8, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_9_rec <- recode(data_R$values_9, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_10_rec <- recode(data_R$values_10, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_11_rec <- recode(data_R$values_11, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_12_rec <- recode(data_R$values_12, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_13_rec <- recode(data_R$values_13, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_14_rec <- recode(data_R$values_14, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_15_rec <- recode(data_R$values_15, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_16_rec <- recode(data_R$values_16, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)

table(data_R$values_16)
table(data_R$values_16_rec)
```


### Average items
```{r aggregate values}
data_R$biospheric <- data_R %>%
  select(values_1_rec:values_4_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$altruistic <- data_R %>%
  select(values_5_rec:values_8_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$egoistic <- data_R %>%
  select(values_9_rec:values_13_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$hedonic <- data_R %>%
  select(values_14_rec:values_16_rec) %>%
  rowMeans(na.rm = TRUE)
```




## Socially Desirable Responding

### Reverse-code
```{r reverse code socially desirable items}
data_R <- data_R %>%
  mutate(across(c(socially_desirable_1,
                  socially_desirable_3,
                  socially_desirable_5,
                  socially_desirable_8,
                  socially_desirable_9,
                  socially_desirable_11,
                  socially_desirable_12,
                  socially_desirable_13), ~8 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```

### Average items
```{r aggregate socially desirable}
data_R$socially_desirable <- data_R %>%
  select(socially_desirable_1:socially_desirable_16) %>%
  rowMeans(na.rm = TRUE)
```



## Consumer Intentions

### Reverse-code

Higher scores mean better consumer intentions (intentions to *reduce* future consumption):
```{r reverse code consumer intentions}
data_R <- data_R %>%
  mutate(across(c(consumer_intentions_2,
                  consumer_intentions_4,
                  consumer_intentions_7,
                  consumer_intentions_9), ~8 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```

### Average items

```{r aggregate consumer intentions}
data_R$consumer_intentions <- data_R %>%
  select(consumer_intentions_1:consumer_intentions_9) %>%
  rowMeans(na.rm = TRUE)
```



### Reorder levels

Reorder the levels of norm condition:
```{r reorder norm condition levels}
data_R %>%
  group_by(norm_condition) %>%
  summarize(M = mean(consumer_intentions, na.rm = TRUE))

data_R$norm_condition <- factor(data_R$norm_condition, levels = c("control_norm", "descriptive_norm", "convention_norm", "social_norm", "moral_norm"))
```



# Regression Analysis for Consumer Intentions

## Center Covariates

- Socially desirable responding
- Clothing interest
- Values
- Ingroup identification
- Age
- Gender
- Income (not sure how to handle inconsistencies in this variable was responded to)

```{r center covariates, echo = FALSE}
data_R$socially_desirable_center <- data_R$socially_desirable - mean(data_R$socially_desirable, na.rm = TRUE)

data_R$clothing_interest_center <- data_R$clothing_interest - mean(data_R$clothing_interest, na.rm = TRUE)

data_R$Age_center <- data_R$Age - mean(data_R$Age, na.rm = TRUE)

data_R$ingroup_identification_center <- data_R$ingroup_identification - mean(data_R$ingroup_identification, na.rm = TRUE)

data_R$biospheric_center <- data_R$biospheric - mean(data_R$biospheric, na.rm = TRUE)

data_R$altruistic_center <- data_R$altruistic - mean(data_R$altruistic, na.rm = TRUE)

data_R$egoistic_center <- data_R$egoistic - mean(data_R$egoistic, na.rm = TRUE)

data_R$hedonic_center <- data_R$hedonic - mean(data_R$hedonic, na.rm = TRUE)

data_R$extraversion_center <- data_R$extraversion - mean(data_R$extraversion, na.rm = TRUE)
  
data_R$conscientiousness_center <- data_R$conscientiousness - mean(data_R$conscientiousness, na.rm = TRUE)

data_R$agreeableness_center <- data_R$agreeableness - mean(data_R$agreeableness, na.rm = TRUE)

data_R$neuroticism_center <- data_R$neuroticism - mean(data_R$neuroticism, na.rm = TRUE)

data_R$openness_center <- data_R$openness - mean(data_R$openness, na.rm = TRUE)

data_R$honesty_center <- data_R$honesty - mean(data_R$honesty, na.rm = TRUE)

```


```{r reduce levels of gender, echo = FALSE}
data_R$Gender[data_R$Gender == "Non-binary"] <- NA
data_R$Gender[data_R$Gender == "I prefer not to identify"] <- NA
data_R$Gender[data_R$Gender == "Other"] <- NA

data_R$Gender <- droplevels(data_R$Gender)
```



## Multiple Imputation using `smcfcs` - alt Coding Approach

## Contrast Coding 

Data to practice alt approach on:
```{r echo = FALSE}
data_R_alt <- data_R %>%
  select(hedonic_center, egoistic_center, altruistic_center, biospheric_center, ingroup_identification_center, Age_center, clothing_interest_center, socially_desirable_center, consumer_intentions, consumer_behaviors, Gender, framing_condition, norm_condition, extraversion_center, conscientiousness_center, agreeableness_center, neuroticism_center, openness_center, honesty_center)
```


Contrast Coding using ifelse() approach:
```{r alt coding}
# Gender
#data_R_alt$GenderCode <- ifelse(data_R$Gender == "Woman", 1, 0)

# Framing X Norm
#data_R_alt$framingXnorm <- interaction(data_R_alt$framing_condition, data_R_alt$norm_condition)


# Framing
data_R_alt$FramingCode1 <- ifelse(data_R_alt$framing_condition == "control_framing", -1/2, ifelse(data_R_alt$framing_condition == "self_enh_framing", 1/2, 0))

data_R_alt$FramingCode2 <- ifelse(data_R_alt$framing_condition == "pro_env_framing", 2/3, -1/3)

# Norm
contr.helmert(5)

data_R_alt$NormCode1 <- ifelse(data_R_alt$norm_condition == "moral_norm", 4, -1)

data_R_alt$NormCode2 <- ifelse(data_R_alt$norm_condition == "social_norm", 3, ifelse(data_R_alt$norm_condition == "moral_norm", 0, -1))

data_R_alt$NormCode3 <- ifelse(data_R_alt$norm_condition == "convention_norm", 2, ifelse(data_R_alt$norm_condition == "moral_norm", 0, ifelse(data_R_alt$norm_condition == "social_norm", 0, -1)))
data_R_alt$NormCode4 <- ifelse(data_R_alt$norm_condition == "descriptive_norm", 1, ifelse(data_R_alt$norm_condition == "control_norm", -1, 0))


## Adding contrast codes to Framing & Norm Condition
# Framing
FrameCode1 <- c(-1/2, 0, 1/2) # control vs self-enhancing
FrameCode2 <- c(-1/3, 2/3, -1/3) # arbitrary code

contrasts(data_R_alt$framing_condition) <- cbind(FrameCode1, FrameCode2)
contrasts(data_R_alt$framing_condition)

# Norm
contrasts(data_R_alt$norm_condition) <- contr.helmert(5)
contrasts(data_R_alt$norm_condition) # control vs DN

# Gender
contrasts(data_R_alt$Gender) <- c(1, 0)
```


Examine missingness:
```{r}
data_R_alt %>%
  vis_miss()

sum(is.na(data_R_alt$extraversion_center))
sum(is.na(data_R_alt$agreeableness_center))
sum(is.na(data_R_alt$openness_center))
sum(is.na(data_R_alt$conscientiousness_center))
sum(is.na(data_R_alt$neuroticism_center))
sum(is.na(data_R_alt$honesty_center))

```

Variables with NO missing data:

* ingroup_identification_center
* clothing_interest_center
* consumer_intentions
* framing_condition
* norm_condition


Adding interaction terms:
```{r echo = FALSE}
data_R_alt <- data_R_alt %>%
  mutate(framing1Xbiospheric = (FramingCode1)*(biospheric_center),
         framing2Xbiospheric = (FramingCode2)*(biospheric_center),
         norm1Xbiospheric = (NormCode1)*(biospheric_center),
         norm2Xbiospheric = (NormCode2)*(biospheric_center),
         norm3Xbiospheric = (NormCode3)*(biospheric_center),
         norm4Xbiospheric = (NormCode4)*(biospheric_center),
         framing1Xnorm1Xbiospheric = (FramingCode1)*(NormCode1)*(biospheric_center),
         framing1Xnorm2Xbiospheric = (FramingCode1)*(NormCode2)*(biospheric_center),
         framing1Xnorm3Xbiospheric = (FramingCode1)*(NormCode3)*(biospheric_center),
         framing1Xnorm4Xbiospheric = (FramingCode1)*(NormCode4)*(biospheric_center),
         framing2Xnorm1Xbiospheric = (FramingCode2)*(NormCode1)*(biospheric_center),
         framing2Xnorm2Xbiospheric = (FramingCode2)*(NormCode2)*(biospheric_center),
         framing2Xnorm3Xbiospheric = (FramingCode2)*(NormCode3)*(biospheric_center),
         framing2Xnorm4Xbiospheric = (FramingCode2)*(NormCode4)*(biospheric_center),
         
         framing1Xaltruistic = (FramingCode1)*(altruistic_center),
         framing2Xaltruistic = (FramingCode2)*(altruistic_center),
         norm1Xaltruistic = (NormCode1)*(altruistic_center),
         norm2Xaltruistic = (NormCode2)*(altruistic_center),
         norm3Xaltruistic = (NormCode3)*(altruistic_center),
         norm4Xaltruistic = (NormCode4)*(altruistic_center),
         framing1Xnorm1Xaltruistic = (FramingCode1)*(NormCode1)*(altruistic_center),
         framing1Xnorm2Xaltruistic = (FramingCode1)*(NormCode2)*(altruistic_center),
         framing1Xnorm3Xaltruistic = (FramingCode1)*(NormCode3)*(altruistic_center),
         framing1Xnorm4Xaltruistic = (FramingCode1)*(NormCode4)*(altruistic_center),
         framing2Xnorm1Xaltruistic = (FramingCode2)*(NormCode1)*(altruistic_center),
         framing2Xnorm2Xaltruistic = (FramingCode2)*(NormCode2)*(altruistic_center),
         framing2Xnorm3Xaltruistic = (FramingCode2)*(NormCode3)*(altruistic_center),
         framing2Xnorm4Xaltruistic = (FramingCode2)*(NormCode4)*(altruistic_center),
         
         framing1Xegoistic = (FramingCode1)*(egoistic_center),
         framing2Xegoistic = (FramingCode2)*(egoistic_center),
         norm1Xegoistic = (NormCode1)*(egoistic_center),
         norm2Xegoistic = (NormCode2)*(egoistic_center),
         norm3Xegoistic = (NormCode3)*(egoistic_center),
         norm4Xegoistic = (NormCode4)*(egoistic_center),
         framing1Xnorm1Xegoistic = (FramingCode1)*(NormCode1)*(egoistic_center),
         framing1Xnorm2Xegoistic = (FramingCode1)*(NormCode2)*(egoistic_center),
         framing1Xnorm3Xegoistic = (FramingCode1)*(NormCode3)*(egoistic_center),
         framing1Xnorm4Xegoistic = (FramingCode1)*(NormCode4)*(egoistic_center),
         framing2Xnorm1Xegoistic = (FramingCode2)*(NormCode1)*(egoistic_center),
         framing2Xnorm2Xegoistic = (FramingCode2)*(NormCode2)*(egoistic_center),
         framing2Xnorm3Xegoistic = (FramingCode2)*(NormCode3)*(egoistic_center),
         framing2Xnorm4Xegoistic = (FramingCode2)*(NormCode4)*(egoistic_center),
         
         framing1Xhedonic = (FramingCode1)*(hedonic_center),
         framing2Xhedonic = (FramingCode2)*(hedonic_center),
         norm1Xhedonic = (NormCode1)*(hedonic_center),
         norm2Xhedonic = (NormCode2)*(hedonic_center),
         norm3Xhedonic = (NormCode3)*(hedonic_center),
         norm4Xhedonic = (NormCode4)*(hedonic_center),
         framing1Xnorm1Xhedonic = (FramingCode1)*(NormCode1)*(hedonic_center),
         framing1Xnorm2Xhedonic = (FramingCode1)*(NormCode2)*(hedonic_center),
         framing1Xnorm3Xhedonic = (FramingCode1)*(NormCode3)*(hedonic_center),
         framing1Xnorm4Xhedonic = (FramingCode1)*(NormCode4)*(hedonic_center),
         framing2Xnorm1Xhedonic = (FramingCode2)*(NormCode1)*(hedonic_center),
         framing2Xnorm2Xhedonic = (FramingCode2)*(NormCode2)*(hedonic_center),
         framing2Xnorm3Xhedonic = (FramingCode2)*(NormCode3)*(hedonic_center),
         framing2Xnorm4Xhedonic = (FramingCode2)*(NormCode4)*(hedonic_center),
         
         framing1Xingroup = (FramingCode1)*(ingroup_identification_center),
         framing2Xingroup = (FramingCode2)*(ingroup_identification_center),
         norm1Xingroup = (NormCode1)*(ingroup_identification_center),
         norm2Xingroup = (NormCode2)*(ingroup_identification_center),
         norm3Xingroup = (NormCode3)*(ingroup_identification_center),
         norm4Xingroup = (NormCode4)*(ingroup_identification_center),
         framing1Xnorm1Xingroup = (FramingCode1)*(NormCode1)*(ingroup_identification_center),
         framing1Xnorm2Xingroup = (FramingCode1)*(NormCode2)*(ingroup_identification_center),
         framing1Xnorm3Xingroup = (FramingCode1)*(NormCode3)*(ingroup_identification_center),
         framing1Xnorm4Xingroup = (FramingCode1)*(NormCode4)*(ingroup_identification_center),
         framing2Xnorm1Xingroup = (FramingCode2)*(NormCode1)*(ingroup_identification_center),
         framing2Xnorm2Xingroup = (FramingCode2)*(NormCode2)*(ingroup_identification_center),
         framing2Xnorm3Xingroup = (FramingCode2)*(NormCode3)*(ingroup_identification_center),
         framing2Xnorm4Xingroup = (FramingCode2)*(NormCode4)*(ingroup_identification_center),
         
         framing1Xextraversion = (FramingCode1)*(extraversion_center),
         framing2Xextraversion = (FramingCode2)*(extraversion_center),
         norm1Xextraversion = (NormCode1)*(extraversion_center),
         norm2Xextraversion = (NormCode2)*(extraversion_center),
         norm3Xextraversion = (NormCode3)*(extraversion_center),
         norm4Xextraversion = (NormCode4)*(extraversion_center),
         framing1Xnorm1Xextraversion = (FramingCode1)*(NormCode1)*(extraversion_center),
         framing1Xnorm2Xextraversion = (FramingCode1)*(NormCode2)*(extraversion_center),
         framing1Xnorm3Xextraversion = (FramingCode1)*(NormCode3)*(extraversion_center),
         framing1Xnorm4Xextraversion = (FramingCode1)*(NormCode4)*(extraversion_center),
         framing2Xnorm1Xextraversion = (FramingCode2)*(NormCode1)*(extraversion_center),
         framing2Xnorm2Xextraversion = (FramingCode2)*(NormCode2)*(extraversion_center),
         framing2Xnorm3Xextraversion = (FramingCode2)*(NormCode3)*(extraversion_center),
         framing2Xnorm4Xextraversion = (FramingCode2)*(NormCode4)*(extraversion_center),
         
         framing1Xagreeableness = (FramingCode1)*(agreeableness_center),
         framing2Xagreeableness = (FramingCode2)*(agreeableness_center),
         norm1Xagreeableness = (NormCode1)*(agreeableness_center),
         norm2Xagreeableness = (NormCode2)*(agreeableness_center),
         norm3Xagreeableness = (NormCode3)*(agreeableness_center),
         norm4Xagreeableness = (NormCode4)*(agreeableness_center),
         framing1Xnorm1Xagreeableness = (FramingCode1)*(NormCode1)*(agreeableness_center),
         framing1Xnorm2Xagreeableness = (FramingCode1)*(NormCode2)*(agreeableness_center),
         framing1Xnorm3Xagreeableness = (FramingCode1)*(NormCode3)*(agreeableness_center),
         framing1Xnorm4Xagreeableness = (FramingCode1)*(NormCode4)*(agreeableness_center),
         framing2Xnorm1Xagreeableness = (FramingCode2)*(NormCode1)*(agreeableness_center),
         framing2Xnorm2Xagreeableness = (FramingCode2)*(NormCode2)*(agreeableness_center),
         framing2Xnorm3Xagreeableness = (FramingCode2)*(NormCode3)*(agreeableness_center),
         framing2Xnorm4Xagreeableness = (FramingCode2)*(NormCode4)*(agreeableness_center),
         
         framing1Xopenness = (FramingCode1)*(openness_center),
         framing2Xopenness = (FramingCode2)*(openness_center),
         norm1Xopenness = (NormCode1)*(openness_center),
         norm2Xopenness = (NormCode2)*(openness_center),
         norm3Xopenness = (NormCode3)*(openness_center),
         norm4Xopenness = (NormCode4)*(openness_center),
         framing1Xnorm1Xopenness = (FramingCode1)*(NormCode1)*(openness_center),
         framing1Xnorm2Xopenness = (FramingCode1)*(NormCode2)*(openness_center),
         framing1Xnorm3Xopenness = (FramingCode1)*(NormCode3)*(openness_center),
         framing1Xnorm4Xopenness = (FramingCode1)*(NormCode4)*(openness_center),
         framing2Xnorm1Xopenness = (FramingCode2)*(NormCode1)*(openness_center),
         framing2Xnorm2Xopenness = (FramingCode2)*(NormCode2)*(openness_center),
         framing2Xnorm3Xopenness = (FramingCode2)*(NormCode3)*(openness_center),
         framing2Xnorm4Xopenness = (FramingCode2)*(NormCode4)*(openness_center),
         
         framing1Xconscientiousness = (FramingCode1)*(conscientiousness_center),
         framing2Xconscientiousness = (FramingCode2)*(conscientiousness_center),
         norm1Xconscientiousness = (NormCode1)*(conscientiousness_center),
         norm2Xconscientiousness = (NormCode2)*(conscientiousness_center),
         norm3Xconscientiousness = (NormCode3)*(conscientiousness_center),
         norm4Xconscientiousness = (NormCode4)*(conscientiousness_center),
         framing1Xnorm1Xconscientiousness = (FramingCode1)*(NormCode1)*(conscientiousness_center),
         framing1Xnorm2Xconscientiousness = (FramingCode1)*(NormCode2)*(conscientiousness_center),
         framing1Xnorm3Xconscientiousness = (FramingCode1)*(NormCode3)*(conscientiousness_center),
         framing1Xnorm4Xconscientiousness = (FramingCode1)*(NormCode4)*(conscientiousness_center),
         framing2Xnorm1Xconscientiousness = (FramingCode2)*(NormCode1)*(conscientiousness_center),
         framing2Xnorm2Xconscientiousness = (FramingCode2)*(NormCode2)*(conscientiousness_center),
         framing2Xnorm3Xconscientiousness = (FramingCode2)*(NormCode3)*(conscientiousness_center),
         framing2Xnorm4Xconscientiousness = (FramingCode2)*(NormCode4)*(conscientiousness_center),
         
         framing1Xneuroticism = (FramingCode1)*(neuroticism_center),
         framing2Xneuroticism = (FramingCode2)*(neuroticism_center),
         norm1Xneuroticism = (NormCode1)*(neuroticism_center),
         norm2Xneuroticism = (NormCode2)*(neuroticism_center),
         norm3Xneuroticism = (NormCode3)*(neuroticism_center),
         norm4Xneuroticism = (NormCode4)*(neuroticism_center),
         framing1Xnorm1Xneuroticism = (FramingCode1)*(NormCode1)*(neuroticism_center),
         framing1Xnorm2Xneuroticism = (FramingCode1)*(NormCode2)*(neuroticism_center),
         framing1Xnorm3Xneuroticism = (FramingCode1)*(NormCode3)*(neuroticism_center),
         framing1Xnorm4Xneuroticism = (FramingCode1)*(NormCode4)*(neuroticism_center),
         framing2Xnorm1Xneuroticism = (FramingCode2)*(NormCode1)*(neuroticism_center),
         framing2Xnorm2Xneuroticism = (FramingCode2)*(NormCode2)*(neuroticism_center),
         framing2Xnorm3Xneuroticism = (FramingCode2)*(NormCode3)*(neuroticism_center),
         framing2Xnorm4Xneuroticism = (FramingCode2)*(NormCode4)*(neuroticism_center),
         
         framing1Xhonesty = (FramingCode1)*(honesty_center),
         framing2Xhonesty = (FramingCode2)*(honesty_center),
         norm1Xhonesty = (NormCode1)*(honesty_center),
         norm2Xhonesty = (NormCode2)*(honesty_center),
         norm3Xhonesty = (NormCode3)*(honesty_center),
         norm4Xhonesty = (NormCode4)*(honesty_center),
         framing1Xnorm1Xhonesty = (FramingCode1)*(NormCode1)*(honesty_center),
         framing1Xnorm2Xhonesty = (FramingCode1)*(NormCode2)*(honesty_center),
         framing1Xnorm3Xhonesty = (FramingCode1)*(NormCode3)*(honesty_center),
         framing1Xnorm4Xhonesty = (FramingCode1)*(NormCode4)*(honesty_center),
         framing2Xnorm1Xhonesty = (FramingCode2)*(NormCode1)*(honesty_center),
         framing2Xnorm2Xhonesty = (FramingCode2)*(NormCode2)*(honesty_center),
         framing2Xnorm3Xhonesty = (FramingCode2)*(NormCode3)*(honesty_center),
         framing2Xnorm4Xhonesty = (FramingCode2)*(NormCode4)*(honesty_center))
```




Imputation model:

```{r}
set.seed(114950518)
```

```{r include = FALSE}
imps <- smcfcs(data_R_alt, 
               smtype = "lm", 
               smformula = "consumer_intentions ~ framing_condition + norm_condition + framing_condition*norm_condition + biospheric_center + altruistic_center + egoistic_center + hedonic_center + ingroup_identification_center + clothing_interest_center + socially_desirable_center + Age_center + Gender + extraversion_center + agreeableness_center + openness_center + conscientiousness_center + neuroticism_center + honesty_center + framing1Xbiospheric + framing2Xbiospheric + norm1Xbiospheric + norm2Xbiospheric + norm3Xbiospheric + norm4Xbiospheric + framing1Xnorm1Xbiospheric + framing1Xnorm2Xbiospheric + framing1Xnorm3Xbiospheric + framing1Xnorm4Xbiospheric + framing2Xnorm1Xbiospheric + framing2Xnorm2Xbiospheric + framing2Xnorm3Xbiospheric + framing2Xnorm4Xbiospheric + framing1Xaltruistic + framing2Xaltruistic + norm1Xaltruistic + norm2Xaltruistic + norm3Xaltruistic + norm4Xaltruistic + framing1Xnorm1Xaltruistic + framing1Xnorm2Xaltruistic + framing1Xnorm3Xaltruistic + framing1Xnorm4Xaltruistic + framing2Xnorm1Xaltruistic + framing2Xnorm2Xaltruistic + framing2Xnorm3Xaltruistic + framing2Xnorm4Xaltruistic + framing1Xegoistic + framing2Xegoistic + norm1Xegoistic + norm2Xegoistic + norm3Xegoistic + norm4Xegoistic + framing1Xnorm1Xegoistic + framing1Xnorm2Xegoistic + framing1Xnorm3Xegoistic + framing1Xnorm4Xegoistic + framing2Xnorm1Xegoistic + framing2Xnorm2Xegoistic + framing2Xnorm3Xegoistic + framing2Xnorm4Xegoistic + framing1Xhedonic + framing2Xhedonic + norm1Xhedonic + norm2Xhedonic + norm3Xhedonic + norm4Xhedonic + framing1Xnorm1Xhedonic + framing1Xnorm2Xhedonic + framing1Xnorm3Xhedonic + framing1Xnorm4Xhedonic + framing2Xnorm1Xhedonic + framing2Xnorm2Xhedonic + framing2Xnorm3Xhedonic + framing2Xnorm4Xhedonic + framing1Xingroup + framing2Xingroup + norm1Xingroup + norm2Xingroup + norm3Xingroup + norm4Xingroup + framing1Xnorm1Xingroup + framing1Xnorm2Xingroup + framing1Xnorm3Xingroup + framing1Xnorm4Xingroup + framing2Xnorm1Xingroup + framing2Xnorm2Xingroup + framing2Xnorm3Xingroup + framing2Xnorm4Xingroup + framing1Xextraversion + framing2Xextraversion + norm1Xextraversion + norm2Xextraversion + norm3Xextraversion + norm4Xextraversion + framing1Xnorm1Xextraversion + framing1Xnorm2Xextraversion + framing1Xnorm3Xextraversion + framing1Xnorm4Xextraversion + framing2Xnorm1Xextraversion + framing2Xnorm2Xextraversion + framing2Xnorm3Xextraversion + framing2Xnorm4Xextraversion + framing1Xagreeableness + framing2Xagreeableness + norm1Xagreeableness + norm2Xagreeableness + norm3Xagreeableness + norm4Xagreeableness + framing1Xnorm1Xagreeableness + framing1Xnorm2Xagreeableness + framing1Xnorm3Xagreeableness + framing1Xnorm4Xagreeableness + framing2Xnorm1Xagreeableness + framing2Xnorm2Xagreeableness + framing2Xnorm3Xagreeableness + framing2Xnorm4Xagreeableness + framing1Xopenness + framing2Xopenness + norm1Xopenness + norm2Xopenness + norm3Xopenness + norm4Xopenness + framing1Xnorm1Xopenness + framing1Xnorm2Xopenness + framing1Xnorm3Xopenness + framing1Xnorm4Xopenness + framing2Xnorm1Xopenness + framing2Xnorm2Xopenness + framing2Xnorm3Xopenness + framing2Xnorm4Xopenness + framing1Xconscientiousness + framing2Xconscientiousness + norm1Xconscientiousness + norm2Xconscientiousness + norm3Xconscientiousness + norm4Xconscientiousness + framing1Xnorm1Xconscientiousness + framing1Xnorm2Xconscientiousness + framing1Xnorm3Xconscientiousness + framing1Xnorm4Xconscientiousness + framing2Xnorm1Xconscientiousness + framing2Xnorm2Xconscientiousness + framing2Xnorm3Xconscientiousness + framing2Xnorm4Xconscientiousness + framing1Xneuroticism + framing2Xneuroticism + norm1Xneuroticism + norm2Xneuroticism + norm3Xneuroticism + norm4Xneuroticism + framing1Xnorm1Xneuroticism + framing1Xnorm2Xneuroticism + framing1Xnorm3Xneuroticism + framing1Xnorm4Xneuroticism + framing2Xnorm1Xneuroticism + framing2Xnorm2Xneuroticism + framing2Xnorm3Xneuroticism + framing2Xnorm4Xneuroticism + framing1Xhonesty + framing2Xhonesty + norm1Xhonesty + norm2Xhonesty + norm3Xhonesty + norm4Xhonesty + framing1Xnorm1Xhonesty + framing1Xnorm2Xhonesty + framing1Xnorm3Xhonesty + framing1Xnorm4Xhonesty + framing2Xnorm1Xhonesty + framing2Xnorm2Xhonesty + framing2Xnorm3Xhonesty + framing2Xnorm4Xhonesty", 
               method = c("norm","norm","norm","norm","","norm","","norm","","logreg","logreg","","","norm","norm","norm","norm","norm","norm","","","","","","","FramingCode1*biospheric_center","FramingCode2*biospheric_center","NormCode1*biospheric_center","NormCode2*biospheric_center","NormCode3*biospheric_center","NormCode4*biospheric_center","FramingCode1*NormCode1*biospheric_center","FramingCode1*NormCode2*biospheric_center","FramingCode1*NormCode3*biospheric_center","FramingCode1*NormCode4*biospheric_center","FramingCode2*NormCode1*biospheric_center","FramingCode2*NormCode2*biospheric_center","FramingCode2*NormCode3*biospheric_center","FramingCode2*NormCode4*biospheric_center","FramingCode1*altruistic_center","FramingCode2*altruistic_center","NormCode1*altruistic_center","NormCode2*altruistic_center","NormCode3*altruistic_center","NormCode4*altruistic_center","FramingCode1*NormCode1*altruistic_center","FramingCode1*NormCode2*altruistic_center","FramingCode1*NormCode3*altruistic_center","FramingCode1*NormCode4*altruistic_center","FramingCode2*NormCode1*altruistic_center","FramingCode2*NormCode2*altruistic_center","FramingCode2*NormCode3*altruistic_center","FramingCode2*NormCode4*altruistic_center","FramingCode1*egoistic_center","FramingCode2*egoistic_center","NormCode1*egoistic_center","NormCode2*egoistic_center","NormCode3*egoistic_center","NormCode4*egoistic_center","FramingCode1*NormCode1*egoistic_center","FramingCode1*NormCode2*egoistic_center","FramingCode1*NormCode3*egoistic_center","FramingCode1*NormCode4*egoistic_center","FramingCode2*NormCode1*egoistic_center","FramingCode2*NormCode2*egoistic_center","FramingCode2*NormCode3*egoistic_center","FramingCode2*NormCode4*egoistic_center","FramingCode1*hedonic_center","FramingCode2*hedonic_center","NormCode1*hedonic_center","NormCode2*hedonic_center","NormCode3*hedonic_center","NormCode4*hedonic_center","FramingCode1*NormCode1*hedonic_center","FramingCode1*NormCode2*hedonic_center","FramingCode1*NormCode3*hedonic_center","FramingCode1*NormCode4*hedonic_center","FramingCode2*NormCode1*hedonic_center","FramingCode2*NormCode2*hedonic_center","FramingCode2*NormCode3*hedonic_center","FramingCode2*NormCode4*hedonic_center","","","","","","","","","","","","","","","FramingCode1*extraversion_center","FramingCode2*extraversion_center","NormCode1*extraversion_center","NormCode2*extraversion_center","NormCode3*extraversion_center","NormCode4*extraversion_center","FramingCode1*NormCode1*extraversion_center","FramingCode1*NormCode2*extraversion_center","FramingCode1*NormCode3*extraversion_center","FramingCode1*NormCode4*extraversion_center","FramingCode2*NormCode1*extraversion_center","FramingCode2*NormCode2*extraversion_center","FramingCode2*NormCode3*extraversion_center","FramingCode2*NormCode4*extraversion_center","FramingCode1*agreeableness_center","FramingCode2*agreeableness_center","NormCode1*agreeableness_center","NormCode2*agreeableness_center","NormCode3*agreeableness_center","NormCode4*agreeableness_center","FramingCode1*NormCode1*agreeableness_center","FramingCode1*NormCode2*agreeableness_center","FramingCode1*NormCode3*agreeableness_center","FramingCode1*NormCode4*agreeableness_center","FramingCode2*NormCode1*agreeableness_center","FramingCode2*NormCode2*agreeableness_center","FramingCode2*NormCode3*agreeableness_center","FramingCode2*NormCode4*agreeableness_center","FramingCode1*openness_center","FramingCode2*openness_center","NormCode1*openness_center","NormCode2*openness_center","NormCode3*openness_center","NormCode4*openness_center","FramingCode1*NormCode1*openness_center","FramingCode1*NormCode2*openness_center","FramingCode1*NormCode3*openness_center","FramingCode1*NormCode4*openness_center","FramingCode2*NormCode1*openness_center","FramingCode2*NormCode2*openness_center","FramingCode2*NormCode3*openness_center","FramingCode2*NormCode4*openness_center","FramingCode1*conscientiousness_center","FramingCode2*conscientiousness_center","NormCode1*conscientiousness_center","NormCode2*conscientiousness_center","NormCode3*conscientiousness_center","NormCode4*conscientiousness_center","FramingCode1*NormCode1*conscientiousness_center","FramingCode1*NormCode2*conscientiousness_center","FramingCode1*NormCode3*conscientiousness_center","FramingCode1*NormCode4*conscientiousness_center","FramingCode2*NormCode1*conscientiousness_center","FramingCode2*NormCode2*conscientiousness_center","FramingCode2*NormCode3*conscientiousness_center","FramingCode2*NormCode4*conscientiousness_center","FramingCode1*neuroticism_center","FramingCode2*neuroticism_center","NormCode1*neuroticism_center","NormCode2*neuroticism_center","NormCode3*neuroticism_center","NormCode4*neuroticism_center","FramingCode1*NormCode1*neuroticism_center","FramingCode1*NormCode2*neuroticism_center","FramingCode1*NormCode3*neuroticism_center","FramingCode1*NormCode4*neuroticism_center","FramingCode2*NormCode1*neuroticism_center","FramingCode2*NormCode2*neuroticism_center","FramingCode2*NormCode3*neuroticism_center","FramingCode2*NormCode4*neuroticism_center","FramingCode1*honesty_center","FramingCode2*honesty_center","NormCode1*honesty_center","NormCode2*honesty_center","NormCode3*honesty_center","NormCode4*honesty_center","FramingCode1*NormCode1*honesty_center","FramingCode1*NormCode2*honesty_center","FramingCode1*NormCode3*honesty_center","FramingCode1*NormCode4*honesty_center","FramingCode2*NormCode1*honesty_center","FramingCode2*NormCode2*honesty_center","FramingCode2*NormCode3*honesty_center","FramingCode2*NormCode4*honesty_center"))
```

```{r}
names(data_R_alt)
```


Storing imputed data sets:

```{r include = FALSE}
impobject <- imputationList(imps$impDatasets)
```


## Convert imputed data to `mice` compatible object

Convert `scmfcs` object to a `mids` object:
```{r include = FALSE}
mids_obj <- datlist2mids(impobject)
```

Running model:
```{r include = FALSE}
mod_mice <- with(mids_obj, lm(consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_identification_center + framing_condition*norm_condition*extraversion_center + framing_condition*norm_condition*conscientiousness_center + framing_condition*norm_condition*agreeableness_center + framing_condition*norm_condition*neuroticism_center + framing_condition*norm_condition*openness_center + framing_condition*norm_condition*honesty_center + socially_desirable_center + clothing_interest_center + Gender + Age_center))
```


## Pooled Regression Results

Using `mice` package:
```{r}
summary(pool(mod_mice)) %>%
  knitr::kable(digits = 3)
```


```{r complete imputed data set, include = FALSE}
complete_data <- complete(mids_obj, "long")
```



# Simple Effects

## Personality Interactions

### Extraversion

First, relationship between extraversion & consumer intentions for each norm condition:
```{r}
emtrends(mod_mice, ~norm_condition, var = "extraversion_center", adjust = "none")

# On a single graph
at_list <- list(extraversion_center = seq(-2.2, 2, by = 1))

emmip(mod_mice, norm_condition ~ extraversion_center, at = at_list, CIs = TRUE, xlab = "Extraversion (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(mod_mice, ~ extraversion_center | norm_condition, at = at_list, CIs = TRUE, xlab = "Extraversion (centered)", ylab = "Consumer Intentions")
```


Is the slope of the relationship between extraversion & consumer intentions stronger in any one of the norm conditions compared to the others?

```{r}
emtrends(mod_mice, pairwise~norm_condition, var = "extraversion_center", adjust = "none")
```


Second, relationship between extraversion & consumer intentions for each framing condition:
```{r}
emtrends(mod_mice, ~framing_condition, var = "extraversion_center", adjust = "none")

# On a single graph
at_list <- list(extraversion_center = seq(-2.2, 2, by = 1))

emmip(mod_mice, framing_condition ~ extraversion_center, at = at_list, CIs = TRUE, xlab = "Extraversion (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(mod_mice, ~ extraversion_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Extraversion (centered)", ylab = "Consumer Intentions")
```


Is the slope of the relationship between extraversion & consumer intentions stronger in any one of the framing conditions compared to the others?

```{r}
emtrends(mod_mice, pairwise~framing_condition, var = "extraversion_center", adjust = "none")
```


Third, interaction between extraversion, framing, & norm condition:
```{r}
emtrends(mod_mice, ~norm_condition | framing_condition, var = "extraversion_center", adjust = "none")

# Separate graph for each framing condition
at_list <- list(extraversion_center = seq(-2.2, 2, by = 1))

emmip(mod_mice, norm_condition ~ extraversion_center | framing_condition, at = at_list, CIs = TRUE, xlab = "Extraversion (centered)", ylab = "Consumer Intentions")
```





### Agreeableness

First, relationship between agreeableness & consumer intentions for each norm condition:
```{r}
emtrends(mod_mice, ~norm_condition, var = "agreeableness_center", adjust = "none")

# On a single graph
at_list <- list(agreeableness_center = seq(-2, 1.4, by = 1))

emmip(mod_mice, norm_condition ~ agreeableness_center, at = at_list, CIs = TRUE, xlab = "agreeableness (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(mod_mice, ~ agreeableness_center | norm_condition, at = at_list, CIs = TRUE, xlab = "agreeableness (centered)", ylab = "Consumer Intentions")
```


Is the slope of the relationship between agreeableness & consumer intentions stronger in any one of the norm conditions compared to the others?

```{r}
emtrends(mod_mice, pairwise~norm_condition, var = "agreeableness_center", adjust = "none")
```


Second, relationship between agreeableness & consumer intentions for each framing condition:
```{r}
emtrends(mod_mice, ~framing_condition, var = "agreeableness_center", adjust = "none")

# On a single graph
at_list <- list(agreeableness_center = seq(-2, 1.4, by = 1))

emmip(mod_mice, framing_condition ~ agreeableness_center, at = at_list, CIs = TRUE, xlab = "agreeableness (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(mod_mice, ~ agreeableness_center | framing_condition, at = at_list, CIs = TRUE, xlab = "agreeableness (centered)", ylab = "Consumer Intentions")
```


Is the slope of the relationship between agreeableness & consumer intentions stronger in any one of the framing conditions compared to the others?

```{r}
emtrends(mod_mice, pairwise~framing_condition, var = "agreeableness_center", adjust = "none")
```


Third, interaction between agreeableness, framing, & norm condition:
```{r}
emtrends(mod_mice, ~norm_condition | framing_condition, var = "agreeableness_center", adjust = "none")

# Separate graph for each framing condition
at_list <- list(agreeableness_center = seq(-2, 1.4, by = 1))

emmip(mod_mice, norm_condition ~ agreeableness_center | framing_condition, at = at_list, CIs = TRUE, xlab = "agreeableness (centered)", ylab = "Consumer Intentions")
```





### Openness

First, relationship between openness & consumer intentions for each norm condition:
```{r}
emtrends(mod_mice, ~norm_condition, var = "openness_center", adjust = "none")

# On a single graph
at_list <- list(openness_center = seq(-2.5, 1.4, by = 1))

emmip(mod_mice, norm_condition ~ openness_center, at = at_list, CIs = TRUE, xlab = "openness (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(mod_mice, ~ openness_center | norm_condition, at = at_list, CIs = TRUE, xlab = "openness (centered)", ylab = "Consumer Intentions")
```


Is the slope of the relationship between openness & consumer intentions stronger in any one of the norm conditions compared to the others?

```{r}
emtrends(mod_mice, pairwise~norm_condition, var = "openness_center", adjust = "none")
```


Second, relationship between openness & consumer intentions for each framing condition:
```{r}
emtrends(mod_mice, ~framing_condition, var = "openness_center", adjust = "none")

# On a single graph
at_list <- list(openness_center = seq(-2.5, 1.4, by = 1))

emmip(mod_mice, framing_condition ~ openness_center, at = at_list, CIs = TRUE, xlab = "openness (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(mod_mice, ~ openness_center | framing_condition, at = at_list, CIs = TRUE, xlab = "openness (centered)", ylab = "Consumer Intentions")
```


Is the slope of the relationship between openness & consumer intentions stronger in any one of the framing conditions compared to the others?

```{r}
emtrends(mod_mice, pairwise~framing_condition, var = "openness_center", adjust = "none")
```


Third, interaction between openness, framing, & norm condition:
```{r}
emtrends(mod_mice, ~norm_condition | framing_condition, var = "openness_center", adjust = "none")

# Separate graph for each framing condition
at_list <- list(openness_center = seq(-2.5, 1.4, by = 1))

emmip(mod_mice, norm_condition ~ openness_center | framing_condition, at = at_list, CIs = TRUE, xlab = "openness (centered)", ylab = "Consumer Intentions")
```





### Conscientiousness

First, relationship between conscientiousness & consumer intentions for each norm condition:
```{r}
emtrends(mod_mice, ~norm_condition, var = "conscientiousness_center", adjust = "none")

# On a single graph
at_list <- list(conscientiousness_center = seq(-2.1, 1.7, by = 1))

emmip(mod_mice, norm_condition ~ conscientiousness_center, at = at_list, CIs = TRUE, xlab = "conscientiousness (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(mod_mice, ~ conscientiousness_center | norm_condition, at = at_list, CIs = TRUE, xlab = "conscientiousness (centered)", ylab = "Consumer Intentions")
```


Is the slope of the relationship between conscientiousness & consumer intentions stronger in any one of the norm conditions compared to the others?

```{r}
emtrends(mod_mice, pairwise~norm_condition, var = "conscientiousness_center", adjust = "none")
```


Second, relationship between conscientiousness & consumer intentions for each framing condition:
```{r}
emtrends(mod_mice, ~framing_condition, var = "conscientiousness_center", adjust = "none")

# On a single graph
at_list <- list(conscientiousness_center = seq(-2.1, 1.7, by = 1))

emmip(mod_mice, framing_condition ~ conscientiousness_center, at = at_list, CIs = TRUE, xlab = "conscientiousness (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(mod_mice, ~ conscientiousness_center | framing_condition, at = at_list, CIs = TRUE, xlab = "conscientiousness (centered)", ylab = "Consumer Intentions")
```


Is the slope of the relationship between conscientiousness & consumer intentions stronger in any one of the framing conditions compared to the others?

```{r}
emtrends(mod_mice, pairwise~framing_condition, var = "conscientiousness_center", adjust = "none")
```


Third, interaction between conscientiousness, framing, & norm condition:
```{r}
emtrends(mod_mice, ~norm_condition | framing_condition, var = "conscientiousness_center", adjust = "none")

# Separate graph for each framing condition
at_list <- list(conscientiousness_center = seq(-2.1, 1.7, by = 1))

emmip(mod_mice, norm_condition ~ conscientiousness_center | framing_condition, at = at_list, CIs = TRUE, xlab = "conscientiousness (centered)", ylab = "Consumer Intentions")
```




### Neuroticism

First, relationship between neuroticism & consumer intentions for each norm condition:
```{r}
emtrends(mod_mice, ~norm_condition, var = "neuroticism_center", adjust = "none")

# On a single graph
at_list <- list(neuroticism_center = seq(-2.2, 2.1, by = 1))

emmip(mod_mice, norm_condition ~ neuroticism_center, at = at_list, CIs = TRUE, xlab = "neuroticism (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(mod_mice, ~ neuroticism_center | norm_condition, at = at_list, CIs = TRUE, xlab = "neuroticism (centered)", ylab = "Consumer Intentions")
```


Is the slope of the relationship between neuroticism & consumer intentions stronger in any one of the norm conditions compared to the others?

```{r}
emtrends(mod_mice, pairwise~norm_condition, var = "neuroticism_center", adjust = "none")
```


Second, relationship between neuroticism & consumer intentions for each framing condition:
```{r}
emtrends(mod_mice, ~framing_condition, var = "neuroticism_center", adjust = "none")

# On a single graph
at_list <- list(neuroticism_center = seq(-2.2, 2.1, by = 1))

emmip(mod_mice, framing_condition ~ neuroticism_center, at = at_list, CIs = TRUE, xlab = "neuroticism (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(mod_mice, ~ neuroticism_center | framing_condition, at = at_list, CIs = TRUE, xlab = "neuroticism (centered)", ylab = "Consumer Intentions")
```


Is the slope of the relationship between neuroticism & consumer intentions stronger in any one of the framing conditions compared to the others?

```{r}
emtrends(mod_mice, pairwise~framing_condition, var = "neuroticism_center", adjust = "none")
```


Third, interaction between neuroticism, framing, & norm condition:
```{r}
emtrends(mod_mice, ~norm_condition | framing_condition, var = "neuroticism_center", adjust = "none")

# Separate graph for each framing condition
at_list <- list(neuroticism_center = seq(-2.2, 2.1, by = 1))

emmip(mod_mice, norm_condition ~ neuroticism_center | framing_condition, at = at_list, CIs = TRUE, xlab = "neuroticism (centered)", ylab = "Consumer Intentions")
```



### Honesty

First, relationship between honesty & consumer intentions for each norm condition:
```{r}
emtrends(mod_mice, ~norm_condition, var = "honesty_center", adjust = "none")

# On a single graph
at_list <- list(honesty_center = seq(-2.5, 1.6, by = 1))

emmip(mod_mice, norm_condition ~ honesty_center, at = at_list, CIs = TRUE, xlab = "honesty (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(mod_mice, ~ honesty_center | norm_condition, at = at_list, CIs = TRUE, xlab = "honesty (centered)", ylab = "Consumer Intentions")
```


Is the slope of the relationship between honesty & consumer intentions stronger in any one of the norm conditions compared to the others?

```{r}
emtrends(mod_mice, pairwise~norm_condition, var = "honesty_center", adjust = "none")
```


Second, relationship between honesty & consumer intentions for each framing condition:
```{r}
emtrends(mod_mice, ~framing_condition, var = "honesty_center", adjust = "none")

# On a single graph
at_list <- list(honesty_center = seq(-2.5, 1.6, by = 1))

emmip(mod_mice, framing_condition ~ honesty_center, at = at_list, CIs = TRUE, xlab = "honesty (centered)", ylab = "Consumer Intentions")

# Separate graph for each norm
emmip(mod_mice, ~ honesty_center | framing_condition, at = at_list, CIs = TRUE, xlab = "honesty (centered)", ylab = "Consumer Intentions")
```


Is the slope of the relationship between honesty & consumer intentions stronger in any one of the framing conditions compared to the others?

```{r}
emtrends(mod_mice, pairwise~framing_condition, var = "honesty_center", adjust = "none")
```


Third, interaction between honesty, framing, & norm condition:
```{r}
emtrends(mod_mice, ~norm_condition | framing_condition, var = "honesty_center", adjust = "none")

# Separate graph for each framing condition
at_list <- list(honesty_center = seq(-2.5, 1.6, by = 1))

emmip(mod_mice, norm_condition ~ honesty_center | framing_condition, at = at_list, CIs = TRUE, xlab = "honesty (centered)", ylab = "Consumer Intentions")
```