---
title: "log_analysis_with_MI_smcfcs"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
date: "2023-03-29"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r clear environment, echo = FALSE}
rm(list = ls())
```


```{r libraries, message = FALSE, warning = FALSE, include = FALSE}
library(Rmisc)
library(Hmisc)
library(rio)
library(tidyverse)
library(psych)
library(gtools) # rbinding data frames
library(corrplot)
library(jtools) # for pretty printing tables
library(sjPlot) # pretty printing tables
library(sjmisc) # pretty printing
library(mice) # handling missing values
library(naniar) # visualizaing missingness & MCAR test
library(miceadds) # for mi.anova
library(emmeans) # simple effects analyses
library(broom)     # for extracting residuals and outlier indices
library(olsrr)     # for creating outlier plots
library(smcfcs) # for multiple imputation with interactions
library(mitools) # for pooling MI results
library(marginaleffects) # for plotting marginal means 
library(installr)
library(epiDisplay) # for frequency tables
library(papaja)
library(car)

options(max.print = 100000) # max rows to print in output
options(scipen = 1000) # turn off sci notation
```

# Data Import & Cleaning

## Import data
```{r import data}
raw_psych_hum_subj <- import("data/raw/raw_psych_hum_subj.csv")
raw_mktg_hum_subj <- import("data/raw/raw_mktg_hum_subj.csv")
raw_gen_uo_pop <- import("data/raw/raw_gen_uo_pop.csv")
pre_fall22 <- import("data/prescreen/dittersdorf_matches_f22.csv")
pre_winter23 <- import("data/prescreen/dittersdorf_matches_w23.csv")
pre_spring23 <- import("data/prescreen/dittersdorf_matches_s23.csv")
participant_list <- import("data/prescreen/dittersdorf_participants.csv")
```



Fix age before converting variable types
```{r}
table(raw_psych_hum_subj$Age) # 18 years old = 18
table(raw_mktg_hum_subj$Age) # 1999 = 24
table(raw_gen_uo_pop$Age)

raw_psych_hum_subj$Age[raw_psych_hum_subj$Age == "18 years old"] <- 18
raw_mktg_hum_subj$Age[raw_mktg_hum_subj$Age == 1999] <- 24

table(raw_psych_hum_subj$Age) # 18 years old = 18
table(raw_mktg_hum_subj$Age) # 1999 = 24
```



## Combine dataframes 
```{r update var types, warning = FALSE}
raw_psych_hum_subj <- raw_psych_hum_subj %>%
  mutate(Age = as.integer(Age),
         Gender = as.factor(Gender),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors),
         skepticism = as.factor(skepticism),
         id = as.factor(id),
         source = strrep("psych_hsp", times = 1))

levels(raw_psych_hum_subj$framing_condition_DO)

raw_mktg_hum_subj <- raw_mktg_hum_subj %>%
  mutate(Age = as.integer(Age),
         Gender = as.factor(Gender),
         Gender_5_TEXT = as.character(Gender_5_TEXT),
         Class_Lvl_7_TEXT = as.character(Class_Lvl_7_TEXT),
         Pol_Ornt_8_TEXT = as.character(Pol_Ornt_8_TEXT),
         Ethnicity_8_TEXT = as.character(Ethnicity_8_TEXT),
         skept_open = as.character(skept_open),
         skepticism = as.factor(skepticism),
         id = as.factor(id),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors),
         source = strrep("mktg_hsp", times = 1))

raw_gen_uo_pop <- raw_gen_uo_pop %>%
  mutate(Gender = as.factor(Gender),
         Gender_5_TEXT = as.character(Gender_5_TEXT),
         Class_Lvl_7_TEXT = as.character(Class_Lvl_7_TEXT),
         Pol_Ornt_8_TEXT = as.character(Pol_Ornt_8_TEXT),
         skept_open = as.character(skept_open),
         skepticism = as.factor(skepticism),
         id = as.factor(id),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors),
         source = strrep("gen_UO", times = 1))
```


Specify unique variables to combine prescreen data sets
```{r prep prescreen dfs}
# Create unique full_name variable
pre_fall22$full_name <- paste(pre_fall22$first_name, pre_fall22$last_name, sep="_")

pre_winter23$full_name <- paste(pre_winter23$first_name, pre_winter23$last_name, sep="_")

pre_spring23$full_name <- paste(pre_spring23$first_name, pre_spring23$last_name, sep="_")

participant_list$full_name <- paste(participant_list$first_name, participant_list$last_name, sep="_")

# Create column indicating which data set rows came from

pre_fall22 <- pre_fall22 %>%
  mutate(term = "fall22")

pre_winter23 <- pre_winter23 %>%
  mutate(term = "winter23")

pre_spring23 <- pre_spring23 %>%
  mutate(term = "spring23")
```


Combine prescreen data
```{r combine prescreen dfs}
combine1 <- smartbind(pre_fall22, pre_winter23)
combined_prescreen <- smartbind(combine1, pre_spring23)

# nrow(pre_fall22) + nrow(pre_winter23) + nrow(pre_spring23) # n = 1167

combined_prescreen_unique <- combined_prescreen[!duplicated(combined_prescreen$full_name), ] # keeps first row (fall22)
```

Subset key variables
```{r subset key vars}
combined_prescreen_key <- combined_prescreen_unique %>%
  dplyr::select(full_name, term, respecting:gratification, honest:gossip)

participant_list_key <- participant_list %>%
  dplyr::select(full_name, survey_id)
```

Merge with participant list
```{r merge participant list}
merged_prescreen <- merge(combined_prescreen_key, participant_list_key, by = "full_name")
```


Rename SDR items to match
```{r clean merged prescreen, warning = FALSE, include = FALSE}
merged_prescreen <- merged_prescreen %>%
  rename("lose_out" = "lose-out", 
         "cover_up" = "cover-up",
         "get_even" = "get-even",
         "behind_back" = "behind-back",
         "private_talk" = "private-talk",
         "take_things" = "take-things",
         "id" = "survey_id")
```

Convert variable types
```{r}
merged_prescreen <- merged_prescreen %>%
  mutate(respecting = as.integer(respecting),
         unity = as.integer(unity),
         protecting = as.integer(protecting),
         preventing = as.integer(preventing),
         equality = as.integer(equality),
         peace = as.integer(peace),
         justice = as.integer(justice),
         helpful = as.integer(helpful),
         power = as.integer(power),
         wealth = as.integer(wealth),
         authority = as.integer(authority),
         influential = as.integer(influential),
         ambition = as.integer(ambition),
         pleasures = as.integer(pleasures),
         enjoying = as.integer(enjoying),
         gratification = as.integer(gratification),
         honest = as.integer(honest),
         like = as.integer(like),
         disturbing = as.integer(disturbing),
         regret = as.integer(regret),
         lose_out = as.integer(lose_out),
         rational = as.integer(rational),
         confident = as.integer(confident),
         lover = as.integer(lover),
         lies = as.integer(lies),
         cover_up = as.integer(cover_up),
         advantage = as.integer(advantage),
         get_even = as.integer(get_even),
         behind_back = as.integer(behind_back),
         private_talk = as.integer(private_talk),
         take_things = as.integer(take_things),
         gossip = as.integer(gossip),
         id = as.factor(id))
```


Rename values & socially desirable items in prescreen data to match names in main data:
```{r rename prescreen vars, include = FALSE}
merged_prescreen <- merged_prescreen %>%
  rename("values_1" = "respecting",
         "values_2" = "unity",
         "values_3" = "protecting",
         "values_4" = "preventing",
         "values_5" = "equality",
         "values_6" = "peace",
         "values_7" = "justice",
         "values_8" = "helpful",
         "values_9" = "power",
         "values_10" = "wealth",
         "values_11" = "authority",
         "values_12" = "influential",
         "values_13" = "ambition",
         "values_14" = "pleasures",
         "values_15" = "enjoying",
         "values_16" = "gratification",
         "socially_desirable_1" = "honest",
         "socially_desirable_2" = "like",
         "socially_desirable_3" = "disturbing",
         "socially_desirable_4" = "regret",
         "socially_desirable_5" = "lose_out",
         "socially_desirable_6" = "rational",
         "socially_desirable_7" = "confident",
         "socially_desirable_8" = "lover",
         "socially_desirable_9" = "lies",
         "socially_desirable_10" = "cover_up",
         "socially_desirable_11" = "advantage",
         "socially_desirable_12" = "get_even",
         "socially_desirable_13" = "behind_back",
         "socially_desirable_14" = "private_talk",
         "socially_desirable_15" = "take_things",
         "socially_desirable_16" = "gossip")
```


Combine all data

- First, combine Psych Hum Subj data with Prescreen data based on `id`
- Second, add Mktg Hum Subj data
- Third, add gen UO Pop data
```{r combine all data}
combine1 <- merge(raw_psych_hum_subj, merged_prescreen, by = "id")
combine2 <- smartbind(combine1, raw_mktg_hum_subj)
combine3 <- smartbind(combine2, raw_gen_uo_pop)
```


## Remove duplicate cases

Identify duplicate cases
```{r id duplicate cases, results = 'hide'}
# first, add unique row #s
combine3 <- combine3 %>%
  mutate(row = 1:nrow(combine3))

combine3[duplicated(combine3$id),] # Only rows 1 through 858 have unique id #s

# write.csv(combine3, "combined_data.csv")
```

Row IDs to remove:

* 13 (participant's second time completing study)
* 134 (participant didn't complete study first time)
* 145 (participant didn't complete study first time)
* 308 (participant's second time completing study)
* 672 (participant's second time completing study)
* 743 (participant didn't complete study first time)
* 790 (participant didn't complete study first time)
* 800 (participant didn't complete study first time)

Remove duplicate rows after resolving:
```{r remove duplicate cases}
combine3 <- combine3 %>%
  filter(!row %in% c(13, 134, 145, 308, 672, 743, 790, 800))
```


## Remove rows of all NAs

Identify completely missing rows:
```{r id all NA rows, results = 'hide'}
key_vars <- combine3 %>%
  dplyr::select(row, big_2_1:big_2_65, consumer_intentions_1:consumer_intentions_9, consumer_behaviors, clothing_interest_1:clothing_interest_20, ingroup_ident_1:ingroup_ident_14, values_1:values_16, socially_desirable_1:socially_desirable_16, source)

ncol(key_vars) # number of columns - the row # & source column = 141

all_NA_rows <- key_vars[rowSums(is.na(key_vars)) == 141,] # identify rows with 141 NAs (all missing values), row numbers are preserved

all_NA_rows
```

Removing rows of fully missing data
```{r remove all NA rows}
data <- combine3 %>%
  dplyr::filter(!row %in% c(859, 860, 900, 926, 927, 941, 1139, 1141, 1142, 1143, 1144, 1146, 1149, 1150, 1152)) %>% # remove rows containing all NAs
  dplyr::select(-StartDate, -EndDate, -Status, -Progress, -"Duration (in seconds)", -Finished, -RecordedDate, -ResponseId, -DistributionChannel, -UserLanguage, -big_2_DO, -consumer_intentions_DO, -consumer_behaviors_DO, -clothing_interest_DO, -ingroup_ident_DO, -full_name, -code, -socially_desirable_DO, -values_DO, -email_giftcard, -term) # removing variables not in analysis
```


## Number per source
```{r}
table(data$source)
```

* 850 = psych human subjects pool
* 276 = mktg human subjects pool
* 7 = general UO pop


Rename variables
```{r rename vars}
data <- data %>%
  rename("framing_condition" = "framing_condition_DO", 
         "norm_condition" = "norm_condition_DO")
```

Drop unused levels
```{r include = FALSE}
levels(data$framing_condition)
levels(data$norm_condition)

data$framing_condition <- droplevels(data$framing_condition)
data$norm_condition <- droplevels(data$norm_condition)

levels(data$framing_condition)
levels(data$norm_condition)
```


Re-order levels of norm condition
```{r}
data$norm_condition <- factor(data$norm_condition, levels = c("control_norm", "descriptive_norm", "convention_norm", "social_norm", "moral_norm"))
```


## Inspect final data 
```{r inspect final df, results = 'hide'}
str(data, list.len = ncol(data))

# write.csv(data, "final_data.csv")
```


# Aggregate Variables 

## Personality

### Reverse-code

```{r reverse personality items}
data_R <- data %>%
  mutate(across(c(big_2_11,
                  big_2_16,
                  big_2_26,
                  big_2_31,
                  big_2_36,
                  big_2_51,
                  big_2_12,
                  big_2_17,
                  big_2_22,
                  big_2_37,
                  big_2_42,
                  big_2_47,
                  big_2_3,
                  big_2_8,
                  big_2_23,
                  big_2_28,
                  big_2_48,
                  big_2_58,
                  big_2_4,
                  big_2_9,
                  big_2_24,
                  big_2_29,
                  big_2_44,
                  big_2_49,
                  big_2_5,
                  big_2_25,
                  big_2_30,
                  big_2_45,
                  big_2_50,
                  big_2_55,
                  big_2_63), ~6 - .)) # replace '6' with the max possible value plus 1 for any particular scale
```

### Average items

```{r aggregate personality}
data_R$extraversion <- data_R %>%
  dplyr::select(big_2_1, big_2_6, big_2_11, big_2_16, big_2_21, big_2_26, big_2_31, big_2_36, big_2_41, big_2_46, big_2_51, big_2_56) %>%
  rowMeans(na.rm = TRUE) 


data_R$conscientiousness <- data_R %>%
  dplyr::select(big_2_3, big_2_8, big_2_13, big_2_18, big_2_23, big_2_28, big_2_33, big_2_38, big_2_43, big_2_48, big_2_53, big_2_58) %>%
  rowMeans(na.rm = TRUE)


data_R$agreeableness <- data_R %>%
  dplyr::select(big_2_2, big_2_7, big_2_12, big_2_17, big_2_22, big_2_27, big_2_32, big_2_37, big_2_42, big_2_47, big_2_52, big_2_57) %>%
  rowMeans(na.rm = TRUE)


data_R$neuroticism <- data_R %>%
  dplyr::select(big_2_4, big_2_9, big_2_14, big_2_19, big_2_24, big_2_29, big_2_34, big_2_39, big_2_44, big_2_49, big_2_54, big_2_59) %>%
  rowMeans(na.rm = TRUE)


data_R$openness <- data_R %>%
  dplyr::select(big_2_5, big_2_10, big_2_15, big_2_20, big_2_25, big_2_30, big_2_35, big_2_40, big_2_45, big_2_50, big_2_55, big_2_60) %>%
  rowMeans(na.rm = TRUE)


data_R$honesty <- data_R %>%
  dplyr::select(big_2_61, big_2_62, big_2_63, big_2_64, big_2_65) %>%
  rowMeans(na.rm = TRUE)
```

### Visually inspect
```{r warning = FALSE}
data_R %>%
  dplyr::select(extraversion, agreeableness, conscientiousness, openness, neuroticism, honesty) %>%
  hist()
```


## Clothing Interest

### Reverse-code

```{r reverse clothing items}
data_R <- data_R %>%
  mutate(across(c(clothing_interest_3,
                  clothing_interest_5,
                  clothing_interest_7,
                  clothing_interest_9,
                  clothing_interest_12,
                  clothing_interest_14,
                  clothing_interest_15,
                  clothing_interest_16,
                  clothing_interest_18,
                  clothing_interest_20), ~6 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```


### Average items
```{r aggregate clothing interest}
data_R$clothing_interest <- data_R %>%
  dplyr::select(clothing_interest_1:clothing_interest_20) %>%
  rowMeans(na.rm = TRUE)
```


### Visually Inspect
```{r}
data_R %>%
  dplyr::select(clothing_interest) %>%
  hist()
```



## In-group Identification

### Reverse-code

No items need to be reverse-coded.

### Average items
```{r aggegate ingroup ident}
data_R$ingroup_identification <- data_R %>%
  dplyr::select(ingroup_ident_1:ingroup_ident_14) %>%
  rowMeans(na.rm = TRUE)
```

### Visually Inspect

```{r}
data_R %>%
  dplyr::select(ingroup_identification) %>%
  hist()
```

## Values

### Reverse-code

No items need to be reverse-coded.

### Recoding scale options

Recoding values:

* -3 = 1
* -2 = 2
* -1 = 3
* 0 = 4
* +1 = 5
* +2 = 6
* +3 = 7

```{r recode values}
table(data_R$values_1)

data_R$values_1_rec <- dplyr::recode(data_R$values_1, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)

table(data_R$values_1_rec)

data_R$values_2_rec <- dplyr::recode(data_R$values_2, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_3_rec <- dplyr::recode(data_R$values_3, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_4_rec <- dplyr::recode(data_R$values_4, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_5_rec <- dplyr::recode(data_R$values_5, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_6_rec <- dplyr::recode(data_R$values_6, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_7_rec <- dplyr::recode(data_R$values_7, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_8_rec <- dplyr::recode(data_R$values_8, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_9_rec <- dplyr::recode(data_R$values_9, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_10_rec <- dplyr::recode(data_R$values_10, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_11_rec <- dplyr::recode(data_R$values_11, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_12_rec <- dplyr::recode(data_R$values_12, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_13_rec <- dplyr::recode(data_R$values_13, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_14_rec <- dplyr::recode(data_R$values_14, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_15_rec <- dplyr::recode(data_R$values_15, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_16_rec <- dplyr::recode(data_R$values_16, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)

table(data_R$values_16)
table(data_R$values_16_rec)
```


### Average items
```{r aggregate values}
data_R$biospheric <- data_R %>%
  dplyr::select(values_1_rec:values_4_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$altruistic <- data_R %>%
  dplyr::select(values_5_rec:values_8_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$egoistic <- data_R %>%
  dplyr::select(values_9_rec:values_13_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$hedonic <- data_R %>%
  dplyr::select(values_14_rec:values_16_rec) %>%
  rowMeans(na.rm = TRUE)
```


### Visually inspect
```{r}
values_df <- data_R %>%
  dplyr::select(biospheric, altruistic, egoistic, hedonic)

values_df %>%
  hist()
```

### Frequency tables
```{r}
# Biospheric values
tab1(values_df$biospheric, sort.group = "descending", cum.percent = TRUE, missing = FALSE, horiz = TRUE)

# Altruistic values
tab1(values_df$altruistic, sort.group = "descending", cum.percent = TRUE, missing = FALSE, horiz = TRUE)

# Egoistic values
tab1(values_df$egoistic, sort.group = "descending", cum.percent = TRUE, missing = FALSE, horiz = TRUE)

# Hedonic values
tab1(values_df$hedonic, sort.group = "descending", cum.percent = TRUE, missing = FALSE, horiz = TRUE)
```




## Socially Desirable Responding

### Reverse-code
```{r reverse code socially desirable items}
data_R <- data_R %>%
  mutate(across(c(socially_desirable_1,
                  socially_desirable_3,
                  socially_desirable_5,
                  socially_desirable_8,
                  socially_desirable_9,
                  socially_desirable_11,
                  socially_desirable_12,
                  socially_desirable_13), ~8 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```

### Average items
```{r aggregate socially desirable}
data_R$self_deceptive_sdr <- data_R %>%
  dplyr::select(socially_desirable_1:socially_desirable_8) %>%
  rowMeans(na.rm = TRUE)
  
data_R$impress_manag_sdr <- data_R %>%
  dplyr::select(socially_desirable_9:socially_desirable_16) %>%
  rowMeans(na.rm = TRUE)
```

### Visually inspect

```{r warning = FALSE}
data_R %>%
  dplyr::select(self_deceptive_sdr, impress_manag_sdr) %>%
  hist()
```


## Consumer Intentions

### Reverse-code

Higher scores mean better consumer intentions (intentions to *reduce* future consumption):
```{r reverse code consumer intentions}
data_R <- data_R %>%
  mutate(across(c(consumer_intentions_2,
                  consumer_intentions_4,
                  consumer_intentions_7,
                  consumer_intentions_9), ~8 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```

### Average items

```{r aggregate consumer intentions}
data_R$consumer_intentions <- data_R %>%
  dplyr::select(consumer_intentions_1:consumer_intentions_9) %>%
  rowMeans(na.rm = TRUE)
```

### Visually inspect

```{r warning = FALSE}
data_R %>%
  dplyr::select(consumer_intentions) %>%
  hist()
```


# Contrast Coding 

Subset variables
```{r echo = FALSE}
data_R_alt <- data_R %>%
  dplyr::select(hedonic, egoistic, altruistic, biospheric, ingroup_identification, Age, clothing_interest, self_deceptive_sdr, impress_manag_sdr, consumer_intentions, consumer_behaviors, Gender, framing_condition, norm_condition)
```


Contrast Coding using ifelse() approach:
```{r alt coding}
# Framing
data_R_alt$FramingCode1 <- ifelse(data_R_alt$framing_condition == "control_framing", -1/2, ifelse(data_R_alt$framing_condition == "self_enh_framing", 1/2, 0))

data_R_alt$FramingCode2 <- ifelse(data_R_alt$framing_condition == "pro_env_framing", 2/3, -1/3)


# Norm
data_R_alt$NormCode1 <- ifelse(data_R_alt$norm_condition == "moral_norm", 4, -1)

data_R_alt$NormCode2 <- ifelse(data_R_alt$norm_condition == "social_norm", 3, ifelse(data_R_alt$norm_condition == "moral_norm", 0, -1))

data_R_alt$NormCode3 <- ifelse(data_R_alt$norm_condition == "convention_norm", 2, ifelse(data_R_alt$norm_condition == "moral_norm", 0, ifelse(data_R_alt$norm_condition == "social_norm", 0, -1)))
data_R_alt$NormCode4 <- ifelse(data_R_alt$norm_condition == "descriptive_norm", 1, ifelse(data_R_alt$norm_condition == "control_norm", -1, 0))


## Adding contrast codes to Framing & Norm Condition
# Framing
FrameCode1 <- c(-1/2, 0, 1/2) # control vs self-enhancing
FrameCode2 <- c(-1/3, 2/3, -1/3) # arbitrary code

contrasts(data_R_alt$framing_condition) <- cbind(FrameCode1, FrameCode2)
contrasts(data_R_alt$framing_condition)

# Norm
contrasts(data_R_alt$norm_condition) <- contr.helmert(5)
contrasts(data_R_alt$norm_condition) # control vs DN

# Gender
levels(data_R_alt$Gender) <- c("Woman", "Man", "Non-binary", "I prefer not to identify", "Other")

data_R_alt$Gender[data_R_alt$Gender == "Non-binary"] <- NA
data_R_alt$Gender[data_R_alt$Gender == "I prefer not to identify"] <- NA
data_R_alt$Gender[data_R_alt$Gender == "Other"] <- NA

data_R_alt$Gender <- droplevels(data_R_alt$Gender)

contrasts(data_R_alt$Gender) <- c(1, 0)
levels(data_R_alt$Gender)
```

Coding consumer_behaviors 0/1 and numeric because required by smcfcs imputation function:
```{r}
data_R_alt$consumer_behaviors <- as.numeric(data_R_alt$consumer_behaviors)

data_R_alt$consumer_behaviors <- ifelse(data_R_alt$consumer_behaviors == 1, 0, 1)
```


# Multiple Imputation 

## Examine Missingness

Examine missingness:
```{r}
data_R_alt %>%
  vis_miss()
```

Variables with NO missing data:

* ingroup_identification
* clothing_interest
* consumer_intentions
* framing_condition
* norm_condition

## Adding interaction terms

```{r include = FALSE}
data_R_alt <- data_R_alt %>%
  mutate(framing1Xbiospheric = (FramingCode1)*(biospheric),
         framing2Xbiospheric = (FramingCode2)*(biospheric),
         norm1Xbiospheric = (NormCode1)*(biospheric),
         norm2Xbiospheric = (NormCode2)*(biospheric),
         norm3Xbiospheric = (NormCode3)*(biospheric),
         norm4Xbiospheric = (NormCode4)*(biospheric),
         framing1Xnorm1Xbiospheric = (FramingCode1)*(NormCode1)*(biospheric),
         framing1Xnorm2Xbiospheric = (FramingCode1)*(NormCode2)*(biospheric),
         framing1Xnorm3Xbiospheric = (FramingCode1)*(NormCode3)*(biospheric),
         framing1Xnorm4Xbiospheric = (FramingCode1)*(NormCode4)*(biospheric),
         framing2Xnorm1Xbiospheric = (FramingCode2)*(NormCode1)*(biospheric),
         framing2Xnorm2Xbiospheric = (FramingCode2)*(NormCode2)*(biospheric),
         framing2Xnorm3Xbiospheric = (FramingCode2)*(NormCode3)*(biospheric),
         framing2Xnorm4Xbiospheric = (FramingCode2)*(NormCode4)*(biospheric),
         
         framing1Xaltruistic = (FramingCode1)*(altruistic),
         framing2Xaltruistic = (FramingCode2)*(altruistic),
         norm1Xaltruistic = (NormCode1)*(altruistic),
         norm2Xaltruistic = (NormCode2)*(altruistic),
         norm3Xaltruistic = (NormCode3)*(altruistic),
         norm4Xaltruistic = (NormCode4)*(altruistic),
         framing1Xnorm1Xaltruistic = (FramingCode1)*(NormCode1)*(altruistic),
         framing1Xnorm2Xaltruistic = (FramingCode1)*(NormCode2)*(altruistic),
         framing1Xnorm3Xaltruistic = (FramingCode1)*(NormCode3)*(altruistic),
         framing1Xnorm4Xaltruistic = (FramingCode1)*(NormCode4)*(altruistic),
         framing2Xnorm1Xaltruistic = (FramingCode2)*(NormCode1)*(altruistic),
         framing2Xnorm2Xaltruistic = (FramingCode2)*(NormCode2)*(altruistic),
         framing2Xnorm3Xaltruistic = (FramingCode2)*(NormCode3)*(altruistic),
         framing2Xnorm4Xaltruistic = (FramingCode2)*(NormCode4)*(altruistic),
         
         framing1Xegoistic = (FramingCode1)*(egoistic),
         framing2Xegoistic = (FramingCode2)*(egoistic),
         norm1Xegoistic = (NormCode1)*(egoistic),
         norm2Xegoistic = (NormCode2)*(egoistic),
         norm3Xegoistic = (NormCode3)*(egoistic),
         norm4Xegoistic = (NormCode4)*(egoistic),
         framing1Xnorm1Xegoistic = (FramingCode1)*(NormCode1)*(egoistic),
         framing1Xnorm2Xegoistic = (FramingCode1)*(NormCode2)*(egoistic),
         framing1Xnorm3Xegoistic = (FramingCode1)*(NormCode3)*(egoistic),
         framing1Xnorm4Xegoistic = (FramingCode1)*(NormCode4)*(egoistic),
         framing2Xnorm1Xegoistic = (FramingCode2)*(NormCode1)*(egoistic),
         framing2Xnorm2Xegoistic = (FramingCode2)*(NormCode2)*(egoistic),
         framing2Xnorm3Xegoistic = (FramingCode2)*(NormCode3)*(egoistic),
         framing2Xnorm4Xegoistic = (FramingCode2)*(NormCode4)*(egoistic),
         
         framing1Xhedonic = (FramingCode1)*(hedonic),
         framing2Xhedonic = (FramingCode2)*(hedonic),
         norm1Xhedonic = (NormCode1)*(hedonic),
         norm2Xhedonic = (NormCode2)*(hedonic),
         norm3Xhedonic = (NormCode3)*(hedonic),
         norm4Xhedonic = (NormCode4)*(hedonic),
         framing1Xnorm1Xhedonic = (FramingCode1)*(NormCode1)*(hedonic),
         framing1Xnorm2Xhedonic = (FramingCode1)*(NormCode2)*(hedonic),
         framing1Xnorm3Xhedonic = (FramingCode1)*(NormCode3)*(hedonic),
         framing1Xnorm4Xhedonic = (FramingCode1)*(NormCode4)*(hedonic),
         framing2Xnorm1Xhedonic = (FramingCode2)*(NormCode1)*(hedonic),
         framing2Xnorm2Xhedonic = (FramingCode2)*(NormCode2)*(hedonic),
         framing2Xnorm3Xhedonic = (FramingCode2)*(NormCode3)*(hedonic),
         framing2Xnorm4Xhedonic = (FramingCode2)*(NormCode4)*(hedonic),
         
         framing1Xingroup = (FramingCode1)*(ingroup_identification),
         framing2Xingroup = (FramingCode2)*(ingroup_identification),
         norm1Xingroup = (NormCode1)*(ingroup_identification),
         norm2Xingroup = (NormCode2)*(ingroup_identification),
         norm3Xingroup = (NormCode3)*(ingroup_identification),
         norm4Xingroup = (NormCode4)*(ingroup_identification),
         framing1Xnorm1Xingroup = (FramingCode1)*(NormCode1)*(ingroup_identification),
         framing1Xnorm2Xingroup = (FramingCode1)*(NormCode2)*(ingroup_identification),
         framing1Xnorm3Xingroup = (FramingCode1)*(NormCode3)*(ingroup_identification),
         framing1Xnorm4Xingroup = (FramingCode1)*(NormCode4)*(ingroup_identification),
         framing2Xnorm1Xingroup = (FramingCode2)*(NormCode1)*(ingroup_identification),
         framing2Xnorm2Xingroup = (FramingCode2)*(NormCode2)*(ingroup_identification),
         framing2Xnorm3Xingroup = (FramingCode2)*(NormCode3)*(ingroup_identification),
         framing2Xnorm4Xingroup = (FramingCode2)*(NormCode4)*(ingroup_identification))
```



## Imputation Model

```{r}
set.seed(114950518)
```

```{r echo = FALSE}
imps <- smcfcs(data_R_alt, 
               smtype = "logistic", 
               smformula = "consumer_behaviors ~ framing_condition + norm_condition + framing_condition*norm_condition + ingroup_identification + framing1Xingroup + framing2Xingroup + norm1Xingroup + norm2Xingroup + norm3Xingroup + norm4Xingroup + framing1Xnorm1Xingroup + framing1Xnorm2Xingroup + framing1Xnorm3Xingroup + framing1Xnorm4Xingroup + framing2Xnorm1Xingroup + framing2Xnorm2Xingroup + framing2Xnorm3Xingroup + framing2Xnorm4Xingroup + consumer_intentions + clothing_interest + self_deceptive_sdr + impress_manag_sdr + biospheric + framing1Xbiospheric + framing2Xbiospheric + norm1Xbiospheric + norm2Xbiospheric + norm3Xbiospheric + norm4Xbiospheric + framing1Xnorm1Xbiospheric + framing1Xnorm2Xbiospheric + framing1Xnorm3Xbiospheric + framing1Xnorm4Xbiospheric + framing2Xnorm1Xbiospheric + framing2Xnorm2Xbiospheric + framing2Xnorm3Xbiospheric + framing2Xnorm4Xbiospheric + altruistic + framing1Xaltruistic + framing2Xaltruistic + norm1Xaltruistic + norm2Xaltruistic + norm3Xaltruistic + norm4Xaltruistic + framing1Xnorm1Xaltruistic + framing1Xnorm2Xaltruistic + framing1Xnorm3Xaltruistic + framing1Xnorm4Xaltruistic + framing2Xnorm1Xaltruistic + framing2Xnorm2Xaltruistic + framing2Xnorm3Xaltruistic + framing2Xnorm4Xaltruistic + egoistic + framing1Xegoistic + framing2Xegoistic + norm1Xegoistic + norm2Xegoistic + norm3Xegoistic + norm4Xegoistic + framing1Xnorm1Xegoistic + framing1Xnorm2Xegoistic + framing1Xnorm3Xegoistic + framing1Xnorm4Xegoistic + framing2Xnorm1Xegoistic + framing2Xnorm2Xegoistic + framing2Xnorm3Xegoistic + framing2Xnorm4Xegoistic + hedonic + framing1Xhedonic + framing2Xhedonic + norm1Xhedonic + norm2Xhedonic + norm3Xhedonic + norm4Xhedonic + framing1Xnorm1Xhedonic + framing1Xnorm2Xhedonic + framing1Xnorm3Xhedonic + framing1Xnorm4Xhedonic + framing2Xnorm1Xhedonic + framing2Xnorm2Xhedonic + framing2Xnorm3Xhedonic + framing2Xnorm4Xhedonic + consumer_intentions + Gender + Age", 
               method = c("norm","norm","norm","norm","","norm","","norm","norm","","","logreg","","","","","","","","","FramingCode1*biospheric","FramingCode2*biospheric","NormCode1*biospheric","NormCode2*biospheric","NormCode3*biospheric","NormCode4*biospheric","FramingCode1*NormCode1*biospheric","FramingCode1*NormCode2*biospheric","FramingCode1*NormCode3*biospheric","FramingCode1*NormCode4*biospheric","FramingCode2*NormCode1*biospheric","FramingCode2*NormCode2*biospheric","FramingCode2*NormCode3*biospheric","FramingCode2*NormCode4*biospheric","FramingCode1*altruistic","FramingCode2*altruistic","NormCode1*altruistic","NormCode2*altruistic","NormCode3*altruistic","NormCode4*altruistic","FramingCode1*NormCode1*altruistic","FramingCode1*NormCode2*altruistic","FramingCode1*NormCode3*altruistic","FramingCode1*NormCode4*altruistic","FramingCode2*NormCode1*altruistic","FramingCode2*NormCode2*altruistic","FramingCode2*NormCode3*altruistic","FramingCode2*NormCode4*altruistic","FramingCode1*egoistic","FramingCode2*egoistic","NormCode1*egoistic","NormCode2*egoistic","NormCode3*egoistic","NormCode4*egoistic","FramingCode1*NormCode1*egoistic","FramingCode1*NormCode2*egoistic","FramingCode1*NormCode3*egoistic","FramingCode1*NormCode4*egoistic","FramingCode2*NormCode1*egoistic","FramingCode2*NormCode2*egoistic","FramingCode2*NormCode3*egoistic","FramingCode2*NormCode4*egoistic","FramingCode1*hedonic","FramingCode2*hedonic","NormCode1*hedonic","NormCode2*hedonic","NormCode3*hedonic","NormCode4*hedonic","FramingCode1*NormCode1*hedonic","FramingCode1*NormCode2*hedonic","FramingCode1*NormCode3*hedonic","FramingCode1*NormCode4*hedonic","FramingCode2*NormCode1*hedonic","FramingCode2*NormCode2*hedonic","FramingCode2*NormCode3*hedonic","FramingCode2*NormCode4*hedonic","","","","","","","","","","","","","",""))
```


Storing imputed data sets
```{r}
impobject <- imputationList(imps$impDatasets)
```


Restrict range of values on imputed variables
```{r}
# bio values
impobject$imputations[[1]]$biospheric <- ifelse(impobject$imputations[[1]]$biospheric > 7, 7, impobject$imputations[[1]]$biospheric)

impobject$imputations[[2]]$biospheric <- ifelse(impobject$imputations[[2]]$biospheric > 7, 7, impobject$imputations[[2]]$biospheric)

impobject$imputations[[3]]$biospheric <- ifelse(impobject$imputations[[3]]$biospheric > 7, 7, impobject$imputations[[3]]$biospheric)

impobject$imputations[[4]]$biospheric <- ifelse(impobject$imputations[[4]]$biospheric > 7, 7, impobject$imputations[[4]]$biospheric)

impobject$imputations[[5]]$biospheric <- ifelse(impobject$imputations[[5]]$biospheric > 7, 7, impobject$imputations[[5]]$biospheric)


# alt values
impobject$imputations[[1]]$altruistic <- ifelse(impobject$imputations[[1]]$altruistic > 7, 7, impobject$imputations[[1]]$altruistic)

impobject$imputations[[2]]$altruistic <- ifelse(impobject$imputations[[2]]$altruistic > 7, 7, impobject$imputations[[2]]$altruistic)

impobject$imputations[[3]]$altruistic <- ifelse(impobject$imputations[[3]]$altruistic > 7, 7, impobject$imputations[[3]]$altruistic)

impobject$imputations[[4]]$altruistic <- ifelse(impobject$imputations[[4]]$altruistic > 7, 7, impobject$imputations[[4]]$altruistic)

impobject$imputations[[5]]$altruistic <- ifelse(impobject$imputations[[5]]$altruistic > 7, 7, impobject$imputations[[5]]$altruistic)


# ego values
impobject$imputations[[1]]$egoistic <- ifelse(impobject$imputations[[1]]$egoistic > 7, 7, impobject$imputations[[1]]$egoistic)

impobject$imputations[[2]]$egoistic <- ifelse(impobject$imputations[[2]]$egoistic > 7, 7, impobject$imputations[[2]]$egoistic)

impobject$imputations[[3]]$egoistic <- ifelse(impobject$imputations[[3]]$egoistic > 7, 7, impobject$imputations[[3]]$egoistic)

impobject$imputations[[4]]$egoistic <- ifelse(impobject$imputations[[4]]$egoistic > 7, 7, impobject$imputations[[4]]$egoistic)

impobject$imputations[[5]]$egoistic <- ifelse(impobject$imputations[[5]]$egoistic > 7, 7, impobject$imputations[[5]]$egoistic)


# hed values
impobject$imputations[[1]]$hedonic <- ifelse(impobject$imputations[[1]]$hedonic > 7, 7, impobject$imputations[[1]]$hedonic)

impobject$imputations[[2]]$hedonic <- ifelse(impobject$imputations[[2]]$hedonic > 7, 7, impobject$imputations[[2]]$hedonic)

impobject$imputations[[3]]$hedonic <- ifelse(impobject$imputations[[3]]$hedonic > 7, 7, impobject$imputations[[3]]$hedonic)

impobject$imputations[[4]]$hedonic <- ifelse(impobject$imputations[[4]]$hedonic > 7, 7, impobject$imputations[[4]]$hedonic)

impobject$imputations[[5]]$hedonic <- ifelse(impobject$imputations[[5]]$hedonic > 7, 7, impobject$imputations[[5]]$hedonic)


# self-deceptive enhancement
with(impobject, describe(self_deceptive_sdr))

impobject$imputations[[4]]$self_deceptive_sdr <- ifelse(impobject$imputations[[4]]$self_deceptive_sdr < 1, 1, impobject$imputations[[4]]$self_deceptive_sdr)


# impr manag
with(impobject, describe(impress_manag_sdr))

# Age
describe(data_R_alt$Age)
with(impobject, describe(Age))

impobject$imputations[[1]]$Age <- ifelse(impobject$imputations[[1]]$Age < 18, 18, impobject$imputations[[1]]$Age)

impobject$imputations[[2]]$Age <- ifelse(impobject$imputations[[2]]$Age < 18, 18, impobject$imputations[[2]]$Age)

impobject$imputations[[3]]$Age <- ifelse(impobject$imputations[[3]]$Age < 18, 18, impobject$imputations[[3]]$Age)

impobject$imputations[[4]]$Age <- ifelse(impobject$imputations[[4]]$Age < 18, 18, impobject$imputations[[4]]$Age)

impobject$imputations[[5]]$Age <- ifelse(impobject$imputations[[5]]$Age < 18, 18, impobject$imputations[[5]]$Age)
```


### Centering continuous predictors
```{r}
# Biospheric values
impobject$imputations[[1]]$biospheric_center <- impobject$imputations[[1]]$biospheric - mean(impobject$imputations[[1]]$biospheric)

impobject$imputations[[2]]$biospheric_center <- impobject$imputations[[2]]$biospheric - mean(impobject$imputations[[2]]$biospheric)

impobject$imputations[[3]]$biospheric_center <- impobject$imputations[[3]]$biospheric - mean(impobject$imputations[[3]]$biospheric)

impobject$imputations[[4]]$biospheric_center <- impobject$imputations[[4]]$biospheric - mean(impobject$imputations[[4]]$biospheric)

impobject$imputations[[5]]$biospheric_center <- impobject$imputations[[5]]$biospheric - mean(impobject$imputations[[5]]$biospheric)


# Altruistic values
impobject$imputations[[1]]$altruistic_center <- impobject$imputations[[1]]$altruistic - mean(impobject$imputations[[1]]$altruistic)

impobject$imputations[[2]]$altruistic_center <- impobject$imputations[[2]]$altruistic - mean(impobject$imputations[[2]]$altruistic)

impobject$imputations[[3]]$altruistic_center <- impobject$imputations[[3]]$altruistic - mean(impobject$imputations[[3]]$altruistic)

impobject$imputations[[4]]$altruistic_center <- impobject$imputations[[4]]$altruistic - mean(impobject$imputations[[4]]$altruistic)

impobject$imputations[[5]]$altruistic_center <- impobject$imputations[[5]]$altruistic - mean(impobject$imputations[[5]]$altruistic)


# Egoistic values
impobject$imputations[[1]]$egoistic_center <- impobject$imputations[[1]]$egoistic - mean(impobject$imputations[[1]]$egoistic)

impobject$imputations[[2]]$egoistic_center <- impobject$imputations[[2]]$egoistic - mean(impobject$imputations[[2]]$egoistic)

impobject$imputations[[3]]$egoistic_center <- impobject$imputations[[3]]$egoistic - mean(impobject$imputations[[3]]$egoistic)

impobject$imputations[[4]]$egoistic_center <- impobject$imputations[[4]]$egoistic - mean(impobject$imputations[[4]]$egoistic)

impobject$imputations[[5]]$egoistic_center <- impobject$imputations[[5]]$egoistic - mean(impobject$imputations[[5]]$egoistic)


# Hedonic values
impobject$imputations[[1]]$hedonic_center <- impobject$imputations[[1]]$hedonic - mean(impobject$imputations[[1]]$hedonic)

impobject$imputations[[2]]$hedonic_center <- impobject$imputations[[2]]$hedonic - mean(impobject$imputations[[2]]$hedonic)

impobject$imputations[[3]]$hedonic_center <- impobject$imputations[[3]]$hedonic - mean(impobject$imputations[[3]]$hedonic)

impobject$imputations[[4]]$hedonic_center <- impobject$imputations[[4]]$hedonic - mean(impobject$imputations[[4]]$hedonic)

impobject$imputations[[5]]$hedonic_center <- impobject$imputations[[5]]$hedonic - mean(impobject$imputations[[5]]$hedonic)



# Ingroup identification
impobject$imputations[[1]]$ingroup_center <- impobject$imputations[[1]]$ingroup_identification - mean(impobject$imputations[[1]]$ingroup_identification)

impobject$imputations[[2]]$ingroup_center <- impobject$imputations[[2]]$ingroup_identification - mean(impobject$imputations[[2]]$ingroup_identification)

impobject$imputations[[3]]$ingroup_center <- impobject$imputations[[3]]$ingroup_identification - mean(impobject$imputations[[3]]$ingroup_identification)

impobject$imputations[[4]]$ingroup_center <- impobject$imputations[[4]]$ingroup_identification - mean(impobject$imputations[[4]]$ingroup_identification)

impobject$imputations[[5]]$ingroup_center <- impobject$imputations[[5]]$ingroup_identification - mean(impobject$imputations[[5]]$ingroup_identification)


# Age
impobject$imputations[[1]]$Age_center <- impobject$imputations[[1]]$Age - mean(impobject$imputations[[1]]$Age)

impobject$imputations[[2]]$Age_center <- impobject$imputations[[2]]$Age - mean(impobject$imputations[[2]]$Age)

impobject$imputations[[3]]$Age_center <- impobject$imputations[[3]]$Age - mean(impobject$imputations[[3]]$Age)

impobject$imputations[[4]]$Age_center <- impobject$imputations[[4]]$Age - mean(impobject$imputations[[4]]$Age)

impobject$imputations[[5]]$Age_center <- impobject$imputations[[5]]$Age - mean(impobject$imputations[[5]]$Age)



# Clothing interest
impobject$imputations[[1]]$clothing_center <- impobject$imputations[[1]]$clothing_interest - mean(impobject$imputations[[1]]$clothing_interest)

impobject$imputations[[2]]$clothing_center <- impobject$imputations[[2]]$clothing_interest - mean(impobject$imputations[[2]]$clothing_interest)

impobject$imputations[[3]]$clothing_center <- impobject$imputations[[3]]$clothing_interest - mean(impobject$imputations[[3]]$clothing_interest)

impobject$imputations[[4]]$clothing_center <- impobject$imputations[[4]]$clothing_interest - mean(impobject$imputations[[4]]$clothing_interest)

impobject$imputations[[5]]$clothing_center <- impobject$imputations[[5]]$clothing_interest - mean(impobject$imputations[[5]]$clothing_interest)



# Self deceptive SDR
impobject$imputations[[1]]$self_dec_center <- impobject$imputations[[1]]$self_deceptive_sdr - mean(impobject$imputations[[1]]$self_deceptive_sdr)

impobject$imputations[[2]]$self_dec_center <- impobject$imputations[[2]]$self_deceptive_sdr - mean(impobject$imputations[[2]]$self_deceptive_sdr)

impobject$imputations[[3]]$self_dec_center <- impobject$imputations[[3]]$self_deceptive_sdr - mean(impobject$imputations[[3]]$self_deceptive_sdr)

impobject$imputations[[4]]$self_dec_center <- impobject$imputations[[4]]$self_deceptive_sdr - mean(impobject$imputations[[4]]$self_deceptive_sdr)

impobject$imputations[[5]]$self_dec_center <- impobject$imputations[[5]]$self_deceptive_sdr - mean(impobject$imputations[[5]]$self_deceptive_sdr)


# Impression management SDR
impobject$imputations[[1]]$impress_manag_center <- impobject$imputations[[1]]$impress_manag_sdr - mean(impobject$imputations[[1]]$impress_manag_sdr)

impobject$imputations[[2]]$impress_manag_center <- impobject$imputations[[2]]$impress_manag_sdr - mean(impobject$imputations[[2]]$impress_manag_sdr)

impobject$imputations[[3]]$impress_manag_center <- impobject$imputations[[3]]$impress_manag_sdr - mean(impobject$imputations[[3]]$impress_manag_sdr)

impobject$imputations[[4]]$impress_manag_center <- impobject$imputations[[4]]$impress_manag_sdr - mean(impobject$imputations[[4]]$impress_manag_sdr)

impobject$imputations[[5]]$impress_manag_center <- impobject$imputations[[5]]$impress_manag_sdr - mean(impobject$imputations[[5]]$impress_manag_sdr)

# Coding Gender
contrasts(impobject$imputations[[1]]$Gender) <- c(1/2, -1/2)
contrasts(impobject$imputations[[2]]$Gender) <- c(1/2, -1/2)
contrasts(impobject$imputations[[3]]$Gender) <- c(1/2, -1/2)
contrasts(impobject$imputations[[4]]$Gender) <- c(1/2, -1/2)
contrasts(impobject$imputations[[5]]$Gender) <- c(1/2, -1/2)
```



Convert `scmfcs` object to a `mids` object (to make the object compatible with `mice`, and thus, `emmeans`):
```{r}
mids_obj <- datlist2mids(impobject)
```

Complete data set:
```{r complete imputed data set, include = FALSE}
complete_data <- complete(mids_obj, "long")
```


# Descriptive Statistics
```{r}
freqs <- with(mids_obj, table(consumer_behaviors))
freqs$analyses

props1 <- with(mids_obj, prop.table(table(consumer_behaviors)))
props1$analyses
```




# Logistic Analysis (DV = Consumer Behaviors)

Consumer Behaviors

* 0 = New Clothing
* 1 = Secondhand Clothing


## Running Model
```{r echo = FALSE}
log_mice <- with(mids_obj, glm(consumer_behaviors ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center, family = "binomial"))
```

```{r}
log_pool_obj <- pool(log_mice)
```

```{r include = FALSE}
log_mice
```

* df_residual = 1038
* residual deviance: 1329

## Model Summary

Full summary
```{r include = FALSE}
log_summ_pool <- summary(pool(log_mice))
log_summ_pool
```


## Pooled Regression Results

```{r}
summary(pool(log_mice)) %>%
  knitr::kable(digits = 3)
```

APA-style table
```{r}
pool_summ <- summary(pool(log_mice))

apa_table(pool_summ,
          caption = "Pooled Logistic Regression Results",
          note = "DV = Consumer Behaviors")
```


### Odds Ratios

Converting log odds estimates to odds ratios:
```{r}
ORs_pool <- cbind(log_summ_pool$term, exp(log_summ_pool$estimate))

ORs_pool %>%
  knitr::kable(digits = 2)
```



## Pooled Anova Results

Using Anova()
```{r include = FALSE, echo = FALSE, warning = FALSE}
anova_mod2 <- with(mids_obj, Anova(glm(consumer_behaviors ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center, family = "binomial"), type = "III"))
```

doesn't have a pooling option
```{r}
# anova_mod2
```

### Imputed data 1
```{r}
imp1_log <- anova_mod2$analyses[[1]]

imp1_log %>%
  knitr::kable(digits = c(2,2,3))

imp1_log
```

### Imputed data 2
```{r}
anova_mod2$analyses[[2]] %>%
  knitr::kable(digits = c(2,2,3))
```

### Imputed data 3
```{r}
anova_mod2$analyses[[3]] %>%
  knitr::kable(digits = c(2,2,3))
```

### Imputed data 4
```{r}
anova_mod2$analyses[[4]] %>%
  knitr::kable(digits = c(2,2,3))
```

### Imputed data 5
```{r}
anova_mod2$analyses[[5]] %>%
  knitr::kable(digits = c(2,2,3))
```


### Main Effects

Framing 
```{r}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[1]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[1]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[1]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[1]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[1]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[1]]
df2 <- anova_mod2$analyses[[2]]$Df[[1]]
df3 <- anova_mod2$analyses[[3]]$Df[[1]]
df4 <- anova_mod2$analyses[[4]]$Df[[1]]
df5 <- anova_mod2$analyses[[5]]$Df[[1]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```

Norm
```{r}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[2]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[2]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[2]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[2]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[2]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[2]]
df2 <- anova_mod2$analyses[[2]]$Df[[2]]
df3 <- anova_mod2$analyses[[3]]$Df[[2]]
df4 <- anova_mod2$analyses[[4]]$Df[[2]]
df5 <- anova_mod2$analyses[[5]]$Df[[2]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```

Biospheric
```{r}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[3]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[3]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[3]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[3]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[3]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[3]]
df2 <- anova_mod2$analyses[[2]]$Df[[3]]
df3 <- anova_mod2$analyses[[3]]$Df[[3]]
df4 <- anova_mod2$analyses[[4]]$Df[[3]]
df5 <- anova_mod2$analyses[[5]]$Df[[3]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```

Altruistic
```{r}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[4]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[4]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[4]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[4]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[4]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[4]]
df2 <- anova_mod2$analyses[[2]]$Df[[4]]
df3 <- anova_mod2$analyses[[3]]$Df[[4]]
df4 <- anova_mod2$analyses[[4]]$Df[[4]]
df5 <- anova_mod2$analyses[[5]]$Df[[4]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```

Egoistic
```{r}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[5]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[5]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[5]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[5]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[5]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[5]]
df2 <- anova_mod2$analyses[[2]]$Df[[5]]
df3 <- anova_mod2$analyses[[3]]$Df[[5]]
df4 <- anova_mod2$analyses[[4]]$Df[[5]]
df5 <- anova_mod2$analyses[[5]]$Df[[5]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```

Hedonic
```{r}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[6]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[6]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[6]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[6]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[6]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[6]]
df2 <- anova_mod2$analyses[[2]]$Df[[6]]
df3 <- anova_mod2$analyses[[3]]$Df[[6]]
df4 <- anova_mod2$analyses[[4]]$Df[[6]]
df5 <- anova_mod2$analyses[[5]]$Df[[6]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```

Ingroup
```{r}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[7]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[7]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[7]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[7]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[7]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[7]]
df2 <- anova_mod2$analyses[[2]]$Df[[7]]
df3 <- anova_mod2$analyses[[3]]$Df[[7]]
df4 <- anova_mod2$analyses[[4]]$Df[[7]]
df5 <- anova_mod2$analyses[[5]]$Df[[7]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```

Self-deceptive enhancement
```{r}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[8]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[8]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[8]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[8]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[8]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[8]]
df2 <- anova_mod2$analyses[[2]]$Df[[8]]
df3 <- anova_mod2$analyses[[3]]$Df[[8]]
df4 <- anova_mod2$analyses[[4]]$Df[[8]]
df5 <- anova_mod2$analyses[[5]]$Df[[8]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```

Impression management
```{r}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[9]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[9]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[9]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[9]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[9]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[9]]
df2 <- anova_mod2$analyses[[2]]$Df[[9]]
df3 <- anova_mod2$analyses[[3]]$Df[[9]]
df4 <- anova_mod2$analyses[[4]]$Df[[9]]
df5 <- anova_mod2$analyses[[5]]$Df[[9]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```

Clothing interest
```{r}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[10]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[10]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[10]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[10]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[10]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[10]]
df2 <- anova_mod2$analyses[[2]]$Df[[10]]
df3 <- anova_mod2$analyses[[3]]$Df[[10]]
df4 <- anova_mod2$analyses[[4]]$Df[[10]]
df5 <- anova_mod2$analyses[[5]]$Df[[10]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```

Gender
```{r}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[11]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[11]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[11]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[11]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[11]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[11]]
df2 <- anova_mod2$analyses[[2]]$Df[[11]]
df3 <- anova_mod2$analyses[[3]]$Df[[11]]
df4 <- anova_mod2$analyses[[4]]$Df[[11]]
df5 <- anova_mod2$analyses[[5]]$Df[[11]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```

Age
```{r}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[12]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[12]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[12]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[12]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[12]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[12]]
df2 <- anova_mod2$analyses[[2]]$Df[[12]]
df3 <- anova_mod2$analyses[[3]]$Df[[12]]
df4 <- anova_mod2$analyses[[4]]$Df[[12]]
df5 <- anova_mod2$analyses[[5]]$Df[[12]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```


### Interaction effects

FramingXNorm Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[13]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[13]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[13]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[13]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[13]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[13]]
df2 <- anova_mod2$analyses[[2]]$Df[[13]]
df3 <- anova_mod2$analyses[[3]]$Df[[13]]
df4 <- anova_mod2$analyses[[4]]$Df[[13]]
df5 <- anova_mod2$analyses[[5]]$Df[[13]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```


FramingXBio Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[14]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[14]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[14]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[14]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[14]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[14]]
df2 <- anova_mod2$analyses[[2]]$Df[[14]]
df3 <- anova_mod2$analyses[[3]]$Df[[14]]
df4 <- anova_mod2$analyses[[4]]$Df[[14]]
df5 <- anova_mod2$analyses[[5]]$Df[[14]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```



NormXBio Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[15]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[15]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[15]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[15]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[15]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[15]]
df2 <- anova_mod2$analyses[[2]]$Df[[15]]
df3 <- anova_mod2$analyses[[3]]$Df[[15]]
df4 <- anova_mod2$analyses[[4]]$Df[[15]]
df5 <- anova_mod2$analyses[[5]]$Df[[15]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```




FrameXAlt Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[16]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[16]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[16]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[16]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[16]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[16]]
df2 <- anova_mod2$analyses[[2]]$Df[[16]]
df3 <- anova_mod2$analyses[[3]]$Df[[16]]
df4 <- anova_mod2$analyses[[4]]$Df[[16]]
df5 <- anova_mod2$analyses[[5]]$Df[[16]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```



NormXAlt Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[17]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[17]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[17]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[17]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[17]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[17]]
df2 <- anova_mod2$analyses[[2]]$Df[[17]]
df3 <- anova_mod2$analyses[[3]]$Df[[17]]
df4 <- anova_mod2$analyses[[4]]$Df[[17]]
df5 <- anova_mod2$analyses[[5]]$Df[[17]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```




FrameXEgo Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[18]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[18]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[18]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[18]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[18]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[18]]
df2 <- anova_mod2$analyses[[2]]$Df[[18]]
df3 <- anova_mod2$analyses[[3]]$Df[[18]]
df4 <- anova_mod2$analyses[[4]]$Df[[18]]
df5 <- anova_mod2$analyses[[5]]$Df[[18]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```


NormxEgo Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[19]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[19]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[19]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[19]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[19]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[19]]
df2 <- anova_mod2$analyses[[2]]$Df[[19]]
df3 <- anova_mod2$analyses[[3]]$Df[[19]]
df4 <- anova_mod2$analyses[[4]]$Df[[19]]
df5 <- anova_mod2$analyses[[5]]$Df[[19]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```



FrameXHed Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[20]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[20]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[20]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[20]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[20]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[20]]
df2 <- anova_mod2$analyses[[2]]$Df[[20]]
df3 <- anova_mod2$analyses[[3]]$Df[[20]]
df4 <- anova_mod2$analyses[[4]]$Df[[20]]
df5 <- anova_mod2$analyses[[5]]$Df[[20]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```



NormXHed Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[21]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[21]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[21]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[21]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[21]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[21]]
df2 <- anova_mod2$analyses[[2]]$Df[[21]]
df3 <- anova_mod2$analyses[[3]]$Df[[21]]
df4 <- anova_mod2$analyses[[4]]$Df[[21]]
df5 <- anova_mod2$analyses[[5]]$Df[[21]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```



FrameXIngroup Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[22]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[22]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[22]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[22]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[22]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[22]]
df2 <- anova_mod2$analyses[[2]]$Df[[22]]
df3 <- anova_mod2$analyses[[3]]$Df[[22]]
df4 <- anova_mod2$analyses[[4]]$Df[[22]]
df5 <- anova_mod2$analyses[[5]]$Df[[22]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```



NormXIngroup Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[23]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[23]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[23]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[23]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[23]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[23]]
df2 <- anova_mod2$analyses[[2]]$Df[[23]]
df3 <- anova_mod2$analyses[[3]]$Df[[23]]
df4 <- anova_mod2$analyses[[4]]$Df[[23]]
df5 <- anova_mod2$analyses[[5]]$Df[[23]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```


frameXnormXbio Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[24]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[24]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[24]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[24]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[24]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[24]]
df2 <- anova_mod2$analyses[[2]]$Df[[24]]
df3 <- anova_mod2$analyses[[3]]$Df[[24]]
df4 <- anova_mod2$analyses[[4]]$Df[[24]]
df5 <- anova_mod2$analyses[[5]]$Df[[24]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```



frameXnormXalt Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[25]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[25]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[25]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[25]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[25]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[25]]
df2 <- anova_mod2$analyses[[2]]$Df[[25]]
df3 <- anova_mod2$analyses[[3]]$Df[[25]]
df4 <- anova_mod2$analyses[[4]]$Df[[25]]
df5 <- anova_mod2$analyses[[5]]$Df[[25]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```


frameXnormXego Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[26]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[26]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[26]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[26]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[26]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[26]]
df2 <- anova_mod2$analyses[[2]]$Df[[26]]
df3 <- anova_mod2$analyses[[3]]$Df[[26]]
df4 <- anova_mod2$analyses[[4]]$Df[[26]]
df5 <- anova_mod2$analyses[[5]]$Df[[26]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```



frameXnormXhed Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[27]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[27]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[27]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[27]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[27]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[27]]
df2 <- anova_mod2$analyses[[2]]$Df[[27]]
df3 <- anova_mod2$analyses[[3]]$Df[[27]]
df4 <- anova_mod2$analyses[[4]]$Df[[27]]
df5 <- anova_mod2$analyses[[5]]$Df[[27]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```



frameXnormXingroup Interaction
```{r include = FALSE}
chi_sq1 <- anova_mod2$analyses[[1]]$`LR Chisq`[[28]]
chi_sq2 <- anova_mod2$analyses[[2]]$`LR Chisq`[[28]]
chi_sq3 <- anova_mod2$analyses[[3]]$`LR Chisq`[[28]]
chi_sq4 <- anova_mod2$analyses[[4]]$`LR Chisq`[[28]]
chi_sq5 <- anova_mod2$analyses[[5]]$`LR Chisq`[[28]]

chi_sq <- cbind(chi_sq1, chi_sq2, chi_sq3, chi_sq4, chi_sq5)

df1 <- anova_mod2$analyses[[1]]$Df[[28]]
df2 <- anova_mod2$analyses[[2]]$Df[[28]]
df3 <- anova_mod2$analyses[[3]]$Df[[28]]
df4 <- anova_mod2$analyses[[4]]$Df[[28]]
df5 <- anova_mod2$analyses[[5]]$Df[[28]]

df <- cbind(df1, df2, df3, df4, df5)
```

```{r}
micombine.chisquare(chi_sq, df, display=TRUE, version=1)
```





# Simple Effects

## Framing Condition

>>H1: Consumer intentions/behaviors will be lower in the self-enhancing framing than in the pro-environmental or control framing conditions.

EM Means
```{r}
# logit scale
frame_emmeans_logit <- emmeans(log_mice, ~ framing_condition)
frame_emmeans_logit %>%
  knitr::kable(digits = 2)

# probability scale
frame_emmeans_prob <- emmeans(log_mice, ~ framing_condition, type = "response")
frame_emmeans_prob %>%
  knitr::kable(digits = 2)
```

Text Settings
```{r}
text_settings <- theme(text = element_text(size = 20)) +
  theme(plot.title = element_text(size = 20, face = 'bold')) +
  theme(axis.title.x = element_text(face = 'bold')) +
  theme(axis.title.y = element_text(face = 'bold')) +
  theme(axis.text.x = element_text(size = 20)) +
  theme(axis.text.y = element_text(size = 20)) +
  theme(axis.ticks = element_blank())
```

Visualization
```{r}
# logit scale
plot(frame_emmeans_logit)

# probability scale
plot(frame_emmeans_prob)

emmip(log_mice, ~ framing_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 2, alpha = 0.5), xlab = "Framing Condition", ylab = "Consumer Behaviors") + scale_x_discrete(breaks=c("control_framing","pro_env_framing","self_enh_framing"),
        labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) + theme_apa() + text_settings
```


Planned comparisons
```{r}
# custom contrasts
SE_F_EMM <- c(0,0,1)
C_F_EMM <- c(1,0,0)
PE_F_EMM <- c(0,1,0)

# logit scale
framing_comparisons <- contrast(frame_emmeans_logit, 
                          method = list("SE Frame - Control Frame" = SE_F_EMM - C_F_EMM,
                                        "PE Frame - SE Frame" = PE_F_EMM - SE_F_EMM,
                                        "PE Frame - Control" = PE_F_EMM - C_F_EMM), adjust = "none")
                          
framing_comparisons %>%
  knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
framing_comparisons %>% confint() %>%
  knitr::kable(digits = 2)



# probability scale
framing_comparisons <- contrast(frame_emmeans_prob, 
                          method = list("SE Frame - Control Frame" = SE_F_EMM - C_F_EMM,
                                        "PE Frame - SE Frame" = PE_F_EMM - SE_F_EMM,
                                        "PE Frame - Control" = PE_F_EMM - C_F_EMM), adjust = "none")
                          
framing_comparisons %>%
  knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
framing_comparisons %>% confint() %>%
  knitr::kable(digits = 2)
```



## Norm Condition

EM Means
```{r}
norm_emmeans_logit <- emmeans(log_mice, ~ norm_condition)
norm_emmeans_logit %>%
  knitr::kable(digits = 2)

norm_emmeans_prob <- emmeans(log_mice, ~ norm_condition, type = "response")
norm_emmeans_prob %>%
  knitr::kable(digits = 2)
```


Visualization
```{r}
# logit scale
plot(norm_emmeans_logit)

# probability scale
plot(norm_emmeans_prob)

emmip(log_mice, ~ norm_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 2, alpha = 0.5), xlab = "Norm Condition", ylab = "Consumer Behaviors") + scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"),
        labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + theme_apa() + text_settings
```


Planned comparisons
```{r}
# custom contrasts
Control_N_EMM <- c(1,0,0,0,0)
DN_EMM <- c(0,1,0,0,0)
Conv_EMM <- c(0,0,1,0,0)
SN_EMM <- c(0,0,0,1,0)
MN_EMM <- c(0,0,0,0,1)

# logit scale
norm_comparisons <- contrast(norm_emmeans_logit, 
                          method = list("Descriptive Norm - Control" = DN_EMM - Control_N_EMM,
                                        "Convention - Control" = Conv_EMM - Control_N_EMM,
                                        "Social Norm - Control" = SN_EMM - Control_N_EMM,
                                        "Moral Norm - Control" = MN_EMM - Control_N_EMM), adjust = "none")

                          
norm_comparisons %>%
  knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
norm_comparisons %>% confint() %>%
  knitr::kable(digits = 2)


# probability scale
norm_comparisons <- contrast(norm_emmeans_prob, 
                          method = list("Descriptive Norm - Control" = DN_EMM - Control_N_EMM,
                                        "Convention - Control" = Conv_EMM - Control_N_EMM,
                                        "Social Norm - Control" = SN_EMM - Control_N_EMM,
                                        "Moral Norm - Control" = MN_EMM - Control_N_EMM), adjust = "none")

                          
norm_comparisons %>%
  knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
norm_comparisons %>% confint() %>%
  knitr::kable(digits = 2)
```


## Framing x Norm 

EM Means
```{r}
cell_emmeans_logit <- emmeans(log_mice, ~ norm_condition*framing_condition)
cell_emmeans_logit %>%
  knitr::kable(digits = c(NA,NA,2,2,2,2,3))

cell_emmeans_prob <- emmeans(log_mice, ~ norm_condition*framing_condition, type = "response")
cell_emmeans_prob %>%
  knitr::kable(digits = c(NA,NA,2,2,2,2,3))
```


Visualization
```{r}
plot(cell_emmeans_logit)
plot(cell_emmeans_prob)

emmip(log_mice, framing_condition ~ norm_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 2, alpha = 0.5), xlab = "Norm Condition", ylab = "Consumer Behaviors") + scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"),
        labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) + theme_apa() + text_settings
```


Planned comparisons
```{r}
# custom contrasts
cf_cn_emm <- c(1,rep(0,14)) ## control framings
cf_dn_emm <- c(0,1,rep(0,13))
cf_conv_emm <- c(0,0,1,rep(0,12))
cf_sn_emm <- c(0,0,0,1,rep(0,11))
cf_mn_emm <- c(0,0,0,0,1,rep(0,10))

pf_cn_emm <- c(0,0,0,0,0,1,rep(0,9)) ## pro-environmental framings
pf_dn_emm <- c(0,0,0,0,0,0,1,rep(0,8))
pf_conv_emm <- c(rep(0,7),1,(rep(0,7)))
pf_sn_emm <- c(rep(0,8),1,(rep(0,6)))
pf_mn_emm <- c(rep(0,9),1,(rep(0,5)))

sf_cn_emm <- c(rep(0,10),1,(rep(0,4))) ## self-enhancing framings
sf_dn_emm <- c(rep(0,11),1,(rep(0,3)))
sf_conv_emm <- c(rep(0,12),1,(rep(0,2)))
sf_sn_emm <- c(rep(0,13),1,0)
sf_mn_emm <- c(rep(0,14),1)


# logit scale
FxN_comparisons_logit <- contrast(cell_emmeans_logit, 
                          method = list("Control Frame + DN - Control Frame + Ctrl" = cf_dn_emm - cf_cn_emm,
                                        "Control Frame + Conv - Control Frame + Ctrl" = cf_conv_emm - cf_cn_emm,
                                        "Control Frame + SN - Control Frame + Ctrl" = cf_sn_emm - cf_cn_emm,
                                        "Control Frame + MN - Control Frame + Ctrl" = cf_mn_emm - cf_cn_emm,
                                        "PE Frame + DN - PE Frame + Ctrl" = pf_dn_emm - pf_cn_emm,
                                        "PE Frame + Conv - PE Frame + Ctrl" = pf_conv_emm - pf_cn_emm,
                                        "PE Frame + SN - PE Frame + Ctrl" = pf_sn_emm - pf_cn_emm,
                                        "PE Frame + MN - PE Frame + Ctrl" = pf_mn_emm - pf_cn_emm,
                                        "SE Frame + DN - SE Frame + Ctrl" = sf_dn_emm - sf_cn_emm,
                                        "SE Frame + Conv - SE Frame + Ctrl" = sf_conv_emm - sf_cn_emm,
                                        "SE Frame + SN - SE Frame + Ctrl" = sf_sn_emm - sf_cn_emm,
                                        "SE Frame + MN - SE Frame + Ctrl" = sf_mn_emm - sf_cn_emm), adjust = "none")

FxN_comparisons_logit %>%
  knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
FxN_comparisons_logit %>% confint() %>%
  knitr::kable(digits = 2)




# probability scale
FxN_comparisons_prob <- contrast(cell_emmeans_prob, 
                          method = list("Control Frame + DN - Control Frame + Ctrl" = cf_dn_emm - cf_cn_emm,
                                        "Control Frame + Conv - Control Frame + Ctrl" = cf_conv_emm - cf_cn_emm,
                                        "Control Frame + SN - Control Frame + Ctrl" = cf_sn_emm - cf_cn_emm,
                                        "Control Frame + MN - Control Frame + Ctrl" = cf_mn_emm - cf_cn_emm,
                                        "PE Frame + DN - PE Frame + Ctrl" = pf_dn_emm - pf_cn_emm,
                                        "PE Frame + Conv - PE Frame + Ctrl" = pf_conv_emm - pf_cn_emm,
                                        "PE Frame + SN - PE Frame + Ctrl" = pf_sn_emm - pf_cn_emm,
                                        "PE Frame + MN - PE Frame + Ctrl" = pf_mn_emm - pf_cn_emm,
                                        "SE Frame + DN - SE Frame + Ctrl" = sf_dn_emm - sf_cn_emm,
                                        "SE Frame + Conv - SE Frame + Ctrl" = sf_conv_emm - sf_cn_emm,
                                        "SE Frame + SN - SE Frame + Ctrl" = sf_sn_emm - sf_cn_emm,
                                        "SE Frame + MN - SE Frame + Ctrl" = sf_mn_emm - sf_cn_emm), adjust = "none")

FxN_comparisons_prob %>%
  knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
FxN_comparisons_prob %>% confint() %>%
  knitr::kable(digits = 2)

```


Planned comparisons of comparisons

```{r}
# convert odds ratios to log OR
FxN_comparisons_prob %>%
  knitr::kable(digits = 8)

ORs <- c(0.6561187, 0.8977581, 0.6945434, 0.8725906, 2.0902685, 1.4270474, 1.9059225, 1.4663723, 1.6572961, 1.1991170, 1.3415565, 1.5980479)
ORs

log_ORs <- log(ORs)
log_ORs 
log_ORs %>% knitr::kable(digits = 2)

SEs <- c(0.2484442, 0.3500453, 0.2446919, 0.3517633, 0.8578687, 0.5170541, 0.7480687, 0.5472816, 0.6238446, 0.4836775, 0.5379552, 0.6271797)

# effect of descriptive norm 
## PE vs control
diff <- log_ORs[5] - log_ORs[1]
diff

SE_combine <- sqrt(SEs[5]^2 + SEs[1]^2)
SE_combine

z <- diff/SE_combine
z

p <- 2*pnorm(q=z, lower.tail=FALSE)
p

## SE vs control
diff <- log_ORs[9] - log_ORs[1]
diff

SE_combine <- sqrt(SEs[9]^2 + SEs[1]^2)
SE_combine

z <- diff/SE_combine
z

p <- 2*pnorm(q=z, lower.tail=FALSE)
p

## SE vs PE
diff <- log_ORs[9] - log_ORs[5]
diff

SE_combine <- sqrt(SEs[9]^2 + SEs[5]^2)
SE_combine

z <- diff/SE_combine
z

p <- 2*pnorm(q=z, lower.tail=TRUE)
p



# effect of convention
## PE vs control
diff <- log_ORs[6] - log_ORs[2]
diff

SE_combine <- sqrt(SEs[6]^2 + SEs[2]^2)
SE_combine

z <- diff/SE_combine
z

p <- 2*pnorm(q=z, lower.tail=FALSE)
p

## SE vs control
diff <- log_ORs[10] - log_ORs[2]
diff

SE_combine <- sqrt(SEs[10]^2 + SEs[2]^2)
SE_combine

z <- diff/SE_combine
z

p <- 2*pnorm(q=z, lower.tail=FALSE)
p

## SE vs PE
diff <- log_ORs[10] - log_ORs[6]
diff

SE_combine <- sqrt(SEs[10]^2 + SEs[6]^2)
SE_combine

z <- diff/SE_combine
z

p <- 2*pnorm(q=z, lower.tail=TRUE)
p



# effect of social norm
## PE vs control
diff <- log_ORs[7] - log_ORs[3]
diff

SE_combine <- sqrt(SEs[7]^2 + SEs[3]^2)
SE_combine

z <- diff/SE_combine
z

p <- 2*pnorm(q=z, lower.tail=FALSE)
p

## SE vs control
diff <- log_ORs[11] - log_ORs[3]
diff

SE_combine <- sqrt(SEs[11]^2 + SEs[3]^2)
SE_combine

z <- diff/SE_combine
z

p <- 2*pnorm(q=z, lower.tail=FALSE)
p

## SE vs PE
diff <- log_ORs[11] - log_ORs[7]
diff

SE_combine <- sqrt(SEs[11]^2 + SEs[7]^2)
SE_combine

z <- diff/SE_combine
z

p <- 2*pnorm(q=z, lower.tail=TRUE)
p




# effect of moral norm
## PE vs control
diff <- log_ORs[8] - log_ORs[4]
diff

SE_combine <- sqrt(SEs[8]^2 + SEs[4]^2)
SE_combine

z <- diff/SE_combine
z

p <- 2*pnorm(q=z, lower.tail=FALSE)
p

## SE vs control
diff <- log_ORs[12] - log_ORs[4]
diff

SE_combine <- sqrt(SEs[12]^2 + SEs[4]^2)
SE_combine

z <- diff/SE_combine
z

p <- 2*pnorm(q=z, lower.tail=FALSE)
p

## SE vs PE
diff <- log_ORs[12] - log_ORs[8]
diff

SE_combine <- sqrt(SEs[12]^2 + SEs[8]^2)
SE_combine

z <- diff/SE_combine
z

p <- 2*pnorm(q=z, lower.tail=FALSE)
p
```




## Exploratory RQ2: Cell differences from control

>> Exploratory RQ2: Which combination of framing and norm condition produced the strongest reductions in consumer intentions compared to the control condition?

```{r}
# custom contrasts
cf_cn_emm <- c(1,rep(0,14)) ## control framings
cf_dn_emm <- c(0,1,rep(0,13))
cf_conv_emm <- c(0,0,1,rep(0,12))
cf_sn_emm <- c(0,0,0,1,rep(0,11))
cf_mn_emm <- c(0,0,0,0,1,rep(0,10))

pf_cn_emm <- c(0,0,0,0,0,1,rep(0,9)) ## pro-environmental framings
pf_dn_emm <- c(0,0,0,0,0,0,1,rep(0,8))
pf_conv_emm <- c(rep(0,7),1,(rep(0,7)))
pf_sn_emm <- c(rep(0,8),1,(rep(0,6)))
pf_mn_emm <- c(rep(0,9),1,(rep(0,5)))

sf_cn_emm <- c(rep(0,10),1,(rep(0,4))) ## self-enhancing framings
sf_dn_emm <- c(rep(0,11),1,(rep(0,3)))
sf_conv_emm <- c(rep(0,12),1,(rep(0,2)))
sf_sn_emm <- c(rep(0,13),1,0)
sf_mn_emm <- c(rep(0,14),1)



# logit scale
RQ2 <- contrast(cell_emmeans_logit, 
                          method = list("Pro-env Frame + Control vs Control" = pf_cn_emm - cf_cn_emm,
                                        "Pro-env Frame + DN vs Control" = pf_dn_emm - cf_cn_emm,
                                        "Pro-env Frame + Conv vs Control" = pf_conv_emm - cf_cn_emm,
                                        "Pro-env Frame + SN vs Control" = pf_sn_emm - cf_cn_emm,
                                        "Pro-env Frame + MN vs Control" = pf_mn_emm - cf_cn_emm,
                                        "Self-enh Frame + Control vs Control" = sf_cn_emm - cf_cn_emm,
                                        "Self-enh Frame + DN vs Control" = sf_dn_emm - cf_cn_emm,
                                        "Self-enh Frame + Conv vs Control" = sf_conv_emm - cf_cn_emm,
                                        "Self-enh Frame + SN vs Control" = sf_sn_emm - cf_cn_emm,
                                        "Self-enh Frame + MN vs Control" = sf_mn_emm - cf_cn_emm), adjust = "sidak")

RQ2 %>%
  knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
RQ2 %>% confint() %>%
  knitr::kable(digits = 2)



# probability scale
RQ2 <- contrast(cell_emmeans_prob, 
                          method = list("Pro-env Frame + Control vs Control" = pf_cn_emm - cf_cn_emm,
                                        "Pro-env Frame + DN vs Control" = pf_dn_emm - cf_cn_emm,
                                        "Pro-env Frame + Conv vs Control" = pf_conv_emm - cf_cn_emm,
                                        "Pro-env Frame + SN vs Control" = pf_sn_emm - cf_cn_emm,
                                        "Pro-env Frame + MN vs Control" = pf_mn_emm - cf_cn_emm,
                                        "Self-enh Frame + Control vs Control" = sf_cn_emm - cf_cn_emm,
                                        "Self-enh Frame + DN vs Control" = sf_dn_emm - cf_cn_emm,
                                        "Self-enh Frame + Conv vs Control" = sf_conv_emm - cf_cn_emm,
                                        "Self-enh Frame + SN vs Control" = sf_sn_emm - cf_cn_emm,
                                        "Self-enh Frame + MN vs Control" = sf_mn_emm - cf_cn_emm), adjust = "sidak")

RQ2 %>%
  knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
RQ2 %>% confint() %>%
  knitr::kable(digits = 2)
```





# Values and Ingroup Interactions

>>H4: There will be a three-way interaction between values (biospheric, egoistic, altruistic, hedonic), framing condition, & norm condition such that when a pro-environmental or control framing is used, values will moderate the effect of each norm condition, but not when a self-enhancing framing is used.

Labels to use with facet_wrap
```{r}
norm_labs <- c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")
names(norm_labs) <- c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm")

frame_labs <- c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")
names(frame_labs) <- c("control_framing","pro_env_framing","self_enh_framing")
```

Averaging scores across imputations
```{r}
complete_data_subset <- complete_data %>%
  dplyr::select(.imp, .id, consumer_intentions, consumer_behaviors, Gender, framing_condition, norm_condition, biospheric_center, altruistic_center, egoistic_center, hedonic_center, ingroup_center, Age_center, clothing_center, self_dec_center, impress_manag_center)

average_df <- complete_data_subset %>% 
  group_by(.id) %>%
  transmute(.imp = .imp, 
            consumer_behaviors = consumer_behaviors, 
            Gender = Gender,
            framing_condition = framing_condition,
            norm_condition = norm_condition,
            biospheric_center = mean(biospheric_center),
         altruistic_center = mean(altruistic_center),
         egoistic_center = mean(egoistic_center),
         hedonic_center = mean(hedonic_center),
         ingroup_center = mean(ingroup_center),
         Age_center = mean(Age_center),
         clothing_center = mean(clothing_center),
         self_dec_center = mean(self_dec_center),
         impress_manag_center = mean(impress_manag_center),
         consumer_intentions = mean(consumer_intentions))


average_df <- average_df %>%
  filter(.imp == 1)
```


## Biospheric values

### Overall effect

Storing low (-1SD) and high (+1SD) biospheric values
```{r}
sd_below <- mean(average_df$biospheric_center) - sd(average_df$biospheric_center)

sd_above <- mean(average_df$biospheric_center) + sd(average_df$biospheric_center)
```

EMM for low and high bio
```{r}
# emmeans
atlist <- list(biospheric_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ biospheric_center, at = atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMM for low and high bio
```{r}
# custom contrast
low_bio <- c(1,0)
hi_bio <- c(0,1)

# compare
effect_bio <- contrast(emms, method = list("High Bio - Low Bio" = hi_bio - low_bio), adjust = "none")
effect_bio %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_bio %>% confint() %>%
  knitr::kable(digits = 2)
```


### Framing Condition

EMM for low vs high bio in each framing
```{r}
atlist <- list(biospheric_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ biospheric_center*framing_condition, at=atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMMs for low vs high bio in each framing 
```{r}
# custom contrasts
control_low_bio <- c(1,0,0,0,0,0)
control_hi_bio <- c(0,1,0,0,0,0)
proenv_low_bio <- c(0,0,1,0,0,0)
proenv_hi_bio <- c(0,0,0,1,0,0)
selfenh_low_bio <- c(0,0,0,0,1,0)
self_enh_hi_bio <- c(0,0,0,0,0,1)

# compare
effect_frame_bio <- contrast(emms, method = list("Control: High Bio - Low Bio" = control_hi_bio - control_low_bio,
                                                 "Pro-env: High Bio - Low Bio" = proenv_hi_bio - proenv_low_bio,
                                                 "Self-enh: High Bio - Low Bio" = self_enh_hi_bio - selfenh_low_bio), adjust = "none")
effect_frame_bio %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_frame_bio %>% confint() %>%
  knitr::kable(digits = 2)
```




### Norm Condition

EMM for low vs high bio in each norm
```{r}
atlist <- list(biospheric_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ biospheric_center*norm_condition, at=atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMMs for low vs high bio in each framing 
```{r}
# custom contrasts
control_low_bio <- c(1,rep(0,9))
control_hi_bio <- c(0,1,rep(0,8))
dn_low_bio <- c(0,0,1,rep(0,7))
dn_hi_bio <- c(0,0,0,1,rep(0,6))
conv_low_bio <- c(0,0,0,0,1,rep(0,5))
conv_hi_bio <- c(rep(0,5),1,rep(0,4))
sn_low_bio <- c(rep(0,6),1,0,0,0)
sn_hi_bio <- c(rep(0,7),1,0,0)
mn_low_bio <- c(rep(0,8),1,0)
mn_hi_bio <- c(rep(0,9),1)

# compare
effect_norm_bio <- contrast(emms, method = list("Control: High Bio - Low Bio" = control_hi_bio - control_low_bio,
                                                 "DN: High Bio - Low Bio" = dn_hi_bio - dn_low_bio,
                                                 "Conv: High Bio - Low Bio" = conv_hi_bio - conv_low_bio,
                                                 "SN: High Bio - Low Bio" = sn_hi_bio - sn_low_bio,
                                                 "MN: High Bio - Low Bio" = mn_hi_bio - mn_low_bio), adjust = "none")
effect_norm_bio %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_norm_bio %>% confint() %>%
  knitr::kable(digits = 2)
```






Is the difference between Control Norm and Other Norm different for people low vs high on biospheric values? Does this vary across framing conditions?


### Visualization
```{r}
text_settings <- theme(text = element_text(size = 20)) +
  theme(plot.title = element_text(size = 20, face = 'bold')) +
  theme(axis.title.x = element_text(face = 'bold')) +
  theme(axis.title.y = element_text(face = 'bold')) +
  theme(axis.text.x = element_text(size = 14)) +
  theme(axis.text.y = element_text(size = 20)) +
  theme(axis.ticks = element_blank())
```

#### Bio x Framing
```{r}
sd_below <- mean(average_df$biospheric_center) - sd(average_df$biospheric_center)
sd_above <- mean(average_df$biospheric_center) + sd(average_df$biospheric_center)

at_list <- list(biospheric_center = c(sd_below, sd_above))

emmip(log_mice, biospheric_center ~ framing_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 1), xlab = "Framing Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_framing","pro_env_framing", "self_enh_framing"), labels = c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Biospheric Values", breaks = c(-0.992493391146803, 0.992493391146803), labels = c("-1SD Biospheric", "+1SD Biospheric"), values = c("#00BFC4","#C77CFF"))
```

#### Bio x Norm
```{r}
emmip(log_mice, biospheric_center ~ norm_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 1), xlab = "Norm Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels = c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Biospheric Values", breaks = c(-0.992493391146803, 0.992493391146803), labels = c("-1SD Biospheric", "+1SD Biospheric"), values = c("#00BFC4","#C77CFF"))
```


#### Bio, Framing, & Norm
```{r}
emmip(log_mice, biospheric_center ~ norm_condition | framing_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 1), xlab = "Norm Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels = c("Control", "Descriptive", "Convention", "Social", "Moral")) +
  facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Biospheric Values", breaks = c(-0.992493391146803, 0.992493391146803), labels = c("-1SD Biospheric", "+1SD Biospheric"), values = c("#00BFC4","#C77CFF"))
  
```


### Planned Comparisons

#### Storing low (-1SD) and high (+1SD) biospheric values
```{r}
sd_below <- mean(average_df$biospheric_center) - sd(average_df$biospheric_center)
sd_above <- mean(average_df$biospheric_center) + sd(average_df$biospheric_center)
```


#### Calculate EM Means at low and high bio
```{r}
atlist <- list(biospheric_center = c(sd_below, sd_above))

combinations <- emmeans(log_mice, ~ norm_condition*biospheric_center*framing_condition, at=atlist, type = "response")

combinations %>% knitr::kable(digits = 2)
```

#### Custom contrasts
```{r}
cf_cn_low_bio <- c(1, rep(0,29)) # control framing
cf_dn_low_bio <- c(0,1,rep(0,28))
cf_conv_low_bio <- c(0,0,1,rep(0,27))
cf_sn_low_bio <- c(0,0,0,1,rep(0,26))
cf_mn_low_bio <- c(rep(0,4),1,(rep(0,25)))

cf_cn_hi_bio <- c(rep(0,5),1,(rep(0,24))) 
cf_dn_hi_bio <- c(rep(0,6),1,(rep(0,23)))
cf_conv_hi_bio <- c(rep(0,7),1,(rep(0,22)))
cf_sn_hi_bio <- c(rep(0,8),1,(rep(0,21)))
cf_mn_hi_bio <- c(rep(0,9),1,(rep(0,20)))


pf_cn_low_bio <- c(rep(0,10),1,(rep(0,19))) # pro-environmental framing
pf_dn_low_bio <- c(rep(0,11),1,(rep(0,18)))
pf_conv_low_bio <- c(rep(0,12),1,(rep(0,17)))
pf_sn_low_bio <- c(rep(0,13),1,(rep(0,16)))
pf_mn_low_bio <- c(rep(0,14),1,(rep(0,15)))

pf_cn_hi_bio <- c(rep(0,15),1,(rep(0,14))) 
pf_dn_hi_bio <- c(rep(0,16),1,(rep(0,13)))
pf_conv_hi_bio <- c(rep(0,17),1,(rep(0,12)))
pf_sn_hi_bio <- c(rep(0,18),1,(rep(0,11)))
pf_mn_hi_bio <- c(rep(0,19),1,(rep(0,10)))


sf_cn_low_bio <- c(rep(0,20),1,(rep(0,9))) # self-enhancing framing
sf_dn_low_bio <- c(rep(0,21),1,(rep(0,8)))
sf_conv_low_bio <- c(rep(0,22),1,(rep(0,7)))
sf_sn_low_bio <- c(rep(0,23),1,(rep(0,6)))
sf_mn_low_bio <- c(rep(0,24),1,(rep(0,5)))

sf_cn_hi_bio <- c(rep(0,25),1,(rep(0,4))) 
sf_dn_hi_bio <- c(rep(0,26),1,(rep(0,3)))
sf_conv_hi_bio <- c(rep(0,27),1,(rep(0,2)))
sf_sn_hi_bio <- c(rep(0,28),1,(rep(0,1)))
sf_mn_hi_bio <- c(rep(0,29),1)
```


Effect of norm for people low vs high on biospheric values across framing conditions

#### Control framing
```{r}
controlframe_lowvshi_bio <- contrast(combinations, 
                       method = list("CF/DN/LowBio - CF/CN/LowBio" = cf_dn_low_bio - cf_cn_low_bio,
                                     "CF/Conv/LowBio - CF/CN/LowBio" = cf_conv_low_bio - cf_cn_low_bio,
                                     "CF/SN/LowBio - CF/CN/LowBio" = cf_sn_low_bio - cf_cn_low_bio,
                                     "CF/MN/LowBio - CF/CN/LowBio" = cf_mn_low_bio - cf_cn_low_bio,
                                     "CF/DN/HiBio - CF/CN/HiBio" = cf_dn_hi_bio - cf_cn_hi_bio,
                                     "CF/Conv/HiBio - CF/CN/HiBio" = cf_conv_hi_bio - cf_cn_hi_bio,
                                     "CF/SN/HiBio - CF/CN/HiBio" = cf_sn_hi_bio - cf_cn_hi_bio,
                                     "CF/MN/HiBio - CF/CN/HiBio" = cf_mn_hi_bio - cf_cn_hi_bio), 
                       adjust = "none")

controlframe_lowvshi_bio %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
controlframe_lowvshi_bio %>% confint() %>%
  knitr::kable(digits = 2)
```


Planned comparisons

Custom contrasts
```{r}
controlframe_lowvshi_bio

dn_vs_c_lowbio <- c(1,rep(0,7))
conv_vs_c_lowbio <- c(0,1,rep(0,6))
sn_vs_c_lowbio <- c(0,0,1,rep(0,5))
mn_vs_c_lowbio <- c(0,0,0,1,rep(0,4))

dn_vs_c_hibio <- c(rep(0,4),1,rep(0,3))
conv_vs_c_hibio <- c(rep(0,5),1,rep(0,2))
sn_vs_c_hibio <- c(rep(0,6),1,rep(0,1))
mn_vs_c_hibio <- c(rep(0,7),1)
```

```{r}
compare_bio <- contrast(controlframe_lowvshi_bio, method = list("Effect of DN (Low - High Bio)" = dn_vs_c_lowbio - dn_vs_c_hibio, 
                                                                "Effect of Conv (Low - High Bio)" = conv_vs_c_lowbio - conv_vs_c_hibio,
                                                                "Effect of SN (Low - High Bio)" = sn_vs_c_lowbio - sn_vs_c_hibio,
                                                                "Effect of MN (Low - High Bio)" = mn_vs_c_lowbio - mn_vs_c_hibio), adjust = "none")

compare_bio %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_bio %>% confint() %>%
  knitr::kable(digits = 2)
```


#### Pro-environmental framing
```{r}
proenvframe_lowvshi_bio <- contrast(combinations, 
                       method = list("PF/DN/LowBio - PF/CN/LowBio" = pf_dn_low_bio - pf_cn_low_bio,
                                     "PF/Conv/LowBio - PF/CN/LowBio" = pf_conv_low_bio - pf_cn_low_bio,
                                     "PF/SN/LowBio - PF/CN/LowBio" = pf_sn_low_bio - pf_cn_low_bio,
                                     "PF/MN/LowBio - PF/CN/LowBio" = pf_mn_low_bio - pf_cn_low_bio,
                                     "PF/DN/HiBio - PF/CN/HiBio" = pf_dn_hi_bio - pf_cn_hi_bio,
                                     "PF/Conv/HiBio - PF/CN/HiBio" = pf_conv_hi_bio - pf_cn_hi_bio,
                                     "PF/SN/HiBio - PF/CN/HiBio" = pf_sn_hi_bio - pf_cn_hi_bio,
                                     "PF/MN/HiBio - PF/CN/HiBio" = pf_mn_hi_bio - pf_cn_hi_bio), 
                       adjust = "none")

proenvframe_lowvshi_bio %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
proenvframe_lowvshi_bio %>% confint() %>%
  knitr::kable(digits = 2)
```

Planned comparisons

Custom contrasts
```{r}
proenvframe_lowvshi_bio

dn_vs_c_lowbio <- c(1,rep(0,7))
conv_vs_c_lowbio <- c(0,1,rep(0,6))
sn_vs_c_lowbio <- c(0,0,1,rep(0,5))
mn_vs_c_lowbio <- c(0,0,0,1,rep(0,4))

dn_vs_c_hibio <- c(rep(0,4),1,rep(0,3))
conv_vs_c_hibio <- c(rep(0,5),1,rep(0,2))
sn_vs_c_hibio <- c(rep(0,6),1,rep(0,1))
mn_vs_c_hibio <- c(rep(0,7),1)
```

```{r}
compare_bio <- contrast(proenvframe_lowvshi_bio, method = list("Effect of DN (Low - High Bio)" = dn_vs_c_lowbio - dn_vs_c_hibio, 
                                                                "Effect of Conv (Low - High Bio)" = conv_vs_c_lowbio - conv_vs_c_hibio,
                                                                "Effect of SN (Low - High Bio)" = sn_vs_c_lowbio - sn_vs_c_hibio,
                                                                "Effect of MN (Low - High Bio)" = mn_vs_c_lowbio - mn_vs_c_hibio), adjust = "none")

compare_bio %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_bio %>% confint() %>%
  knitr::kable(digits = 2)
```



#### Self-enhancing framing
```{r}
selfenhframe_lowvshi_bio <- contrast(combinations, 
                       method = list("SF/DN/LowBio - SF/CN/LowBio" = sf_dn_low_bio - sf_cn_low_bio,
                                     "SF/Conv/LowBio - SF/CN/LowBio" = sf_conv_low_bio - sf_cn_low_bio,
                                     "SF/SN/LowBio - SF/CN/LowBio" = sf_sn_low_bio - sf_cn_low_bio,
                                     "SF/MN/LowBio - SF/CN/LowBio" = sf_mn_low_bio - sf_cn_low_bio,
                                     "SF/DN/HiBio - SF/CN/HiBio" = sf_dn_hi_bio - sf_cn_hi_bio,
                                     "SF/Conv/HiBio - SF/CN/HiBio" = sf_conv_hi_bio - sf_cn_hi_bio,
                                     "SF/SN/HiBio - SF/CN/HiBio" = sf_sn_hi_bio - sf_cn_hi_bio,
                                     "SF/MN/HiBio - SF/CN/HiBio" = sf_mn_hi_bio - sf_cn_hi_bio), 
                       adjust = "none")

selfenhframe_lowvshi_bio %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
selfenhframe_lowvshi_bio %>% confint() %>%
  knitr::kable(digits = 2)
```

Planned comparisons

Custom contrasts
```{r}
selfenhframe_lowvshi_bio

dn_vs_c_lowbio <- c(1,rep(0,7))
conv_vs_c_lowbio <- c(0,1,rep(0,6))
sn_vs_c_lowbio <- c(0,0,1,rep(0,5))
mn_vs_c_lowbio <- c(0,0,0,1,rep(0,4))

dn_vs_c_hibio <- c(rep(0,4),1,rep(0,3))
conv_vs_c_hibio <- c(rep(0,5),1,rep(0,2))
sn_vs_c_hibio <- c(rep(0,6),1,rep(0,1))
mn_vs_c_hibio <- c(rep(0,7),1)
```

```{r}
compare_bio <- contrast(selfenhframe_lowvshi_bio, method = list("Effect of DN (Low - High Bio)" = dn_vs_c_lowbio - dn_vs_c_hibio, 
                                                                "Effect of Conv (Low - High Bio)" = conv_vs_c_lowbio - conv_vs_c_hibio,
                                                                "Effect of SN (Low - High Bio)" = sn_vs_c_lowbio - sn_vs_c_hibio,
                                                                "Effect of MN (Low - High Bio)" = mn_vs_c_lowbio - mn_vs_c_hibio), adjust = "none")

compare_bio %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_bio %>% confint() %>%
  knitr::kable(digits = 2)
```




## Altruistic values

### Overall effect

Storing low (-1SD) and high (+1SD) altruistic values
```{r}
sd_below <- mean(average_df$altruistic_center) - sd(average_df$altruistic_center)

sd_above <- mean(average_df$altruistic_center) + sd(average_df$altruistic_center)
```

EMM for low and high alt
```{r}
# emmeans
atlist <- list(altruistic_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ altruistic_center, at = atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMM for low and high alt
```{r}
# custom contrast
low_alt <- c(1,0)
hi_alt <- c(0,1)

# compare
effect_alt <- contrast(emms, method = list("High alt - Low alt" = hi_alt - low_alt), adjust = "none")
effect_alt %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_alt %>% confint() %>%
  knitr::kable(digits = 2)
```


### Framing Condition

EMM for low vs high alt in each framing
```{r}
atlist <- list(altruistic_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ altruistic_center*framing_condition, at=atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMMs for low vs high alt in each framing 
```{r}
# custom contrasts
control_low_alt <- c(1,0,0,0,0,0)
control_hi_alt <- c(0,1,0,0,0,0)
proenv_low_alt <- c(0,0,1,0,0,0)
proenv_hi_alt <- c(0,0,0,1,0,0)
selfenh_low_alt <- c(0,0,0,0,1,0)
self_enh_hi_alt <- c(0,0,0,0,0,1)

# compare
effect_frame_alt <- contrast(emms, method = list("Control: High alt - Low alt" = control_hi_alt - control_low_alt,
                                                 "Pro-env: High alt - Low alt" = proenv_hi_alt - proenv_low_alt,
                                                 "Self-enh: High alt - Low alt" = self_enh_hi_alt - selfenh_low_alt), adjust = "none")
effect_frame_alt %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_frame_alt %>% confint() %>%
  knitr::kable(digits = 2)
```




### Norm Condition

EMM for low vs high alt in each norm
```{r}
atlist <- list(altruistic_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ altruistic_center*norm_condition, at=atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMMs for low vs high alt in each framing 
```{r}
# custom contrasts
control_low_alt <- c(1,rep(0,9))
control_hi_alt <- c(0,1,rep(0,8))
dn_low_alt <- c(0,0,1,rep(0,7))
dn_hi_alt <- c(0,0,0,1,rep(0,6))
conv_low_alt <- c(0,0,0,0,1,rep(0,5))
conv_hi_alt <- c(rep(0,5),1,rep(0,4))
sn_low_alt <- c(rep(0,6),1,0,0,0)
sn_hi_alt <- c(rep(0,7),1,0,0)
mn_low_alt <- c(rep(0,8),1,0)
mn_hi_alt <- c(rep(0,9),1)

# compare
effect_norm_alt <- contrast(emms, method = list("Control: High alt - Low alt" = control_hi_alt - control_low_alt,
                                                 "DN: High alt - Low alt" = dn_hi_alt - dn_low_alt,
                                                 "Conv: High alt - Low alt" = conv_hi_alt - conv_low_alt,
                                                 "SN: High alt - Low alt" = sn_hi_alt - sn_low_alt,
                                                 "MN: High alt - Low alt" = mn_hi_alt - mn_low_alt), adjust = "none")
effect_norm_alt %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_norm_alt %>% confint() %>%
  knitr::kable(digits = 2)
```




Is the difference between Control Norm and Other Norm different for people low vs high on altruistic values? Does this vary across framing conditions?

### Visualization

```{r}
text_settings <- theme(text = element_text(size = 20)) +
  theme(plot.title = element_text(size = 20, face = 'bold')) +
  theme(axis.title.x = element_text(face = 'bold')) +
  theme(axis.title.y = element_text(face = 'bold')) +
  theme(axis.text.x = element_text(size = 14)) +
  theme(axis.text.y = element_text(size = 20)) +
  theme(axis.ticks = element_blank())
```

#### Alt x Framing
```{r}
sd_below <- mean(average_df$altruistic_center) - sd(average_df$altruistic_center)
sd_above <- mean(average_df$altruistic_center) + sd(average_df$altruistic_center)

at_list <- list(altruistic_center = c(sd_below, sd_above))

emmip(log_mice, altruistic_center ~ framing_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 1), xlab = "Framing Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_framing","pro_env_framing", "self_enh_framing"), labels = c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Altruistic Values", breaks = c(-0.802959343713252, 0.802959343713252), labels = c("-1SD Altruistic", "+1SD Altruistic"), values = c("#00BFC4","#C77CFF"))
  
```

#### Alt x Norm
```{r}
emmip(log_mice, altruistic_center ~ norm_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 1), xlab = "Norm Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels = c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Altruistic Values", breaks = c(-0.802959343713252, 0.802959343713252), labels = c("-1SD Altruistic", "+1SD Altruistic"), values = c("#00BFC4","#C77CFF"))
```

#### Alt, Framing, Norm
```{r}
emmip(log_mice, altruistic_center ~ norm_condition | framing_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 1), xlab = "Norm Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels = c("Control", "Descriptive", "Convention", "Social", "Moral")) +
  facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Altruistic Values", breaks = c(-0.802959343713252, 0.802959343713252), labels = c("-1SD Altruistic", "+1SD Altruistic"), values = c("#00BFC4","#C77CFF"))
  
```


### Planned Comparisons

#### Storing low (-1SD) and high (+1SD) altspheric values
```{r}
sd_below <- mean(average_df$altruistic_center) - sd(average_df$altruistic_center)
sd_above <- mean(average_df$altruistic_center) + sd(average_df$altruistic_center)
```


#### Calculate EM Means at low and high alt
```{r}
atlist <- list(altruistic_center = c(sd_below, sd_above))

combinations <- emmeans(log_mice, ~ norm_condition*altruistic_center*framing_condition, at=atlist, type = "response")

combinations %>% knitr::kable(digits = 2)
```

### Custom contrasts
```{r}
cf_cn_low_alt <- c(1, rep(0,29)) # control framing
cf_dn_low_alt <- c(0,1,rep(0,28))
cf_conv_low_alt <- c(0,0,1,rep(0,27))
cf_sn_low_alt <- c(0,0,0,1,rep(0,26))
cf_mn_low_alt <- c(rep(0,4),1,(rep(0,25)))

cf_cn_hi_alt <- c(rep(0,5),1,(rep(0,24))) 
cf_dn_hi_alt <- c(rep(0,6),1,(rep(0,23)))
cf_conv_hi_alt <- c(rep(0,7),1,(rep(0,22)))
cf_sn_hi_alt <- c(rep(0,8),1,(rep(0,21)))
cf_mn_hi_alt <- c(rep(0,9),1,(rep(0,20)))


pf_cn_low_alt <- c(rep(0,10),1,(rep(0,19))) # pro-environmental framing
pf_dn_low_alt <- c(rep(0,11),1,(rep(0,18)))
pf_conv_low_alt <- c(rep(0,12),1,(rep(0,17)))
pf_sn_low_alt <- c(rep(0,13),1,(rep(0,16)))
pf_mn_low_alt <- c(rep(0,14),1,(rep(0,15)))

pf_cn_hi_alt <- c(rep(0,15),1,(rep(0,14))) 
pf_dn_hi_alt <- c(rep(0,16),1,(rep(0,13)))
pf_conv_hi_alt <- c(rep(0,17),1,(rep(0,12)))
pf_sn_hi_alt <- c(rep(0,18),1,(rep(0,11)))
pf_mn_hi_alt <- c(rep(0,19),1,(rep(0,10)))


sf_cn_low_alt <- c(rep(0,20),1,(rep(0,9))) # self-enhancing framing
sf_dn_low_alt <- c(rep(0,21),1,(rep(0,8)))
sf_conv_low_alt <- c(rep(0,22),1,(rep(0,7)))
sf_sn_low_alt <- c(rep(0,23),1,(rep(0,6)))
sf_mn_low_alt <- c(rep(0,24),1,(rep(0,5)))

sf_cn_hi_alt <- c(rep(0,25),1,(rep(0,4))) 
sf_dn_hi_alt <- c(rep(0,26),1,(rep(0,3)))
sf_conv_hi_alt <- c(rep(0,27),1,(rep(0,2)))
sf_sn_hi_alt <- c(rep(0,28),1,(rep(0,1)))
sf_mn_hi_alt <- c(rep(0,29),1)
```


Effect of norm for people low vs high on altruistic values across framing conditions

#### Control framing
```{r}
controlframe_lowvshi_alt <- contrast(combinations, 
                       method = list("CF/DN/LowAlt - CF/CN/LowAlt" = cf_dn_low_alt - cf_cn_low_alt,
                                     "CF/Conv/LowAlt - CF/CN/LowAlt" = cf_conv_low_alt - cf_cn_low_alt,
                                     "CF/SN/LowAlt - CF/CN/LowAlt" = cf_sn_low_alt - cf_cn_low_alt,
                                     "CF/MN/LowAlt - CF/CN/LowAlt" = cf_mn_low_alt - cf_cn_low_alt,
                                     "CF/DN/HiAlt - CF/CN/HiAlt" = cf_dn_hi_alt - cf_cn_hi_alt,
                                     "CF/Conv/HiAlt - CF/CN/HiAlt" = cf_conv_hi_alt - cf_cn_hi_alt,
                                     "CF/SN/HiAlt - CF/CN/HiAlt" = cf_sn_hi_alt - cf_cn_hi_alt,
                                     "CF/MN/HiAlt - CF/CN/HiAlt" = cf_mn_hi_alt - cf_cn_hi_alt), 
                       adjust = "none")

controlframe_lowvshi_alt %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
controlframe_lowvshi_alt %>% confint() %>%
  knitr::kable(digits = 2)
```


Planned Comparisons

Custom contrasts
```{r}
controlframe_lowvshi_alt

dn_vs_c_LowAlt <- c(1,rep(0,7))
conv_vs_c_LowAlt <- c(0,1,rep(0,6))
sn_vs_c_LowAlt <- c(0,0,1,rep(0,5))
mn_vs_c_LowAlt <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiAlt <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiAlt <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiAlt <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiAlt <- c(rep(0,7),1)
```

```{r}
compare_alt <- contrast(controlframe_lowvshi_alt, method = list("Effect of DN (Low - High alt)" = dn_vs_c_LowAlt - dn_vs_c_HiAlt, 
                                                                "Effect of Conv (Low - High alt)" = conv_vs_c_LowAlt - conv_vs_c_HiAlt,
                                                                "Effect of SN (Low - High alt)" = sn_vs_c_LowAlt - sn_vs_c_HiAlt,
                                                                "Effect of MN (Low - High alt)" = mn_vs_c_LowAlt - mn_vs_c_HiAlt), adjust = "none")

compare_alt %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_alt %>% confint() %>%
  knitr::kable(digits = 2)
```



#### Pro-environmental framing
```{r}
proenvframe_lowvshi_alt <- contrast(combinations, 
                       method = list("PF/DN/LowAlt - PF/CN/LowAlt" = pf_dn_low_alt - pf_cn_low_alt,
                                     "PF/Conv/LowAlt - PF/CN/LowAlt" = pf_conv_low_alt - pf_cn_low_alt,
                                     "PF/SN/LowAlt - PF/CN/LowAlt" = pf_sn_low_alt - pf_cn_low_alt,
                                     "PF/MN/LowAlt - PF/CN/LowAlt" = pf_mn_low_alt - pf_cn_low_alt,
                                     "PF/DN/HiAlt - PF/CN/HiAlt" = pf_dn_hi_alt - pf_cn_hi_alt,
                                     "PF/Conv/HiAlt - PF/CN/HiAlt" = pf_conv_hi_alt - pf_cn_hi_alt,
                                     "PF/SN/HiAlt - PF/CN/HiAlt" = pf_sn_hi_alt - pf_cn_hi_alt,
                                     "PF/MN/HiAlt - PF/CN/HiAlt" = pf_mn_hi_alt - pf_cn_hi_alt), 
                       adjust = "none")

proenvframe_lowvshi_alt %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
proenvframe_lowvshi_alt %>% confint() %>%
  knitr::kable(digits = 2)
```


Planned Comparisons

Custom contrasts
```{r}
proenvframe_lowvshi_alt

dn_vs_c_LowAlt <- c(1,rep(0,7))
conv_vs_c_LowAlt <- c(0,1,rep(0,6))
sn_vs_c_LowAlt <- c(0,0,1,rep(0,5))
mn_vs_c_LowAlt <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiAlt <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiAlt <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiAlt <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiAlt <- c(rep(0,7),1)
```

```{r}
compare_alt <- contrast(proenvframe_lowvshi_alt, method = list("Effect of DN (Low - High alt)" = dn_vs_c_LowAlt - dn_vs_c_HiAlt, 
                                                                "Effect of Conv (Low - High alt)" = conv_vs_c_LowAlt - conv_vs_c_HiAlt,
                                                                "Effect of SN (Low - High alt)" = sn_vs_c_LowAlt - sn_vs_c_HiAlt,
                                                                "Effect of MN (Low - High alt)" = mn_vs_c_LowAlt - mn_vs_c_HiAlt), adjust = "none")

compare_alt %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_alt %>% confint() %>%
  knitr::kable(digits = 2)
```



#### Self-enhancing framing
```{r}
selfenhframe_lowvshi_alt <- contrast(combinations, 
                       method = list("SF/DN/LowAlt - SF/CN/LowAlt" = sf_dn_low_alt - sf_cn_low_alt,
                                     "SF/Conv/LowAlt - SF/CN/LowAlt" = sf_conv_low_alt - sf_cn_low_alt,
                                     "SF/SN/LowAlt - SF/CN/LowAlt" = sf_sn_low_alt - sf_cn_low_alt,
                                     "SF/MN/LowAlt - SF/CN/LowAlt" = sf_mn_low_alt - sf_cn_low_alt,
                                     "SF/DN/HiAlt - SF/CN/HiAlt" = sf_dn_hi_alt - sf_cn_hi_alt,
                                     "SF/Conv/HiAlt - SF/CN/HiAlt" = sf_conv_hi_alt - sf_cn_hi_alt,
                                     "SF/SN/HiAlt - SF/CN/HiAlt" = sf_sn_hi_alt - sf_cn_hi_alt,
                                     "SF/MN/HiAlt - SF/CN/HiAlt" = sf_mn_hi_alt - sf_cn_hi_alt), 
                       adjust = "none")

selfenhframe_lowvshi_alt %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
selfenhframe_lowvshi_alt %>% confint() %>%
  knitr::kable(digits = 2)
```


Planned Comparisons

Custom contrasts
```{r}
selfenhframe_lowvshi_alt

dn_vs_c_LowAlt <- c(1,rep(0,7))
conv_vs_c_LowAlt <- c(0,1,rep(0,6))
sn_vs_c_LowAlt <- c(0,0,1,rep(0,5))
mn_vs_c_LowAlt <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiAlt <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiAlt <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiAlt <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiAlt <- c(rep(0,7),1)
```

```{r}
compare_alt <- contrast(selfenhframe_lowvshi_alt, method = list("Effect of DN (Low - High alt)" = dn_vs_c_LowAlt - dn_vs_c_HiAlt, 
                                                                "Effect of Conv (Low - High alt)" = conv_vs_c_LowAlt - conv_vs_c_HiAlt,
                                                                "Effect of SN (Low - High alt)" = sn_vs_c_LowAlt - sn_vs_c_HiAlt,
                                                                "Effect of MN (Low - High alt)" = mn_vs_c_LowAlt - mn_vs_c_HiAlt), adjust = "none")

compare_alt %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_alt %>% confint() %>%
  knitr::kable(digits = 2)
```




## Egoistic values

### Overall effect

Storing low (-1SD) and high (+1SD) egoistic values
```{r}
sd_below <- mean(average_df$egoistic_center) - sd(average_df$egoistic_center)

sd_above <- mean(average_df$egoistic_center) + sd(average_df$egoistic_center)
```

EMM for low and high ego
```{r}
# emmeans
atlist <- list(egoistic_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ egoistic_center, at = atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMM for low and high ego
```{r}
# custom contrast
low_ego <- c(1,0)
hi_ego <- c(0,1)

# compare
effect_ego <- contrast(emms, method = list("High ego - Low ego" = hi_ego - low_ego), adjust = "none")
effect_ego %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_ego %>% confint() %>%
  knitr::kable(digits = 2)
```


### Framing Condition

EMM for low vs high ego in each framing
```{r}
atlist <- list(egoistic_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ egoistic_center*framing_condition, at=atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMMs for low vs high ego in each framing 
```{r}
# custom contrasts
control_low_ego <- c(1,0,0,0,0,0)
control_hi_ego <- c(0,1,0,0,0,0)
proenv_low_ego <- c(0,0,1,0,0,0)
proenv_hi_ego <- c(0,0,0,1,0,0)
selfenh_low_ego <- c(0,0,0,0,1,0)
self_enh_hi_ego <- c(0,0,0,0,0,1)

# compare
effect_frame_ego <- contrast(emms, method = list("Control: High ego - Low ego" = control_hi_ego - control_low_ego,
                                                 "Pro-env: High ego - Low ego" = proenv_hi_ego - proenv_low_ego,
                                                 "Self-enh: High ego - Low ego" = self_enh_hi_ego - selfenh_low_ego), adjust = "none")
effect_frame_ego %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_frame_ego %>% confint() %>%
  knitr::kable(digits = 2)
```




### Norm Condition

EMM for low vs high ego in each norm
```{r}
atlist <- list(egoistic_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ egoistic_center*norm_condition, at=atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMMs for low vs high ego in each framing 
```{r}
# custom contrasts
control_low_ego <- c(1,rep(0,9))
control_hi_ego <- c(0,1,rep(0,8))
dn_low_ego <- c(0,0,1,rep(0,7))
dn_hi_ego <- c(0,0,0,1,rep(0,6))
conv_low_ego <- c(0,0,0,0,1,rep(0,5))
conv_hi_ego <- c(rep(0,5),1,rep(0,4))
sn_low_ego <- c(rep(0,6),1,0,0,0)
sn_hi_ego <- c(rep(0,7),1,0,0)
mn_low_ego <- c(rep(0,8),1,0)
mn_hi_ego <- c(rep(0,9),1)

# compare
effect_norm_ego <- contrast(emms, method = list("Control: High ego - Low ego" = control_hi_ego - control_low_ego,
                                                 "DN: High ego - Low ego" = dn_hi_ego - dn_low_ego,
                                                 "Conv: High ego - Low ego" = conv_hi_ego - conv_low_ego,
                                                 "SN: High ego - Low ego" = sn_hi_ego - sn_low_ego,
                                                 "MN: High ego - Low ego" = mn_hi_ego - mn_low_ego), adjust = "none")
effect_norm_ego %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_norm_ego %>% confint() %>%
  knitr::kable(digits = 2)
```

Is the difference between Control Norm and Other Norm different for people low vs high on egoistic values? Does this vary across framing conditions?

### Visualization

```{r}
text_settings <- theme(text = element_text(size = 20)) +
  theme(plot.title = element_text(size = 20, face = 'bold')) +
  theme(axis.title.x = element_text(face = 'bold')) +
  theme(axis.title.y = element_text(face = 'bold')) +
  theme(axis.text.x = element_text(size = 14)) +
  theme(axis.text.y = element_text(size = 20)) +
  theme(axis.ticks = element_blank())
```

#### Ego x Framing
```{r}
sd_below <- mean(average_df$egoistic_center) - sd(average_df$egoistic_center)
sd_above <- mean(average_df$egoistic_center) + sd(average_df$egoistic_center)

at_list <- list(egoistic_center = c(sd_below, sd_above))

emmip(log_mice, egoistic_center ~ framing_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 1), xlab = "Framing Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_framing","pro_env_framing", "self_enh_framing"), labels = c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Egoistic Values", breaks = c(-0.91717706890615, 0.917177068906151), labels = c("-1SD Egoistic", "+1SD Egoistic"), values = c("#00BFC4","#C77CFF"))
  
```

#### Ego x Norm
```{r}
emmip(log_mice, egoistic_center ~ norm_condition, CIs = TRUE, type = "response", CIarg = list(lwd = 1.2, alpha = 1), xlab = "Norm Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels = c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Egoistic Values", breaks = c(-0.91717706890615, 0.917177068906151), labels = c("-1SD Egoistic", "+1SD Egoistic"), values = c("#00BFC4","#C77CFF"))
```

#### Ego, Norm, Framing
```{r}
emmip(log_mice, egoistic_center ~ norm_condition | framing_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 1), xlab = "Norm Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels = c("Control", "Descriptive", "Convention", "Social", "Moral")) +
  facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Egoistic Values", breaks = c(-0.91717706890615, 0.917177068906151), labels = c("-1SD Egoistic", "+1SD Egoistic"), values = c("#00BFC4","#C77CFF"))
  
```



### Planned Comparisons

#### Storing low (-1SD) and high (+1SD) egoistic values
```{r}
sd_below <- mean(average_df$egoistic_center) - sd(average_df$egoistic_center)
sd_above <- mean(average_df$egoistic_center) + sd(average_df$egoistic_center)
```


#### Calculate EM Means at low and high ego
```{r}
atlist <- list(egoistic_center = c(sd_below, sd_above))

combinations <- emmeans(log_mice, ~ norm_condition*egoistic_center*framing_condition, at=atlist, type = "response")

combinations %>% knitr::kable(digits = 2)
```

### Custom contrasts
```{r}
cf_cn_low_ego <- c(1, rep(0,29)) # control framing
cf_dn_low_ego <- c(0,1,rep(0,28))
cf_conv_low_ego <- c(0,0,1,rep(0,27))
cf_sn_low_ego <- c(0,0,0,1,rep(0,26))
cf_mn_low_ego <- c(rep(0,4),1,(rep(0,25)))

cf_cn_hi_ego <- c(rep(0,5),1,(rep(0,24))) 
cf_dn_hi_ego <- c(rep(0,6),1,(rep(0,23)))
cf_conv_hi_ego <- c(rep(0,7),1,(rep(0,22)))
cf_sn_hi_ego <- c(rep(0,8),1,(rep(0,21)))
cf_mn_hi_ego <- c(rep(0,9),1,(rep(0,20)))


pf_cn_low_ego <- c(rep(0,10),1,(rep(0,19))) # pro-environmental framing
pf_dn_low_ego <- c(rep(0,11),1,(rep(0,18)))
pf_conv_low_ego <- c(rep(0,12),1,(rep(0,17)))
pf_sn_low_ego <- c(rep(0,13),1,(rep(0,16)))
pf_mn_low_ego <- c(rep(0,14),1,(rep(0,15)))

pf_cn_hi_ego <- c(rep(0,15),1,(rep(0,14))) 
pf_dn_hi_ego <- c(rep(0,16),1,(rep(0,13)))
pf_conv_hi_ego <- c(rep(0,17),1,(rep(0,12)))
pf_sn_hi_ego <- c(rep(0,18),1,(rep(0,11)))
pf_mn_hi_ego <- c(rep(0,19),1,(rep(0,10)))


sf_cn_low_ego <- c(rep(0,20),1,(rep(0,9))) # self-enhancing framing
sf_dn_low_ego <- c(rep(0,21),1,(rep(0,8)))
sf_conv_low_ego <- c(rep(0,22),1,(rep(0,7)))
sf_sn_low_ego <- c(rep(0,23),1,(rep(0,6)))
sf_mn_low_ego <- c(rep(0,24),1,(rep(0,5)))

sf_cn_hi_ego <- c(rep(0,25),1,(rep(0,4))) 
sf_dn_hi_ego <- c(rep(0,26),1,(rep(0,3)))
sf_conv_hi_ego <- c(rep(0,27),1,(rep(0,2)))
sf_sn_hi_ego <- c(rep(0,28),1,(rep(0,1)))
sf_mn_hi_ego <- c(rep(0,29),1)
```


Effect of norm for people low vs high on egoistic values across framing conditions

#### Control framing
```{r}
controlframe_lowvshi_ego <- contrast(combinations, 
                       method = list("CF/DN/LowEgo - CF/CN/LowEgo" = cf_dn_low_ego - cf_cn_low_ego,
                                     "CF/Conv/LowEgo - CF/CN/LowEgo" = cf_conv_low_ego - cf_cn_low_ego,
                                     "CF/SN/LowEgo - CF/CN/LowEgo" = cf_sn_low_ego - cf_cn_low_ego,
                                     "CF/MN/LowEgo - CF/CN/LowEgo" = cf_mn_low_ego - cf_cn_low_ego,
                                     "CF/DN/HiEgo - CF/CN/HiEgo" = cf_dn_hi_ego - cf_cn_hi_ego,
                                     "CF/Conv/HiEgo - CF/CN/HiEgo" = cf_conv_hi_ego - cf_cn_hi_ego,
                                     "CF/SN/HiEgo - CF/CN/HiEgo" = cf_sn_hi_ego - cf_cn_hi_ego,
                                     "CF/MN/HiEgo - CF/CN/HiEgo" = cf_mn_hi_ego - cf_cn_hi_ego), 
                       adjust = "none")

controlframe_lowvshi_ego %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
controlframe_lowvshi_ego %>% confint() %>%
  knitr::kable(digits = 2)
```

Planned Comparisons

Custom contrasts
```{r}
controlframe_lowvshi_ego

dn_vs_c_LowEgo <- c(1,rep(0,7))
conv_vs_c_LowEgo <- c(0,1,rep(0,6))
sn_vs_c_LowEgo <- c(0,0,1,rep(0,5))
mn_vs_c_LowEgo <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiEgo <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiEgo <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiEgo <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiEgo <- c(rep(0,7),1)
```

```{r}
compare_ego <- contrast(controlframe_lowvshi_ego, method = list("Effect of DN (Low - High ego)" = dn_vs_c_LowEgo - dn_vs_c_HiEgo, 
                                                                "Effect of Conv (Low - High ego)" = conv_vs_c_LowEgo - conv_vs_c_HiEgo,
                                                                "Effect of SN (Low - High ego)" = sn_vs_c_LowEgo - sn_vs_c_HiEgo,
                                                                "Effect of MN (Low - High ego)" = mn_vs_c_LowEgo - mn_vs_c_HiEgo), adjust = "none")

compare_ego %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_ego %>% confint() %>%
  knitr::kable(digits = 2)
```



#### Pro-environmental framing
```{r}
proenvframe_lowvshi_ego <- contrast(combinations, 
                       method = list("PF/DN/LowEgo - PF/CN/LowEgo" = pf_dn_low_ego - pf_cn_low_ego,
                                     "PF/Conv/LowEgo - PF/CN/LowEgo" = pf_conv_low_ego - pf_cn_low_ego,
                                     "PF/SN/LowEgo - PF/CN/LowEgo" = pf_sn_low_ego - pf_cn_low_ego,
                                     "PF/MN/LowEgo - PF/CN/LowEgo" = pf_mn_low_ego - pf_cn_low_ego,
                                     "PF/DN/HiEgo - PF/CN/HiEgo" = pf_dn_hi_ego - pf_cn_hi_ego,
                                     "PF/Conv/HiEgo - PF/CN/HiEgo" = pf_conv_hi_ego - pf_cn_hi_ego,
                                     "PF/SN/HiEgo - PF/CN/HiEgo" = pf_sn_hi_ego - pf_cn_hi_ego,
                                     "PF/MN/HiEgo - PF/CN/HiEgo" = pf_mn_hi_ego - pf_cn_hi_ego), 
                       adjust = "none")

proenvframe_lowvshi_ego %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
proenvframe_lowvshi_ego %>% confint() %>%
  knitr::kable(digits = 2)
```

Planned Comparisons

Custom contrasts
```{r}
proenvframe_lowvshi_ego

dn_vs_c_LowEgo <- c(1,rep(0,7))
conv_vs_c_LowEgo <- c(0,1,rep(0,6))
sn_vs_c_LowEgo <- c(0,0,1,rep(0,5))
mn_vs_c_LowEgo <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiEgo <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiEgo <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiEgo <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiEgo <- c(rep(0,7),1)
```

```{r}
compare_ego <- contrast(proenvframe_lowvshi_ego, method = list("Effect of DN (Low - High ego)" = dn_vs_c_LowEgo - dn_vs_c_HiEgo, 
                                                                "Effect of Conv (Low - High ego)" = conv_vs_c_LowEgo - conv_vs_c_HiEgo,
                                                                "Effect of SN (Low - High ego)" = sn_vs_c_LowEgo - sn_vs_c_HiEgo,
                                                                "Effect of MN (Low - High ego)" = mn_vs_c_LowEgo - mn_vs_c_HiEgo), adjust = "none")

compare_ego %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_ego %>% confint() %>%
  knitr::kable(digits = 2)
```



#### Self-enhancing framing
```{r}
selfenhframe_lowvshi_ego <- contrast(combinations, 
                       method = list("SF/DN/LowEgo - SF/CN/LowEgo" = sf_dn_low_ego - sf_cn_low_ego,
                                     "SF/Conv/LowEgo - SF/CN/LowEgo" = sf_conv_low_ego - sf_cn_low_ego,
                                     "SF/SN/LowEgo - SF/CN/LowEgo" = sf_sn_low_ego - sf_cn_low_ego,
                                     "SF/MN/LowEgo - SF/CN/LowEgo" = sf_mn_low_ego - sf_cn_low_ego,
                                     "SF/DN/HiEgo - SF/CN/HiEgo" = sf_dn_hi_ego - sf_cn_hi_ego,
                                     "SF/Conv/HiEgo - SF/CN/HiEgo" = sf_conv_hi_ego - sf_cn_hi_ego,
                                     "SF/SN/HiEgo - SF/CN/HiEgo" = sf_sn_hi_ego - sf_cn_hi_ego,
                                     "SF/MN/HiEgo - SF/CN/HiEgo" = sf_mn_hi_ego - sf_cn_hi_ego), 
                       adjust = "none")

selfenhframe_lowvshi_ego %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
selfenhframe_lowvshi_ego %>% confint() %>%
  knitr::kable(digits = 2)


```

Planned Comparisons

Custom contrasts
```{r}
selfenhframe_lowvshi_ego

dn_vs_c_LowEgo <- c(1,rep(0,7))
conv_vs_c_LowEgo <- c(0,1,rep(0,6))
sn_vs_c_LowEgo <- c(0,0,1,rep(0,5))
mn_vs_c_LowEgo <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiEgo <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiEgo <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiEgo <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiEgo <- c(rep(0,7),1)
```

```{r}
compare_ego <- contrast(selfenhframe_lowvshi_ego, method = list("Effect of DN (Low - High ego)" = dn_vs_c_LowEgo - dn_vs_c_HiEgo, 
                                                                "Effect of Conv (Low - High ego)" = conv_vs_c_LowEgo - conv_vs_c_HiEgo,
                                                                "Effect of SN (Low - High ego)" = sn_vs_c_LowEgo - sn_vs_c_HiEgo,
                                                                "Effect of MN (Low - High ego)" = mn_vs_c_LowEgo - mn_vs_c_HiEgo), adjust = "none")

compare_ego %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_ego %>% confint() %>%
  knitr::kable(digits = 2)
```




## Hedonic values

### Overall effect

Storing low (-1SD) and high (+1SD) hedonic values
```{r}
sd_below <- mean(average_df$hedonic_center) - sd(average_df$hedonic_center)

sd_above <- mean(average_df$hedonic_center) + sd(average_df$hedonic_center)
```

EMM for low and high hed
```{r}
# emmeans
atlist <- list(hedonic_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ hedonic_center, at = atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMM for low and high hed
```{r}
# custom contrast
low_hed <- c(1,0)
hi_hed <- c(0,1)

# compare
effect_hed <- contrast(emms, method = list("High hed - Low hed" = hi_hed - low_hed), adjust = "none")
effect_hed %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_hed %>% confint() %>%
  knitr::kable(digits = 2)
```


### Framing Condition

EMM for low vs high hed in each framing
```{r}
atlist <- list(hedonic_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ hedonic_center*framing_condition, at=atlist, type = "response")
emms %>% knitr::kable(digits = 6)
```

Compare EMMs for low vs high hed in each framing 
```{r}
# custom contrasts
control_low_hed <- c(1,0,0,0,0,0)
control_hi_hed <- c(0,1,0,0,0,0)
proenv_low_hed <- c(0,0,1,0,0,0)
proenv_hi_hed <- c(0,0,0,1,0,0)
selfenh_low_hed <- c(0,0,0,0,1,0)
self_enh_hi_hed <- c(0,0,0,0,0,1)

# compare
effect_frame_hed <- contrast(emms, method = list("Control: High hed - Low hed" = control_hi_hed - control_low_hed,
                                                 "Pro-env: High hed - Low hed" = proenv_hi_hed - proenv_low_hed,
                                                 "Self-enh: High hed - Low hed" = self_enh_hi_hed - selfenh_low_hed), adjust = "none")
effect_frame_hed %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_frame_hed %>% confint() %>%
  knitr::kable(digits = 2)
```




### Norm Condition

EMM for low vs high hed in each norm
```{r}
atlist <- list(hedonic_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ hedonic_center*norm_condition, at=atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMMs for low vs high hed in each framing 
```{r}
# custom contrasts
control_low_hed <- c(1,rep(0,9))
control_hi_hed <- c(0,1,rep(0,8))
dn_low_hed <- c(0,0,1,rep(0,7))
dn_hi_hed <- c(0,0,0,1,rep(0,6))
conv_low_hed <- c(0,0,0,0,1,rep(0,5))
conv_hi_hed <- c(rep(0,5),1,rep(0,4))
sn_low_hed <- c(rep(0,6),1,0,0,0)
sn_hi_hed <- c(rep(0,7),1,0,0)
mn_low_hed <- c(rep(0,8),1,0)
mn_hi_hed <- c(rep(0,9),1)

# compare
effect_norm_hed <- contrast(emms, method = list("Control: High hed - Low hed" = control_hi_hed - control_low_hed,
                                                 "DN: High hed - Low hed" = dn_hi_hed - dn_low_hed,
                                                 "Conv: High hed - Low hed" = conv_hi_hed - conv_low_hed,
                                                 "SN: High hed - Low hed" = sn_hi_hed - sn_low_hed,
                                                 "MN: High hed - Low hed" = mn_hi_hed - mn_low_hed), adjust = "none")
effect_norm_hed %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_norm_hed %>% confint() %>%
  knitr::kable(digits = 2)
```

Is the difference between Control Norm and Other Norm different for people low vs high on hedonic values? Does this vary across framing conditions?


### Visualizations

```{r}
text_settings <- theme(text = element_text(size = 20)) +
  theme(plot.title = element_text(size = 20, face = 'bold')) +
  theme(axis.title.x = element_text(face = 'bold')) +
  theme(axis.title.y = element_text(face = 'bold')) +
  theme(axis.text.x = element_text(size = 14)) +
  theme(axis.text.y = element_text(size = 20)) +
  theme(axis.ticks = element_blank())
```

#### Hed x Framing
```{r}
sd_below <- mean(average_df$hedonic_center) - sd(average_df$hedonic_center)
sd_above <- mean(average_df$hedonic_center) + sd(average_df$hedonic_center)

at_list <- list(hedonic_center = c(sd_below, sd_above))

emmip(log_mice, hedonic_center ~ framing_condition, CIs = TRUE, type = "response", CIarg = list(lwd = 1.2, alpha = 1), xlab = "Framing Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_framing","pro_env_framing", "self_enh_framing"), labels = c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Hedonic Values", breaks = c(-0.790766915042502, 0.790766915042502), labels = c("-1SD Hedonic", "+1SD Hedonic"), values = c("#00BFC4","#C77CFF"))
  
```

#### Hed x Norm
```{r}
emmip(log_mice, hedonic_center ~ norm_condition, CIs = TRUE, type = "response", CIarg = list(lwd = 1.2, alpha = 1), xlab = "Norm Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels = c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Hedonic Values", breaks = c(-0.790766915042502, 0.790766915042502), labels = c("-1SD Hedonic", "+1SD Hedonic"), values = c("#00BFC4","#C77CFF"))
```


#### Hed, Norm, Framing
```{r}
emmip(log_mice, hedonic_center ~ norm_condition | framing_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 1), xlab = "Norm Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels = c("Control", "Descriptive", "Convention", "Social", "Moral")) +
  facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Hedonic Values", breaks = c(-0.790766915042502, 0.790766915042502), labels = c("-1SD Hedonic", "+1SD Hedonic"), values = c("#00BFC4","#C77CFF"))
  
```


## Planned Comparisons

### Storing low (-1SD) and high (+1SD) hedonic values
```{r}
sd_below <- mean(average_df$hedonic_center) - sd(average_df$hedonic_center)
sd_above <- mean(average_df$hedonic_center) + sd(average_df$hedonic_center)
```


### Calculate EM Means at low and high hed
```{r}
atlist <- list(hedonic_center = c(sd_below, sd_above))

combinations <- emmeans(log_mice, ~ norm_condition*hedonic_center*framing_condition, at=atlist, type = "response")

combinations %>% knitr::kable(digits = 2)
```

### Custom contrasts
```{r}
cf_cn_low_hed <- c(1, rep(0,29)) # control framing
cf_dn_low_hed <- c(0,1,rep(0,28))
cf_conv_low_hed <- c(0,0,1,rep(0,27))
cf_sn_low_hed <- c(0,0,0,1,rep(0,26))
cf_mn_low_hed <- c(rep(0,4),1,(rep(0,25)))

cf_cn_hi_hed <- c(rep(0,5),1,(rep(0,24))) 
cf_dn_hi_hed <- c(rep(0,6),1,(rep(0,23)))
cf_conv_hi_hed <- c(rep(0,7),1,(rep(0,22)))
cf_sn_hi_hed <- c(rep(0,8),1,(rep(0,21)))
cf_mn_hi_hed <- c(rep(0,9),1,(rep(0,20)))


pf_cn_low_hed <- c(rep(0,10),1,(rep(0,19))) # pro-environmental framing
pf_dn_low_hed <- c(rep(0,11),1,(rep(0,18)))
pf_conv_low_hed <- c(rep(0,12),1,(rep(0,17)))
pf_sn_low_hed <- c(rep(0,13),1,(rep(0,16)))
pf_mn_low_hed <- c(rep(0,14),1,(rep(0,15)))

pf_cn_hi_hed <- c(rep(0,15),1,(rep(0,14))) 
pf_dn_hi_hed <- c(rep(0,16),1,(rep(0,13)))
pf_conv_hi_hed <- c(rep(0,17),1,(rep(0,12)))
pf_sn_hi_hed <- c(rep(0,18),1,(rep(0,11)))
pf_mn_hi_hed <- c(rep(0,19),1,(rep(0,10)))


sf_cn_low_hed <- c(rep(0,20),1,(rep(0,9))) # self-enhancing framing
sf_dn_low_hed <- c(rep(0,21),1,(rep(0,8)))
sf_conv_low_hed <- c(rep(0,22),1,(rep(0,7)))
sf_sn_low_hed <- c(rep(0,23),1,(rep(0,6)))
sf_mn_low_hed <- c(rep(0,24),1,(rep(0,5)))

sf_cn_hi_hed <- c(rep(0,25),1,(rep(0,4))) 
sf_dn_hi_hed <- c(rep(0,26),1,(rep(0,3)))
sf_conv_hi_hed <- c(rep(0,27),1,(rep(0,2)))
sf_sn_hi_hed <- c(rep(0,28),1,(rep(0,1)))
sf_mn_hi_hed <- c(rep(0,29),1)
```


Effect of norm for people low vs high on hedonic values across framing conditions

#### Control framing
```{r}
controlframe_lowvshi_hed <- contrast(combinations, 
                       method = list("CF/DN/LowHed - CF/CN/LowHed" = cf_dn_low_hed - cf_cn_low_hed,
                                     "CF/Conv/LowHed - CF/CN/LowHed" = cf_conv_low_hed - cf_cn_low_hed,
                                     "CF/SN/LowHed - CF/CN/LowHed" = cf_sn_low_hed - cf_cn_low_hed,
                                     "CF/MN/LowHed - CF/CN/LowHed" = cf_mn_low_hed - cf_cn_low_hed,
                                     "CF/DN/HiHed - CF/CN/HiHed" = cf_dn_hi_hed - cf_cn_hi_hed,
                                     "CF/Conv/HiHed - CF/CN/HiHed" = cf_conv_hi_hed - cf_cn_hi_hed,
                                     "CF/SN/HiHed - CF/CN/HiHed" = cf_sn_hi_hed - cf_cn_hi_hed,
                                     "CF/MN/HiHed - CF/CN/HiHed" = cf_mn_hi_hed - cf_cn_hi_hed), 
                       adjust = "none")

controlframe_lowvshi_hed %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
controlframe_lowvshi_hed %>% confint() %>%
  knitr::kable(digits = 2)


```

Planned Comparisons

Custom contrasts
```{r}
controlframe_lowvshi_hed

dn_vs_c_LowHed <- c(1,rep(0,7))
conv_vs_c_LowHed <- c(0,1,rep(0,6))
sn_vs_c_LowHed <- c(0,0,1,rep(0,5))
mn_vs_c_LowHed <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiHed <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiHed <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiHed <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiHed <- c(rep(0,7),1)
```

```{r}
compare_hed <- contrast(controlframe_lowvshi_hed, method = list("Effect of DN (Low - High hed)" = dn_vs_c_LowHed - dn_vs_c_HiHed, 
                                                                "Effect of Conv (Low - High hed)" = conv_vs_c_LowHed - conv_vs_c_HiHed,
                                                                "Effect of SN (Low - High hed)" = sn_vs_c_LowHed - sn_vs_c_HiHed,
                                                                "Effect of MN (Low - High hed)" = mn_vs_c_LowHed - mn_vs_c_HiHed), adjust = "none")

compare_hed %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_hed %>% confint() %>%
  knitr::kable(digits = 2)


```



#### Pro-environmental framing
```{r}
proenvframe_lowvshi_hed <- contrast(combinations, 
                       method = list("PF/DN/LowHed - PF/CN/LowHed" = pf_dn_low_hed - pf_cn_low_hed,
                                     "PF/Conv/LowHed - PF/CN/LowHed" = pf_conv_low_hed - pf_cn_low_hed,
                                     "PF/SN/LowHed - PF/CN/LowHed" = pf_sn_low_hed - pf_cn_low_hed,
                                     "PF/MN/LowHed - PF/CN/LowHed" = pf_mn_low_hed - pf_cn_low_hed,
                                     "PF/DN/HiHed - PF/CN/HiHed" = pf_dn_hi_hed - pf_cn_hi_hed,
                                     "PF/Conv/HiHed - PF/CN/HiHed" = pf_conv_hi_hed - pf_cn_hi_hed,
                                     "PF/SN/HiHed - PF/CN/HiHed" = pf_sn_hi_hed - pf_cn_hi_hed,
                                     "PF/MN/HiHed - PF/CN/HiHed" = pf_mn_hi_hed - pf_cn_hi_hed), 
                       adjust = "none")

proenvframe_lowvshi_hed %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
proenvframe_lowvshi_hed %>% confint() %>%
  knitr::kable(digits = 2)


```

Planned Comparisons

Custom contrasts
```{r}
proenvframe_lowvshi_hed

dn_vs_c_LowHed <- c(1,rep(0,7))
conv_vs_c_LowHed <- c(0,1,rep(0,6))
sn_vs_c_LowHed <- c(0,0,1,rep(0,5))
mn_vs_c_LowHed <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiHed <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiHed <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiHed <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiHed <- c(rep(0,7),1)
```

```{r}
compare_hed <- contrast(proenvframe_lowvshi_hed, method = list("Effect of DN (Low - High hed)" = dn_vs_c_LowHed - dn_vs_c_HiHed, 
                                                                "Effect of Conv (Low - High hed)" = conv_vs_c_LowHed - conv_vs_c_HiHed,
                                                                "Effect of SN (Low - High hed)" = sn_vs_c_LowHed - sn_vs_c_HiHed,
                                                                "Effect of MN (Low - High hed)" = mn_vs_c_LowHed - mn_vs_c_HiHed), adjust = "none")

compare_hed %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_hed %>% confint() %>%
  knitr::kable(digits = 2)


```



#### Self-enhancing framing
```{r}
selfenhframe_lowvshi_hed <- contrast(combinations, 
                       method = list("SF/DN/LowHed - SF/CN/LowHed" = sf_dn_low_hed - sf_cn_low_hed,
                                     "SF/Conv/LowHed - SF/CN/LowHed" = sf_conv_low_hed - sf_cn_low_hed,
                                     "SF/SN/LowHed - SF/CN/LowHed" = sf_sn_low_hed - sf_cn_low_hed,
                                     "SF/MN/LowHed - SF/CN/LowHed" = sf_mn_low_hed - sf_cn_low_hed,
                                     "SF/DN/HiHed - SF/CN/HiHed" = sf_dn_hi_hed - sf_cn_hi_hed,
                                     "SF/Conv/HiHed - SF/CN/HiHed" = sf_conv_hi_hed - sf_cn_hi_hed,
                                     "SF/SN/HiHed - SF/CN/HiHed" = sf_sn_hi_hed - sf_cn_hi_hed,
                                     "SF/MN/HiHed - SF/CN/HiHed" = sf_mn_hi_hed - sf_cn_hi_hed), 
                       adjust = "none")

selfenhframe_lowvshi_hed %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
selfenhframe_lowvshi_hed %>% confint() %>%
  knitr::kable(digits = 2)


```

Planned Comparisons

Custom contrasts
```{r}
selfenhframe_lowvshi_hed

dn_vs_c_LowHed <- c(1,rep(0,7))
conv_vs_c_LowHed <- c(0,1,rep(0,6))
sn_vs_c_LowHed <- c(0,0,1,rep(0,5))
mn_vs_c_LowHed <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiHed <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiHed <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiHed <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiHed <- c(rep(0,7),1)
```

```{r}
compare_hed <- contrast(selfenhframe_lowvshi_hed, method = list("Effect of DN (Low - High hed)" = dn_vs_c_LowHed - dn_vs_c_HiHed, 
                                                                "Effect of Conv (Low - High hed)" = conv_vs_c_LowHed - conv_vs_c_HiHed,
                                                                "Effect of SN (Low - High hed)" = sn_vs_c_LowHed - sn_vs_c_HiHed,
                                                                "Effect of MN (Low - High hed)" = mn_vs_c_LowHed - mn_vs_c_HiHed), adjust = "none")

compare_hed %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_hed %>% confint() %>%
  knitr::kable(digits = 2)

```






## Ingroup Identification

### Overall effect

Storing low (-1SD) and high (+1SD) ingroup values
```{r}
sd_below <- mean(average_df$ingroup_center) - sd(average_df$ingroup_center)

sd_above <- mean(average_df$ingroup_center) + sd(average_df$ingroup_center)
```

EMM for low and high ing
```{r}
# emmeans
atlist <- list(ingroup_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ ingroup_center, at = atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMM for low and high ing
```{r}
# custom contrast
low_ing <- c(1,0)
hi_ing <- c(0,1)

# compare
effect_ing <- contrast(emms, method = list("High ing - Low ing" = hi_ing - low_ing), adjust = "none")
effect_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_ing %>% confint() %>%
  knitr::kable(digits = 2)
```


### Framing Condition

EMM for low vs high ing in each framing
```{r}
atlist <- list(ingroup_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ ingroup_center*framing_condition, at=atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMMs for low vs high ing in each framing 
```{r}
# custom contrasts
control_low_ing <- c(1,0,0,0,0,0)
control_hi_ing <- c(0,1,0,0,0,0)
proenv_low_ing <- c(0,0,1,0,0,0)
proenv_hi_ing <- c(0,0,0,1,0,0)
selfenh_low_ing <- c(0,0,0,0,1,0)
self_enh_hi_ing <- c(0,0,0,0,0,1)

# compare
effect_frame_ing <- contrast(emms, method = list("Control: High ing - Low ing" = control_hi_ing - control_low_ing,
                                                 "Pro-env: High ing - Low ing" = proenv_hi_ing - proenv_low_ing,
                                                 "Self-enh: High ing - Low ing" = self_enh_hi_ing - selfenh_low_ing), adjust = "none")
effect_frame_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_frame_ing %>% confint() %>%
  knitr::kable(digits = 2)
```




### Norm Condition

EMM for low vs high ing in each norm
```{r}
atlist <- list(ingroup_center = c(sd_below, sd_above))

emms <- emmeans(log_mice, ~ ingroup_center*norm_condition, at=atlist, type = "response")
emms %>% knitr::kable(digits = 2)
```

Compare EMMs for low vs high ing in each framing 
```{r}
# custom contrasts
control_low_ing <- c(1,rep(0,9))
control_hi_ing <- c(0,1,rep(0,8))
dn_low_ing <- c(0,0,1,rep(0,7))
dn_hi_ing <- c(0,0,0,1,rep(0,6))
conv_low_ing <- c(0,0,0,0,1,rep(0,5))
conv_hi_ing <- c(rep(0,5),1,rep(0,4))
sn_low_ing <- c(rep(0,6),1,0,0,0)
sn_hi_ing <- c(rep(0,7),1,0,0)
mn_low_ing <- c(rep(0,8),1,0)
mn_hi_ing <- c(rep(0,9),1)

# compare
effect_norm_ing <- contrast(emms, method = list("Control: High ing - Low ing" = control_hi_ing - control_low_ing,
                                                 "DN: High ing - Low ing" = dn_hi_ing - dn_low_ing,
                                                 "Conv: High ing - Low ing" = conv_hi_ing - conv_low_ing,
                                                 "SN: High ing - Low ing" = sn_hi_ing - sn_low_ing,
                                                 "MN: High ing - Low ing" = mn_hi_ing - mn_low_ing), adjust = "none")
effect_norm_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
effect_norm_ing %>% confint() %>%
  knitr::kable(digits = 2)
```

>>Exploratory Research Question 1: Is there a three-way interaction between in-group identification, framing condition, and norm-intervention condition?

Is the difference between Control Norm and Other Norm different for people low vs high on ingroup identification? Does this vary across framing conditions?


### Visualization

```{r}
text_settings <- theme(text = element_text(size = 20)) +
  theme(plot.title = element_text(size = 20, face = 'bold')) +
  theme(axis.title.x = element_text(face = 'bold')) +
  theme(axis.title.y = element_text(face = 'bold')) +
  theme(axis.text.x = element_text(size = 14)) +
  theme(axis.text.y = element_text(size = 20)) +
  theme(axis.ticks = element_blank())
```


#### Ingroup x Framing
```{r}
sd_below <- mean(average_df$ingroup_center) - sd(average_df$ingroup_center)
sd_above <- mean(average_df$ingroup_center) + sd(average_df$ingroup_center)

at_list <- list(ingroup_center = c(sd_below, sd_above))

emmip(log_mice, ingroup_center ~ framing_condition, CIs = TRUE, type = "response", CIarg = list(lwd = 1.2, alpha = 1), xlab = "Framing Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_framing","pro_env_framing", "self_enh_framing"), labels = c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Ingroup Identification", breaks = c(-1.01218644014995, 1.01218644014995), labels = c("-1SD Ingroup", "+1SD Ingroup"), values = c("#00BFC4","#C77CFF"))
  
```

#### Ingroup x Norm
```{r}
emmip(log_mice, ingroup_center ~ norm_condition, CIs = TRUE, type = "response", CIarg = list(lwd = 1.2, alpha = 1), xlab = "Norm Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels = c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Ingroup Identification", breaks = c(-1.01218644014995, 1.01218644014995), labels = c("-1SD Ingroup", "+1SD Ingroup"), values = c("#00BFC4","#C77CFF"))
```


#### Ingroup, Norm, Framing

```{r}
emmip(log_mice, ingroup_center ~ norm_condition | framing_condition, type = "response", CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 1), xlab = "Norm Condition", ylab = "Consumer Behaviors", at = at_list) + 
  scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels = c("Control", "Descriptive", "Convention", "Social", "Moral")) +
  facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +
  theme_apa() +
  text_settings +
  scale_color_manual(name = "Ingroup Identification", breaks = c(-1.01218644014995, 1.01218644014995), labels = c("-1SD Ingroup", "+1SD Ingroup"), values = c("#00BFC4","#C77CFF"))
  
```


### Planned Comparisons

#### Storing low (-1SD) and high (+1SD) ingroup identification
```{r}
sd_below <- mean(average_df$ingroup_center) - sd(average_df$ingroup_center)
sd_above <- mean(average_df$ingroup_center) + sd(average_df$ingroup_center)
```


#### Calculate EM Means at low and high ingroup
```{r}
atlist <- list(ingroup_center = c(sd_below, sd_above))

combinations <- emmeans(log_mice, ~ norm_condition*ingroup_center*framing_condition, at=atlist, type = "response")

combinations %>% knitr::kable(digits = 2)
```

### Custom contrasts
```{r}
cf_cn_low_ing <- c(1, rep(0,29)) # control framing
cf_dn_low_ing <- c(0,1,rep(0,28))
cf_conv_low_ing <- c(0,0,1,rep(0,27))
cf_sn_low_ing <- c(0,0,0,1,rep(0,26))
cf_mn_low_ing <- c(rep(0,4),1,(rep(0,25)))

cf_cn_hi_ing <- c(rep(0,5),1,(rep(0,24))) 
cf_dn_hi_ing <- c(rep(0,6),1,(rep(0,23)))
cf_conv_hi_ing <- c(rep(0,7),1,(rep(0,22)))
cf_sn_hi_ing <- c(rep(0,8),1,(rep(0,21)))
cf_mn_hi_ing <- c(rep(0,9),1,(rep(0,20)))


pf_cn_low_ing <- c(rep(0,10),1,(rep(0,19))) # pro-environmental framing
pf_dn_low_ing <- c(rep(0,11),1,(rep(0,18)))
pf_conv_low_ing <- c(rep(0,12),1,(rep(0,17)))
pf_sn_low_ing <- c(rep(0,13),1,(rep(0,16)))
pf_mn_low_ing <- c(rep(0,14),1,(rep(0,15)))

pf_cn_hi_ing <- c(rep(0,15),1,(rep(0,14))) 
pf_dn_hi_ing <- c(rep(0,16),1,(rep(0,13)))
pf_conv_hi_ing <- c(rep(0,17),1,(rep(0,12)))
pf_sn_hi_ing <- c(rep(0,18),1,(rep(0,11)))
pf_mn_hi_ing <- c(rep(0,19),1,(rep(0,10)))


sf_cn_low_ing <- c(rep(0,20),1,(rep(0,9))) # self-enhancing framing
sf_dn_low_ing <- c(rep(0,21),1,(rep(0,8)))
sf_conv_low_ing <- c(rep(0,22),1,(rep(0,7)))
sf_sn_low_ing <- c(rep(0,23),1,(rep(0,6)))
sf_mn_low_ing <- c(rep(0,24),1,(rep(0,5)))

sf_cn_hi_ing <- c(rep(0,25),1,(rep(0,4))) 
sf_dn_hi_ing <- c(rep(0,26),1,(rep(0,3)))
sf_conv_hi_ing <- c(rep(0,27),1,(rep(0,2)))
sf_sn_hi_ing <- c(rep(0,28),1,(rep(0,1)))
sf_mn_hi_ing <- c(rep(0,29),1)
```


Effect of norm for people low vs high on ingroup identification across framing conditions

#### Control framing
```{r}
controlframe_lowvshi_ing <- contrast(combinations, 
                       method = list("CF/DN/LowIng - CF/CN/LowIng" = cf_dn_low_ing - cf_cn_low_ing,
                                     "CF/Conv/LowIng - CF/CN/LowIng" = cf_conv_low_ing - cf_cn_low_ing,
                                     "CF/SN/LowIng - CF/CN/LowIng" = cf_sn_low_ing - cf_cn_low_ing,
                                     "CF/MN/LowIng - CF/CN/LowIng" = cf_mn_low_ing - cf_cn_low_ing,
                                     "CF/DN/HiIng - CF/CN/HiIng" = cf_dn_hi_ing - cf_cn_hi_ing,
                                     "CF/Conv/HiIng - CF/CN/HiIng" = cf_conv_hi_ing - cf_cn_hi_ing,
                                     "CF/SN/HiIng - CF/CN/HiIng" = cf_sn_hi_ing - cf_cn_hi_ing,
                                     "CF/MN/HiIng - CF/CN/HiIng" = cf_mn_hi_ing - cf_cn_hi_ing), 
                       adjust = "sidak")

controlframe_lowvshi_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
controlframe_lowvshi_ing %>% confint() %>%
  knitr::kable(digits = 2)

```

Planned Comparisons

Custom contrasts
```{r}
controlframe_lowvshi_ing

dn_vs_c_LowIng <- c(1,rep(0,7))
conv_vs_c_LowIng <- c(0,1,rep(0,6))
sn_vs_c_LowIng <- c(0,0,1,rep(0,5))
mn_vs_c_LowIng <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiIng <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiIng <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiIng <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiIng <- c(rep(0,7),1)
```

```{r}
compare_ing <- contrast(controlframe_lowvshi_ing, method = list("Effect of DN (Low - High ing)" = dn_vs_c_LowIng - dn_vs_c_HiIng, 
                                                                "Effect of Conv (Low - High ing)" = conv_vs_c_LowIng - conv_vs_c_HiIng,
                                                                "Effect of SN (Low - High ing)" = sn_vs_c_LowIng - sn_vs_c_HiIng,
                                                                "Effect of MN (Low - High ing)" = mn_vs_c_LowIng - mn_vs_c_HiIng), adjust = "sidak")

compare_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_ing %>% confint() %>%
  knitr::kable(digits = 2)

```



#### Pro-environmental framing
```{r}
proenvframe_lowvshi_ing <- contrast(combinations, 
                       method = list("PF/DN/LowIng - PF/CN/LowIng" = pf_dn_low_ing - pf_cn_low_ing,
                                     "PF/Conv/LowIng - PF/CN/LowIng" = pf_conv_low_ing - pf_cn_low_ing,
                                     "PF/SN/LowIng - PF/CN/LowIng" = pf_sn_low_ing - pf_cn_low_ing,
                                     "PF/MN/LowIng - PF/CN/LowIng" = pf_mn_low_ing - pf_cn_low_ing,
                                     "PF/DN/HiIng - PF/CN/HiIng" = pf_dn_hi_ing - pf_cn_hi_ing,
                                     "PF/Conv/HiIng - PF/CN/HiIng" = pf_conv_hi_ing - pf_cn_hi_ing,
                                     "PF/SN/HiIng - PF/CN/HiIng" = pf_sn_hi_ing - pf_cn_hi_ing,
                                     "PF/MN/HiIng - PF/CN/HiIng" = pf_mn_hi_ing - pf_cn_hi_ing), 
                       adjust = "sidak")

proenvframe_lowvshi_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
proenvframe_lowvshi_ing %>% confint() %>%
  knitr::kable(digits = 2)

```

Planned Comparisons

Custom contrasts
```{r}
proenvframe_lowvshi_ing

dn_vs_c_LowIng <- c(1,rep(0,7))
conv_vs_c_LowIng <- c(0,1,rep(0,6))
sn_vs_c_LowIng <- c(0,0,1,rep(0,5))
mn_vs_c_LowIng <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiIng <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiIng <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiIng <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiIng <- c(rep(0,7),1)
```

```{r}
compare_ing <- contrast(proenvframe_lowvshi_ing, method = list("Effect of DN (Low - High ing)" = dn_vs_c_LowIng - dn_vs_c_HiIng, 
                                                                "Effect of Conv (Low - High ing)" = conv_vs_c_LowIng - conv_vs_c_HiIng,
                                                                "Effect of SN (Low - High ing)" = sn_vs_c_LowIng - sn_vs_c_HiIng,
                                                                "Effect of MN (Low - High ing)" = mn_vs_c_LowIng - mn_vs_c_HiIng), adjust = "sidak")

compare_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_ing %>% confint() %>%
  knitr::kable(digits = 2)

```



#### Self-enhancing framing
```{r}
selfenhframe_lowvshi_ing <- contrast(combinations, 
                       method = list("SF/DN/LowIng - SF/CN/LowIng" = sf_dn_low_ing - sf_cn_low_ing,
                                     "SF/Conv/LowIng - SF/CN/LowIng" = sf_conv_low_ing - sf_cn_low_ing,
                                     "SF/SN/LowIng - SF/CN/LowIng" = sf_sn_low_ing - sf_cn_low_ing,
                                     "SF/MN/LowIng - SF/CN/LowIng" = sf_mn_low_ing - sf_cn_low_ing,
                                     "SF/DN/HiIng - SF/CN/HiIng" = sf_dn_hi_ing - sf_cn_hi_ing,
                                     "SF/Conv/HiIng - SF/CN/HiIng" = sf_conv_hi_ing - sf_cn_hi_ing,
                                     "SF/SN/HiIng - SF/CN/HiIng" = sf_sn_hi_ing - sf_cn_hi_ing,
                                     "SF/MN/HiIng - SF/CN/HiIng" = sf_mn_hi_ing - sf_cn_hi_ing), 
                       adjust = "sidak")

selfenhframe_lowvshi_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
selfenhframe_lowvshi_ing %>% confint() %>%
  knitr::kable(digits = 2)


```

Planned Comparisons

Custom contrasts
```{r}
selfenhframe_lowvshi_ing

dn_vs_c_LowIng <- c(1,rep(0,7))
conv_vs_c_LowIng <- c(0,1,rep(0,6))
sn_vs_c_LowIng <- c(0,0,1,rep(0,5))
mn_vs_c_LowIng <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiIng <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiIng <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiIng <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiIng <- c(rep(0,7),1)
```

```{r}
compare_ing <- contrast(selfenhframe_lowvshi_ing, method = list("Effect of DN (Low - High ing)" = dn_vs_c_LowIng - dn_vs_c_HiIng, 
                                                                "Effect of Conv (Low - High ing)" = conv_vs_c_LowIng - conv_vs_c_HiIng,
                                                                "Effect of SN (Low - High ing)" = sn_vs_c_LowIng - sn_vs_c_HiIng,
                                                                "Effect of MN (Low - High ing)" = mn_vs_c_LowIng - mn_vs_c_HiIng), adjust = "sidak")

compare_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
compare_ing %>% confint() %>%
  knitr::kable(digits = 2)

```



>>H5: In-group identification will moderate the effect of norm-intervention condition on peoples clothing consumption intentions and behaviors such that the effect of each norm-intervention condition will be stronger when people are high, versus low, on in-group identification.


### Storing low (-1SD) and high (+1SD) ingroup identification
```{r}
sd_below <- mean(average_df$ingroup_center) - sd(average_df$ingroup_center)
sd_above <- mean(average_df$ingroup_center) + sd(average_df$ingroup_center)
```


### Calculate EM Means at low and high ing
```{r}
atlist <- list(ingroup_center = c(sd_below, sd_above))

combinations <- emmeans(log_mice, ~ norm_condition*ingroup_center, at=atlist, type = "response")

combinations %>% knitr::kable(digits = 2)
```

### Custom contrasts
```{r}
cn_low_ing <- c(1,rep(0,9))
dn_low_ing <- c(0,1,rep(0,8))
conv_low_ing <- c(0,0,1,rep(0,7))
sn_low_ing <- c(rep(0,3),1,rep(0,6))
mn_low_ing <- c(rep(0,4),1,rep(0,5))

cn_hi_ing <- c(rep(0,5),1,rep(0,4))
dn_hi_ing <- c(rep(0,6),1,rep(0,3))
conv_hi_ing <- c(rep(0,7),1,rep(0,2))
sn_hi_ing <- c(rep(0,8),1,rep(0,1))
mn_hi_ing <- c(rep(0,9),1)
```


```{r}
norm_effect_ing <- contrast(combinations, 
                       method = list("DN Low Ing - Control Low Ing" = dn_low_ing - cn_low_ing,
                                     "Conv Low Ing - Control Low Ing" = conv_low_ing - cn_low_ing,
                                     "SN Low Ing - Control Low Ing" = sn_low_ing - cn_low_ing,
                                     "MN Low Ing - Control Low Ing" = mn_low_ing - cn_low_ing,
                                     "DN Hi Ing - Control Hi Ing" = dn_hi_ing - cn_hi_ing,
                                     "Conv Hi Ing - Control Hi Ing" = conv_hi_ing - cn_hi_ing,
                                     "SN Hi Ing - Control Hi Ing" = sn_hi_ing - cn_hi_ing,
                                     "MN Hi Ing - Control Hi Ing" = mn_hi_ing - cn_hi_ing), 
                       adjust = "none")

norm_effect_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
norm_effect_ing %>% confint() %>%
  knitr::kable(digits = 2)


```

Planned Comparisons

Custom contrasts
```{r}
norm_effect_ing

dn_vs_c_LowIng <- c(1,rep(0,7))
conv_vs_c_LowIng <- c(0,1,rep(0,6))
sn_vs_c_LowIng <- c(0,0,1,rep(0,5))
mn_vs_c_LowIng <- c(0,0,0,1,rep(0,4))

dn_vs_c_HiIng <- c(rep(0,4),1,rep(0,3))
conv_vs_c_HiIng <- c(rep(0,5),1,rep(0,2))
sn_vs_c_HiIng <- c(rep(0,6),1,rep(0,1))
mn_vs_c_HiIng <- c(rep(0,7),1)
```

```{r}
norm_compare_ing <- contrast(norm_effect_ing, method = list("Effect of DN (Low - High ing)" = dn_vs_c_LowIng - dn_vs_c_HiIng, 
                                                                "Effect of Conv (Low - High ing)" = conv_vs_c_LowIng - conv_vs_c_HiIng,
                                                                "Effect of SN (Low - High ing)" = sn_vs_c_LowIng - sn_vs_c_HiIng,
                                                                "Effect of MN (Low - High ing)" = mn_vs_c_LowIng - mn_vs_c_HiIng), adjust = "none")

norm_compare_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
norm_compare_ing %>% confint() %>%
  knitr::kable(digits = 2)
```




# updated ingroup interaction examinations

## Ingroup by Norm interaction

### Storing low (-1SD) and high (+1SD) ingroup identification
```{r}
sd_below <- mean(average_df$ingroup_center) - sd(average_df$ingroup_center)
sd_above <- mean(average_df$ingroup_center) + sd(average_df$ingroup_center)
```


### Calculate EM Means 
```{r}
atlist <- list(ingroup_center = c(sd_below, sd_above))

combinations <- emmeans(log_mice, ~ norm_condition*ingroup_center, at=atlist, type = "response")

combinations %>% knitr::kable(digits = 2)
```


### Custom contrasts
```{r}
control_low_ing <- c(1, rep(0,9))
dn_low_ing <- c(0,1,rep(0,8))
conv_low_ing <- c(0,0,1,rep(0,7))
sn_low_ing <- c(0,0,0,1,rep(0,6))
mn_low_ing <- c(rep(0,4),1,(rep(0,5)))

control_hi_ing <- c(rep(0,5),1,rep(0,4))
dn_hi_ing <- c(rep(0,6),1,0,0,0)
conv_hi_ing <- c(rep(0,7),1,0,0)
sn_hi_ing <- c(rep(0,8),1,0)
mn_hi_ing <- c(rep(0,9),1)
```



```{r}
two_way_ing <- contrast(combinations, 
                       method = list("Low Ing: DN - C" = dn_low_ing - control_low_ing,
                                     "Low Ing: Conv - C" = conv_low_ing - control_low_ing,
                                     "Low Ing: SN - C" = sn_low_ing - control_low_ing,
                                     "Low Ing: MN - C" = mn_low_ing - control_low_ing,
                                     "Hi Ing: DN - C" = dn_hi_ing - control_hi_ing,
                                     "Hi Ing: Conv - C" = conv_hi_ing - control_hi_ing,
                                     "Hi Ing: SN - C" = sn_hi_ing - control_hi_ing,
                                     "Hi Ing: MN - C" = mn_hi_ing - control_hi_ing), 
                       adjust = "none")

two_way_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
two_way_ing %>% confint() %>%
  knitr::kable(digits = 2)
```



## Ingroup by framing interaction

### Calculate EM Means 
```{r}
atlist <- list(ingroup_center = c(sd_below, sd_above))

combinations <- emmeans(log_mice, ~ framing_condition*ingroup_center, at=atlist, type = "response")

combinations %>% knitr::kable(digits = 2)
```


Custom contrasts
```{r}
control_low_ing <- c(1, rep(0,5))
pe_low_ing <- c(0,1,rep(0,4))
se_low_ing <- c(0,0,1,rep(0,3))

control_hi_ing <- c(0,0,0,1,0,0)
pe_hi_ing <- c(0,0,0,0,1,0)
se_hi_ing <- c(rep(0,5),1)
```


```{r}
two_way_ing <- contrast(combinations, 
                       method = list("Low Ing: PE - C" = pe_low_ing - control_low_ing,
                                     "Low Ing: SE - C" = se_low_ing - control_low_ing,
                                     "Low Ing: PE - SE" = pe_low_ing - se_low_ing,
                                     "Hi Ing: PE - C" = pe_hi_ing - control_hi_ing,
                                     "Hi Ing: SE - C" = se_hi_ing - control_hi_ing,
                                     "Hi Ing: PE - SE" = pe_hi_ing - se_hi_ing), 
                       adjust = "none")

two_way_ing %>% knitr::kable(digits = c(NA,2,2,2,2,2,3))

# confidence intervals
two_way_ing %>% confint() %>%
  knitr::kable(digits = 2)
```