---
title: "Analysis using Multiple Imputation (scmfcs)"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
date: "2023-03-29"
editor_options:
  chunk_output_type: console
---

To do:
  * add CIs to simple slope comparison tables
    + should CIs or effect sizes be added to anything else?
  * how to test H3?
  * logistic analysis...
  * analysis with missing data...

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r clear environment, echo = FALSE}
rm(list = ls())
```


```{r libraries, message = FALSE, warning = FALSE, include = FALSE}
library(Rmisc)
library(Hmisc)
library(rio)
library(tidyverse)
library(psych)
library(gtools) # rbinding data frames
library(corrplot)
library(jtools) # for pretty printing tables
library(sjPlot) # pretty printing tables
library(sjmisc) # pretty printing
library(mice) # handling missing values
library(naniar) # visualizaing missingness & MCAR test
library(miceadds) # for mi.anova
library(emmeans) # simple effects analyses
library(broom)     # for extracting residuals and outlier indices
library(olsrr)     # for creating outlier plots
library(smcfcs) # for multiple imputation with interactions
library(mitools) # for pooling MI results
library(marginaleffects) # for plotting marginal means 
library(installr)
library(epiDisplay) # for frequency tables
library(papaja) # for APA printing
library(car) # for Anova function (type III ss)
library(lsr) # for etaSquared


options(max.print = 100000) # max rows to print in output
options(scipen = 1000) # turn off sci notation
```

# Data Import & Cleaning

## Import data
```{r import data}
raw_psych_hum_subj <- import("data/raw/raw_psych_hum_subj.csv")
raw_mktg_hum_subj <- import("data/raw/raw_mktg_hum_subj.csv")
raw_gen_uo_pop <- import("data/raw/raw_gen_uo_pop.csv")
pre_fall22 <- import("data/prescreen/dittersdorf_matches_f22.csv")
pre_winter23 <- import("data/prescreen/dittersdorf_matches_w23.csv")
pre_spring23 <- import("data/prescreen/dittersdorf_matches_s23.csv")
participant_list <- import("data/prescreen/dittersdorf_participants.csv")
```



Fix age before converting variable types
```{r}
table(raw_psych_hum_subj$Age) # 18 years old = 18
table(raw_mktg_hum_subj$Age) # 1999 = 24
table(raw_gen_uo_pop$Age)

raw_psych_hum_subj$Age[raw_psych_hum_subj$Age == "18 years old"] <- 18
raw_mktg_hum_subj$Age[raw_mktg_hum_subj$Age == 1999] <- 24

table(raw_psych_hum_subj$Age) # 18 years old = 18
table(raw_mktg_hum_subj$Age) # 1999 = 24
```



## Combine dataframes 
```{r update var types, warning = FALSE}
raw_psych_hum_subj <- raw_psych_hum_subj %>%
  mutate(Age = as.integer(Age),
         Gender = as.factor(Gender),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors),
         skepticism = as.factor(skepticism),
         id = as.factor(id),
         source = strrep("psych_hsp", times = 1))

levels(raw_psych_hum_subj$framing_condition_DO)

raw_mktg_hum_subj <- raw_mktg_hum_subj %>%
  mutate(Age = as.integer(Age),
         Gender = as.factor(Gender),
         Gender_5_TEXT = as.character(Gender_5_TEXT),
         Class_Lvl_7_TEXT = as.character(Class_Lvl_7_TEXT),
         Pol_Ornt_8_TEXT = as.character(Pol_Ornt_8_TEXT),
         Ethnicity_8_TEXT = as.character(Ethnicity_8_TEXT),
         skept_open = as.character(skept_open),
         skepticism = as.factor(skepticism),
         id = as.factor(id),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors),
         source = strrep("mktg_hsp", times = 1))

raw_gen_uo_pop <- raw_gen_uo_pop %>%
  mutate(Gender = as.factor(Gender),
         Gender_5_TEXT = as.character(Gender_5_TEXT),
         Class_Lvl_7_TEXT = as.character(Class_Lvl_7_TEXT),
         Pol_Ornt_8_TEXT = as.character(Pol_Ornt_8_TEXT),
         skept_open = as.character(skept_open),
         skepticism = as.factor(skepticism),
         id = as.factor(id),
         framing_condition_DO = as.factor(framing_condition_DO),
         norm_condition_DO = as.factor(norm_condition_DO),
         consumer_behaviors = as.factor(consumer_behaviors),
         source = strrep("gen_UO", times = 1))
```


Specify unique variables to combine prescreen data sets
```{r prep prescreen dfs}
# Create unique full_name variable
pre_fall22$full_name <- paste(pre_fall22$first_name, pre_fall22$last_name, sep="_")

pre_winter23$full_name <- paste(pre_winter23$first_name, pre_winter23$last_name, sep="_")

pre_spring23$full_name <- paste(pre_spring23$first_name, pre_spring23$last_name, sep="_")

participant_list$full_name <- paste(participant_list$first_name, participant_list$last_name, sep="_")

# Create column indicating which data set rows came from

pre_fall22 <- pre_fall22 %>%
  mutate(term = "fall22")

pre_winter23 <- pre_winter23 %>%
  mutate(term = "winter23")

pre_spring23 <- pre_spring23 %>%
  mutate(term = "spring23")
```


Combine prescreen data
```{r combine prescreen dfs}
combine1 <- smartbind(pre_fall22, pre_winter23)
combined_prescreen <- smartbind(combine1, pre_spring23)

# nrow(pre_fall22) + nrow(pre_winter23) + nrow(pre_spring23) # n = 1167

combined_prescreen_unique <- combined_prescreen[!duplicated(combined_prescreen$full_name), ] # keeps first row (fall22)
```

Subset key variables
```{r subset key vars}
combined_prescreen_key <- combined_prescreen_unique %>%
  dplyr::select(full_name, term, respecting:gratification, honest:gossip)

participant_list_key <- participant_list %>%
  dplyr::select(full_name, survey_id)
```

Merge with participant list
```{r merge participant list}
merged_prescreen <- merge(combined_prescreen_key, participant_list_key, by = "full_name")
```


Rename SDR items to match
```{r clean merged prescreen, warning = FALSE, include = FALSE}
merged_prescreen <- merged_prescreen %>%
  rename("lose_out" = "lose-out", 
         "cover_up" = "cover-up",
         "get_even" = "get-even",
         "behind_back" = "behind-back",
         "private_talk" = "private-talk",
         "take_things" = "take-things",
         "id" = "survey_id")
```

Convert variable types
```{r}
merged_prescreen <- merged_prescreen %>%
  mutate(respecting = as.integer(respecting),
         unity = as.integer(unity),
         protecting = as.integer(protecting),
         preventing = as.integer(preventing),
         equality = as.integer(equality),
         peace = as.integer(peace),
         justice = as.integer(justice),
         helpful = as.integer(helpful),
         power = as.integer(power),
         wealth = as.integer(wealth),
         authority = as.integer(authority),
         influential = as.integer(influential),
         ambition = as.integer(ambition),
         pleasures = as.integer(pleasures),
         enjoying = as.integer(enjoying),
         gratification = as.integer(gratification),
         honest = as.integer(honest),
         like = as.integer(like),
         disturbing = as.integer(disturbing),
         regret = as.integer(regret),
         lose_out = as.integer(lose_out),
         rational = as.integer(rational),
         confident = as.integer(confident),
         lover = as.integer(lover),
         lies = as.integer(lies),
         cover_up = as.integer(cover_up),
         advantage = as.integer(advantage),
         get_even = as.integer(get_even),
         behind_back = as.integer(behind_back),
         private_talk = as.integer(private_talk),
         take_things = as.integer(take_things),
         gossip = as.integer(gossip),
         id = as.factor(id))
```


Rename values & socially desirable items in prescreen data to match names in main data:
```{r rename prescreen vars, include = FALSE}
merged_prescreen <- merged_prescreen %>%
  rename("values_1" = "respecting",
         "values_2" = "unity",
         "values_3" = "protecting",
         "values_4" = "preventing",
         "values_5" = "equality",
         "values_6" = "peace",
         "values_7" = "justice",
         "values_8" = "helpful",
         "values_9" = "power",
         "values_10" = "wealth",
         "values_11" = "authority",
         "values_12" = "influential",
         "values_13" = "ambition",
         "values_14" = "pleasures",
         "values_15" = "enjoying",
         "values_16" = "gratification",
         "socially_desirable_1" = "honest",
         "socially_desirable_2" = "like",
         "socially_desirable_3" = "disturbing",
         "socially_desirable_4" = "regret",
         "socially_desirable_5" = "lose_out",
         "socially_desirable_6" = "rational",
         "socially_desirable_7" = "confident",
         "socially_desirable_8" = "lover",
         "socially_desirable_9" = "lies",
         "socially_desirable_10" = "cover_up",
         "socially_desirable_11" = "advantage",
         "socially_desirable_12" = "get_even",
         "socially_desirable_13" = "behind_back",
         "socially_desirable_14" = "private_talk",
         "socially_desirable_15" = "take_things",
         "socially_desirable_16" = "gossip")
```


Combine all data

- First, combine Psych Hum Subj data with Prescreen data based on `id`
- Second, add Mktg Hum Subj data
- Third, add gen UO Pop data
```{r combine all data}
combine1 <- merge(raw_psych_hum_subj, merged_prescreen, by = "id")
combine2 <- smartbind(combine1, raw_mktg_hum_subj)
combine3 <- smartbind(combine2, raw_gen_uo_pop)
```


## Remove duplicate cases

Identify duplicate cases
```{r id duplicate cases, results = 'hide'}
# first, add unique row #s
combine3 <- combine3 %>%
  mutate(row = 1:nrow(combine3))

combine3[duplicated(combine3$id),] # Only rows 1 through 858 have unique id #s

# write.csv(combine3, "combined_data.csv")
```

Row IDs to remove:

* 13 (participant's second time completing study)
* 134 (participant didn't complete study first time)
* 145 (participant didn't complete study first time)
* 308 (participant's second time completing study)
* 672 (participant's second time completing study)
* 743 (participant didn't complete study first time)
* 790 (participant didn't complete study first time)
* 800 (participant didn't complete study first time)

Remove duplicate rows after resolving:
```{r remove duplicate cases}
combine3 <- combine3 %>%
  filter(!row %in% c(13, 134, 145, 308, 672, 743, 790, 800))
```


## Remove rows of all NAs

Identify completely missing rows:
```{r id all NA rows, results = 'hide'}
key_vars <- combine3 %>%
  dplyr::select(row, big_2_1:big_2_65, consumer_intentions_1:consumer_intentions_9, consumer_behaviors, clothing_interest_1:clothing_interest_20, ingroup_ident_1:ingroup_ident_14, values_1:values_16, socially_desirable_1:socially_desirable_16, source)

ncol(key_vars) # number of columns - the row # & source column = 141

all_NA_rows <- key_vars[rowSums(is.na(key_vars)) == 141,] # identify rows with 141 NAs (all missing values), row numbers are preserved

all_NA_rows
```

Removing rows of fully missing data
```{r remove all NA rows}
data <- combine3 %>%
  dplyr::filter(!row %in% c(859, 860, 900, 926, 927, 941, 1139, 1141, 1142, 1143, 1144, 1146, 1149, 1150, 1152)) %>% # remove rows containing all NAs
  dplyr::select(-StartDate, -EndDate, -Status, -Progress, -"Duration (in seconds)", -Finished, -RecordedDate, -ResponseId, -DistributionChannel, -UserLanguage, -big_2_DO, -consumer_intentions_DO, -consumer_behaviors_DO, -clothing_interest_DO, -ingroup_ident_DO, -full_name, -code, -socially_desirable_DO, -values_DO, -email_giftcard, -term) # removing variables not in analysis
```


## Number per source
```{r}
table(data$source)
```

* 850 = psych human subjects pool
* 276 = mktg human subjects pool
* 7 = general UO pop


Rename variables
```{r rename vars}
data <- data %>%
  rename("framing_condition" = "framing_condition_DO", 
         "norm_condition" = "norm_condition_DO")
```

Drop unused levels
```{r include = FALSE}
levels(data$framing_condition)
levels(data$norm_condition)

data$framing_condition <- droplevels(data$framing_condition)
data$norm_condition <- droplevels(data$norm_condition)

levels(data$framing_condition)
levels(data$norm_condition)
```


Re-order levels of norm condition
```{r}
data$norm_condition <- factor(data$norm_condition, levels = c("control_norm", "descriptive_norm", "convention_norm", "social_norm", "moral_norm"))
```


## Inspect final data 
```{r inspect final df, results = 'hide'}
str(data, list.len = ncol(data))

# write.csv(data, "final_data.csv")
```


# Aggregate Variables 

## Personality

### Reverse-code

```{r reverse personality items}
data_R <- data %>%
  mutate(across(c(big_2_11,
                  big_2_16,
                  big_2_26,
                  big_2_31,
                  big_2_36,
                  big_2_51,
                  big_2_12,
                  big_2_17,
                  big_2_22,
                  big_2_37,
                  big_2_42,
                  big_2_47,
                  big_2_3,
                  big_2_8,
                  big_2_23,
                  big_2_28,
                  big_2_48,
                  big_2_58,
                  big_2_4,
                  big_2_9,
                  big_2_24,
                  big_2_29,
                  big_2_44,
                  big_2_49,
                  big_2_5,
                  big_2_25,
                  big_2_30,
                  big_2_45,
                  big_2_50,
                  big_2_55,
                  big_2_63), ~6 - .)) # replace '6' with the max possible value plus 1 for any particular scale
```

### Average items

```{r aggregate personality}
data_R$extraversion <- data_R %>%
  dplyr::select(big_2_1, big_2_6, big_2_11, big_2_16, big_2_21, big_2_26, big_2_31, big_2_36, big_2_41, big_2_46, big_2_51, big_2_56) %>%
  rowMeans(na.rm = TRUE) 


data_R$conscientiousness <- data_R %>%
  dplyr::select(big_2_3, big_2_8, big_2_13, big_2_18, big_2_23, big_2_28, big_2_33, big_2_38, big_2_43, big_2_48, big_2_53, big_2_58) %>%
  rowMeans(na.rm = TRUE)


data_R$agreeableness <- data_R %>%
  dplyr::select(big_2_2, big_2_7, big_2_12, big_2_17, big_2_22, big_2_27, big_2_32, big_2_37, big_2_42, big_2_47, big_2_52, big_2_57) %>%
  rowMeans(na.rm = TRUE)


data_R$neuroticism <- data_R %>%
  dplyr::select(big_2_4, big_2_9, big_2_14, big_2_19, big_2_24, big_2_29, big_2_34, big_2_39, big_2_44, big_2_49, big_2_54, big_2_59) %>%
  rowMeans(na.rm = TRUE)


data_R$openness <- data_R %>%
  dplyr::select(big_2_5, big_2_10, big_2_15, big_2_20, big_2_25, big_2_30, big_2_35, big_2_40, big_2_45, big_2_50, big_2_55, big_2_60) %>%
  rowMeans(na.rm = TRUE)


data_R$honesty <- data_R %>%
  dplyr::select(big_2_61, big_2_62, big_2_63, big_2_64, big_2_65) %>%
  rowMeans(na.rm = TRUE)
```

### Visually inspect
```{r warning = FALSE}
data_R %>%
  dplyr::select(extraversion, agreeableness, conscientiousness, openness, neuroticism, honesty) %>%
  hist()
```


## Clothing Interest

### Reverse-code

```{r reverse clothing items}
data_R <- data_R %>%
  mutate(across(c(clothing_interest_3,
                  clothing_interest_5,
                  clothing_interest_7,
                  clothing_interest_9,
                  clothing_interest_12,
                  clothing_interest_14,
                  clothing_interest_15,
                  clothing_interest_16,
                  clothing_interest_18,
                  clothing_interest_20), ~6 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```


### Average items
```{r aggregate clothing interest}
data_R$clothing_interest <- data_R %>%
  dplyr::select(clothing_interest_1:clothing_interest_20) %>%
  rowMeans(na.rm = TRUE)
```


### Visually Inspect
```{r}
data_R %>%
  dplyr::select(clothing_interest) %>%
  hist()
```



## In-group Identification

### Reverse-code

No items need to be reverse-coded.

### Average items
```{r aggegate ingroup ident}
data_R$ingroup_identification <- data_R %>%
  dplyr::select(ingroup_ident_1:ingroup_ident_14) %>%
  rowMeans(na.rm = TRUE)
```

### Visually Inspect

```{r}
data_R %>%
  dplyr::select(ingroup_identification) %>%
  hist()
```

## Values

### Reverse-code

No items need to be reverse-coded.

### Recoding scale options

Recoding values:

* -3 = 1
* -2 = 2
* -1 = 3
* 0 = 4
* +1 = 5
* +2 = 6
* +3 = 7

```{r recode values}
table(data_R$values_1)

data_R$values_1_rec <- dplyr::recode(data_R$values_1, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)

table(data_R$values_1_rec)

data_R$values_2_rec <- dplyr::recode(data_R$values_2, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_3_rec <- dplyr::recode(data_R$values_3, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_4_rec <- dplyr::recode(data_R$values_4, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_5_rec <- dplyr::recode(data_R$values_5, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_6_rec <- dplyr::recode(data_R$values_6, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_7_rec <- dplyr::recode(data_R$values_7, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_8_rec <- dplyr::recode(data_R$values_8, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_9_rec <- dplyr::recode(data_R$values_9, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_10_rec <- dplyr::recode(data_R$values_10, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_11_rec <- dplyr::recode(data_R$values_11, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_12_rec <- dplyr::recode(data_R$values_12, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_13_rec <- dplyr::recode(data_R$values_13, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_14_rec <- dplyr::recode(data_R$values_14, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_15_rec <- dplyr::recode(data_R$values_15, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)
data_R$values_16_rec <- dplyr::recode(data_R$values_16, `-3` = 1, `-2` = 2, `-1` = 3, `0` = 4, `1` = 5, `2` = 6, `3` = 7)

table(data_R$values_16)
table(data_R$values_16_rec)
```


### Average items
```{r aggregate values}
data_R$biospheric <- data_R %>%
  dplyr::select(values_1_rec:values_4_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$altruistic <- data_R %>%
  dplyr::select(values_5_rec:values_8_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$egoistic <- data_R %>%
  dplyr::select(values_9_rec:values_13_rec) %>%
  rowMeans(na.rm = TRUE)

data_R$hedonic <- data_R %>%
  dplyr::select(values_14_rec:values_16_rec) %>%
  rowMeans(na.rm = TRUE)
```


### Visually inspect
```{r}
values_df <- data_R %>%
  dplyr::select(biospheric, altruistic, egoistic, hedonic)

values_df %>%
  hist()
```

### Frequency tables
```{r}
# Biospheric values
tab1(values_df$biospheric, sort.group = "descending", cum.percent = TRUE, missing = FALSE, horiz = TRUE)

# Altruistic values
tab1(values_df$altruistic, sort.group = "descending", cum.percent = TRUE, missing = FALSE, horiz = TRUE)

# Egoistic values
tab1(values_df$egoistic, sort.group = "descending", cum.percent = TRUE, missing = FALSE, horiz = TRUE)

# Hedonic values
tab1(values_df$hedonic, sort.group = "descending", cum.percent = TRUE, missing = FALSE, horiz = TRUE)
```




## Socially Desirable Responding

### Reverse-code
```{r reverse code socially desirable items}
data_R <- data_R %>%
  mutate(across(c(socially_desirable_1,
                  socially_desirable_3,
                  socially_desirable_5,
                  socially_desirable_8,
                  socially_desirable_9,
                  socially_desirable_11,
                  socially_desirable_12,
                  socially_desirable_13), ~8 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```

### Average items
```{r aggregate socially desirable}
data_R$self_deceptive_sdr <- data_R %>%
  dplyr::select(socially_desirable_1:socially_desirable_8) %>%
  rowMeans(na.rm = TRUE)
  
data_R$impress_manag_sdr <- data_R %>%
  dplyr::select(socially_desirable_9:socially_desirable_16) %>%
  rowMeans(na.rm = TRUE)
```

### Visually inspect

```{r warning = FALSE}
data_R %>%
  dplyr::select(self_deceptive_sdr, impress_manag_sdr) %>%
  hist()
```


## Consumer Intentions

### Reverse-code

Higher scores mean better consumer intentions (intentions to *reduce* future consumption):
```{r reverse code consumer intentions}
data_R <- data_R %>%
  mutate(across(c(consumer_intentions_2,
                  consumer_intentions_4,
                  consumer_intentions_7,
                  consumer_intentions_9), ~8 - .)) # replace '#' with the max possible value plus 1 for any particular scale
```

### Average items

```{r aggregate consumer intentions}
data_R$consumer_intentions <- data_R %>%
  dplyr::select(consumer_intentions_1:consumer_intentions_9) %>%
  rowMeans(na.rm = TRUE)
```

### Visually inspect

```{r warning = FALSE}
data_R %>%
  dplyr::select(consumer_intentions) %>%
  hist()
```




# Contrast Coding 

Subset variables
```{r echo = FALSE}
data_R_alt <- data_R %>%
  dplyr::select(hedonic, egoistic, altruistic, biospheric, ingroup_identification, Age, clothing_interest, self_deceptive_sdr, impress_manag_sdr, consumer_intentions, consumer_behaviors, Gender, framing_condition, norm_condition)
```

Contrast Coding using ifelse() approach:
```{r alt coding}
# Framing
data_R_alt$FramingCode1 <- ifelse(data_R_alt$framing_condition == "control_framing", -1/2, ifelse(data_R_alt$framing_condition == "self_enh_framing", 1/2, 0))

data_R_alt$FramingCode2 <- ifelse(data_R_alt$framing_condition == "pro_env_framing", 2/3, -1/3)


# Norm
data_R_alt$NormCode1 <- ifelse(data_R_alt$norm_condition == "moral_norm", 4, -1)

data_R_alt$NormCode2 <- ifelse(data_R_alt$norm_condition == "social_norm", 3, ifelse(data_R_alt$norm_condition == "moral_norm", 0, -1))

data_R_alt$NormCode3 <- ifelse(data_R_alt$norm_condition == "convention_norm", 2, ifelse(data_R_alt$norm_condition == "moral_norm", 0, ifelse(data_R_alt$norm_condition == "social_norm", 0, -1)))
data_R_alt$NormCode4 <- ifelse(data_R_alt$norm_condition == "descriptive_norm", 1, ifelse(data_R_alt$norm_condition == "control_norm", -1, 0))


## Adding contrast codes to Framing & Norm Condition
# Framing
FrameCode1 <- c(-1/2, 0, 1/2) # control vs self-enhancing
FrameCode2 <- c(-1/3, 2/3, -1/3) # arbitrary code

contrasts(data_R_alt$framing_condition) <- cbind(FrameCode1, FrameCode2)
contrasts(data_R_alt$framing_condition)

# Norm
contrasts(data_R_alt$norm_condition) <- contr.helmert(5)
contrasts(data_R_alt$norm_condition) # control vs DN

# Gender
levels(data_R_alt$Gender) <- c("Woman", "Man", "Non-binary", "I prefer not to identify", "Other")

data_R_alt$Gender[data_R_alt$Gender == "Non-binary"] <- NA
data_R_alt$Gender[data_R_alt$Gender == "I prefer not to identify"] <- NA
data_R_alt$Gender[data_R_alt$Gender == "Other"] <- NA

data_R_alt$Gender <- droplevels(data_R_alt$Gender)


contrasts(data_R_alt$Gender) <- c(1, 0)
levels(data_R_alt$Gender)
```


# Multiple Imputation 

## Examine Missingness

```{r}
data_R_alt %>%
  vis_miss()
```

Variables with NO missing data:

* ingroup_identification
* clothing_interest
* consumer_intentions
* framing_condition
* norm_condition


## Adding interaction terms
```{r include = FALSE}
data_R_alt <- data_R_alt %>%
  mutate(framing1Xbiospheric = (FramingCode1)*(biospheric),
         framing2Xbiospheric = (FramingCode2)*(biospheric),
         norm1Xbiospheric = (NormCode1)*(biospheric),
         norm2Xbiospheric = (NormCode2)*(biospheric),
         norm3Xbiospheric = (NormCode3)*(biospheric),
         norm4Xbiospheric = (NormCode4)*(biospheric),
         framing1Xnorm1Xbiospheric = (FramingCode1)*(NormCode1)*(biospheric),
         framing1Xnorm2Xbiospheric = (FramingCode1)*(NormCode2)*(biospheric),
         framing1Xnorm3Xbiospheric = (FramingCode1)*(NormCode3)*(biospheric),
         framing1Xnorm4Xbiospheric = (FramingCode1)*(NormCode4)*(biospheric),
         framing2Xnorm1Xbiospheric = (FramingCode2)*(NormCode1)*(biospheric),
         framing2Xnorm2Xbiospheric = (FramingCode2)*(NormCode2)*(biospheric),
         framing2Xnorm3Xbiospheric = (FramingCode2)*(NormCode3)*(biospheric),
         framing2Xnorm4Xbiospheric = (FramingCode2)*(NormCode4)*(biospheric),
         
         framing1Xaltruistic = (FramingCode1)*(altruistic),
         framing2Xaltruistic = (FramingCode2)*(altruistic),
         norm1Xaltruistic = (NormCode1)*(altruistic),
         norm2Xaltruistic = (NormCode2)*(altruistic),
         norm3Xaltruistic = (NormCode3)*(altruistic),
         norm4Xaltruistic = (NormCode4)*(altruistic),
         framing1Xnorm1Xaltruistic = (FramingCode1)*(NormCode1)*(altruistic),
         framing1Xnorm2Xaltruistic = (FramingCode1)*(NormCode2)*(altruistic),
         framing1Xnorm3Xaltruistic = (FramingCode1)*(NormCode3)*(altruistic),
         framing1Xnorm4Xaltruistic = (FramingCode1)*(NormCode4)*(altruistic),
         framing2Xnorm1Xaltruistic = (FramingCode2)*(NormCode1)*(altruistic),
         framing2Xnorm2Xaltruistic = (FramingCode2)*(NormCode2)*(altruistic),
         framing2Xnorm3Xaltruistic = (FramingCode2)*(NormCode3)*(altruistic),
         framing2Xnorm4Xaltruistic = (FramingCode2)*(NormCode4)*(altruistic),
         
         framing1Xegoistic = (FramingCode1)*(egoistic),
         framing2Xegoistic = (FramingCode2)*(egoistic),
         norm1Xegoistic = (NormCode1)*(egoistic),
         norm2Xegoistic = (NormCode2)*(egoistic),
         norm3Xegoistic = (NormCode3)*(egoistic),
         norm4Xegoistic = (NormCode4)*(egoistic),
         framing1Xnorm1Xegoistic = (FramingCode1)*(NormCode1)*(egoistic),
         framing1Xnorm2Xegoistic = (FramingCode1)*(NormCode2)*(egoistic),
         framing1Xnorm3Xegoistic = (FramingCode1)*(NormCode3)*(egoistic),
         framing1Xnorm4Xegoistic = (FramingCode1)*(NormCode4)*(egoistic),
         framing2Xnorm1Xegoistic = (FramingCode2)*(NormCode1)*(egoistic),
         framing2Xnorm2Xegoistic = (FramingCode2)*(NormCode2)*(egoistic),
         framing2Xnorm3Xegoistic = (FramingCode2)*(NormCode3)*(egoistic),
         framing2Xnorm4Xegoistic = (FramingCode2)*(NormCode4)*(egoistic),
         
         framing1Xhedonic = (FramingCode1)*(hedonic),
         framing2Xhedonic = (FramingCode2)*(hedonic),
         norm1Xhedonic = (NormCode1)*(hedonic),
         norm2Xhedonic = (NormCode2)*(hedonic),
         norm3Xhedonic = (NormCode3)*(hedonic),
         norm4Xhedonic = (NormCode4)*(hedonic),
         framing1Xnorm1Xhedonic = (FramingCode1)*(NormCode1)*(hedonic),
         framing1Xnorm2Xhedonic = (FramingCode1)*(NormCode2)*(hedonic),
         framing1Xnorm3Xhedonic = (FramingCode1)*(NormCode3)*(hedonic),
         framing1Xnorm4Xhedonic = (FramingCode1)*(NormCode4)*(hedonic),
         framing2Xnorm1Xhedonic = (FramingCode2)*(NormCode1)*(hedonic),
         framing2Xnorm2Xhedonic = (FramingCode2)*(NormCode2)*(hedonic),
         framing2Xnorm3Xhedonic = (FramingCode2)*(NormCode3)*(hedonic),
         framing2Xnorm4Xhedonic = (FramingCode2)*(NormCode4)*(hedonic),
         
         framing1Xingroup = (FramingCode1)*(ingroup_identification),
         framing2Xingroup = (FramingCode2)*(ingroup_identification),
         norm1Xingroup = (NormCode1)*(ingroup_identification),
         norm2Xingroup = (NormCode2)*(ingroup_identification),
         norm3Xingroup = (NormCode3)*(ingroup_identification),
         norm4Xingroup = (NormCode4)*(ingroup_identification),
         framing1Xnorm1Xingroup = (FramingCode1)*(NormCode1)*(ingroup_identification),
         framing1Xnorm2Xingroup = (FramingCode1)*(NormCode2)*(ingroup_identification),
         framing1Xnorm3Xingroup = (FramingCode1)*(NormCode3)*(ingroup_identification),
         framing1Xnorm4Xingroup = (FramingCode1)*(NormCode4)*(ingroup_identification),
         framing2Xnorm1Xingroup = (FramingCode2)*(NormCode1)*(ingroup_identification),
         framing2Xnorm2Xingroup = (FramingCode2)*(NormCode2)*(ingroup_identification),
         framing2Xnorm3Xingroup = (FramingCode2)*(NormCode3)*(ingroup_identification),
         framing2Xnorm4Xingroup = (FramingCode2)*(NormCode4)*(ingroup_identification))
```



## Imputation model

```{r}
set.seed(114950518)
```

- check out mice.impute.smcfcs 

```{r echo = FALSE}
imps <- smcfcs(data_R_alt, 
               smtype = "lm", 
               smformula = "consumer_intentions ~ framing_condition + norm_condition + framing_condition*norm_condition + ingroup_identification + framing1Xingroup + framing2Xingroup + norm1Xingroup + norm2Xingroup + norm3Xingroup + norm4Xingroup + framing1Xnorm1Xingroup + framing1Xnorm2Xingroup + framing1Xnorm3Xingroup + framing1Xnorm4Xingroup + framing2Xnorm1Xingroup + framing2Xnorm2Xingroup + framing2Xnorm3Xingroup + framing2Xnorm4Xingroup + clothing_interest + self_deceptive_sdr + impress_manag_sdr + biospheric + framing1Xbiospheric + framing2Xbiospheric + norm1Xbiospheric + norm2Xbiospheric + norm3Xbiospheric + norm4Xbiospheric + framing1Xnorm1Xbiospheric + framing1Xnorm2Xbiospheric + framing1Xnorm3Xbiospheric + framing1Xnorm4Xbiospheric + framing2Xnorm1Xbiospheric + framing2Xnorm2Xbiospheric + framing2Xnorm3Xbiospheric + framing2Xnorm4Xbiospheric + altruistic + framing1Xaltruistic + framing2Xaltruistic + norm1Xaltruistic + norm2Xaltruistic + norm3Xaltruistic + norm4Xaltruistic + framing1Xnorm1Xaltruistic + framing1Xnorm2Xaltruistic + framing1Xnorm3Xaltruistic + framing1Xnorm4Xaltruistic + framing2Xnorm1Xaltruistic + framing2Xnorm2Xaltruistic + framing2Xnorm3Xaltruistic + framing2Xnorm4Xaltruistic + egoistic + framing1Xegoistic + framing2Xegoistic + norm1Xegoistic + norm2Xegoistic + norm3Xegoistic + norm4Xegoistic + framing1Xnorm1Xegoistic + framing1Xnorm2Xegoistic + framing1Xnorm3Xegoistic + framing1Xnorm4Xegoistic + framing2Xnorm1Xegoistic + framing2Xnorm2Xegoistic + framing2Xnorm3Xegoistic + framing2Xnorm4Xegoistic + hedonic + framing1Xhedonic + framing2Xhedonic + norm1Xhedonic + norm2Xhedonic + norm3Xhedonic + norm4Xhedonic + framing1Xnorm1Xhedonic + framing1Xnorm2Xhedonic + framing1Xnorm3Xhedonic + framing1Xnorm4Xhedonic + framing2Xnorm1Xhedonic + framing2Xnorm2Xhedonic + framing2Xnorm3Xhedonic + framing2Xnorm4Xhedonic + consumer_behaviors + Gender + Age", 
               method = c("norm","norm","norm","norm","","norm","","norm","norm","","logreg","logreg","","","","","","","","","FramingCode1*biospheric","FramingCode2*biospheric","NormCode1*biospheric","NormCode2*biospheric","NormCode3*biospheric","NormCode4*biospheric","FramingCode1*NormCode1*biospheric","FramingCode1*NormCode2*biospheric","FramingCode1*NormCode3*biospheric","FramingCode1*NormCode4*biospheric","FramingCode2*NormCode1*biospheric","FramingCode2*NormCode2*biospheric","FramingCode2*NormCode3*biospheric","FramingCode2*NormCode4*biospheric","FramingCode1*altruistic","FramingCode2*altruistic","NormCode1*altruistic","NormCode2*altruistic","NormCode3*altruistic","NormCode4*altruistic","FramingCode1*NormCode1*altruistic","FramingCode1*NormCode2*altruistic","FramingCode1*NormCode3*altruistic","FramingCode1*NormCode4*altruistic","FramingCode2*NormCode1*altruistic","FramingCode2*NormCode2*altruistic","FramingCode2*NormCode3*altruistic","FramingCode2*NormCode4*altruistic","FramingCode1*egoistic","FramingCode2*egoistic","NormCode1*egoistic","NormCode2*egoistic","NormCode3*egoistic","NormCode4*egoistic","FramingCode1*NormCode1*egoistic","FramingCode1*NormCode2*egoistic","FramingCode1*NormCode3*egoistic","FramingCode1*NormCode4*egoistic","FramingCode2*NormCode1*egoistic","FramingCode2*NormCode2*egoistic","FramingCode2*NormCode3*egoistic","FramingCode2*NormCode4*egoistic","FramingCode1*hedonic","FramingCode2*hedonic","NormCode1*hedonic","NormCode2*hedonic","NormCode3*hedonic","NormCode4*hedonic","FramingCode1*NormCode1*hedonic","FramingCode1*NormCode2*hedonic","FramingCode1*NormCode3*hedonic","FramingCode1*NormCode4*hedonic","FramingCode2*NormCode1*hedonic","FramingCode2*NormCode2*hedonic","FramingCode2*NormCode3*hedonic","FramingCode2*NormCode4*hedonic","","","","","","","","","","","","","",""))
```


Storing imputed data sets
```{r echo = FALSE}
impobject <- imputationList(imps$impDatasets)
```

## Centering continuous predictors
```{r echo = FALSE}
# Biospheric values
impobject$imputations[[1]]$biospheric_center <- impobject$imputations[[1]]$biospheric - mean(impobject$imputations[[1]]$biospheric)

impobject$imputations[[2]]$biospheric_center <- impobject$imputations[[2]]$biospheric - mean(impobject$imputations[[2]]$biospheric)

impobject$imputations[[3]]$biospheric_center <- impobject$imputations[[3]]$biospheric - mean(impobject$imputations[[3]]$biospheric)

impobject$imputations[[4]]$biospheric_center <- impobject$imputations[[4]]$biospheric - mean(impobject$imputations[[4]]$biospheric)

impobject$imputations[[5]]$biospheric_center <- impobject$imputations[[5]]$biospheric - mean(impobject$imputations[[5]]$biospheric)


# Altruistic values
impobject$imputations[[1]]$altruistic_center <- impobject$imputations[[1]]$altruistic - mean(impobject$imputations[[1]]$altruistic)

impobject$imputations[[2]]$altruistic_center <- impobject$imputations[[2]]$altruistic - mean(impobject$imputations[[2]]$altruistic)

impobject$imputations[[3]]$altruistic_center <- impobject$imputations[[3]]$altruistic - mean(impobject$imputations[[3]]$altruistic)

impobject$imputations[[4]]$altruistic_center <- impobject$imputations[[4]]$altruistic - mean(impobject$imputations[[4]]$altruistic)

impobject$imputations[[5]]$altruistic_center <- impobject$imputations[[5]]$altruistic - mean(impobject$imputations[[5]]$altruistic)


# Egoistic values
impobject$imputations[[1]]$egoistic_center <- impobject$imputations[[1]]$egoistic - mean(impobject$imputations[[1]]$egoistic)

impobject$imputations[[2]]$egoistic_center <- impobject$imputations[[2]]$egoistic - mean(impobject$imputations[[2]]$egoistic)

impobject$imputations[[3]]$egoistic_center <- impobject$imputations[[3]]$egoistic - mean(impobject$imputations[[3]]$egoistic)

impobject$imputations[[4]]$egoistic_center <- impobject$imputations[[4]]$egoistic - mean(impobject$imputations[[4]]$egoistic)

impobject$imputations[[5]]$egoistic_center <- impobject$imputations[[5]]$egoistic - mean(impobject$imputations[[5]]$egoistic)


# Hedonic values
impobject$imputations[[1]]$hedonic_center <- impobject$imputations[[1]]$hedonic - mean(impobject$imputations[[1]]$hedonic)

impobject$imputations[[2]]$hedonic_center <- impobject$imputations[[2]]$hedonic - mean(impobject$imputations[[2]]$hedonic)

impobject$imputations[[3]]$hedonic_center <- impobject$imputations[[3]]$hedonic - mean(impobject$imputations[[3]]$hedonic)

impobject$imputations[[4]]$hedonic_center <- impobject$imputations[[4]]$hedonic - mean(impobject$imputations[[4]]$hedonic)

impobject$imputations[[5]]$hedonic_center <- impobject$imputations[[5]]$hedonic - mean(impobject$imputations[[5]]$hedonic)



# Ingroup identification
impobject$imputations[[1]]$ingroup_center <- impobject$imputations[[1]]$ingroup_identification - mean(impobject$imputations[[1]]$ingroup_identification)

impobject$imputations[[2]]$ingroup_center <- impobject$imputations[[2]]$ingroup_identification - mean(impobject$imputations[[2]]$ingroup_identification)

impobject$imputations[[3]]$ingroup_center <- impobject$imputations[[3]]$ingroup_identification - mean(impobject$imputations[[3]]$ingroup_identification)

impobject$imputations[[4]]$ingroup_center <- impobject$imputations[[4]]$ingroup_identification - mean(impobject$imputations[[4]]$ingroup_identification)

impobject$imputations[[5]]$ingroup_center <- impobject$imputations[[5]]$ingroup_identification - mean(impobject$imputations[[5]]$ingroup_identification)


# Age
impobject$imputations[[1]]$Age_center <- impobject$imputations[[1]]$Age - mean(impobject$imputations[[1]]$Age)

impobject$imputations[[2]]$Age_center <- impobject$imputations[[2]]$Age - mean(impobject$imputations[[2]]$Age)

impobject$imputations[[3]]$Age_center <- impobject$imputations[[3]]$Age - mean(impobject$imputations[[3]]$Age)

impobject$imputations[[4]]$Age_center <- impobject$imputations[[4]]$Age - mean(impobject$imputations[[4]]$Age)

impobject$imputations[[5]]$Age_center <- impobject$imputations[[5]]$Age - mean(impobject$imputations[[5]]$Age)



# Clothing interest
impobject$imputations[[1]]$clothing_center <- impobject$imputations[[1]]$clothing_interest - mean(impobject$imputations[[1]]$clothing_interest)

impobject$imputations[[2]]$clothing_center <- impobject$imputations[[2]]$clothing_interest - mean(impobject$imputations[[2]]$clothing_interest)

impobject$imputations[[3]]$clothing_center <- impobject$imputations[[3]]$clothing_interest - mean(impobject$imputations[[3]]$clothing_interest)

impobject$imputations[[4]]$clothing_center <- impobject$imputations[[4]]$clothing_interest - mean(impobject$imputations[[4]]$clothing_interest)

impobject$imputations[[5]]$clothing_center <- impobject$imputations[[5]]$clothing_interest - mean(impobject$imputations[[5]]$clothing_interest)



# Self deceptive SDR
impobject$imputations[[1]]$self_dec_center <- impobject$imputations[[1]]$self_deceptive_sdr - mean(impobject$imputations[[1]]$self_deceptive_sdr)

impobject$imputations[[2]]$self_dec_center <- impobject$imputations[[2]]$self_deceptive_sdr - mean(impobject$imputations[[2]]$self_deceptive_sdr)

impobject$imputations[[3]]$self_dec_center <- impobject$imputations[[3]]$self_deceptive_sdr - mean(impobject$imputations[[3]]$self_deceptive_sdr)

impobject$imputations[[4]]$self_dec_center <- impobject$imputations[[4]]$self_deceptive_sdr - mean(impobject$imputations[[4]]$self_deceptive_sdr)

impobject$imputations[[5]]$self_dec_center <- impobject$imputations[[5]]$self_deceptive_sdr - mean(impobject$imputations[[5]]$self_deceptive_sdr)


# Impression management SDR
impobject$imputations[[1]]$impress_manag_center <- impobject$imputations[[1]]$impress_manag_sdr - mean(impobject$imputations[[1]]$impress_manag_sdr)

impobject$imputations[[2]]$impress_manag_center <- impobject$imputations[[2]]$impress_manag_sdr - mean(impobject$imputations[[2]]$impress_manag_sdr)

impobject$imputations[[3]]$impress_manag_center <- impobject$imputations[[3]]$impress_manag_sdr - mean(impobject$imputations[[3]]$impress_manag_sdr)

impobject$imputations[[4]]$impress_manag_center <- impobject$imputations[[4]]$impress_manag_sdr - mean(impobject$imputations[[4]]$impress_manag_sdr)

impobject$imputations[[5]]$impress_manag_center <- impobject$imputations[[5]]$impress_manag_sdr - mean(impobject$imputations[[5]]$impress_manag_sdr)


# Coding Gender
contrasts(impobject$imputations[[1]]$Gender) <- c(1/2, -1/2)
contrasts(impobject$imputations[[2]]$Gender) <- c(1/2, -1/2)
contrasts(impobject$imputations[[3]]$Gender) <- c(1/2, -1/2)
contrasts(impobject$imputations[[4]]$Gender) <- c(1/2, -1/2)
contrasts(impobject$imputations[[5]]$Gender) <- c(1/2, -1/2)
```



Convert `scmfcs` object to a `mids` object (to make the object compatible with `mice`, and thus, `emmeans`):
```{r}
mids_obj <- datlist2mids(impobject)
```

Complete data set:
```{r complete imputed data set, include = FALSE}
complete_data <- complete(mids_obj, "long")
```



# Regression Analysis (DV = Consumer Intentions)

## Running Model
```{r echo = FALSE}
mod_mice <- with(mids_obj, lm(consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center))
```

```{r echo = FALSE}
pool_obj <- pool(mod_mice)
pool_obj
```


## Pooled Regression Results

Using `mice` package:
```{r echo = FALSE}
pool_summ <- summary(pool(mod_mice))
pool_summ %>%
  knitr::kable(digits = 5)
```

APA style table for regression summary
```{r}
apa_table(pool_summ,
          caption = "Table 1 Pooled Regression Results",
          note = "DV = Consumer Intentions")
```





## Standardized Regression Coefficients

Using scale()
```{r echo = FALSE}
mod_mice_std <- with(mids_obj, lm(scale(consumer_intentions) ~ framing_condition*norm_condition*scale(biospheric) + framing_condition*norm_condition*scale(altruistic) + framing_condition*norm_condition*scale(egoistic) + framing_condition*norm_condition*scale(hedonic) + framing_condition*norm_condition*scale(ingroup_identification) + scale(self_deceptive_sdr) + scale(impress_manag_sdr) + scale(clothing_interest) + Gender + scale(Age)))
```


```{r}
pool_summ_std <- summary(pool(mod_mice_std))

pool_summ_std %>%
  knitr::kable(digits = 5)
```

APA style table for regression summary
```{r}
apa_table(pool_summ_std,
          caption = "Table 1b Pooled Standardized Regression Results",
          note = "DV = Consumer Intentions")
```



## Pooled Anova Results


Using Anova()
```{r echo = FALSE, warning = FALSE}
anova_mod2 <- with(mids_obj, Anova(lm(consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center), type = "III"))
```

```{r}
anova_mod2
```




Using mi.anova()
```{r}
anova_mod3 <- mi.anova(mi.res = mids_obj, formula = "consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center", type = 3)
```

```{r}
anova_mod3 %>%
  knitr::kable(digits = c(2, 2, 2, 2, 3, 3, 3))
```

```{r}
MS_btw <- (67.71/1)
MS_wth <- (1185.172/1038)
F <- MS_btw/MS_wth
F # 59.459
```


## Analysis in each imputed data set 

### Imputed Data 1
```{r echo = FALSE}
#data_imp1a <- complete_data %>%
 # filter(.imp == 1)

data_imp1 <- impobject$imputations[[1]]

mod_mice_imp1 <-lm(consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center, data = data_imp1)
```

#### Regression summary
```{r include = FALSE}
summary_imp1 <- summary(mod_mice_imp1)
summary_imp1
```

Succinct summary
```{r echo = FALSE}
summary_imp1_print <- summary_imp1$coefficients

summary_imp1_print  %>%
  knitr::kable(digits = c(2, 2, 2, 3))
```


APA style table for regression summary
```{r}
apa_summ_imp1 <- apa_print(summary_imp1)

apa_summ_imp1$table %>%
apa_table(caption = "Table 2 Regression Results Using Imputed Data 1",
          note = "DV = Consumer Intentions")
```


Standardized regression coefficients
```{r include = FALSE}
std_imp1 <- lm(scale(consumer_intentions) ~ framing_condition*norm_condition*scale(biospheric) + framing_condition*norm_condition*scale(altruistic) + framing_condition*norm_condition*scale(egoistic) + framing_condition*norm_condition*scale(hedonic) + framing_condition*norm_condition*scale(ingroup_identification) + scale(self_deceptive_sdr) + scale(impress_manag_sdr) + scale(clothing_interest) + Gender + scale(Age), data = data_imp1)

summ_std_imp1 <- summary(std_imp1)
```

APA summary of standardized coefficients
```{r}
print_summ_std_imp1 <- apa_print(summ_std_imp1)

apa_table(print_summ_std_imp1)
```


#### ANOVA summary
```{r}
anova(mod_mice_imp1) %>%
  knitr::kable(digits = c(1, 2, 2, 2, 3))
```

Effect Size
```{r}
etaSquared(mod_mice_imp1) %>% 
  knitr::kable(digits = 3)
```


### Imputed Data 2
```{r}
data_imp2 <- impobject$imputations[[2]]

mod_mice_imp2 <-lm(consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center, data = data_imp2)
```

#### Regression summary
```{r include = FALSE, echo = FALSE}
summary_imp2 <- summary(mod_mice_imp2)
summary_imp2
```

Succinct summary
```{r echo = FALSE} 
summary_imp2$coefficients %>%
  knitr::kable(digits = c(2, 2, 2, 3))
```

APA style table for regression summary
```{r}
apa_summ_imp2 <- apa_print(summary_imp2)

apa_summ_imp2$table %>%
apa_table(caption = "Table 3 Regression Results Using Imputed Data 2",
          note = "DV = Consumer Intentions")
```


Standardized regression coefficients
```{r include = FALSE}
std_imp2 <- lm(scale(consumer_intentions) ~ framing_condition*norm_condition*scale(biospheric) + framing_condition*norm_condition*scale(altruistic) + framing_condition*norm_condition*scale(egoistic) + framing_condition*norm_condition*scale(hedonic) + framing_condition*norm_condition*scale(ingroup_identification) + scale(self_deceptive_sdr) + scale(impress_manag_sdr) + scale(clothing_interest) + Gender + scale(Age), data = data_imp2)

summ_std_imp2 <- summary(std_imp2)
```

APA summary of standardized coefficients
```{r}
print_summ_std_imp2 <- apa_print(summ_std_imp2)

apa_table(print_summ_std_imp2)
```


#### ANOVA summary
```{r}
anova(mod_mice_imp2) %>%
  knitr::kable(digits = c(1, 2, 2, 2, 3))
```

Effect Size
```{r}
etaSquared(mod_mice_imp2) %>% 
  knitr::kable(digits = 3)
```


### Imputed Data 3
```{r echo = FALSE}
data_imp3 <- impobject$imputations[[3]]

mod_mice_imp3 <-lm(consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center, data = data_imp3)
```

#### Regression summary
```{r include = FALSE, echo = FALSE}
summary_imp3 <- summary(mod_mice_imp3)
summary_imp3
```

Succinct summary
```{r}
summary_imp3$coefficients %>%
  knitr::kable(digits = c(2, 2, 2, 3))
```

APA style table for regression summary
```{r}
apa_summ_imp3 <- apa_print(summary_imp3)

apa_summ_imp3$table %>%
apa_table(caption = "Table 4 Regression Results Using Imputed Data 3",
          note = "DV = Consumer Intentions")
```


Standardized regression coefficients
```{r include = FALSE}
std_imp3 <- lm(scale(consumer_intentions) ~ framing_condition*norm_condition*scale(biospheric) + framing_condition*norm_condition*scale(altruistic) + framing_condition*norm_condition*scale(egoistic) + framing_condition*norm_condition*scale(hedonic) + framing_condition*norm_condition*scale(ingroup_identification) + scale(self_deceptive_sdr) + scale(impress_manag_sdr) + scale(clothing_interest) + Gender + scale(Age), data = data_imp3)

summ_std_imp3 <- summary(std_imp3)
```

APA summary of standardized coefficients
```{r}
print_summ_std_imp3 <- apa_print(summ_std_imp3)

apa_table(print_summ_std_imp1)
```


#### ANOVA summary
```{r}
anova(mod_mice_imp3) %>%
  knitr::kable(digits = c(1, 2, 2, 2, 3))
```

Effect Size
```{r}
etaSquared(mod_mice_imp3) %>% 
  knitr::kable(digits = 3)
```


### Imputed Data 4
```{r echo = FALSE}
data_imp4 <- impobject$imputations[[4]]

mod_mice_imp4 <-lm(consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center, data = data_imp4)
```

#### Regression summary
```{r include = FALSE, echo = FALSE}
summary_imp4 <- summary(mod_mice_imp4)
summary_imp4
```

Succinct summary
```{r echo = FALSE}
summary_imp4$coefficients %>%
  knitr::kable(digits = c(2, 2, 2, 3))
```


APA style table for regression summary
```{r}
apa_summ_imp4 <- apa_print(summary_imp4)

apa_summ_imp4$table %>%
apa_table(caption = "Table 5 Regression Results Using Imputed Data 4",
          note = "DV = Consumer Intentions")
```


Standardized regression coefficients
```{r include = FALSE}
std_imp4 <- lm(scale(consumer_intentions) ~ framing_condition*norm_condition*scale(biospheric) + framing_condition*norm_condition*scale(altruistic) + framing_condition*norm_condition*scale(egoistic) + framing_condition*norm_condition*scale(hedonic) + framing_condition*norm_condition*scale(ingroup_identification) + scale(self_deceptive_sdr) + scale(impress_manag_sdr) + scale(clothing_interest) + Gender + scale(Age), data = data_imp4)

summ_std_imp4 <- summary(std_imp4)
```

APA summary of standardized coefficients
```{r}
print_summ_std_imp4 <- apa_print(summ_std_imp4)

apa_table(print_summ_std_imp4)
```


#### ANOVA summary
```{r}
anova(mod_mice_imp4) %>%
  knitr::kable(digits = c(1, 2, 2, 2, 3))
```

Effect Size
```{r}
etaSquared(mod_mice_imp4) %>% 
  knitr::kable(digits = 3)
```



### Imputed Data 5
```{r echo = FALSE}
data_imp5 <- impobject$imputations[[5]]

mod_mice_imp5 <-lm(consumer_intentions ~ framing_condition*norm_condition*biospheric_center + framing_condition*norm_condition*altruistic_center + framing_condition*norm_condition*egoistic_center + framing_condition*norm_condition*hedonic_center + framing_condition*norm_condition*ingroup_center + self_dec_center + impress_manag_center + clothing_center + Gender + Age_center, data = data_imp5)
```

#### Regression summary
```{r include = FALSE, echo = FALSE}
summary_imp5 <- summary(mod_mice_imp5)
summary_imp5
```

Succinct summary
```{r echo = FALSE}
summary_imp5$coefficients %>%
  knitr::kable(digits = c(2, 2, 2, 3))
```

APA style table for regression summary
```{r}
apa_summ_imp5 <- apa_print(summary_imp5)

apa_summ_imp5$table %>%
apa_table(caption = "Table 6 Regression Results Using Imputed Data 5",
          note = "DV = Consumer Intentions")
```


Standardized regression coefficients
```{r include = FALSE}
std_imp5 <- lm(scale(consumer_intentions) ~ framing_condition*norm_condition*scale(biospheric) + framing_condition*norm_condition*scale(altruistic) + framing_condition*norm_condition*scale(egoistic) + framing_condition*norm_condition*scale(hedonic) + framing_condition*norm_condition*scale(ingroup_identification) + scale(self_deceptive_sdr) + scale(impress_manag_sdr) + scale(clothing_interest) + Gender + scale(Age), data = data_imp5)

summ_std_imp5 <- summary(std_imp5)
```

APA summary of standardized coefficients
```{r}
print_summ_std_imp5 <- apa_print(summ_std_imp5)

apa_table(print_summ_std_imp5)
```


#### ANOVA summary
```{r}
anova(mod_mice_imp5) %>%
  knitr::kable(digits = c(1, 2, 2, 2, 3))
```

Effect Size
```{r}
etaSquared(mod_mice_imp5) %>% 
  knitr::kable(digits = 3)
```




## Simple Effects

Averaging scores across imputations
```{r}
complete_data_subset <- complete_data %>%
  dplyr::select(.imp, .id, consumer_intentions, consumer_behaviors, Gender, framing_condition, norm_condition, biospheric_center, altruistic_center, egoistic_center, hedonic_center, ingroup_center, Age_center, clothing_center, self_dec_center, impress_manag_center)

average_df <- complete_data_subset %>% 
  group_by(.id) %>%
  transmute(.imp = .imp, 
            consumer_behaviors = consumer_behaviors, 
            Gender = Gender,
            framing_condition = framing_condition,
            norm_condition = norm_condition,
            biospheric_center = mean(biospheric_center),
         altruistic_center = mean(altruistic_center),
         egoistic_center = mean(egoistic_center),
         hedonic_center = mean(hedonic_center),
         ingroup_center = mean(ingroup_center),
         Age_center = mean(Age_center),
         clothing_center = mean(clothing_center),
         self_dec_center = mean(self_dec_center),
         impress_manag_center = mean(impress_manag_center),
         consumer_intentions = mean(consumer_intentions))


average_df <- average_df %>%
  filter(.imp == 1)
```


Labels to use with facet_wrap
```{r}
norm_labs <- c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")
names(norm_labs) <- c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm")

frame_labs <- c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")
names(frame_labs) <- c("control_framing","pro_env_framing","self_enh_framing")
```


Text Settings
```{r}
text_settings <- theme(text = element_text(size = 20)) +
  theme(plot.title = element_text(size = 20, face = 'bold')) +
  theme(axis.title.x = element_text(face = 'bold')) +
  theme(axis.title.y = element_text(face = 'bold')) +
  theme(axis.text.x = element_text(size = 20)) +
  theme(axis.text.y = element_text(size = 20)) +
  theme(axis.ticks = element_blank())
```


### Framing Condition

>>H1: Consumer intentions/behaviors will be lower in the self-enhancing framing than in the pro-environmental or control framing conditions.

Comparing each level of framing condition
```{r}
frame_means <- emmeans(mod_mice, pairwise ~ framing_condition, adjust = "none")

frame_means$emmeans %>%
  knitr::kable(digits = 2)

frame_means$contrasts %>%
  knitr::kable(digits = 3)
```


```{r}
# without data overlaid
emmip(mod_mice, ~ framing_condition, CIs = TRUE, CIarg = list(lwd = 2, alpha = 0.5), xlab = "Framing Condition", ylab = "Consumer Intentions") + scale_x_discrete(breaks=c("control_framing","pro_env_framing","self_enh_framing"),
        labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +theme_apa() + text_settings
                                                                                                                      
# with data overlaid (scores averaged across imputations)
emmip(mod_mice, ~ framing_condition, CIs = TRUE, CIarg = list(lwd = 1, alpha = 0.5), xlab = "Framing Condition", ylab = "Consumer Intentions") + geom_point(data = average_df, aes(x = framing_condition, y = consumer_intentions), alpha = 0.1, color = "blue") + scale_x_discrete(breaks=c("control_framing","pro_env_framing","self_enh_framing"),
        labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) + theme_apa() + text_settings
```


* Intentions are highest in the pro-environmental condition

* No significant difference in consumer intentions between the pro-environmental and self-enhancing framing conditions, t(1039) = 1.33, p = .184
* No significant difference in consumer intentions between the pro-environmental and control framing conditions, t(1039) = -1.85, p = .064
* No significant difference in consumer intentions between the self-enhancing and control framing conditions, t(1039) = -0.54, p = .592


Effect Sizes (Cohen's D)
```{r}
sigma_pool <- mean(pool_obj$glanced$sigma)
df_resid_pool <- mean(pool_obj$glanced$df.residual)

eff_size(frame_means, sigma = sigma_pool, edf = df_resid_pool) %>% knitr::kable(digits = 2)
```


### Norm Condition

>>H2: Consumer intentions/behaviors will be lower in each norm condition compared to the control norm condition.

Comparing each level of norm condition:
```{r}
norm_means <- emmeans(mod_mice, pairwise ~ norm_condition, adjust = "none")

norm_means$emmeans %>% 
  knitr::kable(digits = 2)

norm_means$contrasts %>%
  knitr::kable(digits = 3)
```


```{r}
# without data overlaid
emmip(mod_mice, ~ norm_condition, CIs = TRUE, CIarg = list(lwd = 2, alpha = 0.5), xlab = "Norm Condition", ylab = "Consumer Intentions") + scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"),
        labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + theme_apa() + text_settings

# with data overlaid
emmip(mod_mice, ~ norm_condition, CIs = TRUE, xlab = "Norm Condition", ylab = "Consumer Intentions") + geom_point(data = average_df, aes(x = norm_condition, y = consumer_intentions), alpha = 0.1, color = "blue") + scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + theme_apa() + text_settings
```


* There was no significant difference between any norm condition compared to the control condition (all ps > .129)

Effect Sizes (Cohen's D):
```{r}
eff_size(norm_means, sigma = sigma_pool, edf = df_resid_pool) %>%
  knitr::kable(digits = 2)
```


Exploratory finding:

* Intentions were significantly higher in the convention versus the social norm condition, t(1039) = 2.20, p = .028.



### Framing X Norm

>>H3: There will be a two-way interaction between framing & norm condition such that the effect of each norm will be stronger in the self-enhancing framing than in the pro-environmental or control framing conditions.


Effect of norm condition at each level of framing condition:
```{r}
cell_means <- emmeans(mod_mice, pairwise ~ norm_condition | framing_condition, adjust = "none")

cell_means$emmeans %>%
  knitr::kable(digits = 2)

cell_means$contrasts %>%
  knitr::kable(digits = 3)
```



```{r}
# without data overlaid
emmip(mod_mice, framing_condition ~ norm_condition, CIs = TRUE, CIarg = list(lwd = 2, alpha = 0.5), xlab = "Norm Condition", ylab = "Consumer Intentions") + scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"),
        labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) + theme_apa() + text_settings

# with data overlaid
emmip(mod_mice, ~ norm_condition | framing_condition, CIs = TRUE, CIarg = list(lwd = 1, alpha = 0.5), xlab = "Norm Condition", ylab = "Consumer Intentions") + geom_point(data = average_df, aes(x = norm_condition, y = consumer_intentions, color = norm_condition), alpha = 0.2, show.legend = FALSE) + scale_x_discrete(breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"),
        labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) + theme_apa() + text_settings
```

* Differences between the control norm condition & other norm conditions were not significant within any of the framing conditions.

Effect Sizes (Cohen's D):
```{r}
eff_size(cell_means, sigma = sigma_pool, edf = df_resid_pool) %>%
  knitr::kable(digits = 2)
```

Exploratory finding:

* In the control framing condition, consumer intentions were close to being significantly higher in the convention norm condition (M = 4.51) compared to the social norm condition (M = 4.17), Mdiff = 0.34, t(1039) = 1.91, p = .056



Comparing consumer intentions for each norm condition between each framing condition:
```{r}
# Control norm
chosen_values <- list(norm_condition = c("control_norm"), framing_condition = c("control_framing", "pro_env_framing", "self_enh_framing"))

control_norm_means <- emmeans(mod_mice, pairwise ~ norm_condition*framing_condition, at = chosen_values, adjust = "none")

control_norm_means$emmeans %>% 
  knitr::kable(digits = 2)

control_norm_means$contrasts %>%
  knitr::kable(digits = 3)

eff_size(control_norm_means, sigma = sigma_pool, edf = df_resid_pool) %>%
  knitr::kable(digits = 2)
```



```{r}
# Descriptive norm
chosen_values <- list(norm_condition = c("descriptive_norm"), framing_condition = c("control_framing", "pro_env_framing", "self_enh_framing"))

descr_norm_means <- emmeans(mod_mice, pairwise ~ norm_condition*framing_condition, at = chosen_values, adjust = "none")

descr_norm_means$emmeans %>%
  knitr::kable(digits = 2)

descr_norm_means$contrasts %>%
  knitr::kable(digits = 3)

eff_size(descr_norm_means, sigma = sigma_pool, edf = df_resid_pool) %>%
  knitr::kable(digits = 2)
```



```{r}
# Convention norm
chosen_values <- list(norm_condition = c("convention_norm"), framing_condition = c("control_framing", "pro_env_framing", "self_enh_framing"))

conv_norm_means <- emmeans(mod_mice, pairwise ~ norm_condition*framing_condition, at = chosen_values, adjust = "none")

conv_norm_means$emmeans %>%
  knitr::kable(digits = 2)

conv_norm_means$contrasts %>%
  knitr::kable(digits = 3)

eff_size(conv_norm_means, sigma = sigma_pool, edf = df_resid_pool) %>%
  knitr::kable(digits = 2)
```



```{r}
# Social norm
chosen_values <- list(norm_condition = c("social_norm"), framing_condition = c("control_framing", "pro_env_framing", "self_enh_framing"))

soc_norm_means <- emmeans(mod_mice, pairwise ~ norm_condition*framing_condition, at = chosen_values, adjust = "none")

soc_norm_means$emmeans %>%
  knitr::kable(digits = 2)

soc_norm_means$contrasts %>%
  knitr::kable(digits = 3)

eff_size(soc_norm_means, sigma = sigma_pool, edf = df_resid_pool) %>%
  knitr::kable(digits = 2)
```



```{r}
# Moral norm
chosen_values <- list(norm_condition = c("moral_norm"), framing_condition = c("control_framing", "pro_env_framing", "self_enh_framing"))

moral_norm_means <- emmeans(mod_mice, pairwise ~ norm_condition*framing_condition, at = chosen_values, adjust = "none")

moral_norm_means$emmeans %>%
  knitr::kable(digits = 2)

moral_norm_means$contrasts %>%
  knitr::kable(digits = 3)

eff_size(moral_norm_means, sigma = sigma_pool, edf = df_resid_pool) %>%
  knitr::kable(digits = 2)
```



### Values Interactions

>>H4: There will be a three-way interaction between values (biospheric, egoistic, altruistic, hedonic), framing condition, & norm condition such that when a pro-environmental or control framing is used, values will moderate the effect of each norm condition, but not when a self-enhancing framing is used.


### Biospheric Values

First, relationship between biospheric values & consumer intentions for each norm condition:
```{r}
bio_norm_means <- emtrends(mod_mice, ~norm_condition, var = "biospheric_center", adjust = "none")

bio_norm_means %>%
  knitr::kable(digits = 2)

bio_norm_contr <- contrast(bio_norm_means, "pairwise")

bio_norm_contr %>%
  knitr::kable(digits = 3)
```

Confidence interval
```{r}
confint(bio_norm_contr) %>%
  knitr:kable(digits = 2)
```


```{r}
# On a single graph
describe(average_df$biospheric_center)
at_list <- list(biospheric_center = seq(-4.9, 1.2, by = 1)) # add .05 to the bounds set by min and max

# without data overlaid
emmip(mod_mice, norm_condition ~ biospheric_center, at = at_list, CIs = TRUE, CIarg = list(lwd = 1, alpha = 0.8), xlab = "Biospheric Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"),
        labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + theme_apa() + text_settings


# with data overlaid
emmip(mod_mice, ~ biospheric_center | norm_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 0.8, alpha = 0.5), xlab = "Biospheric Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + geom_point(data = average_df, aes(x = biospheric_center, y = consumer_intentions, color = norm_condition), alpha = 0.5) + facet_wrap(~norm_condition, labeller = labeller(norm_condition = norm_labs)) + theme_apa() + text_settings
```

* Biospheric values was a significant, positive predictor of consumer intentions in all norm conditions except for the moral norm conditions in which it was a non-significant, positive predictor.



Is the slope of the relationship between biospheric values & consumer intentions stronger in any one of the norm conditions compared to the others?

```{r}
bio_norm_slopes <- emtrends(mod_mice, pairwise~norm_condition, var = "biospheric_center", adjust = "none")

bio_norm_slopes$emtrends %>%
  knitr::kable(digits = 2)

bio_norm_slopes$contrasts %>%
  knitr::kable(digits = 3)
```

Confidence interval
```{r}
confint(bio_norm_slopes$contrasts) %>%
  knitr:kable(digits = 2)
```

The relationship between biospheric values and consumer intentions was significantly stronger in the convention norm condition (b = 0.61) compared to the moral norm condition (b = 0.20), t(1039) = -2.69, p = .007, and in the convention norm condition compared to the social norm condition (b = 0.26), t(1039) = 2.49, p = .013, and in the convention norm condition compared to the descriptive norm condition (b = 0.32), t(1039) = -1.98, p = .048.



Second, relationship between biospheric values & consumer intentions for each framing condition:
```{r}
bio_frame_slopes <- emtrends(mod_mice, ~framing_condition, var = "biospheric_center", adjust = "none")

bio_frame_slopes %>% 
  knitr::kable(digits = 2)
```

Confidence interval
```{r}
confint(bio_frame_slopes) %>%
  knitr:kable(digits = 2)
```

```{r}
# without data overlaid
emmip(mod_mice, framing_condition ~ biospheric_center, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.5, alpha = 0.6), xlab = "Biospheric Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"),
        labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) + theme_apa() + text_settings

# with data overlaid
emmip(mod_mice, ~ biospheric_center | framing_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 0.8, alpha = 0.5), xlab = "Biospheric Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) + geom_point(data = average_df, aes(x = biospheric_center, y = consumer_intentions, color = framing_condition), alpha = 0.5) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) + theme_apa() + text_settings
```

* Biospheric values were significantly, positively related to consumer intentions in all framing conditions.


Is the slope of the relationship between biospheric values & consumer intentions stronger in any one of the framing conditions compared to the others?

```{r}
bio_frame_trends <- emtrends(mod_mice, pairwise~framing_condition, var = "biospheric_center", adjust = "none")

bio_frame_trends$emtrends %>%
  knitr::kable(digits = 2)

bio_frame_trends$contrasts %>%
  knitr::kable(digits = 3)
```

Confidence interval
```{r}
confint(bio_frame_trends$contrasts) %>%
  knitr:kable(digits = 2)
```

No, the relationship between biospheric values and consumer intentions was similarly strong across all framing conditions.


Third, interaction between biospheric values, framing, & norm condition:
```{r}
bio_frame_norm_trends <- emtrends(mod_mice, pairwise~norm_condition | framing_condition, var = "biospheric_center", adjust = "none")

bio_frame_norm_trends$emtrends %>%
  knitr::kable(digits = 2)

bio_frame_norm_trends$contrasts %>%
  knitr::kable(digits = 3)
```

Confidence interval
```{r}
confint(bio_frame_norm_trends$contrasts) %>%
  knitr:kable(digits = 2)
```


```{r}
# without data overlaid
emmip(mod_mice, norm_condition ~ biospheric_center | framing_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Biospheric Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) + theme_apa() + text_settings


# with data overlaid - doesn't work
```

* In the control framing condition, biospheric values were significantly, positively related to consumer intentions in the **control norm**, **descriptive norm**, and **convention** conditions but non-significantly, negatively related in the **social norm** and **moral norm** conditions.

* In the pro-environmental framing condition, biospheric values were significantly, positively related to consumer intentions in the **convention**, **social norm** and **moral norm** conditions, and non-significantly, positively related in the **control norm** and **descriptive norm** conditions.

* In the self-enhancing framing condition, biospheric values were significantly, positively related to consumer intentions in the **control norm** condition, but non-significantly, positively related in all other norm conditions.



### Altruistic Values


First, relationship between altruistic values & consumer intentions for each norm condition:
```{r}
emtrends(mod_mice, ~norm_condition, var = "altruistic_center", adjust = "none") %>%
  knitr::kable(digits = 2)
```


```{r}
# On a single graph
describe(average_df$altruistic_center)
at_list <- list(altruistic_center = seq(-5.26, 0.84, by = 1))

# without data overlaid
emmip(mod_mice, norm_condition ~ altruistic_center, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Altruistic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) +theme_apa() + text_settings


# with data overlaid
emmip(mod_mice, ~ altruistic_center | norm_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 0.8, alpha = 0.5), xlab = "Altruistic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + geom_point(data = average_df, aes(x = altruistic_center, y = consumer_intentions, color = norm_condition), alpha = 0.5) + facet_wrap(~norm_condition, labeller = labeller(norm_condition = norm_labs)) +theme_apa() + text_settings

```

* Altruistic values was a non-significant predictor of consumer intentions in the **control norm**, **descriptive norm**, **convention**, and **social norm** conditions.

* Altruistic values was a significant, positive predictor of consumer intentions in the **moral norm** condition.



Is the slope of the relationship between altruistic values & consumer intentions stronger in any one of the norm conditions compared to the others?

```{r}
alt_norm_trends <- emtrends(mod_mice, pairwise~norm_condition, var = "altruistic_center", adjust = "none")

alt_norm_trends$emtrends %>%
  knitr::kable(digits = 2)

alt_norm_trends$contrasts %>%
  knitr::kable(digits = 3)
```

Confidence interval
```{r}
confint(alt_norm_trends$contrasts) %>%
  knitr:kable(digits = 2)
```

The relationship between altruistic values and consumer intentions was significantly stronger in the moral norm condition (b = 0.36) compared to the descriptive norm condition (b = -0.10), t(1039) = -2.46, p = .014.

The relationship between altruistic values and consumer intentions was also significantly stronger in the moral norm condition (b = 0.36) compared to the convention norm condition (b = -0.05), t(1039) = -2.17, p = .031. 



Second, relationship between altruistic values & consumer intentions for each framing condition:
```{r}
emtrends(mod_mice, ~framing_condition, var = "altruistic_center", adjust = "none") %>%
  knitr::kable(digits = 2)
```

```{r}
# without data overlaid
emmip(mod_mice, framing_condition ~ altruistic_center, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Altruistic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +theme_apa() + text_settings

# with data overlaid
emmip(mod_mice, ~ altruistic_center | framing_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 0.8, alpha = 0.5), xlab = "Altruistic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) + geom_point(data = average_df, aes(x = altruistic_center, y = consumer_intentions, color = framing_condition), alpha = 0.5) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +theme_apa() + text_settings
```

* Altruistic values are positively, but non-significantly, related to consumer intentions in each framing condition.


Is the slope of the relationship between altruistic values & consumer intentions stronger in any one of the framing conditions compared to the others?

```{r}
alt_frame_trends <- emtrends(mod_mice, pairwise~framing_condition, var = "altruistic_center", adjust = "none")

alt_frame_trends$emtrends %>%
  knitr::kable(digits = 2)

alt_frame_trends$contrasts %>%
  knitr::kable(digits = 3)
```


Confidence interval
```{r}
confint(alt_frame_trends$contrasts) %>%
  knitr:kable(digits = 2)
```

No, the difference between any two slopes was not significant.
 



Third, interaction between altruistic values, framing, & norm condition:
```{r}
emtrends(mod_mice, ~norm_condition | framing_condition, var = "altruistic_center", adjust = "none") %>%
  knitr::kable(digits = 2)
```


```{r}
# without data overlaid
emmip(mod_mice, norm_condition ~ altruistic_center | framing_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Altruistic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +theme_apa() + text_settings
```

* In the control framing condition, altruistic values were not significantly related to consumer intentions in any of the norm conditions.

* In the pro-environmental framing condition, altruistic values were not significantly related to consumer intentions in any of the norm conditions.

* In the self-enhancing framing condition, altruistic values were significantly, positively related to consumer intentions in the **moral norm** condition, but non-significantly related in all other norm conditions.

  




### Egoistic Values

First, relationship between egoistic values & consumer intentions for each norm condition:
```{r}
emtrends(mod_mice, ~norm_condition, var = "egoistic_center", adjust = "none") %>%
  knitr::kable(digits = 2)
```


```{r}
# On a single graph
describe(average_df$egoistic_center)
at_list <- list(egoistic_center = seq(-3.45, 2.05, by = 1))

# without data overlaid
emmip(mod_mice, norm_condition ~ egoistic_center, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Egoistic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) +theme_apa() + text_settings


# with data overlaid
emmip(mod_mice, ~ egoistic_center | norm_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 0.8, alpha = 0.5), xlab = "Egoistic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + geom_point(data = average_df, aes(x = egoistic_center, y = consumer_intentions, color = norm_condition), alpha = 0.5) + facet_wrap(~norm_condition, labeller = labeller(norm_condition = norm_labs)) +theme_apa() + text_settings
```

* Egoistic values were a significant, negative predictor of consumer intentions within each norm condition


Is the slope of the relationship between egoistic values & consumer intentions stronger in any one of the norm conditions compared to the others?

```{r}
ego_norm_trends <- emtrends(mod_mice, pairwise~norm_condition, var = "egoistic_center", adjust = "none")

ego_norm_trends$emtrends %>%
  knitr::kable(digits = 2)

ego_norm_trends$contrasts %>%
  knitr::kable(digits = 3)
```


Confidence interval
```{r}
confint(ego_norm_trends$contrasts) %>%
  knitr:kable(digits = 2)
```

No, the difference between any two slopes was not significant.



Second, relationship between egoistic values & consumer intentions for each framing condition:
```{r}
emtrends(mod_mice, ~framing_condition, var = "egoistic_center", adjust = "none") %>%
  knitr::kable(digits = 2)
```


```{r}
# without data overlaid
emmip(mod_mice, framing_condition ~ egoistic_center, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Egoistic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +theme_apa() + text_settings

# with data overlaid
emmip(mod_mice, ~ egoistic_center | framing_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 0.8, alpha = 0.5), xlab = "Egoistic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) + geom_point(data = average_df, aes(x = egoistic_center, y = consumer_intentions, color = framing_condition), alpha = 0.5) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +theme_apa() + text_settings
```

* Egoistic values were a significant, negative predictor of consumer intentions within each framing condition


Is the slope of the relationship between egoistic values & consumer intentions stronger in any one of the framing conditions compared to the others?

```{r}
ego_frame_trends <- emtrends(mod_mice, pairwise~framing_condition, var = "egoistic_center", adjust = "none")

ego_frame_trends$emtrends %>%
  knitr::kable(digits = 2)

ego_frame_trends$contrasts %>%
  knitr::kable(digits = 3)
```


Confidence interval
```{r}
confint(ego_frame_trends$contrasts) %>%
  knitr:kable(digits = 2)
```

No, the difference between any two slopes was not significant.




Third, interaction between egoistic values, framing, & norm condition:
```{r}
emtrends(mod_mice, ~norm_condition | framing_condition, var = "egoistic_center", adjust = "none") %>%
  knitr::kable(digits = 2)
```


```{r}
# without data overlaid
emmip(mod_mice, norm_condition ~ egoistic_center | framing_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Egoistic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +theme_apa() + text_settings
```

* In the control framing condition, egoistic values were *not* significantly related to consumer intentions in the **control norm**, **descriptive norm**, or **moral norm** conditions (but were signifcantly, negatively related to consumer intentions in the **convention** and **social norm** conditions).

* In the pro-environmental framing condition, egoistic values were *not* significantly related to consumer intentions in the **descriptive norm**, **convention**, or **social norm** conditions (but were significantly, negatively related in the **control norm** and **moral norm** conditions).

* In the self-enhancing framing condition, egoistic values were *not* significantly related to consumer intentions in the **descriptive norm** and **social norm** conditions (but were significantly, negatively related in the **control norm**, **convention** & **moral norm** conditions).





### Hedonic Values

First, relationship between hedonic values & consumer intentions for each norm condition:
```{r}
emtrends(mod_mice, ~norm_condition, var = "hedonic_center", adjust = "none") %>%
  knitr::kable(digits = 2)
```


```{r}
# On a single graph
describe(average_df$hedonic_center)
at_list <- list(hedonic_center = seq(-5.1, 1, by = 1))

# without data overlaid
emmip(mod_mice, norm_condition ~ hedonic_center, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Hedonic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) +theme_apa() + text_settings


# with data overlaid
emmip(mod_mice, ~ hedonic_center | norm_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 0.8, alpha = 0.5), xlab = "Hedonic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + geom_point(data = average_df, aes(x = hedonic_center, y = consumer_intentions, color = norm_condition), alpha = 0.5) + facet_wrap(~norm_condition, labeller = labeller(norm_condition = norm_labs)) +theme_apa() + text_settings
```

* Hedonic values were not significantly related to consumer intentions in any norm condition except for the **moral norm** condition in which they were significantly, negatively related to consumer intentions.


Is the slope of the relationship between hedonic values & consumer intentions stronger in any one of the norm conditions compared to the others?

```{r}
hed_norm_trends <- emtrends(mod_mice, pairwise~norm_condition, var = "hedonic_center", adjust = "none")

hed_norm_trends$emtrends %>%
  knitr::kable(digits = 2)

hed_norm_trends$contrasts %>%
  knitr::kable(digits = 3)
```


Confidence interval
```{r}
confint(hed_norm_trends$contrasts) %>%
  knitr:kable(digits = 2)
```

There was a significant difference in the relationship between hedonic values and consumer intentions between the convention norm condition (b = 0.12) and the moral norm condition (b = -0.30), t(1039) = 2.66, p = .008.



Second, relationship between hedonic values & consumer intentions for each framing condition:
```{r}
emtrends(mod_mice, ~framing_condition, var = "hedonic_center", adjust = "none") %>%
  knitr::kable(digits = 2)
```

```{r}
# without data overlaid
emmip(mod_mice, framing_condition ~ hedonic_center, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Hedonic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +theme_apa() + text_settings

# with data overlaid
emmip(mod_mice, ~ hedonic_center | framing_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 0.8, alpha = 0.5), xlab = "Hedonic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) + geom_point(data = average_df, aes(x = hedonic_center, y = consumer_intentions, color = framing_condition), alpha = 0.5) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +theme_apa() + text_settings
```

* Hedonic values were non-significantly, negatively related to consumer intentions in all framing conditions.


Is the slope of the relationship between hedonic values & consumer intentions stronger in any one of the framing conditions compared to the others?

```{r}
hed_frame_trends <- emtrends(mod_mice, pairwise~framing_condition, var = "hedonic_center", adjust = "none")

hed_frame_trends$emtrends %>%
  knitr::kable(digits = 2)

hed_frame_trends$contrasts %>%
  knitr::kable(digits = 3)
```


Confidence interval
```{r}
confint(hed_frame_trends$contrasts) %>%
  knitr:kable(digits = 2)
```

No, there was no significant difference between any two pairs of slopes.



Third, interaction between hedonic values, framing, & norm condition:
```{r}
emtrends(mod_mice, ~norm_condition | framing_condition, var = "hedonic_center", adjust = "none") %>% 
  knitr::kable(digits = 2)
```

```{r}
# without data overlaid
emmip(mod_mice, norm_condition ~ hedonic_center | framing_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Hedonic Values (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +theme_apa() + text_settings
```

* In the control framing condition, hedonic values were not significantly related to consumer intentions in any norm condition.

* In the pro-environmental framing condition, hedonic values were not significantly related to consumer intentions in any norm condition.

* In the self-enhancing framing condition, hedonic values were not significantly related to consumer intentions in any norm condition except for the **moral norm** condition in which they were significantly, related.




### Ingroup Identification Interactions

>>H5: There will be a two-way interaction between ingroup identification and norm condition.

First, relationship between ingroup identification & consumer intentions for each norm condition:
```{r}
emtrends(mod_mice, ~norm_condition, var = "ingroup_center", adjust = "none") %>%
  knitr::kable(digits = 2)
```


```{r}
# On a single graph
describe(average_df$ingroup_center)
at_list <- list(ingroup_center = seq(-3.69, 2.41, by = 1))

# without data overlaid
emmip(mod_mice, norm_condition ~ ingroup_center, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Ingroup Identification (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) +theme_apa() + text_settings


# with data overlaid
emmip(mod_mice, ~ ingroup_center | norm_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 0.8, alpha = 0.5), xlab = "Ingroup Identification (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + geom_point(data = average_df, aes(x = ingroup_center, y = consumer_intentions, color = norm_condition), alpha = 0.5) + facet_wrap(~norm_condition, labeller = labeller(norm_condition = norm_labs)) +theme_apa() + text_settings
```

* Ingroup identification was not significantly related to consumer intentions in any of the norm conditions.


Is the slope of the relationship between ingroup idenitification & consumer intentions stronger in any one of the norm conditions compared to the others?

```{r}
ing_norm_trends <- emtrends(mod_mice, pairwise~norm_condition, var = "ingroup_center", adjust = "none")

ing_norm_trends$emtrends %>%
  knitr::kable(digits = 2)

ing_norm_trends$contrasts %>%
  knitr::kable(digits = 3)
```


Confidence interval
```{r}
confint(ing_norm_trends$contrasts) %>%
  knitr:kable(digits = 2)
```

No, there was no significant difference between any two pairs of slopes.



Second, relationship between ingroup idenitification & consumer intentions for each framing condition:
```{r}
emtrends(mod_mice, ~framing_condition, var = "ingroup_center", adjust = "none") %>%
  knitr::kable(digits = 2)
```


```{r}
# without data overlaid
emmip(mod_mice, framing_condition ~ ingroup_center, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Ingroup Identification (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +theme_apa() + text_settings

# with data overlaid
emmip(mod_mice, ~ ingroup_center | framing_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 0.8, alpha = 0.5), xlab = "Ingroup Identification (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) + geom_point(data = average_df, aes(x = ingroup_center, y = consumer_intentions, color = framing_condition), alpha = 0.5) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +theme_apa() + text_settings
```

* Ingroup identification was non-significantly related to consumer intentions in all framing conditions.


Is the slope of the relationship between ingroup identification & consumer intentions stronger in any one of the framing conditions compared to the others?

```{r}
ing_frame_trends <- emtrends(mod_mice, pairwise~framing_condition, var = "ingroup_center", adjust = "none")

ing_frame_trends$emtrends %>%
  knitr::kable(digits = 2)

ing_frame_trends$contrasts %>%
  knitr::kable(digits = 3)
```


Confidence interval
```{r}
confint(ing_frame_trends$contrasts) %>%
  knitr:kable(digits = 2)
```

No, there was no significant difference between any two pairs of slopes.



>> Exploratory RQ1: Is there a three-way interaction between ingroup identification, framing, and norm condition?

Third, interaction between ingroup identification, framing, & norm condition:
```{r}
emtrends(mod_mice, ~norm_condition | framing_condition, var = "ingroup_center", adjust = "none") %>%
  knitr::kable(digits = 2)
```


```{r}
# without data overlaid
emmip(mod_mice, norm_condition ~ ingroup_center | framing_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 1.2, alpha = 0.8), xlab = "Ingroup Identification (Centered)", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +theme_apa() + text_settings
```

* In the control framing condition, ingroup identification was non-significantly related to consumer intentions in all norm conditions.

* In the pro-environmental framing condition, ingroup identification was non-significantly related to consumer intentions in all norm conditions.

* In the self-enhancing framing condition, ingroup identification was non-significantly related to consumer intentions in all norm conditions.


### All cells compared to control

>> Exploratory RQ2: Which combination of framing and norm condition produced the strongest reductions in consumer intentions compared to the control condition?

```{r}
cell_int_means <- emmeans(mod_mice, pairwise ~ norm_condition*framing_condition, adjust = "none")

cell_int_means$emmeans %>%
  knitr::kable(digits = 2)

cell_int_means$contrasts %>%
  knitr::kable(digits = 3)
```


```{r}
emmip(mod_mice, framing_condition ~ norm_condition, CIs = FALSE, xlab = "Norm Condition", ylab = "Consumer Intentions")
```

There are no significant differences between the control norm/control framing condition and any of the other combinations of framing/norm conditions.



### Gender Interactions (exploratory)


Gender X Norm
```{r}
emmeans(mod_mice, ~ norm_condition*Gender*framing_condition, adjust = "none")

emmip(mod_mice, norm_condition ~ Gender, at = at_list, CIs = TRUE, CIarg = list(lwd = 1, alpha = 0.8), xlab = "Gender", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) +theme_apa() + text_settings
```

Gender X Framing
```{r}
emmip(mod_mice, framing_condition ~ Gender, at = at_list, CIs = TRUE, CIarg = list(lwd = 1, alpha = 0.8), xlab = "Gender", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Framing Condition", breaks=c("control_framing","pro_env_framing","self_enh_framing"), labels=c("Control Framing", "Pro-environmental Framing", "Self-enhancing Framing")) +theme_apa() + text_settings
```

Gender X Norm X Framing
```{r}
emmip(mod_mice, norm_condition ~ Gender | framing_condition, at = at_list, CIs = TRUE, CIarg = list(lwd = 1, alpha = 0.8), xlab = "Gender", ylab = "Consumer Intentions") + scale_colour_discrete(name = "Norm Condition", breaks=c("control_norm","descriptive_norm", "convention_norm", "social_norm", "moral_norm"), labels=c("Control Norm", "Descriptive Norm", "Convention", "Social Norm", "Moral Norm")) + facet_wrap(~framing_condition, labeller = labeller(framing_condition = frame_labs)) +theme_apa() + text_settings
```



